---
title: "FakeArt - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute:
  cache: true
---

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)

df <- read.csv("../data/data_participants.csv")
dftask <- read.csv("../data/data_task.csv") |> 
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated")) 

cols <- c(
  # Condition
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "AI Original" = "#1D9AF5",
  "AI Copy" = "#4CAF50",
  "Not recognized" = "#607D8B",
  # Style
  "Abstract and Avant-garde" = "#E41A1C", 
  "Classical" = "#377EB8", 
  "Impressionist and Expressionist" = "#4DAF4A", 
  "Romantic and Realism" = "#FF7F00"
)
```

### Stimuli Selection

```{r}
#| out-width: "100%"

fig_stimselection <- png::readPNG("../experiment/stimuli/stimuli_selection/stimuli_selection_files/figure-html/unnamed-chunk-10-1.png") |>
  grid::rasterGrob(interpolate=TRUE) |> 
  patchwork::wrap_elements()
fig_stimselection
```

## Effect of Condition


### Beauty


```{r}
#| message: false

make_plot  <- function(p, outcome = "Beauty", x_title = NULL, alpha_title=NULL) {
  p <- p + theme_minimal() 
  if (outcome %in%  c("Beauty", "Beauty2")) {
    if(!is.null(x_title) && x_title %in% c("Self-Relevance", "Image Complexity (Norms)", "Image Familiarity (Norms)")) {
      ybreaks <- c(0.4, 0.5, 0.6)
    } else if(!is.null(alpha_title) && alpha_title == "Emotion") {
      ybreaks <- c(0.3, 0.5, 0.7)
      alpha_title <- NULL
    } else {
      ybreaks <- c(0.45, 0.5, 0.55)
    }
    by <- diff(ybreaks)[1]
    title <- "Beauty"
    if (outcome == "Beauty2") title <- "Beauty (Follow-up)"
    p <- p +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray") +
      labs(title = title, y = "This artwork is...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("Ugly", format_percent(ybreaks, digits=0), "Beautiful")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else if (outcome ==  "Valence") {
    if(!is.null(x_title) && x_title %in% c("Self-Relevance", "Image Complexity (Norms)", "Image Familiarity (Norms)")) {
      ybreaks <- c(0.4, 0.5, 0.6)
    } else if(!is.null(alpha_title) && alpha_title == "Emotion") {
      ybreaks <- c(0.3, 0.5, 0.7)
      alpha_title <- NULL
    } else {
      ybreaks <- c(0.45, 0.5, 0.55)
    }
    by <- diff(ybreaks)[1]
    p <- p +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray") +
      labs(title = "Valence", y = "This artwork made me feel...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("Negative", format_percent(ybreaks, digits=0), "Positive")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else if (outcome ==  "Meaning") {
    if(!is.null(x_title) && x_title %in% c("Self-Relevance", "Image Complexity (Norms)", "Image Familiarity (Norms)")) {
      ybreaks <- c(0.35, 0.45, 0.55)
    } else if(!is.null(alpha_title) && alpha_title == "Emotion") {
      ybreaks <- c(0.3, 0.4, 0.5)
      alpha_title <- NULL
    } else {
      ybreaks <- c(0.3, 0.4, 0.5)
    }
    by <- diff(ybreaks)[1]
    p <- p +
      labs(title = "Meaning", y = "This artwork expresses something meaningful and deep...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("Not at all", format_percent(ybreaks, digits=0), "Very much")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else if (outcome ==  "Worth") {
    ylim <- c(0, 3/5)
    p <- p +
      labs(title = "Worth", y = "To own this artwork, I'd be willing to pay...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(0, 1/5, 2/5, 3/5, 4/5, 1), 
        labels = c("$ 0", "$ 10", "$ 100", "$ 1,000", "$ 10,000", "$ 100,000")
      ) +
      coord_cartesian(ylim = ylim) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else if (outcome ==  "Reality") {
    if(!is.null(x_title) && x_title %in% c("Self-Relevance", "Image Complexity (Norms)", "Image Familiarity (Norms)")) {
      ybreaks <- c(0.4, 0.5, 0.6)
    } else if(!is.null(alpha_title) && alpha_title == "Emotion") {
      ybreaks <- c(0.4, 0.5, 0.6)
      alpha_title <- NULL
    } else {
      ybreaks <- c(0.425, 0.5, 0.575)
    }
    by <- diff(ybreaks)[1]
    p <- p +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray") +
      labs(title = "Syntheticness", y = "This artwork is...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("AI-Generated", format_percent(ybreaks, digits=0), "Human Creation")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else if (outcome ==  "Authenticity") {
    if(!is.null(x_title) && x_title %in% c("Self-Relevance", "Image Complexity (Norms)", "Image Familiarity (Norms)")) {
      ybreaks <- c(0.5, 0.6, 0.7)
    } else if(!is.null(alpha_title) && alpha_title == "Emotion") {
      ybreaks <- c(0.5, 0.6, 0.7)
      alpha_title <- NULL
    } else {
      ybreaks <- c(0.55, 0.6, 0.65)
    }
    by <- diff(ybreaks)[1]
    p <- p +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray") +
      labs(title = "Authenticity", y = "This artwork is...", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("Copy / Forgery", format_percent(ybreaks, digits=0), "Original Creation")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  }  else if (outcome ==  "SelfRelevance") {
    ybreaks <- c(0.2, 0.3, 0.4)
    by <- diff(ybreaks)[1]
    p <- p +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray") +
      labs(title = "Self-Relevance", y = "This painting is personally relevant..", x = x_title, alpha = alpha_title) +
      scale_y_continuous(
        breaks = c(min(ybreaks) - by, ybreaks, max(ybreaks) + by), 
        labels = c("Not at all", format_percent(ybreaks, digits=0), "Very much")
      ) +
      coord_cartesian(ylim = c(min(ybreaks) - by, max(ybreaks) + by)) +
      theme(axis.title.y = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } 

  p
}

make_table <- function(rez, outcome = "Beauty", subtitle = NULL) {
  rez <- datawizard::data_select(rez, exclude = "SE")
  t <- format_table(rez, zap_small = TRUE)

  if("Difference" %in% names(rez)) {
    effect_col <- "Difference"
  } else {
    effect_col <- "Slope"
  }
  t$effectsize <- rez[[effect_col]]
  t$sig <- rez$p
  
  gt::gt(t) |> 
    gt::data_color(columns = "effectsize", target_columns = effect_col, method = "numeric",
palette = c("red", "red", "white", "green", "green"), domain = c(-0.6, 0.6)) |> 
    gt::data_color(columns = "sig", target_columns = "p", fn = \(x) {
      ifelse(x < 0.001, "#FFC107", ifelse(x < 0.01, "#FFEB3B", ifelse(x < 0.05, "#FFF59D", "white")))
    }) |> 
    gt::cols_hide(c("effectsize", "sig")) |> 
    gt::tab_header(title = outcome, subtitle = subtitle)

}

make_analysis <- function(dftask, outcome = "Beauty") {
  
  # Descriptive
  bins <- sort(c(unique(dftask[[outcome]]) - 0.05, unique(dftask[[outcome]]) + 0.05))
  if(length(bins) > 100) bins <- seq(-0.01, 1.01, by = 0.02)
  p_desc <- ggplot(dftask, aes(x = Condition, y = .data[[outcome]])) +
    ggdist::stat_histinterval(aes(fill = Condition), point_interval = "mean_qi", side="right",  breaks = bins, align = "center") +
    scale_fill_manual(values = cols) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_minimal() +
    labs(title = paste0("Distribution of ", outcome), y = outcome)

  # Model
  formula <- as.formula(paste0(outcome, " ~ Style * Condition * ManipulationDistrust + (1|Participant) + (1|Item)"))
  model <- lme4::lmer(formula, data = dftask)

  # Performance
  # TODO.

  # Marginal effect of Condition
  t_cond <- estimate_contrasts(model, contrast = "Condition", by = NULL, backend = "marginaleffects") |> 
    arrange(Difference) |> 
    make_table(outcome=outcome, subtitle = "Marginal Contrasts")
  
  p_condition <- estimate_means(model, by = c("Condition"), backend = "marginaleffects") |> 
    ggplot(aes(x = Condition, y = Mean)) 
  p_condition <- make_plot(p_condition, outcome = outcome) +
    geom_line(aes(group=1)) +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high, color = Condition), 
                    linewidth = 1.5, size = 1.5,
                    key_glyph=draw_key_point) +
    scale_color_manual(values = cols) +
    guides(color=guide_legend(override.aes = list(size = 5)))
  

  # By Style
  t_style <- estimate_contrasts(model, contrast = "Condition", by = "Style", backend = "marginaleffects") |> 
    arrange(Style, Difference) |> 
    make_table(outcome=outcome, subtitle = "Marginal Contrasts by Style")

  p_style <- estimate_means(model, by = c("Condition", "Style"), backend = "marginaleffects") |> 
    ggplot(aes(x = Condition, y = Mean)) 
  p_style <- make_plot(p_style, outcome = outcome) +
    geom_line(aes(group = Style, color=Style), position = position_dodge(width = 0.15),
              show.legend  = FALSE) +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high, group = Style, color = Style), 
                    position = position_dodge(width = 0.15), linewidth = 1, size = 1,
                    key_glyph=draw_key_point) +
    scale_color_manual(values = cols)  +
    guides(color=guide_legend(override.aes = list(size = 5)))

  # Manipulation Mistrust
  t_trust <- estimate_contrasts(model, contrast = "Condition", by = "ManipulationDistrust = c(-5, 0, 5)", backend = "marginaleffects") |> 
    arrange(ManipulationDistrust, Difference) |> 
    make_table(outcome=outcome, subtitle = "Manipulation Distrust")

  p_trust <- estimate_means(model, by = c("Condition", "ManipulationDistrust = c(-5, 0, 5)"), backend = "marginaleffects") |> 
    mutate(ManipulationDistrust = as.factor(ManipulationDistrust)) |>
    ggplot(aes(x = Condition, y = Mean)) 
  p_trust <- make_plot(p_trust, outcome = outcome) +
    geom_line(aes(group = ManipulationDistrust, color=ManipulationDistrust), 
              position = position_dodge(width = 0.1), linewidth = 1) +
    labs(color = "Doubts about the cover story") +
    scale_color_manual(breaks = c(-5, 0, 5), labels = c("All images are 'AI'", "No doubts about the manipulation", "All images are 'Real'"), values = c("#2196F3", "black", "#E91E63")) +
    ggnewscale::new_scale_color() +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high, group = ManipulationDistrust, color = Condition), 
                    position = position_dodge(width = 0.1), linewidth = 1, size = 1,
                    key_glyph=draw_key_point) +
    scale_color_manual(values = cols)
  
  # By Emotion
  formula <- as.formula(paste0(outcome, " ~ Condition * Emotion + (1|Participant) + (1|Item)"))
  model <- lme4::lmer(formula, data = dftask)
  
  t_emotion <- estimate_contrasts(model, contrast = "Condition", by = "Emotion", backend = "marginaleffects") |> 
    arrange(Emotion, Difference) |> 
    make_table(outcome=outcome, subtitle = "Marginal Contrasts by Emotion")
  
  p_emotion <- estimate_means(model, by = c("Condition", "Emotion"), backend = "marginaleffects") |> 
    mutate(Emotion = fct_rev(Emotion)) |> 
    ggplot(aes(x = Condition, y = Mean))
  p_emotion <- make_plot(p_emotion, outcome = outcome, alpha_title = "Emotion") +
    geom_line(aes(group = Emotion, color=Emotion), 
              position = position_dodge(width = 0.1), linewidth = 1) +
    labs(color = "Emotion") +
    scale_color_manual(values = c("#C5E1A5", "#4CAF50", "#CE93D8", "#9C27B0")) +
    ggnewscale::new_scale_color() +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high, group = Emotion, color = Condition), 
                    position = position_dodge(width = 0.1), linewidth = 1, size = 1,
                    key_glyph=draw_key_point) +
    scale_color_manual(values = cols) 
  
  
  # Complexity
  formula <- as.formula(paste0(outcome, " ~ Condition * poly(Norms_Complexity, 2) + poly(Norms_Familiarity, 2) + (1|Participant) + (1|Item)"))
  model <- lme4::lmer(formula, data = dftask)

  p_complexity <- estimate_relation(model, by = c("Condition", "Norms_Complexity"), length=20, backend = "marginaleffects") |> 
    ggplot(aes(x = Norms_Complexity, y = Predicted)) 
  p_complexity <- make_plot(p_complexity, outcome = outcome, x_title = "Image Complexity (Norms)") +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.2, show.legend  = FALSE) +
    geom_line(aes(group = Condition, color = Condition), linewidth = 1) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    scale_x_continuous(labels = scales::percent_format()) 
  p_complexity2 <- estimate_relation(model, by = c("Condition", "Norms_Familiarity"), length=20, backend = "marginaleffects") |> 
    ggplot(aes(x = Norms_Familiarity, y = Predicted)) 
  p_complexity2 <- make_plot(p_complexity2, outcome = outcome, x_title = "Image Familiarity (Norms)") +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.2, show.legend  = FALSE) +
    geom_line(aes(group = Condition, color = Condition), linewidth = 1) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    scale_x_continuous(labels = scales::percent_format()) +
    theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(),
          plot.title = element_blank(), plot.subtitle = element_blank())
  p_complexity <- (p_complexity | p_complexity2) + plot_layout(guides = "collect")
  
  # Self-Relevance
  if(outcome != "SelfRelevance") {
    formula <- as.formula(paste0(outcome, " ~ Condition * poly(SelfRelevance, 2) + (1|Participant) + (1|Item)"))
    model <- lme4::lmer(formula, data = filter(dftask, !is.na(SelfRelevance)))
  
    vals <- paste0("SelfRelevance = c(", paste0(as.character(sort(c(0, round(mean(dftask$SelfRelevance, na.rm=TRUE), 2), 0.5, 1))), collapse = ", "), ")")
    t_selfrelevance <- estimate_contrasts(model, contrast = "Condition", by = vals, backend = "marginaleffects") |> 
      arrange(SelfRelevance, Difference) |> 
      make_table(outcome=outcome, subtitle = "Self-Relevance (Marginal Contrasts)")
    t_selfrelevance2 <- estimate_slopes(model, trend = "SelfRelevance", by = c("Condition", "SelfRelevance = c(0, 0.25, 0.5, 0.75, 1)"), backend = "marginaleffects") |> 
      arrange(Condition, SelfRelevance) |> 
      make_table(outcome=outcome, subtitle = "Self-Relevance (Marginal Slopes)")
  
    p_selfrelevance <- estimate_relation(model, by = c("Condition", "SelfRelevance"), length=20, backend = "marginaleffects") |> 
      ggplot(aes(x = SelfRelevance, y = Predicted)) 
    p_selfrelevance <- make_plot(p_selfrelevance, outcome = outcome, x_title = "Self-Relevance") +
      geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.2, show.legend  = FALSE) +
      geom_line(aes(group = Condition, color = Condition), linewidth = 1) +
      scale_color_manual(values = cols) +
      scale_fill_manual(values = cols) +
      scale_x_continuous(labels = scales::percent_format()) 
  } else{
    t_selfrelevance <- "N/A"
    t_selfrelevance2 <- "N/A"
    p_selfrelevance <- "N/A"
  }
  

  # Beauty (Follow-up)
  if(outcome != "Beauty2") {
    formula <- as.formula(paste0("Beauty2 ~ Condition * poly(", outcome, ", 2) + (1|Participant) + (1|Item)"))
    model <- lme4::lmer(formula, data = filter(dftask, !is.na(Beauty2)))
  
    vals <- paste0(outcome, " = c(", paste0(as.character(c(0, 0.25, 0.5, 0.75, 1)), collapse = ", "), ")")
    t_beauty <- estimate_contrasts(model, contrast = "Condition", by = vals, backend = "marginaleffects") |>
      make_table(outcome=outcome, subtitle = "Predicting Follow-up Beauty (Contrasts)")
    t_beauty2 <- estimate_slopes(model, trend = outcome, by = c("Condition", paste0(outcome, "= c(0, 0.25, 0.5, 0.75, 1)")), backend = "marginaleffects") |> 
      arrange(Condition) |> 
      make_table(outcome=outcome, subtitle = "Predicting Follow-up Beauty (Slopes)")
  
    p_beauty <- estimate_relation(model, by = c("Condition", outcome), length=60, backend = "marginaleffects") |>
      ggplot(aes(x = .data[[outcome]], y = Predicted)) +
      geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray")

    if(outcome %in% c("Beauty", "Valence")) p_beauty <- p_beauty + geom_vline(xintercept = 0.5, linetype = "dashed", color = "gray")
    p_beauty <- p_beauty +
      geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.2, show.legend  = FALSE) +
      geom_line(aes(group = Condition, color = Condition), linewidth = 1) +
      scale_color_manual(values = cols) +
      scale_fill_manual(values = cols) +
      scale_x_continuous(labels = scales::percent_format()) +
      scale_y_continuous(
        breaks = c(0.2, 0.35, 0.5, 0.65, 0.8),
        labels = c("Ugly", "35%", "50%", "65%", "Beautiful")
      ) +
      labs(y = "Beauty (Follow-up)", title = "Beauty (Follow-up)", 
           subtitle = "After being reminded that all artworks were Human originals") +
      coord_cartesian(ylim = c(0.2, 0.8)) +
      theme_minimal() +
      theme(plot.subtitle = element_text(face = "italic"), plot.title = element_text(face = "bold"))
  } else {
    t_beauty <- "N/A"
    t_beauty2 <- "N/A"
    p_beauty <- "N/A"
  }
  

  list(p_desc=p_desc, 
       t_condition=t_cond, p_condition=p_condition, 
       t_style=t_style, p_style=p_style, 
       t_emotion=t_emotion, p_emotion=p_emotion,
       p_complexity = p_complexity,
       t_trust=t_trust, p_trust=p_trust,
       t_selfrelevance=t_selfrelevance, t_selfrelevance2=t_selfrelevance2, p_selfrelevance=p_selfrelevance,
       t_beauty=t_beauty, t_beauty2=t_beauty2, p_beauty=p_beauty
  )
}
```

```{r make_analysis_beauty}
rez_beauty <- make_analysis(dftask, outcome="Beauty")
rez_beauty$p_desc
```


#### Condition

```{r}
rez_beauty$p_condition
rez_beauty$t_condition
```

#### Style

```{r}
rez_beauty$p_style
rez_beauty$t_style
```

#### Emotion

```{r}
rez_beauty$p_emotion
rez_beauty$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_beauty$p_complexity
```

#### Manipulation Belief

```{r}
rez_beauty$p_trust
rez_beauty$t_trust
```

#### Self-Relevance

```{r}
rez_beauty$p_selfrelevance
rez_beauty$t_selfrelevance
rez_beauty$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_beauty$p_beauty
rez_beauty$t_beauty
rez_beauty$t_beauty2
```

### Valence

```{r make_analysis_valence}
rez_valence <- make_analysis(dftask, outcome="Valence")
rez_valence$p_desc
```

#### Condition

```{r}
rez_valence$p_condition
rez_valence$t_condition
```

#### Style

```{r}
rez_valence$p_style
rez_valence$t_style
```

#### Emotion

```{r}
rez_valence$p_emotion
rez_valence$t_emotion
```


#### Complexity and Familiarity

```{r}
rez_valence$p_complexity
```

#### Manipulation Belief

```{r}
rez_valence$p_trust
rez_valence$t_trust
```

#### Self-Relevance

```{r}
rez_valence$p_selfrelevance
rez_valence$t_selfrelevance
rez_valence$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_valence$p_beauty
rez_valence$t_beauty
rez_valence$t_beauty2
```

### Meaning

```{r make_analysis_meaning}
rez_meaning <- make_analysis(dftask, outcome="Meaning")
rez_meaning$p_desc
```

#### Condition

```{r}
rez_meaning$p_condition
rez_meaning$t_condition
```

#### Style

```{r}
rez_meaning$p_style
rez_meaning$t_style
```

#### Emotion

```{r}
rez_meaning$p_emotion
rez_meaning$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_meaning$p_complexity
```

#### Manipulation Belief

```{r}
rez_meaning$p_trust
rez_meaning$t_trust
```

#### Self-Relevance

```{r}
rez_meaning$p_selfrelevance
rez_meaning$t_selfrelevance
rez_meaning$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_meaning$p_beauty
rez_meaning$t_beauty
rez_meaning$t_beauty2
```

### Worth

```{r make_analysis_worth}
rez_worth <- make_analysis(dftask, outcome="Worth")
rez_worth$p_desc
```

#### Condition

```{r}
rez_worth$p_condition
rez_worth$t_condition
```

#### Style

```{r}
rez_worth$p_style
rez_worth$t_style
```

#### Emotion

```{r}
rez_worth$p_emotion
rez_worth$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_worth$p_complexity
```

#### Manipulation Belief

```{r}
rez_worth$p_trust
rez_worth$t_trust
```

#### Self-Relevance

```{r}
rez_worth$p_selfrelevance
rez_worth$t_selfrelevance
rez_worth$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_worth$p_beauty
rez_worth$t_beauty
rez_worth$t_beauty2
```


### Syntheticness

```{r make_analysis_reality}
rez_reality <- make_analysis(filter(dftask, !is.na(Reality)), outcome="Reality")
rez_reality$p_desc
```


#### Condition

```{r}
rez_reality$p_condition
rez_reality$t_condition
```

#### Style

```{r}
rez_reality$p_style
rez_reality$t_style
```

#### Emotion

```{r}
rez_reality$p_emotion
rez_reality$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_reality$p_complexity
```

#### Manipulation Belief

```{r}
rez_reality$p_trust
rez_reality$t_trust
```

#### Self-Relevance

```{r}
rez_reality$p_selfrelevance
rez_reality$t_selfrelevance
rez_reality$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_reality$p_beauty
rez_reality$t_beauty
rez_reality$t_beauty2
```



### Authenticity

```{r make_analysis_authenticity}
rez_authenticity <- make_analysis(filter(dftask, !is.na(Authenticity)), outcome="Authenticity")
rez_authenticity$p_desc
```


#### Condition

```{r}
rez_authenticity$p_condition
rez_authenticity$t_condition
```

#### Style

```{r}
rez_authenticity$p_style
rez_authenticity$t_style
```

#### Emotion

```{r}
rez_authenticity$p_emotion
rez_authenticity$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_authenticity$p_complexity
```

#### Manipulation Belief

```{r}
rez_authenticity$p_trust
rez_authenticity$t_trust
```

#### Self-Relevance

```{r}
rez_authenticity$p_selfrelevance
rez_authenticity$t_selfrelevance
rez_authenticity$t_selfrelevance2
```


#### Beauty 2

```{r}
rez_authenticity$p_beauty
rez_authenticity$t_beauty
rez_authenticity$t_beauty2
```


### Self-Relevance

```{r make_analysis_selfrelevance}
rez_selfrelevance <- make_analysis(filter(dftask, !is.na(SelfRelevance)), outcome="SelfRelevance")
rez_selfrelevance$p_desc
```


#### Condition

```{r}
rez_selfrelevance$p_condition
rez_selfrelevance$t_condition
```

#### Style

```{r}
rez_selfrelevance$p_style
rez_selfrelevance$t_style
```

#### Emotion

```{r}
rez_selfrelevance$p_emotion
rez_selfrelevance$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_selfrelevance$p_complexity
```

#### Manipulation Belief

```{r}
rez_selfrelevance$p_trust
rez_selfrelevance$t_trust
```

#### Beauty 2

```{r}
rez_selfrelevance$p_beauty
rez_selfrelevance$t_beauty
rez_selfrelevance$t_beauty2
```

### Beauty 2

```{r make_analysis_beauty2}
rez_beauty2 <- make_analysis(filter(dftask, !is.na(Beauty2)), outcome="Beauty2")
rez_beauty2$p_desc
```


#### Condition

```{r}
rez_beauty2$p_condition
rez_beauty2$t_condition
```

#### Style

```{r}
rez_beauty2$p_style
rez_beauty2$t_style
```

#### Emotion

```{r}
rez_beauty2$p_emotion
rez_beauty2$t_emotion
```

#### Complexity and Familiarity

```{r}
rez_beauty2$p_complexity
```

#### Manipulation Belief

```{r}
rez_beauty2$p_trust
rez_beauty2$t_trust
```



## Figures

```{r}
fig_stimselection 
```

