---
title: "FakeArt - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)

df <- read.csv("../data/rawdata_participants.csv")
dftask <- read.csv("../data/rawdata_task.csv")
```

## Recruitment History

```{r}
#| message: false

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Experiment_StartDate, format = "%Y-%m-%d %H:%M:%S")) |> 
  summarize(N = n(), .by=c("Date", "Recruitment")) |> 
  complete(Date, Recruitment, fill = list(N = 0)) |> 
  mutate(N = cumsum(N), .by="Recruitment") |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Recruitment)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

```{r}
#| message: false

# Table
summarize(df, N = n(), .by=c("Recruitment")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::grand_summary_rows(columns = "N", fns = Total ~ sum(.)) |> 
  gt::opt_stylize(style = 2, color = "gray") |> 
  gt::tab_header("Number of participants per recruitment source") 
```

## Experiment Feedback

### Experiment Enjoyment

```{r}
#| fig-height: 3
#| fig-width: 8

df |> 
  summarise(n = n(), .by=c("Experiment_Enjoyment")) |>
  filter(!is.na(Experiment_Enjoyment)) |> 
  mutate(n = n / sum(n),
         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment))) |>
  ggplot(aes(y = n, x = 1, fill = Experiment_Enjoyment)) +
  geom_bar(stat="identity", position="stack") +
  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
  coord_flip() +
  scale_x_continuous(expand=c(0, 0))  +
  scale_y_continuous(labels = scales::percent)  +
  labs(title="Experiment Enjoyment",
       subtitle="Proportion of participants by condition") + 
  guides(fill = guide_legend(reverse=TRUE)) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "top",
    legend.title = element_blank()) 
```

### Comments

```{r}
data.frame(Comments = df$Experiment_Feedback) |> 
  filter(!tolower(Comments) %in% c(NA, "no", "none", "thank you", "nope", "N/A")) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```


## Task Feedback

::: {.panel-tabset}

### Proportion

```{r}
#| fig-width: 10
#| fig-height: 8

dat <- df |> 
  select(starts_with("Feedback"), -contains("Confidence")) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
  group_by(Question, Answer) |> 
  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
  complete(Question, Answer, fill = list(prop = 0)) |> 
  filter(Answer == TRUE) |> 
  mutate(Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "LabelsNotMatched", "Labels did not always match the images"),
         Question = str_replace(Question, "LabelsReversed", "Labels were Reversed"),
         # Question = str_replace(Question, "DiffNone", "No Difference Real/AI"),
         # Question = str_replace(Question, "DiffObvious", "Obvious Difference Real/AI"),
         # Question = str_replace(Question, "DiffSubtle", "Subtle Difference Real/AI"),
         # Question = str_replace(Question, "AILessAttractive", "AI = less attractive"),
         # Question = str_replace(Question, "AIMoreAttractive", "AI = more attractive"),
         # Question = str_replace(Question, "SomeFacesAttractive", "Some Faces Attractive"),
         Question = str_replace(Question, "GoodForgeries", "Forgeries very convincing and hard to distinguish"),
         Question = str_replace(Question, "BadForgeries", "Forgeries were less well executed")) |>
  mutate(Question = fct_reorder(Question, desc(prop)))

dat |> 
  ggplot(aes(x = Question, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
  labs(x="Feedback", y = "Participants", title = "Feedback") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 90, hjust = 1),
    axis.title.x = element_blank()
  )
```

```{r}
dat |> 
  select(Question, prop) |> 
  arrange(desc(prop)) |> 
  mutate(prop = format_percent(prop)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::tab_header("Proportion of participants who answered 'yes' to each question") |> 
  gt::cols_label(prop = "Proportion of participants who answered 'Yes'")
```


### Co-occurence

```{r}
#| warning: false
#| fig-width: 10
#| fig-height: 8

dat <- df |> 
  select(starts_with("Feedback"), -contains("Confidence"))  |> 
  mutate_all(~ifelse(.==TRUE, 1, 0)) |> 
  correlation(method="tetrachoric", redundant = TRUE) |> 
  correlation::cor_sort() |> 
  correlation::cor_lower() |> 
  mutate(val = paste0(insight::format_value(rho, zap_small=TRUE), format_p(p, stars_only=TRUE))) |>
  mutate(Parameter2 = fct_rev(Parameter2)) |>
  mutate(Parameter1 = fct_relabel(Parameter1, \(x) str_remove_all(x, "Feedback_")),
         Parameter2 = fct_relabel(Parameter2, \(x) str_remove_all(x, "Feedback_")))

dat |>
  ggplot(aes(x=Parameter1, y=Parameter2)) +
  geom_tile(aes(fill = rho), color = "white") +
  geom_tile(data=filter(dat, Parameter1 == "LessBeautifulAI" & Parameter2 == "BigDifferenceRealAI"), color = "red", alpha = 0, linewidth=1) +
  geom_tile(data=filter(dat, Parameter1 == "LabelsPaidAttention" & Parameter2 == "LessBeautifulAI"), color = "red", alpha = 0, linewidth=1) +
  geom_tile(data=filter(dat, Parameter1 == "LabelsPaidAttention" & Parameter2 == "LabelsNotMatched"), color = "red", alpha = 0, linewidth=1) +
  geom_tile(data=filter(dat, Parameter1 == "LabelsNoAttention" & Parameter2 == "LessBeautifulAI"), color = "red", alpha = 0, linewidth=1) +
  geom_text(aes(label = val), size = 3) +
  labs(title = "Feedback Co-occurence Matrix") +
  scale_fill_gradient2(
    low = "#2196F3",
    mid = "white",
    high = "#F44336",
    breaks = c(-1, 0, 1),
    guide = guide_colourbar(ticks=FALSE),
    midpoint = 0,
    na.value = "grey85",
    limit = c(-1, 1))  + 
  theme_minimal() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

:::

- The more people paid attention to the labels, the stronger the self-reported anti-fake bias. 
- The more people paid attention, the less likely to report that labels were not matched.

## Dimension Computation

```{r}
# Should we re-map the Worth values? -----------------------------------
# Re-map to values in dollars
# alldata_task$Worth2 <- ifelse(alldata_task$Worth == 1, 10, alldata_task$Worth)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 2, 100, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 3, 1000, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 4, 10000, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 5, 100000, alldata_task$Worth2)
#
# library(tidyverse)
#
# t <- as.data.frame(table(alldata_task$Worth))
# cor.test(as.numeric(as.character(t$Var1)), t$Freq)
# t <- as.data.frame(table(log1p(alldata_task$Worth2)))
# cor.test(as.numeric(as.character(t$Var1)), t$Freq)
#
# ggplot(alldata_task, aes(x=Worth)) +
#   geom_bar() +
#   geom_abline()
# ggplot(alldata_task, aes(x=log1p(Worth2))) +
#   geom_bar()
# ggplot(alldata_task, aes(x=Worth2)) +
#   geom_bar() +
#   scale_x_continuous(transform = "log1p", breaks = c(0, 10, 100, 1000, 10000, 100000))
# ggplot(alldata_task, aes(x=Worth, y=Beauty)) +
#   geom_smooth(method = "lm") +
#   geom_jitter(height=0)
# ggplot(alldata_task, aes(x=Worth2, y=Beauty)) +
#   geom_smooth(method = "lm") +
#   geom_jitter(height=0) +
#   scale_x_continuous(transform = "log1p", breaks = c(0, 10, 100, 1000, 10000, 100000))
# summary(lm(Beauty ~ Worth, data = alldata_task))
# summary(lm(Beauty ~ log1p(Worth2), data = alldata_task))
```


### MINT

```{r}
#| code-fold: true

compute_and_remove <- function(df, name="BodyAwareness", pattern=name, method="mean") {
  items <- select(df, starts_with(pattern), -contains("AttentionCheck"))
  df <- df[!names(df) %in% names(items)]
  if(method == "mean") {
    df[[name]] <- rowMeans(items, na.rm=TRUE)
  } else {
    df[[name]] <- rowSums(items, na.rm=TRUE)
  }
  df
}
```

```{r}
#| code-fold: false

df <- compute_and_remove(df, name="MINT_Card", method="mean")
df <- compute_and_remove(df, name="MINT_Urin", method="mean")
df <- compute_and_remove(df, name="MINT_SexS", method="mean")
df <- compute_and_remove(df, name="MINT_Gast", method="mean")
df <- compute_and_remove(df, name="MINT_Olfa", method="mean")
df <- compute_and_remove(df, name="MINT_Derm", method="mean")
df <- compute_and_remove(df, name="MINT_ExAc", method="mean")
df <- compute_and_remove(df, name="MINT_RelA", method="mean")
df <- compute_and_remove(df, name="MINT_Resp", method="mean")
df <- compute_and_remove(df, name="MINT_Sati", method="mean")
df <- compute_and_remove(df, name="MINT_CaCo", method="mean")

# df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
# df <- compute_and_remove(df, name="MAIA_AttentionRegulation", method="mean")
```

### VVIQ

```{r}
df <- compute_and_remove(df, name="VVIQ_Friend", method="mean")
df <- compute_and_remove(df, name="VVIQ_Sun", method="mean")
df <- compute_and_remove(df, name="VVIQ_Shop", method="mean")
df <- compute_and_remove(df, name="VVIQ_Country", method="mean")
```

Cronbach's alpha: `r insight::format_value(performance::item_alpha(df[c("VVIQ_Friend", "VVIQ_Sun", "VVIQ_Shop", "VVIQ_Country")]))`


```{r}
df$VVIQ_Total = rowMeans(df[c("VVIQ_Friend", "VVIQ_Sun", "VVIQ_Shop", "VVIQ_Country")], na.rm = TRUE) |> 
  datawizard::reverse_scale()  # Reverse the scale (e.g., 0–4 -> 4–0) so that higher = more vivid
df <- select(df, -VVIQ_Friend, -VVIQ_Sun, -VVIQ_Shop, -VVIQ_Country)
```

### BAIT 

```{r}
#| fig-width: 10
#| fig-height: 8

df$BAIT_Negative <- rowMeans(select(df, BAIT_8_TextIssues, BAIT_2_ImagesIssues, BAIT_3_VideosIssues, BAIT_9_Dangerous, BAIT_13_ArtIssues), na.rm=TRUE)
df$BAIT_Positive <- rowMeans(select(df, BAIT_5_ImitatingReality, BAIT_12_Benefit, BAIT_4_VideosRealistic, BAIT_1_ImagesRealistic, BAIT_14_ArtRealistic, BAIT_6_EnvironmentReal, BAIT_7_TextRealistic), na.rm=TRUE)
df$BAIT_ArtRealistic <- rowMeans(select(mutate(df, BAIT_13_ArtIssues = abs(BAIT_13_ArtIssues - 6)), BAIT_13_ArtIssues, BAIT_14_ArtRealistic), na.rm=TRUE)
df$BAIT_Total <- rowMeans(select(mutate(df, BAIT_Negative = abs(BAIT_Negative - 6)), BAIT_Negative, BAIT_Positive), na.rm=TRUE)

df |> 
  select(starts_with("BAIT")) |>
  mutate(BAIT_AI_Use = case_when(
    BAIT_AI_Use == "Never" ~ 0,
    BAIT_AI_Use == "A few times per month" ~ 1,
    BAIT_AI_Use == "A few times per week" ~ 2,
    BAIT_AI_Use == "Once a day" ~ 3,
    BAIT_AI_Use == "A few times per day" ~ 4,
    .default = NA
  )) |> 
  correlation::correlation(redundant = TRUE) |> 
  correlation::cor_sort() |> 
  correlation::cor_lower() |> 
  summary() |> 
  plot(text = list(size = 2.5)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

df <- select(df, -matches("BAIT_[0-9]+_"))
```

### PHQ-4

```{r}
df <- compute_and_remove(df, name="PHQ4_Depression", method="mean")
df <- compute_and_remove(df, name="PHQ4_Anxiety", method="mean")
```

## Exclusions 

```{r}
exclude <- list()
```

### Questionnaires


```{r}
m <- mgcv::gam(MINT_AttentionCheck ~ s(Duration_MINT),
         data = mutate(df, MINT_AttentionCheck = ifelse(MINT_AttentionCheck != 0, 1, 0)), family = "binomial")

estimate_relation(m, length=50) |>
  ggplot(aes(x = Duration_MINT, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "MINT Attention Check",
       subtitle = "Predicted probability of failing attention check by duration",
       x = "Duration (minutes)",
       y = "Probability of failing attention check")

# Contingency table for attention checks
# table(ifelse(df$MINT_AttentionCheck != 0, 1, 0), ifelse(df$BAIT_AttentionCheck != 6, 1, 0))


for(ppt in df$Participant) {
  if(df[df$Participant == ppt, "MINT_AttentionCheck"] != 0) {
    df[df$Participant == ppt, names(select(df, starts_with("MINT"), -MINT_AttentionCheck))] <- NA
    df[df$Participant == ppt, names(select(df, starts_with("VVIQ")))] <- NA
  }
  
  if(df[df$Participant == ppt, "BAIT_AttentionCheck"] != 6) {
    df[df$Participant == ppt, names(select(df, starts_with("BAIT"), -BAIT_AttentionCheck))] <- NA
  }
}
```



### Attention Checks

```{r}
dfchecks <- data.frame(
  Participant = df$Participant,
  A_MINT = ifelse(df$MINT_AttentionCheck == 0, 0, 1),
  A_BAIT = ifelse(df$BAIT_AttentionCheck == 6, 0, 1),
  A_TASK = 1 - df$Task_AttentionCheck
)

summary(correlation(dfchecks))

dfchecks |>
  mutate(Total = round(A_TASK, 2)) |> 
  ggplot(aes(x = Total)) +
  geom_bar(aes(fill = as.factor(Total))) +
  scale_fill_viridis_d(guide = "none") +
  scale_x_continuous(labels = scales::percent) +
  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.title.x = element_blank(),
  )
```

```{r}
exclude$checks <- as.character(na.omit(dfchecks[dfchecks$A_TASK >= 0.5, "Participant"]))
```


We removed `r length(exclude$checks)` (`r insight::format_percent(length(exclude$checks) / nrow(df))`) participants for having failed at least 50% of attention checks.



### Experiment Duration

```{r}
dfchecks$Duration_Experiment <- df |> 
  mutate(Version = ifelse(Recruitment == "prolific", "long", "short")) |> 
  mutate(Experiment_Duration = as.numeric(standardize(log(Experiment_Duration))), .by = "Version") |>
  pull(Experiment_Duration) 


dfchecks$Duration_Instructions1 <- standardize(log(df$Duration_TaskInstructions1))
dfchecks$Duration_Instructions2 <- standardize(log(df$Duration_TaskInstructions2))

m <- mgcv::gam(A_TASK ~ s(Duration_Experiment), 
             data = dfchecks[!is.na(dfchecks$A_TASK),], family = "quasibinomial")

estimate_relation(m, length=50) |> 
  ggplot(aes(x = Duration_Experiment, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  geom_hline(yintercept=1/3, linetype="dashed", color="darkgrey") +
  geom_vline(xintercept=3, linetype="dashed", color="red") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  ggside::geom_xsidedensity(
    data=mutate(dfchecks[!is.na(dfchecks$A_TASK),], AttentionCheckLabel = ifelse(A_TASK >= 0.5, "Failed 50% attention checks", "Valid")), 
    aes(fill=AttentionCheckLabel), alpha=0.3) +
  ggside::theme_ggside_void() +
  labs(title = "Experiment Duration",
       subtitle = "Predicted probability of failing attention checks by duration",
       x = "Experiment Duration (Z(log))",
       y = "Probability of failing attention checks") 
```

```{r}
exclude$duration <- as.character(dfchecks[dfchecks$Duration_Experiment > 3, "Participant"])
exclude$duration <- exclude$duration[!exclude$duration %in% exclude$checks]
```

<!-- We removed `r length(exclude$duration)` (`r insight::format_percent(length(exclude$duration) / nrow(df))`) participants for having completed the experiment in less than 5 minutes. -->


### Response Consistency

```{r}
#| warning: false
#| fig-width: 10
#| fig-height: 10

dftask |> 
  select(-starts_with("Screen"), -starts_with("Trial")) |> 
  correlation() |> 
  summary() |> 
  plot() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dfchecks <- dftask |> 
  summarize(across(c("Beauty", "Valence", "Meaning", "Worth", "Reality"), 
                   list(M = ~ mean(.x, na.rm = TRUE), SD = ~ sd(.x, na.rm = TRUE))),
            cor_BeautyValence = cor(Beauty, Valence, method = "spearman"),
            cor_MeaningWorth = cor(Meaning, Worth, method = "spearman"),
            cor_BeautyNorm = cor(Beauty, Norms_Liking, method = "spearman"),
            cor_ValenceNorm = cor(Valence, Norms_Valence, method = "spearman"),
            .by = c("Participant")) |> 
  mutate(cor_BeautyValence = ifelse(is.na(cor_BeautyValence), -1, cor_BeautyValence),
         cor_MeaningWorth = ifelse(is.na(cor_MeaningWorth), -1, cor_MeaningWorth),
         cor_BeautyNorm = ifelse(is.na(cor_BeautyNorm), -1, cor_BeautyNorm)) |>
  full_join(dfchecks, by = "Participant", keep = FALSE)
```

### Anomaly Score

```{r}
#| warning: false
#| message: false

features <- dfchecks |> 
  mutate(A_QUESTIONNAIRES = (A_MINT + A_BAIT) / 2) |> 
  select(-A_MINT, -A_BAIT, -A_TASK) |> 
  select(matches("_M|_SD|cor_|A_|SubjectiveQuality|Duration")) |> 
  standardize()

model <- solitude::isolationForest$new(sample_size = nrow(features), num_trees = 500)
model$fit(features)
dfchecks$AnomalyScore <- model$predict(features)$anomaly_score
 
# features <- mice::mice(features, method="pmm", m = 20, seed = 123, printFlag = FALSE) |> 
#   suppressWarnings() |> 
#   mice::complete(1)
```

```{r}
#| warning: false

m <- mgcv::gam(A_TASK ~ s(AnomalyScore), 
               data = dfchecks[!is.na(dfchecks$A_TASK),], 
               family = "quasibinomial")
# m <- mgcv::gam(A_TASK ~ s(log(AnomalyScore), k=20), data = mutate(dfchecks, A_TASK = ifelse(A_TASK >= 0.5, 1, 0)), family = "binomial")

estimate_relation(m, length=100) |> 
  ggplot(aes(x = AnomalyScore, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  geom_vline(xintercept=quantile(dfchecks$AnomalyScore, 0.95), linetype="dashed", color="red") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Experiment Duration",
       subtitle = "Predicted probability of failing attention checks by duration",
       x = "Anomaly Score",
       y = "Probability of failing attention checks") +
  ggside::geom_xsidehistogram(data=dfchecks, alpha=0.3, bins = 60) +
  ggside::geom_ysidedensity(data=dfchecks, aes(y=A_TASK), alpha=0.3) +
  ggside::theme_ggside_void() 
```


```{r}
exclude$anomaly <- as.character(dfchecks[dfchecks$AnomalyScore > quantile(dfchecks$AnomalyScore, 0.95), "Participant"])
exclude$anomaly <- exclude$anomaly[!exclude$anomaly %in% exclude$duration]
exclude$anomaly <- exclude$anomaly[!exclude$anomaly %in% exclude$checks]

length(c(exclude$anomaly, exclude$duration, exclude$checks))
```


<!-- ### Clustering -->

<!-- ```{r} -->
<!-- #| warning: false -->

<!-- rez <- dbscan::optics(features, eps = 100, minPts = 3) -->
<!-- hist(rez$reachdist) -->
<!-- clusters <- dbscan::extractDBSCAN(rez, eps_cl = quantile(rez$reachdist, 0.85)) -->
<!-- dfchecks$Cluster <- as.factor(clusters$cluster) -->
<!-- ``` -->


```{r}
#| warning: false
#| fig-width: 13
#| fig-height: 13

selected_features <- features |>
  mutate(Cluster = ifelse(dfchecks$Participant %in% c(exclude$anomaly, exclude$duration, exclude$checks), "Excluded", "Valid")) |>
  select(Cluster, starts_with("Duration"), starts_with("A_"), starts_with("cor_"), starts_with("Beauty_"))


var_names <- names(select(selected_features, -Cluster))
feature_pairs <- expand_grid(x_var = var_names, y_var = var_names)
feature_pairs <- feature_pairs |>
  mutate(
    triangle = case_when(
      match(x_var, var_names) > match(y_var, var_names) ~ "lower",
      match(x_var, var_names) == match(y_var, var_names) ~ "diag",
      TRUE ~ "upper"
    )
  )
plot_data <- pmap_dfr(feature_pairs, function(x_var, y_var, triangle) {
  selected_features |>
    select(Cluster, x = all_of(x_var), y = all_of(y_var)) |>
    mutate(x_var = x_var, y_var = y_var, triangle = triangle)
}) |>
  mutate(
    x_var = factor(x_var, levels = rev(var_names)),
    y_var = factor(y_var, levels = rev(var_names))
  )

diag_histograms <- map_dfr(var_names, function(var) {
  # histogram bins computed globally for consistent breaks
  breaks <- hist(selected_features[[var]], breaks = 20, plot = FALSE)$breaks
  all_counts <- selected_features |>
    group_by(Cluster) |>
    summarise(counts = list(hist(!!sym(var), breaks = breaks, plot = FALSE)$counts),
              .groups = "drop")

  # max count across all clusters for this variable
  max_count <- max(unlist(all_counts$counts), na.rm = TRUE)
  y_range <- range(selected_features[[var]], na.rm = TRUE)

  all_counts |>
    unnest_wider(counts, names_sep = "_") |>
    pivot_longer(starts_with("counts_"), names_to = "bin", values_to = "count") |>
    mutate(
      bin_id = as.integer(gsub("counts_", "", bin)),
      x = breaks[-length(breaks)][bin_id],
      xmax = breaks[-1][bin_id],
      ymin = y_range[1],
      ymax = ymin + (count / max_count) * diff(y_range),
      var = var
    ) |>
    select(x, xmax, ymin, ymax, var, Cluster)
}) |> mutate(
  x_var = factor(var, levels = rev(var_names)),
  y_var = factor(var, levels = rev(var_names))
)

ggplot(plot_data, aes(x = x)) +
  # stat_density_2d_filled(data = filter(plot_data, triangle == "lower", x_var != "AttentionCheck", y_var != "AttentionCheck"),
  #                        aes(y = y, fill = after_stat(nlevel)), show.legend = FALSE) +
  # scale_fill_gradient(low = "white", high = "darkgreen") +
  # ggnewscale::new_scale_fill() +
  geom_point2(data = filter(plot_data, triangle == "lower"),
              aes(y = y, color = Cluster), alpha = 0.7, size = 3, shape = "+") +
  geom_rect(data = diag_histograms,
          aes(xmin = x, xmax = xmax, ymin = ymin, ymax = ymax, fill = Cluster),
          colour = NA, alpha = 0.5) +
  geom_blank(data = filter(plot_data, triangle != "lower")) +
  facet_grid(y_var ~ x_var, scales = "free", switch = "both") +
  # scale_color_gradient(low = "black", high = "red") +
  labs(color = "Participants", fill = "Participants") +
  theme_minimal() +
  theme(strip.placement = "outside",
        strip.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title = element_blank())
```

<!-- ### UMAP -->

<!-- ```{r} -->
<!-- # Grid search -->
<!-- # UMAP or T-SNE? -->

<!-- param_grid <- expand.grid( -->
<!--   n_neighbors = c(3, 5, 10), -->
<!--   min_dist = c(0.01, 0.05, 0.1, 0.5), -->
<!--   metric = "euclidean" -->
<!-- ) -->

<!-- umap_plots <- list() -->
<!-- for (i in seq_len(nrow(param_grid))) { -->
<!--   params <- param_grid[i, ] -->
<!--   set.seed(123) -->
<!--   out <- uwot::umap(as.matrix(features), -->
<!--                    n_neighbors = params$n_neighbors, -->
<!--                    min_dist = params$min_dist, -->
<!--                    metric = params$metric) |>  -->
<!--     as.data.frame() -->

<!--   colnames(out) <- c("UMAP1", "UMAP2") -->
<!--   out$param_combo <- paste0("nn=", params$n_neighbors, ", md=", params$min_dist) -->
<!--   out$Participant <- dfchecks$Participant -->
<!--   out$AnomalyScore <- selected_features$AnomalyScore -->
<!--   out$Cluster <- selected_features$Cluster -->

<!--   umap_plots[[i]] <- ggplot(out, aes(UMAP1, UMAP2, color = Cluster)) + -->
<!--     # geom_point(size = 3, alpha = 0.8) + -->
<!--     geom_text(aes(label = Participant), size = 3, vjust = 0.5, hjust=0.5) + -->
<!--     # scale_color_viridis_c(option = "plasma") + -->
<!--     theme_minimal() + -->
<!--     labs(title = out$param_combo[1])  -->
<!-- } -->

<!-- wrap_plots(umap_plots, ncol = 4) -->
<!-- ``` -->


### Self-Reported Quality

```{r}
dfchecks$SubjectiveQuality <- df$Experiment_Quality

dfchecks |> 
  ggplot(aes(x = SubjectiveQuality, y = A_TASK)) +
  geom_jitter(width = 0) +
  geom_smooth(method = "lm") 
```



### Effect of Exclusion

```{r}
dftask |> 
  select(Participant, Beauty, Valence, Meaning, Worth, Reality, Authenticity) |> 
  pivot_longer(-Participant, names_to = "Variable", values_to = "Value") |>
  ggplot(aes(x = Value)) +
  geom_histogram(aes(fill = Variable, y = after_stat(density)), bins = 30, position = "identity") +
  facet_wrap(~Variable, scales = "free") 
```

```{r}
library(glmmTMB)

dftask <- mutate(dftask, Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated"))

quick_test <- function(what = "Beauty", family = "gaussian", exclude = c()){
  f <- as.formula(paste0(what, " ~ Condition + (1 + Condition|Participant)"))
  if(family == "ordbeta") {
    dat <- normalize(dftask, select = what)
  } else {
    dat <- dftask
  }
  
  m <- glmmTMB::glmmTMB(f, data = dat, family = family)
  params <-  parameters::parameters(m, effects = "fixed")
  
  m2 <- glmmTMB::glmmTMB(f, data = filter(dat, !Participant %in% exclude), family = family)
  params2 <-  parameters::parameters(m2, effects = "fixed")
  
  params$Coefficient_Excluded <- params2$Coefficient
  params$p_Excluded <- format_p(params2$p, name = NULL)
  params$Result <- ifelse(params$p_Excluded < params$p, "Exclude", "Original")
  
  p <- estimate_means(m, by = "Condition") |> 
    mutate(Exclusion = "Whole sample") |> 
    rbind(estimate_means(m2, by = "Condition") |> 
            mutate(Exclusion = "Excluded")) 
  
  if("Proportion" %in% names(p)) p <- datawizard::data_rename(p, "Proportion", "Mean")
  
  p <- p |>
    ggplot(aes(x = Condition, y = Mean, color = Exclusion, group = Exclusion)) +
    geom_line(position = position_dodge(width = 0.1)) +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1), size = 1) 

  list(params = display(select(params, Parameter, Coefficient, Coefficient_Excluded, p, p_Excluded, Result)),
       plot = p)
}
```

::: {.panel-tabset}

#### Beauty

```{r}
rez <- quick_test(what = "Beauty", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Beauty", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  
```

#### Valence

```{r}
rez <- quick_test(what = "Valence", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Valence", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  
```

#### Meaning

```{r}
rez <- quick_test(what = "Meaning", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Meaning", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  
```

#### Worth

```{r}
rez <- quick_test(what = "Worth", family = "poisson", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  
```

#### Reality

```{r}
rez <- quick_test(what = "Reality", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot

rez <- quick_test(what = "Reality", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot
```

#### Authenticity

```{r}
rez <- quick_test(what = "Authenticity", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot

rez <- quick_test(what = "Authenticity", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot
```

::: 

### Exclude

```{r}
#| code-fold: false

df <- filter(df, !Participant %in% c(exclude$anomaly, exclude$duration, exclude$checks))
dftask <- filter(dftask, !Participant %in% c(exclude$anomaly, exclude$duration, exclude$checks))
```



## Manipulation Check

Did participant doubt the cover story? 

### Post-task Check

```{r}
#| fig-width: 15
#| fig-height: 15

manipcheck <- df |> 
  select(Participant, Feedback_ConfidenceReal, Feedback_ConfidenceAI) |> 
  pivot_longer(-Participant, values_to = "Confidence", names_to = "Answer") |>
  filter(!is.na(Confidence)) |> 
  mutate(Answer = ifelse(str_detect(Answer, "Real"), "All images are real", "All images are fake"))

manipcheck |> 
  ggplot(aes(x=Confidence, fill=Answer)) +
  geom_bar() +
  facet_grid(~Answer) +
  theme_minimal() +
  theme(legend.position = "none") 

manipcheck |> 
  summarize(N = n(), 
            Prop = n() / nrow(df), 
            Mean_Confidence = mean(Confidence, na.rm = TRUE),
            SD_Confidence = sd(Confidence, na.rm = TRUE),
            .by = "Answer") |> 
  gt::gt() |> 
  gt::fmt_auto() |> 
  gt::opt_stylize()

df <- manipcheck |> 
  mutate(Confidence = Confidence + 1,
         Confidence = ifelse(Answer == "All images are fake", -Confidence, Confidence)) |> 
  select(Participant, ManipulationDistrust=Confidence) |> 
  right_join(df, by = "Participant") |> 
  arrange(Participant) |>
  mutate(ManipulationDistrust = ifelse(is.na(ManipulationDistrust), 0, ManipulationDistrust))
```

We added the manipulation distrust as a variable ("all images are fake": -5 to -1, "all images are real": 1 to 5).

```{r}
df_belief <- dftask |> 
  summarize(
    # Reality = sum(Reality > 0) / n(),
    # Authenticity = sum(Authenticity > 0)  / n(),
    Reality = mean(Reality, na.rm=TRUE),
    Authenticity = mean(Authenticity, na.rm=TRUE),
    .by=c("Participant")) |> 
  full_join(manipcheck, by = "Participant") |> 
  mutate(Confidence = ifelse(is.na(Answer), -1, Confidence),
         Answer = ifelse(is.na(Answer), "No doubts", Answer))

df_belief |> 
  ggplot(aes(x = Reality, y = Authenticity, color = Answer)) +
  geom_jitter(aes(size=Confidence), shape = "+", width = 0.01, height=0.01, alpha = 0.9) +
  ggrepel::geom_label_repel(data = filter(df_belief, abs(Reality) > 95 | abs(Authenticity) > 95),
                            aes(label = Participant), size = 3) +
  ggside::geom_xsidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::geom_ysidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::theme_ggside_void() +
  theme_minimal() +
  scale_size_continuous(range = c(4, 8)) 
```

```{r}
exclude$phase2 <- filter(df_belief, Reality > 90 | Authenticity > 90)$Participant
```

Expressing cover story doubts in the post-task check was not associated with answers consistent with these doubts in the phase 2 assessments. In other words, participants that ticked "I think all images were real/fake" did not actually rate all images as being real or fake, aside from `r length(exclude$phase2)` participants, which had their phase 2 data dropped due to lack of variability.

### Phase 2 Instruction Misunderstanding

Did they misunderstand phase 2 and thought it was a recognition task?

```{r}
phase2congruence <- dftask |> 
  summarize(Reality = sum(Reality > 0) / n(), Authenticity = sum(Authenticity > 0)  / n(),
            # Reality = mean(Reality), Authenticity = mean(Authenticity), 
            .by=c("Participant", "Condition")) |> 
  pivot_wider(names_from = Condition, values_from = c(Reality, Authenticity)) |> 
  # mutate(CongruentReality = (Reality_Human + Reality_AI) / 2,
  #        CongruentAuthenticity = (Authenticity_Human + Authenticity_Forgery) / 2) |> 
  full_join(select(df, Participant, Duration_TaskInstructions2), by = "Participant") |> 
  full_join(manipcheck, by = "Participant") |> 
  mutate(Confidence = ifelse(is.na(Answer), -1, Confidence),
         Answer = ifelse(is.na(Answer), "No doubts", Answer)) |> 
  mutate(Mean_Congruence = (`Reality_Human Original` + (1 - `Reality_AI-Generated`) + (1 - `Authenticity_Human Forgery`) + `Authenticity_Human Original`) / 4) |> 
  arrange(desc(Mean_Congruence))

phase2congruence |> 
  ggplot(aes(x=Mean_Congruence)) +
  geom_histogram(bins = 20)

phase2congruence |> 
  ggplot(aes(x = `Reality_Human Original`, y = `Authenticity_Human Original`, color = Answer)) +
  geom_jitter(aes(size=Confidence), shape = "+", width = 0.01, height=0.01, alpha = 0.9) +
  ggrepel::geom_label_repel(data = filter(phase2congruence, `Reality_Human Original` > 0.95 | `Authenticity_Human Original` > 0.95), 
                            aes(label = Participant), size = 3) +
  ggside::geom_xsidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::geom_ysidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::theme_ggside_void() +
  theme_minimal() +
  scale_size_continuous(range = c(4, 8)) 
  

# Note: we know for sure S024 (fghgugdaz0) is an outlier and thought it was recognition
```

```{r}
exclude$phase2
# exclude$phase2_cong <- filter(phase2congruence, Reality_Human == 1 | Authenticity_Human == 1)$Participant
exclude$phase2_cong <- filter(phase2congruence, Mean_Congruence > 0.7 & !Participant %in% exclude$phase2)$Participant

dftask[dftask$Participant %in% c(exclude$phase2, exclude$phase2_cong), "Reality"] <- NA
dftask[dftask$Participant %in% c(exclude$phase2, exclude$phase2_cong), "Authenticity"] <- NA
```


Based on the distribution of congruency scores (i.e., the proportion of items presented as "Human Originals" rated as "Real" and items presented as "Forgeries" rated as "Copies"), we excluded `r length(exclude$phase2_cong)` outlying participants' data of phase 2.

## Final Sample

::: {.panel-tabset}

### Summary


The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.



### Age and Gender

```{r p_demographics_age_gender}
p_age <- df |>
  ggplot(aes(x = Age, fill = Gender)) + 
  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 3) +
  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1, linetype="dashed") +
  scale_fill_viridis_d() +
  scale_x_continuous(expand = c(0, 0), breaks = seq(20, max(df$Age), by = 10 )) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )

p_age
```

### Education

```{r p_demographics_education}
#| warning: false
#| error: false

p_edu <- df |>
  mutate(Student = ifelse(is.na(Student) | (Student == FALSE), "Not studying", "Currently studying"),
         Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Student)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
  see::scale_fill_bluebrown_d() +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2)),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

p_edu
```

### Ethnicity

```{r p_demographics_ethnicity}
#| warning: false
#| error: false

p_eth <- df |>
  mutate(Ethnicity = ifelse(is.na(Ethnicity), "Prefer not to answer", Ethnicity)) |>
  mutate(Freq = format_percent(n() / nrow(df), digits=1), .by=Ethnicity) |> 
  mutate(Ethnicity = fct_infreq(paste0(Ethnicity, " (", Freq, ")"))) |> 
  ggplot(aes(x = "", fill = Ethnicity)) +
  geom_bar() +
  coord_polar("y") +
  see::scale_fill_social_d() +
  labs(title = "Ethnicity", subtitle = "Self-declared ethnicity") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  ) 
    
p_eth
```

### Country

```{r p_demographics_map}
p_map <- df |>
  mutate(Country = case_when(
    Country=="United States"~ "USA",
    Country=="United Kingdom" ~ "UK",
    TRUE ~ Country
  ))|>
  dplyr::select(region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  # mutate(n = replace_na(n, 0)) |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  ) + 
  coord_fixed()

p_map
```

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |>
  rename(Country = Var1) |> 
  arrange(desc(Freq)) |> 
  gt::gt()
```

:::

```{r}
#| fig-width: 15
#| fig-height: 12

(p_age / p_edu) | (p_map / p_eth) 
```

## Save

```{r}
dftask |> 
  left_join(select(df, Participant, ManipulationDistrust), by = c("Participant")) |> 
  left_join(select(read.csv("../data/rawdata_memory_task.csv"), Participant, Item, SelfRelevance, Beauty2), by = c("Participant", "Item")) |> 
  mutate(Emotion = paste0(ifelse(Norms_Valence < median(Norms_Valence), "Negative", "Positive"), ifelse(Norms_Arousal < median(Norms_Arousal), " - Low intensity", " - High intensity")),
         Beauty = datawizard::rescale(Beauty, to = c(0, 1), range = c(-3, 3)),
         Valence = datawizard::rescale(Valence, to = c(0, 1), range = c(-3, 3)),
         Meaning = datawizard::rescale(Meaning, to = c(0, 1), range = c(0, 6)),
         Worth = datawizard::rescale(Worth, to = c(0, 1), range = c(0, 5)),
         Reality = datawizard::rescale(Reality, to = c(0, 1), range = c(-100, 100)),
         Authenticity = datawizard::rescale(Authenticity, to = c(0, 1), range = c(-100, 100)),
         Beauty2 = datawizard::rescale(Beauty2, to = c(0, 1), range = c(-3, 3)),
         SelfRelevance = datawizard::rescale(SelfRelevance, to = c(0, 1), range = c(0, 6))
         ) |>
  datawizard::normalize(select = c("Norms_Liking", "Norms_Valence", "Norms_Arousal", "Norms_Complexity", "Norms_Familiarity")) |>
  write.csv("../data/data_task.csv", row.names = FALSE)




dfmem <- read.csv("../data/rawdata_memory_task.csv") 
# sum(!unique(dfmem$Participant) %in% df$Participant)
dfmem <- dfmem |> 
  filter(Participant %in% df$Participant) |> 
  left_join(select(dftask, Participant, Item, Condition, Reality, Authenticity), by = c("Participant", "Item")) |>
  rename(AnswerCondition = SourceCondition, AnswerBelief = SourceBelief) |> 
  mutate(Type = ifelse(is.na(Condition), "New", "Old"),
         Condition = ifelse(is.na(Condition), "New Items", as.character(Condition)),
         AnswerCondition = ifelse(is.na(AnswerCondition), "Not recognized", AnswerCondition),
         AnswerBelief = ifelse(is.na(AnswerBelief), "Not recognized", AnswerBelief),
         Belief = case_when(
           Reality >= 0.5 & Authenticity >= 0.5 ~ "Human Original",
           Reality < 0.5 & Authenticity >= 0.5 ~ "AI Original",
           Reality >= 0.5 & Authenticity < 0.5 ~ "Human Forgery",
           Reality < 0.5 & Authenticity < 0.5 ~ "AI Copy",
           .default = "None"
         ))
write.csv(dfmem, "../data/data_memory_task.csv", row.names = FALSE)

df |> 
  left_join(select(read.csv("../data/rawdata_memory_participants.csv"), Participant, Experiment_StartDate2 = Experiment_StartDate), 
            by = "Participant") |> 
  mutate(Delay = as.numeric(as.Date(Experiment_StartDate2) - as.Date(Experiment_StartDate))) |> 
  write.csv("../data/data_participants.csv", row.names = FALSE)
```
