---
title: "FictionArt - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)

df <- read.csv("../data/rawdata_participants.csv")
dftask <- read.csv("../data/rawdata_task.csv")
```

## Recruitment History

```{r}
#| message: false

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Experiment_StartDate, format = "%Y-%m-%d %H:%M:%S")) |> 
  summarize(N = n(), .by=c("Date", "Recruitment")) |> 
  complete(Date, Recruitment, fill = list(N = 0)) |> 
  mutate(N = cumsum(N), .by="Recruitment") |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Recruitment)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

```{r}
#| message: false

# Table
summarize(df, N = n(), .by=c("Recruitment")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::grand_summary_rows(columns = "N", fns = Total ~ sum(.)) |> 
  gt::opt_stylize(style = 2, color = "gray") |> 
  gt::tab_header("Number of participants per recruitment source") 
```

## Experiment Feedback

### Experiment Enjoyment

```{r}
#| fig-height: 3
#| fig-width: 8

df |> 
  summarise(n = n(), .by=c("Experiment_Enjoyment")) |>
  filter(!is.na(Experiment_Enjoyment)) |> 
  mutate(n = n / sum(n),
         Experiment_Enjoyment = fct_rev(as.factor(Experiment_Enjoyment))) |>
  ggplot(aes(y = n, x = 1, fill = Experiment_Enjoyment)) +
  geom_bar(stat="identity", position="stack") +
  scale_fill_manual(values=c("green", "yellowgreen",  "yellow", "orange", "red")) +
  coord_flip() +
  scale_x_continuous(expand=c(0, 0))  +
  scale_y_continuous(labels = scales::percent)  +
  labs(title="Experiment Enjoyment",
       subtitle="Proportion of participants by condition") + 
  guides(fill = guide_legend(reverse=TRUE)) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "top",
    legend.title = element_blank()) 
```

### Comments

```{r}
data.frame(Comments = df$Experiment_Feedback) |> 
  filter(!tolower(Comments) %in% c(NA, "no", "none", "thank you", "nope", "N/A")) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```


## Task Feedback

### Proportion

```{r}
dat <- df |> 
  select(starts_with("Feedback"), -contains("Confidence")) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
  group_by(Question, Answer) |> 
  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
  complete(Question, Answer, fill = list(prop = 0)) |> 
  filter(Answer == TRUE) |> 
  mutate(Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "LabelsNotMatched", "Labels did not always match the images"),
         Question = str_replace(Question, "LabelsReversed", "Labels were Reversed"),
         # Question = str_replace(Question, "DiffNone", "No Difference Real/AI"),
         # Question = str_replace(Question, "DiffObvious", "Obvious Difference Real/AI"),
         # Question = str_replace(Question, "DiffSubtle", "Subtle Difference Real/AI"),
         # Question = str_replace(Question, "AILessAttractive", "AI = less attractive"),
         # Question = str_replace(Question, "AIMoreAttractive", "AI = more attractive"),
         # Question = str_replace(Question, "SomeFacesAttractive", "Some Faces Attractive"),
         Question = str_replace(Question, "GoodForgeries", "Forgeries very convincing and hard to distinguish"),
         Question = str_replace(Question, "BadForgeries", "Forgeries were less well executed")) |>
  mutate(Question = fct_reorder(Question, desc(prop)))

dat |> 
  ggplot(aes(x = Question, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
  labs(x="Feedback", y = "Participants", title = "Feedback") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
```

```{r}
dat |> 
  select(Question, prop) |> 
  arrange(desc(prop)) |> 
  mutate(prop = format_percent(prop)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::tab_header("Proportion of participants who answered 'yes' to each question") |> 
  gt::cols_label(prop = "Proportion of participants who answered 'Yes'")
```


### Co-occurence

```{r}
#| warning: false
#| fig-width: 10
#| fig-height: 9

cor <- df |> 
  select(starts_with("Feedback"), -contains("Confidence"))  |> 
  mutate_all(~ifelse(.==TRUE, 1, 0)) |> 
  correlation(method="tetrachoric", redundant = TRUE) |> 
  correlation::cor_sort() |> 
  correlation::cor_lower()

cor |> 
  mutate(val = paste0(insight::format_value(rho), format_p(p, stars_only=TRUE))) |>
  mutate(Parameter2 = fct_rev(Parameter2)) |>
  mutate(Parameter1 = fct_relabel(Parameter1, \(x) str_remove_all(x, "Feedback_")),
         Parameter2 = fct_relabel(Parameter2, \(x) str_remove_all(x, "Feedback_"))) |>
  ggplot(aes(x=Parameter1, y=Parameter2)) +
  geom_tile(aes(fill = rho), color = "white") +
  geom_text(aes(label = val), size = 3) +
  labs(title = "Feedback Co-occurence Matrix") +
  scale_fill_gradient2(
    low = "#2196F3",
    mid = "white",
    high = "#F44336",
    breaks = c(-1, 0, 1),
    guide = guide_colourbar(ticks=FALSE),
    midpoint = 0,
    na.value = "grey85",
    limit = c(-1, 1))  + 
  theme_minimal() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

:::


## Dimension Computation

```{r}
# Should we re-map the Worth values? -----------------------------------
# Re-map to values in dollars
# alldata_task$Worth2 <- ifelse(alldata_task$Worth == 1, 10, alldata_task$Worth)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 2, 100, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 3, 1000, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 4, 10000, alldata_task$Worth2)
# alldata_task$Worth2 <- ifelse(alldata_task$Worth2 == 5, 100000, alldata_task$Worth2)
#
# library(tidyverse)
#
# t <- as.data.frame(table(alldata_task$Worth))
# cor.test(as.numeric(as.character(t$Var1)), t$Freq)
# t <- as.data.frame(table(log1p(alldata_task$Worth2)))
# cor.test(as.numeric(as.character(t$Var1)), t$Freq)
#
# ggplot(alldata_task, aes(x=Worth)) +
#   geom_bar() +
#   geom_abline()
# ggplot(alldata_task, aes(x=log1p(Worth2))) +
#   geom_bar()
# ggplot(alldata_task, aes(x=Worth2)) +
#   geom_bar() +
#   scale_x_continuous(transform = "log1p", breaks = c(0, 10, 100, 1000, 10000, 100000))
# ggplot(alldata_task, aes(x=Worth, y=Beauty)) +
#   geom_smooth(method = "lm") +
#   geom_jitter(height=0)
# ggplot(alldata_task, aes(x=Worth2, y=Beauty)) +
#   geom_smooth(method = "lm") +
#   geom_jitter(height=0) +
#   scale_x_continuous(transform = "log1p", breaks = c(0, 10, 100, 1000, 10000, 100000))
# summary(lm(Beauty ~ Worth, data = alldata_task))
# summary(lm(Beauty ~ log1p(Worth2), data = alldata_task))
```


### MINT

```{r}
#| code-fold: true

compute_and_remove <- function(df, name="BodyAwareness", pattern=name, method="mean") {
  items <- select(df, starts_with(pattern), -contains("AttentionCheck"))
  df <- df[!names(df) %in% names(items)]
  if(method == "mean") {
    df[[name]] <- rowMeans(items, na.rm=TRUE)
  } else {
    df[[name]] <- rowSums(items, na.rm=TRUE)
  }
  df
}
```

```{r}
#| code-fold: false

# > names(df)
#   [1] "Participant"                    "Recruitment"                    "Experiment_StartDate"           "Experiment_Duration"           
#   [5] "Browser_Version"                "Mobile"                         "Platform"                       "Screen_Width"                  
#   [9] "Screen_Height"                  "Gender"                         "Age"                            "Education"                     
#  [13] "Student"                        "Country"                        "Ethnicity"                      "Art_Expertise"                 
#  [17] "Experiment_Enjoyment"           "Experiment_Quality"             "Experiment_Feedback"            "MINT_Derm_16"                  
#  [21] "MINT_Resp_26"                   "MINT_ExAc_1"                    "MINT_Gast_33"                   "MINT_Olfa_23"                  
#  [25] "MINT_Derm_18"                   "MINT_Sati_20"                   "MINT_Resp_25"                   "MINT_ReIA_6"                   
#  [29] "MINT_ReIA_4"                    "MINT_ExAc_2"                    "MINT_SexS_9"                    "MINT_SexS_7"                   
#  [33] "MINT_Gast_32"                   "MINT_Derm_17"                   "MINT_Urin_15"                   "MINT_CaCo_11"                  
#  [37] "MINT_Urin_13"                   "MINT_Sati_21"                   "MINT_Card_29"                   "MINT_CaCo_10"                  
#  [41] "MINT_Resp_27"                   "MINT_Sati_19"                   "MINT_CaCo_12"                   "MINT_AttentionCheck"           
#  [45] "MINT_Olfa_24"                   "MINT_Gast_31"                   "MINT_Urin_14"                   "MINT_ReIA_5"                   
#  [49] "MINT_Card_28"                   "MINT_Card_30"                   "MINT_SexS_8"                    "MINT_ExAc_3"                   
#  [53] "MINT_Olfa_22"                   "Duration_MINT"                  "BAIT_AI_Knowledge"              "BAIT_AI_Use"                   
#  [57] "BAIT_5_ImitatingReality"        "BAIT_12_Benefit"                "BAIT_4_VideosRealistic"         "BAIT_8_TextIssues"             
#  [61] "BAIT_1_ImagesRealistic"         "BAIT_2_ImagesIssues"            "BAIT_3_VideosIssues"            "BAIT_14_ArtRealistic"          
#  [65] "BAIT_6_EnvironmentReal"         "BAIT_9_Dangerous"               "BAIT_7_TextRealistic"           "BAIT_13_ArtIssues"             
#  [69] "BAIT_AttentionCheck"            "BAIT_10_Worry"                  "BAIT_11_Exciting"               "Duration_BAIT"                 
#  [73] "LifeSatisfaction"               "PHQ4_Depression_4"              "PHQ4_Anxiety_1"                 "PHQ4_Depression_3"             
#  [77] "PHQ4_Anxiety_2"                 "Duration_ERNS"                  "ERNS_4_r"                       "ERNS_3_r"                      
#  [81] "ERNS_2_r"                       "ERNS_1"                         "ERNS_8_r"                       "ERNS_7_r"                      
#  [85] "ERNS_6_r"                       "ERNS_5"                         "VVIQ_Friend_1"                  "VVIQ_Friend_2"                 
#  [89] "VVIQ_Friend_3"                  "VVIQ_Friend_4"                  "VVIQ_Sun_5"                     "VVIQ_Sun_7"                    
#  [93] "VVIQ_Sun_6"                     "VVIQ_Sun_8"                     "VVIQ_Shop_9"                    "VVIQ_Shop_10"                  
#  [97] "VVIQ_Shop_11"                   "VVIQ_Shop_12"                   "VVIQ_Country_13"                "VVIQ_Country_14"               
# [101] "VVIQ_Country_15"                "VVIQ_Country_16"                "Duration_VVIQ"                  "Duration_TaskInstructions1"    
# [105] "Duration_TaskInstructions2"     "Feedback_MoreBeautifulAI"       "Feedback_LessBeautifulAI"       "Feedback_BigDifferenceRealAI"  
# [109] "Feedback_SmallDifferenceRealAI" "Feedback_NoDifferenceRealAI"    "Feedback_BadForgeries"          "Feedback_GoodForgeries"        
# [113] "Feedback_LabelsNoAttention"     "Feedback_LabelsPaidAttention"   "Feedback_LabelsNotMatched"      "Feedback_LabelsReversed"       
# [117] "Feedback_LabelsAllReal"         "Feedback_LabelsAllAI"           "Feedback_ConfidenceReal"        "Feedback_ConfidenceAI"         
# [121] "Task_AttentionCheck"            "Eyetracking_Validation1"        "Eyetracking_Validation2"       

df <- compute_and_remove(df, name="MINT_Card", method="mean")
df <- compute_and_remove(df, name="MINT_Urin", method="mean")
df <- compute_and_remove(df, name="MINT_SexS", method="mean")
df <- compute_and_remove(df, name="MINT_Gast", method="mean")
df <- compute_and_remove(df, name="MINT_Olfa", method="mean")
df <- compute_and_remove(df, name="MINT_Derm", method="mean")
df <- compute_and_remove(df, name="MINT_ExAc", method="mean")
df <- compute_and_remove(df, name="MINT_RelA", method="mean")





# df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
# df <- compute_and_remove(df, name="MAIA_AttentionRegulation", method="mean")
```


## Exclusions 

```{r}
exclude <- list()
```

### Questionnaires


```{r}
m <- mgcv::gam(MINT_AttentionCheck ~ s(Duration_MINT), 
         data = mutate(df, MINT_AttentionCheck = ifelse(MINT_AttentionCheck != 0, 1, 0)), family = "binomial")

estimate_relation(m, length=50) |>
  ggplot(aes(x = Duration_MINT, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "MINT Attention Check",
       subtitle = "Predicted probability of failing attention check by duration",
       x = "Duration (minutes)",
       y = "Probability of failing attention check")

table(ifelse(df$MINT_AttentionCheck != 0, 1, 0), ifelse(df$BAIT_AttentionCheck != 6, 1, 0))


for(ppt in df$Participant) {
  if(df[df$Participant == ppt, "MINT_AttentionCheck"] != 0) {
    df[df$Participant == ppt, names(select(df, starts_with("MINT"), -MINT_AttentionCheck))] <- NA
    df[df$Participant == ppt, names(select(df, starts_with("VVIQ")))] <- NA
  }
  
  if(df[df$Participant == ppt, "BAIT_AttentionCheck"] != 6) {
    df[df$Participant == ppt, names(select(df, starts_with("BAIT"), -BAIT_AttentionCheck))] <- NA
  }
}
```



### Attention Checks

```{r}
dfchecks <- data.frame(
  Participant = df$Participant,
  A_MINT = ifelse(df$MINT_AttentionCheck == 0, 0, 1),
  A_BAIT = ifelse(df$BAIT_AttentionCheck == 6, 0, 1),
  A_TASK = 1 - df$Task_AttentionCheck
)

summary(correlation(dfchecks))

dfchecks |>
  mutate(Total = round(A_TASK, 2)) |> 
  ggplot(aes(x = Total)) +
  geom_bar(aes(fill = as.factor(Total))) +
  scale_fill_viridis_d(guide = "none") +
  scale_x_continuous(labels = scales::percent) +
  labs(title = "Failed Attention Checks", y = "Number of Participants", subtitle = "Number of failed attention checks per participant") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.title.x = element_blank(),
  )
```

```{r}
exclude$checks <- as.character(na.omit(dfchecks[dfchecks$A_TASK >= 0.5, "Participant"]))
```


We removed `r length(exclude$checks)` (`r insight::format_percent(length(exclude$checks) / nrow(df))`) participants for having failed at least 50% of attention checks.



### Experiment Duration

```{r}
dfchecks$Duration_Experiment <- df |> 
  mutate(Version = ifelse(Recruitment == "prolific", "long", "short")) |> 
  mutate(Experiment_Duration = as.numeric(standardize(Experiment_Duration)), .by = "Version") |>
  pull(Experiment_Duration) |> 
  normalize() |> 
  log1p()

# hist(dfchecks$Duration_Experiment)

dfchecks$Duration_Instructions1 <- log(df$Duration_TaskInstructions1)
dfchecks$Duration_Instructions2 <- log(df$Duration_TaskInstructions2)

m <- mgcv::gam(A_TASK ~ s(Duration_Experiment), 
               data = dfchecks[!is.na(dfchecks$A_TASK),] |> 
                 mutate(A_TASK = normalize(A_TASK, include_bounds = 0.001)), family = "betar")

estimate_relation(m, length=50) |> 
  ggplot(aes(x = Duration_Experiment, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  geom_hline(yintercept=1/3, linetype="dashed", color="darkgrey") +
  geom_vline(xintercept=0.52, linetype="dashed", color="red") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  ggside::geom_xsidedensity(
    data=mutate(dfchecks[!is.na(dfchecks$A_TASK),], AttentionCheckLabel = ifelse(A_TASK >= 0.5, "Failed 50% attention checks", "Valid")), 
    aes(fill=AttentionCheckLabel), alpha=0.3) +
  ggside::theme_ggside_void() +
  labs(title = "Experiment Duration",
       subtitle = "Predicted probability of failing attention checks by duration",
       x = "Experiment Duration (log(Z))",
       y = "Probability of failing attention checks") 
```

```{r}
exclude$duration <- as.character(dfchecks[dfchecks$Experiment_Duration >= 0.52, "Participant"])
exclude$duration <- exclude$duration[!exclude$duration %in% exclude$checks]
```

<!-- We removed `r length(exclude$duration)` (`r insight::format_percent(length(exclude$duration) / nrow(df))`) participants for having completed the experiment in less than 5 minutes. -->


### Response Consistency

```{r}
#| warning: false
#| fig-width: 10
#| fig-height: 10

dftask |> 
  select(-starts_with("Screen"), -starts_with("Trial")) |> 
  correlation() |> 
  summary() |> 
  plot() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dfchecks <- dftask |> 
  summarize(across(c("Beauty", "Valence", "Meaning", "Worth", "Reality"), 
                   list(M = ~ mean(.x, na.rm = TRUE), SD = ~ sd(.x, na.rm = TRUE))),
            cor_BeautyValence = cor(Beauty, Valence, method = "spearman"),
            cor_MeaningWorth = cor(Meaning, Worth, method = "spearman"),
            cor_BeautyNorm = cor(Beauty, Norms_Liking, method = "spearman"),
            cor_ValenceNorm = cor(Valence, Norms_Valence, method = "spearman"),
            .by = c("Participant")) |> 
  mutate(cor_BeautyValence = ifelse(is.na(cor_BeautyValence), -1, cor_BeautyValence),
         cor_MeaningWorth = ifelse(is.na(cor_MeaningWorth), -1, cor_MeaningWorth),
         cor_BeautyNorm = ifelse(is.na(cor_BeautyNorm), -1, cor_BeautyNorm)) |>
  full_join(dfchecks, by = "Participant", keep = FALSE)
```

### Anomaly Score

```{r}
#| warning: false
#| message: false

features <- dfchecks |> 
  mutate(A_QUESTIONNAIRES = (A_MINT + A_BAIT) / 2) |> 
  select(-A_MINT, -A_BAIT, -A_TASK) |> 
  select(matches("_M|_SD|cor_|A_|SubjectiveQuality|Duration")) |> 
  standardize()

model <- solitude::isolationForest$new(sample_size = nrow(features), num_trees = 500)
model$fit(features)
dfchecks$AnomalyScore <- model$predict(features)$anomaly_score
 
# features <- mice::mice(features, method="pmm", m = 20, seed = 123, printFlag = FALSE) |> 
#   suppressWarnings() |> 
#   mice::complete(1)
```

```{r}
#| warning: false

m <- mgcv::gam(A_TASK ~ s(log(AnomalyScore), k=80), 
               data = dfchecks[!is.na(dfchecks$A_TASK),] |> 
                 mutate(A_TASK = normalize(A_TASK, include_bounds = 0.001)), 
               family = "betar")
# m <- mgcv::gam(A_TASK ~ s(log(AnomalyScore), k=20), data = mutate(dfchecks, A_TASK = ifelse(A_TASK >= 0.5, 1, 0)), family = "binomial")

estimate_relation(m, length=100) |> 
  ggplot(aes(x = AnomalyScore, y = Predicted)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line() +
  geom_vline(xintercept=quantile(dfchecks$AnomalyScore, 0.95), linetype="dashed", color="red") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Experiment Duration",
       subtitle = "Predicted probability of failing attention checks by duration",
       x = "Anomaly Score",
       y = "Probability of failing attention checks") +
  ggside::geom_xsidehistogram(data=dfchecks, alpha=0.3, bins = 60) +
  ggside::geom_ysidedensity(data=dfchecks, aes(y=A_TASK), alpha=0.3) +
  ggside::theme_ggside_void() 
```


```{r}
exclude$anomaly <- as.character(dfchecks[dfchecks$AnomalyScore > quantile(dfchecks$AnomalyScore, 0.95), "Participant"])
exclude$anomaly <- exclude$anomaly[!exclude$anomaly %in% exclude$duration]
exclude$anomaly <- exclude$anomaly[!exclude$anomaly %in% exclude$checks]

length(c(exclude$anomaly, exclude$duration, exclude$checks))
```


<!-- ### Clustering -->

<!-- ```{r} -->
<!-- #| warning: false -->

<!-- rez <- dbscan::optics(features, eps = 100, minPts = 3) -->
<!-- hist(rez$reachdist) -->
<!-- clusters <- dbscan::extractDBSCAN(rez, eps_cl = quantile(rez$reachdist, 0.85)) -->
<!-- dfchecks$Cluster <- as.factor(clusters$cluster) -->
<!-- ``` -->


```{r}
#| warning: false
#| fig-width: 13
#| fig-height: 13

selected_features <- features |>
  mutate(Cluster = ifelse(dfchecks$Participant %in% c(exclude$anomaly, exclude$duration, exclude$checks), "Excluded", "Valid")) |>
  select(Cluster, starts_with("Duration"), starts_with("A_"), starts_with("cor_"), starts_with("Beauty_"))


var_names <- names(select(selected_features, -Cluster))
feature_pairs <- expand_grid(x_var = var_names, y_var = var_names)
feature_pairs <- feature_pairs |>
  mutate(
    triangle = case_when(
      match(x_var, var_names) > match(y_var, var_names) ~ "lower",
      match(x_var, var_names) == match(y_var, var_names) ~ "diag",
      TRUE ~ "upper"
    )
  )
plot_data <- pmap_dfr(feature_pairs, function(x_var, y_var, triangle) {
  selected_features |>
    select(Cluster, x = all_of(x_var), y = all_of(y_var)) |>
    mutate(x_var = x_var, y_var = y_var, triangle = triangle)
}) |>
  mutate(
    x_var = factor(x_var, levels = rev(var_names)),
    y_var = factor(y_var, levels = rev(var_names))
  )

diag_histograms <- map_dfr(var_names, function(var) {
  # histogram bins computed globally for consistent breaks
  breaks <- hist(selected_features[[var]], breaks = 20, plot = FALSE)$breaks
  all_counts <- selected_features |>
    group_by(Cluster) |>
    summarise(counts = list(hist(!!sym(var), breaks = breaks, plot = FALSE)$counts),
              .groups = "drop")

  # max count across all clusters for this variable
  max_count <- max(unlist(all_counts$counts), na.rm = TRUE)
  y_range <- range(selected_features[[var]], na.rm = TRUE)

  all_counts |>
    unnest_wider(counts, names_sep = "_") |>
    pivot_longer(starts_with("counts_"), names_to = "bin", values_to = "count") |>
    mutate(
      bin_id = as.integer(gsub("counts_", "", bin)),
      x = breaks[-length(breaks)][bin_id],
      xmax = breaks[-1][bin_id],
      ymin = y_range[1],
      ymax = ymin + (count / max_count) * diff(y_range),
      var = var
    ) |>
    select(x, xmax, ymin, ymax, var, Cluster)
}) |> mutate(
  x_var = factor(var, levels = rev(var_names)),
  y_var = factor(var, levels = rev(var_names))
)

ggplot(plot_data, aes(x = x)) +
  # stat_density_2d_filled(data = filter(plot_data, triangle == "lower", x_var != "AttentionCheck", y_var != "AttentionCheck"),
  #                        aes(y = y, fill = after_stat(nlevel)), show.legend = FALSE) +
  # scale_fill_gradient(low = "white", high = "darkgreen") +
  # ggnewscale::new_scale_fill() +
  geom_point2(data = filter(plot_data, triangle == "lower"),
              aes(y = y, color = Cluster), alpha = 0.7, size = 3, shape = "+") +
  geom_rect(data = diag_histograms,
          aes(xmin = x, xmax = xmax, ymin = ymin, ymax = ymax, fill = Cluster),
          colour = NA, alpha = 0.5) +
  geom_blank(data = filter(plot_data, triangle != "lower")) +
  facet_grid(y_var ~ x_var, scales = "free", switch = "both") +
  # scale_color_gradient(low = "black", high = "red") +
  labs(color = "Participants", fill = "Participants") +
  theme_minimal() +
  theme(strip.placement = "outside",
        strip.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title = element_blank())
```

<!-- ### UMAP -->

<!-- ```{r} -->
<!-- # Grid search -->
<!-- # UMAP or T-SNE? -->

<!-- param_grid <- expand.grid( -->
<!--   n_neighbors = c(3, 5, 10), -->
<!--   min_dist = c(0.01, 0.05, 0.1, 0.5), -->
<!--   metric = "euclidean" -->
<!-- ) -->

<!-- umap_plots <- list() -->
<!-- for (i in seq_len(nrow(param_grid))) { -->
<!--   params <- param_grid[i, ] -->
<!--   set.seed(123) -->
<!--   out <- uwot::umap(as.matrix(features), -->
<!--                    n_neighbors = params$n_neighbors, -->
<!--                    min_dist = params$min_dist, -->
<!--                    metric = params$metric) |>  -->
<!--     as.data.frame() -->

<!--   colnames(out) <- c("UMAP1", "UMAP2") -->
<!--   out$param_combo <- paste0("nn=", params$n_neighbors, ", md=", params$min_dist) -->
<!--   out$Participant <- dfchecks$Participant -->
<!--   out$AnomalyScore <- selected_features$AnomalyScore -->
<!--   out$Cluster <- selected_features$Cluster -->

<!--   umap_plots[[i]] <- ggplot(out, aes(UMAP1, UMAP2, color = Cluster)) + -->
<!--     # geom_point(size = 3, alpha = 0.8) + -->
<!--     geom_text(aes(label = Participant), size = 3, vjust = 0.5, hjust=0.5) + -->
<!--     # scale_color_viridis_c(option = "plasma") + -->
<!--     theme_minimal() + -->
<!--     labs(title = out$param_combo[1])  -->
<!-- } -->

<!-- wrap_plots(umap_plots, ncol = 4) -->
<!-- ``` -->


### Self-Reported Quality

```{r}
dfchecks$SubjectiveQuality <- df$Experiment_Quality

dfchecks |> 
  ggplot(aes(x = SubjectiveQuality, y = A_TASK)) +
  geom_jitter(width = 0) +
  geom_smooth(method = "lm") 
```



### Effect of Exclusion

```{r}
dftask |> 
  select(Participant, Beauty, Valence, Meaning, Worth, Reality, Authenticity) |> 
  pivot_longer(-Participant, names_to = "Variable", values_to = "Value") |>
  ggplot(aes(x = Value)) +
  geom_histogram(aes(fill = Variable, y = after_stat(density)), bins = 30, position = "identity") +
  facet_wrap(~Variable, scales = "free") 
```

```{r}
library(glmmTMB)

dftask <- mutate(dftask, Condition = fct_relevel(Condition, "Human", "AI", "Forgery"))

quick_test <- function(what = "Beauty", family = "gaussian", exclude = c()){
  f <- as.formula(paste0(what, " ~ Condition + (1 + Condition|Participant)"))
  if(family == "ordbeta") {
    dat <- normalize(dftask, select = what)
  } else {
    dat <- dftask
  }
  
  m <- glmmTMB::glmmTMB(f, data = dat, family = family)
  params <-  parameters::parameters(m, effects = "fixed")
  
  m2 <- glmmTMB::glmmTMB(f, data = filter(dat, !Participant %in% exclude), family = family)
  params2 <-  parameters::parameters(m2, effects = "fixed")
  
  params$Coefficient_Excluded <- params2$Coefficient
  params$p_Excluded <- format_p(params2$p, name = NULL)
  
  p <- estimate_means(m, by = "Condition") |> 
    mutate(Exclusion = "Whole sample") |> 
    rbind(estimate_means(m2, by = "Condition") |> 
            mutate(Exclusion = "Excluded")) 
  
  if("Proportion" %in% names(p)) p <- datawizard::data_rename(p, "Proportion", "Mean")
  
  p <- p |>
    ggplot(aes(x = Condition, y = Mean, color = Exclusion, group = Exclusion)) +
    geom_line(position = position_dodge(width = 0.1)) +
    geom_pointrange(aes(ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1), size = 1) 

  list(params = select(params, Parameter, Coefficient, Coefficient_Excluded, p, p_Excluded),
       plot = p)
}
```

```{r}
rez <- quick_test(what = "Beauty", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Beauty", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Valence", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Valence", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Meaning", family = "gaussian", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Meaning", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Worth", family = "poisson", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot  

rez <- quick_test(what = "Reality", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot
rez <- quick_test(what = "Authenticity", family = "ordbeta", exclude = c(exclude$anomaly, exclude$duration, exclude$checks))
rez$params
rez$plot
```

### Exclude

```{r}
#| code-fold: false

df <- filter(df, !Participant %in% c(exclude$anomaly, exclude$duration, exclude$checks))
```


## Manipulation Check

```{r}
#| fig-width: 15
#| fig-height: 15

manipcheck <- df |> 
  select(Participant, Feedback_ConfidenceReal, Feedback_ConfidenceAI) |> 
  pivot_longer(-Participant, values_to = "Confidence", names_to = "Answer") |>
  filter(!is.na(Confidence)) |> 
  mutate(Answer = ifelse(str_detect(Answer, "Real"), "All images are real", "All images are fake"))

manipcheck |> 
  ggplot(aes(x=Confidence, fill=Answer)) +
  geom_bar() +
  facet_grid(~Answer) +
  theme_minimal() +
  theme(legend.position = "none") 

exclude$manipulation <- filter(manipcheck, Confidence >= 4)$Participant

manipcheck |> 
  summarize(N = n(), 
            Prop = n() / nrow(df), 
            Mean_Confidence = mean(Confidence, na.rm = TRUE),
            SD_Confidence = sd(Confidence, na.rm = TRUE),
            .by = "Answer") |> 
  gt::gt() |> 
  gt::fmt_auto() |> 
  gt::opt_stylize()
```

```{r}
df_belief <- dftask |> 
  summarize(
    # Reality = sum(Reality > 0) / n(),
    # Authenticity = sum(Authenticity > 0)  / n(),
    Reality = mean(Reality, na.rm=TRUE),
    Authenticity = mean(Authenticity, na.rm=TRUE),
    .by=c("Participant")) |> 
  full_join(manipcheck, by = "Participant") |> 
  mutate(Confidence = ifelse(is.na(Answer), -1, Confidence),
         Answer = ifelse(is.na(Answer), "No doubts", Answer))

df_belief |> 
  ggplot(aes(x = Reality, y = Authenticity, color = Answer)) +
  geom_jitter(aes(size=Confidence), shape = "+", width = 0.01, height=0.01, alpha = 0.9) +
  ggrepel::geom_label_repel(data = filter(df_belief, abs(Reality) > 95 | abs(Authenticity) > 95),
                            aes(label = Participant), size = 3) +
  ggside::geom_xsidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::geom_ysidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::theme_ggside_void() +
  theme_minimal() +
  scale_size_continuous(range = c(4, 8)) 
```

```{r}
exclude$phase2 <- filter(df_belief, Reality > 90 | Authenticity > 90)$Participant
```


### Phase 2 Instruction Misunderstanding

Did they misunderstand phase 2 and thought it was a recognition task?

```{r}
phase2congruence <- dftask |> 
  summarize(Reality = sum(Reality > 0) / n(), Authenticity = sum(Authenticity > 0)  / n(),
            # Reality = mean(Reality), Authenticity = mean(Authenticity), 
            .by=c("Participant", "Condition")) |> 
  pivot_wider(names_from = Condition, values_from = c(Reality, Authenticity)) |> 
  # mutate(CongruentReality = (Reality_Human + Reality_AI) / 2,
  #        CongruentAuthenticity = (Authenticity_Human + Authenticity_Forgery) / 2) |> 
  full_join(select(df, Participant, Duration_TaskInstructions2), by = "Participant") |> 
  full_join(manipcheck, by = "Participant") |> 
  mutate(Confidence = ifelse(is.na(Answer), -1, Confidence),
         Answer = ifelse(is.na(Answer), "No doubts", Answer)) |> 
  mutate(Mean_Congruence = (Reality_Human + (1 - Reality_AI) + (1 - Authenticity_Forgery) + Authenticity_Human) / 4) |> 
  arrange(desc(Mean_Congruence))

phase2congruence |> 
  ggplot(aes(x=Mean_Congruence)) +
  geom_histogram(bins = 20)

phase2congruence |> 
  ggplot(aes(x = Reality_Human, y = Authenticity_Human, color = Answer)) +
  geom_jitter(aes(size=Confidence), shape = "+", width = 0.01, height=0.01, alpha = 0.9) +
  ggrepel::geom_label_repel(data = filter(phase2congruence, Reality_Human > 0.95 | Authenticity_Human > 0.95), 
                            aes(label = Participant), size = 3) +
  ggside::geom_xsidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::geom_ysidedensity(aes(fill=Answer), alpha=0.3) +
  ggside::theme_ggside_void() +
  theme_minimal() +
  scale_size_continuous(range = c(4, 8)) 
  

# Note: we know for sure S024 (fghgugdaz0) is an outlier and thought it was recognition
```

```{r}
exclude$phase2
# exclude$phase2_cong <- filter(phase2congruence, Reality_Human == 1 | Authenticity_Human == 1)$Participant
exclude$phase2_cong <- filter(phase2congruence, Mean_Congruence > 0.7 & !Participant %in% exclude$phase2)$Participant

dftask[dftask$Participant %in% c(exclude$phase2, exclude$phase2_cong), "Reality"] <- NA
dftask[dftask$Participant %in% c(exclude$phase2, exclude$phase2_cong), "Authenticity"] <- NA
```




## Final Sample

::: {.panel-tabset}

### Summary


The final sample includes `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.



### Age and Gender

```{r p_demographics_age_gender}
p_age <- df |>
  ggplot(aes(x = Age, fill = Gender)) + 
  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
  scale_fill_viridis_d() +
  scale_x_continuous(expand = c(0, 0), breaks = seq(20, max(df$Age), by = 10 )) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )

p_age
```

### Education

```{r p_demographics_education}
#| warning: false
#| error: false

p_edu <- df |>
  mutate(Student = ifelse(is.na(Student), FALSE, Student),
         Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Student)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

p_edu
```

### Ethnicity

```{r p_demographics_ethnicity}
#| warning: false
#| error: false

p_eth <- df |>
  filter(!is.na(Ethnicity)) |> 
  ggplot(aes(x = "", fill = Ethnicity)) +
  geom_bar() +
  coord_polar("y") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank()
  )
    
p_eth
```

### Country

```{r p_demographics_map}
p_map <- df |>
  mutate(Country = case_when(
    Country=="United States"~ "USA",
    Country=="United Kingdom" ~ "UK",
    TRUE ~ Country
  ))|>
  dplyr::select(region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  # mutate(n = replace_na(n, 0)) |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )

p_map
```

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |>
  rename(Country = Var1) |> 
  arrange(desc(Freq)) |> 
  gt::gt()
```

### BMI

```{r}
p_bmi <- df |> 
  filter(!is.na(BMI), Gender != "Other") |> 
  ggplot(aes(x=BMI)) +
  annotate("rect", xmin=10, xmax=18.5, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
  annotate("rect", xmin=18.5, xmax=25, ymin=0, ymax=Inf, fill="green", alpha=0.25) +
  annotate("rect", xmin=25, xmax=30, ymin=0, ymax=Inf, fill="yellow", alpha=0.25) +
  annotate("rect", xmin=30, xmax=40, ymin=0, ymax=Inf, fill="orange", alpha=0.25) +
  annotate("rect", xmin=40, xmax=Inf, ymin=0, ymax=Inf, fill="red", alpha=0.1) +
  geom_density(aes(color=Gender, fill=Gender), alpha=0.5, linewidth=2) +
  labs(title = "BMI distribution") +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

p_bmi_a <- df |> 
  filter(!is.na(BMI), Gender != "Other") |> 
  ggplot(aes(x=Age, y=BMI, color=Gender)) +
  geom_point(size=3, alpha=0.5) +
  geom_smooth(aes(fill=Gender), alpha=0.3, method = 'loess', formula = 'y ~ x') +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  theme_minimal() +
  theme(legend.position = "none")

p_bmi_b <- df |> 
  filter(!is.na(BMI), Gender != "Other") |> 
  ggplot(aes(x=Physical_Active, y=BMI)) +
  geom_jitter(aes(color=Gender), width=0.1, size=3, alpha=0.5) +
  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
  labs(x = "Physically Active", y = "") +
  scale_x_continuous(breaks=0:7) +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank()) +
  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
  ggside::theme_ggside_void()

df$Physical_Workout[df$Physical_Workout > 25] <- NA

p_bmi_c <- df |> 
  filter(!is.na(BMI) & !is.na(Physical_Workout), Gender != "Other") |> 
  ggplot(aes(x=Physical_Workout, y=BMI)) +
  geom_point(aes(color=Gender), size=3, alpha=0.5) +
  geom_smooth(aes(fill=Gender, color=Gender), alpha=0.3, method = 'lm', formula = 'y ~ x') +
  labs(x = "Hours of Active Workout", y = "") +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_color_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  theme_minimal() +
  theme(legend.position = "none") +
  ggside::geom_xsidehistogram(aes(fill=Gender), bins = 30, position="dodge") +
  ggside::theme_ggside_void()

p_bmi / (p_bmi_a | p_bmi_b | p_bmi_c)
```

### Mental Health


```{r}
df$Disorders_Psychiatric_Mood <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)
df$Disorders_Psychiatric_MoodTreatment <- ifelse(
  df$Disorders_Psychiatric_Mood & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Mood|Antidepressant|Anxiolytic|Psychotherapy"), TRUE, FALSE)

df$Disorders_Psychiatric_Anxiety <- ifelse(str_detect(df$Disorders_Psychiatric, "Panic|GAD|Social Phobia|Phobia"), TRUE, FALSE)
df$Disorders_Psychiatric_AnxietyTreatment <- ifelse(
  df$Disorders_Psychiatric_Anxiety & !is.na(df$Disorders_PsychiatricTreatment) & str_detect(df$Disorders_PsychiatricTreatment, "Anxiolytic|Psychotherapy|Mindfulness"), TRUE, FALSE)

df$Disorders_Psychiatric_Eating <- ifelse(str_detect(df$Disorders_Psychiatric, "Eating"), TRUE, FALSE)
df$Disorders_Psychiatric_Addiction <- ifelse(str_detect(df$Disorders_Psychiatric, "Addiction"), TRUE, FALSE)
df$Disorders_Psychiatric_Borderline <- ifelse(str_detect(df$Disorders_Psychiatric, "BPD"), TRUE, FALSE)

df$Disorders_Psychiatric_Autism <- ifelse(str_detect(df$Disorders_Psychiatric, "ASD"), TRUE, FALSE)
df$Disorders_Psychiatric_ADHD <- ifelse(str_detect(df$Disorders_Psychiatric, "ADHD"), TRUE, FALSE)


# df$Disorders_Psychiatric_Other <- ifelse(str_detect(df$Disorders_Psychiatric, "MDD|GAD|Bipolar"), TRUE, FALSE)

select(df, Participant, Gender, 
             Disorders_Psychiatric_Mood, Disorders_Psychiatric_MoodTreatment,
             Disorders_Psychiatric_Anxiety, Disorders_Psychiatric_AnxietyTreatment,
             Disorders_Psychiatric_Eating, Disorders_Psychiatric_Addiction, Disorders_Psychiatric_Borderline,
             Disorders_Psychiatric_Autism, Disorders_Psychiatric_ADHD) |> 
  pivot_longer(cols = starts_with("Disorders_"), names_to = "Disorder", values_to = "Value") |> 
  mutate(Disorder = str_remove_all(Disorder, fixed("Disorders_Psychiatric_")),
         Disorder = str_replace(Disorder, "MoodTreatment", "Mood Disorder (with treatment)"),
         Disorder = str_replace(Disorder, "AnxietyTreatment", "Anxiety (with treatment)"),
         Disorder = str_replace(Disorder, "Mood$", "Mood Disorder")) |> 
  summarize(N = sum(Value) / nrow(df), .by=c("Gender", "Disorder")) |> 
  mutate(N_tot = sum(N), .by="Disorder") |>
  mutate(Disorder = fct_reorder(Disorder, desc(N_tot)),
         Treatment = ifelse(str_detect(Disorder,  "Treatment"), "With treatment", "Without treatment")) |>
  ggplot(aes(x = Disorder, y = N, fill=Gender)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_y_continuous(expand = c(0, 0), labels=scales::percent) +
  labs(title = "Mood Disorders", y = "Number of Participants", subtitle = "Participants per self-declared mood disorder", x="Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```


### Somatic

```{r}
somatic <- data.frame(
  Hypermobility = ifelse(str_detect(df$Disorders_Somatic, "Hypermobility Syndrome"), TRUE, FALSE),
  Fibromyalgia = ifelse(str_detect(df$Disorders_Somatic, "Fibromyalgia"), TRUE, FALSE),
  ChronicFatigue = ifelse(str_detect(df$Disorders_Somatic, "Chronic Fatigue Syndrome"), TRUE, FALSE),
  ChronicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pain Syndrome"), TRUE, FALSE),
  BackPain = ifelse(str_detect(df$Disorders_Somatic, "Back Pain"), TRUE, FALSE),
  MuscleTension = ifelse(str_detect(df$Disorders_Somatic, "Muscle Tension"), TRUE, FALSE),
  SkinRashes = ifelse(str_detect(df$Disorders_Somatic, "Skin Rashes"), TRUE, FALSE),
  Eczema = ifelse(str_detect(df$Disorders_Somatic, "Eczema"), TRUE, FALSE),
  Psoriasis = ifelse(str_detect(df$Disorders_Somatic, "Psoriasis"), TRUE, FALSE),
   # Dermatological = ifelse(str_detect(df$Disorders_Somatic, "Other Dermatological"), TRUE, FALSE),
  # Musculoskeletal = ifelse(str_detect(df$Disorders_Somatic, "Other Musculoskeletal"), TRUE, FALSE),
  Sjogrens = ifelse(str_detect(df$Disorders_Somatic, "Sjogren"), TRUE, FALSE),
  ChestPain = ifelse(str_detect(df$Disorders_Somatic, "Chest Pain"), TRUE, FALSE),
  Arrhythmia = ifelse(str_detect(df$Disorders_Somatic, "Cardiac Arrhythmia"), TRUE, FALSE),
  Hypertension = ifelse(str_detect(df$Disorders_Somatic, "Hypertension"), TRUE, FALSE),
  Hypotension = ifelse(str_detect(df$Disorders_Somatic, "Hypotension"), TRUE, FALSE),
  IBS = ifelse(str_detect(df$Disorders_Somatic, "IBS"), TRUE, FALSE),
  GERD = ifelse(str_detect(df$Disorders_Somatic, "GERD"), TRUE, FALSE),
  Crohn = ifelse(str_detect(df$Disorders_Somatic, "Crohn"), TRUE, FALSE),
  UlcerativeColitis = ifelse(str_detect(df$Disorders_Somatic, "Ulcerative Colitis"), TRUE, FALSE),
  Celiac = ifelse(str_detect(df$Disorders_Somatic, "Celiac Disease"), TRUE, FALSE),
  Gluten = ifelse(str_detect(df$Disorders_Somatic, "Gluten"), TRUE, FALSE),
  Lactose = ifelse(str_detect(df$Disorders_Somatic, "Lactose"), TRUE, FALSE),
  ShortBreath = ifelse(str_detect(df$Disorders_Somatic, "Shortness of Breath"), TRUE, FALSE),
  Asthma = ifelse(str_detect(df$Disorders_Somatic, "Asthma"), TRUE, FALSE),
  COPD = ifelse(str_detect(df$Disorders_Somatic, "COPD"), TRUE, FALSE),
  SleepApnea = ifelse(str_detect(df$Disorders_Somatic, "Sleep Apnea"), TRUE, FALSE),
  Bronchitis = ifelse(str_detect(df$Disorders_Somatic, "Chronic Bronchitis"), TRUE, FALSE),
  Nausea = ifelse(str_detect(df$Disorders_Somatic, "Nausea/Vomiting"), TRUE, FALSE),
  Dizziness = ifelse(str_detect(df$Disorders_Somatic, "Dizziness/Lightheadedness"), TRUE, FALSE),
  Migraine = ifelse(str_detect(df$Disorders_Somatic, "Migraine"), TRUE, FALSE),
  Neuropathy = ifelse(str_detect(df$Disorders_Somatic, "Neuropathy"), TRUE, FALSE),
  Epilepsy = ifelse(str_detect(df$Disorders_Somatic, "Epilepsy"), TRUE, FALSE),
  MS = ifelse(str_detect(df$Disorders_Somatic, "Multiple Sclerosis"), TRUE, FALSE),
  FrequentUrination = ifelse(str_detect(df$Disorders_Somatic, "Frequent Urination"), TRUE, FALSE),
  Endometriosis = ifelse(str_detect(df$Disorders_Somatic, "Endometriosis"), TRUE, FALSE),
  Cystitis = ifelse(str_detect(df$Disorders_Somatic, "Interstitial Cystitis"), TRUE, FALSE),
  PelvicPain = ifelse(str_detect(df$Disorders_Somatic, "Chronic Pelvic Pain Syndrome"), TRUE, FALSE)
)


somatic |> 
  select(where(~n_distinct(.) > 1)) |> 
  correlation::correlation(redundant = TRUE, p_adjust="none") |>
  correlation::cor_sort() |> 
  mutate(label = ifelse(p < .001, "*", ""),
         label = ifelse(r == 1, "", label)) |> 
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), size=3) +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
  labs(title = "Co-occurence Matrix of Somatic Disorders") +
  theme_minimal()  +
  theme(axis.text.x = element_text(angle=45, hjust=1),
        axis.title = element_blank())
  

# pca <- as.data.frame(prcomp(somatic)$rotation[, 1:5])
# pca$PC <- colnames(pca)[max.col(pca, ties.method='first')]
# 
# pca |> 
#   rownames_to_column(var="Disorder") |> 
#   pivot_longer(-c(Disorder, PC)) |> 
#   filter(PC == name) |> 
#   arrange(name, desc(value)) |> 
#   ggplot(aes(x=value, y=Disorder, fill=name)) +
#   geom_bar(stat = "identity") +
#   facet_wrap(~name, scale="free_y")
```

```{r}
#| fig-keep: "first"

# somatic |> 
#   select(where(~n_distinct(.) > 1)) |> 
#   EGAnet::bootEGA(
#     corr="pearson",
#     EGA.type = "EGA.fit",
#     model = "glasso", 
#     algorithm = "leiden",
#     seed=42)
```

To facilitate mechanistic interpretation and reduce redundancy, self-reported somatic symptoms were grouped into four non-overlapping clusters based on shared physiological pathways and known etiological mechanisms. The **Afferent Sensitivity** cluster included conditions associated with heightened interoceptive awareness and neurogenic excitability, such as migraine, neuropathy, dizziness, nausea, muscle tension, epilepsy, and frequent urination. The **Central Sensitization** cluster comprised syndromes characterized by chronic pain and fatigue, likely reflecting central amplification of sensory signals and HPA-axis dysregulation; this included fibromyalgia, chronic fatigue syndrome, chronic pain, back pain, pelvic pain, endometriosis, irritable bowel syndrome (IBS), and interstitial cystitis. The **Autonomic Dysfunction** cluster captured disorders linked to dysregulation of the autonomic and cardiopulmonary systems, including joint hypermobility, cardiac arrhythmia, chest pain, shortness of breath, hypo-/hypertension, sleep apnea, chronic obstructive pulmonary disease (COPD), and chronic bronchitis. Finally, the **Immune-Inflammatory** cluster encompassed conditions associated with immune dysregulation, barrier dysfunction, and gut-brain axis disturbance, such as eczema, psoriasis, skin rashes, asthma, celiac disease, gluten and lactose sensitivity, inflammatory bowel diseases (Crohn’s disease and ulcerative colitis), gastroesophageal reflux disease (GERD), multiple sclerosis, and Sjögren’s syndrome. Each symptom was assigned to a single cluster to preserve orthogonality and support subsequent analyses linking symptom profiles to interoceptive processes.

```{r}
# df$Disorders_Somatic_Number <- ifelse(df$Disorders_Somatic == "", 0, str_count(df$Disorders_Somatic, ";")+1)

# Cluster A: Afferent Sensitivity (neurogenic excitability, interoceptive hypervigilance)
df$Disorders_Somatic_AfferentSensitivity_N <- rowSums(somatic[, c(
  "Migraine", "Neuropathy", "MuscleTension", "Dizziness", 
  "Nausea", "Epilepsy", "FrequentUrination"
)])
df$Disorders_Somatic_AfferentSensitivity <- df$Disorders_Somatic_AfferentSensitivity_N >= 1

# Cluster B: Central Sensitization (pain and fatigue syndromes)
df$Disorders_Somatic_CentralSensitization_N <- rowSums(somatic[, c(
  "Fibromyalgia", "ChronicPain", "ChronicFatigue", "BackPain", 
  "PelvicPain", "Endometriosis", "IBS", "Cystitis"
)])
df$Disorders_Somatic_CentralSensitization <- df$Disorders_Somatic_CentralSensitization_N >= 1

# Cluster C: Autonomic Dysfunction (dysautonomia and cardiorespiratory instability)
df$Disorders_Somatic_AutonomicDysfunction_N <- rowSums(somatic[, c(
  "Hypermobility", "Arrhythmia", "ChestPain", "ShortBreath", 
  "Hypotension", "Hypertension", "SleepApnea", "COPD", "Bronchitis"
)])
df$Disorders_Somatic_AutonomicDysfunction <- df$Disorders_Somatic_AutonomicDysfunction_N >= 1

# Cluster D: Immune-Inflammatory (gut-brain axis, autoimmune and barrier-related conditions)
df$Disorders_Somatic_ImmuneInflammatory_N <- rowSums(somatic[, c(
  "SkinRashes", "Eczema", "Psoriasis", "Sjogrens", "Asthma", 
  "Celiac", "Gluten", "Lactose", "Crohn", "UlcerativeColitis", 
  "GERD", "MS"
)])
df$Disorders_Somatic_ImmuneInflammatory <- df$Disorders_Somatic_ImmuneInflammatory_N >= 1




p2 <- df |> 
  select(starts_with("Disorders_Somatic_"), Gender, Participant) |> 
  select(ends_with("_N"), Gender, Participant) |>
  pivot_longer(starts_with("Disorders_Somatic_")) |> 
  summarize(n = n(), .by=c("name", "value", "Gender")) |> 
  mutate(name = str_remove(name, "Disorders_Somatic_"),
         name = str_remove(name, "_N")) |> 
  ggplot(aes(x = value, y=n, fill=Gender)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Number of Issues") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~name)
p2
# 
# p2 <- df |> 
#   select(starts_with("Disorders_Somatic_"), Gender, Participant) |> 
#   select(-ends_with("_N"), Gender, Participant) |>
#   pivot_longer(starts_with("Disorders_Somatic_")) |> 
#   summarize(n = n(), .by=c("name", "value", "Gender")) |> 
#   filter(value == TRUE) |> 
#   ggplot(aes(x = name, y=n, fill=Gender)) +
#   geom_bar(stat="identity") +
#   scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292", "Other"="orange", "Missing"="brown")) +
#   scale_y_continuous(expand = c(0, 0)) +
#   labs(title = "Somatic Issues", y = "Number of Participants", subtitle = "Participants per somatic issues", x="Type") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
# p2
```

### Wearables 

```{r}
#| fig-height: 12

p1 <- df |> 
  ggplot(aes(x = Wearables_Number)) +
  geom_bar() +
  scale_x_continuous(breaks = c(0:max(df$Wearables_Number)), expand=c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Number of Wearable Devices", y = "Number of Participants", x="Number Owned") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme_minimal()


p2 <- df |> 
  select(contains("Wearables"), -contains("Importance"), -Wearables_Number) |> 
  pivot_longer(everything()) |> 
  summarize(n = n(), .by=c("name", "value")) |> 
  mutate(value = fct_relevel(value, "Not owning", "Never", "Very rarely", "A few times per week", "Once a day", "A few times per day", "A few times per hour"),
         name = str_remove(name, "Wearables_")) |> 
  ggplot(aes(x=value, y=n, fill=name)) +
  geom_bar(stat = "identity") +
  labs(x = "Usage frequency", y = "") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


get_databubble <- function(df, var="Heart") {
  x <- paste0("Wearables_", var)
  y <- paste0("Wearables_", var, "Importance")
  dat <- df[df[[x]] != "Not owning", ]
  dat <- summarize(dat, n = n(), .by = all_of(c(x, y)))
  lvl <- c("Never", "Very rarely", "A few times per week", "Once a day", "A few times per day", "A few times per hour")
  dat[[x]] <- factor(dat[[x]], levels=lvl[lvl %in% unique(dat[[x]])])
  names(dat) <- c("Usage", "Importance", "n")
  dat$Device <- var
  dat
}

p3 <- rbind(
  get_databubble(df, "Heart"),
  get_databubble(df, "Sleep"),
  get_databubble(df, "Steps"),
  get_databubble(df, "Weight"),
  get_databubble(df, "CalorieIntake"),
  get_databubble(df, "CaloriesBurnt")
) |> 
  filter(!is.na(Importance)) |> 
  ggplot(aes(x=Usage, y=Importance)) +
  geom_jitter(aes(size = n, color = Device), width = 0.2, height = 0.2, alpha = 0.5) +
  geom_smooth(aes(x=as.numeric(Usage), color = Device), method = "lm", se = FALSE, formula = 'y ~ x') +
  labs(x = "Usage frequency") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

p1 / p2 / p3
```



:::

## Save

```{r}
df |> 
  select(-contains("AttentionCheck")) |> 
  write.csv("../data/data_participants.csv", row.names = FALSE)
```
