---
title: "FictionArt - Eyetracking"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---


```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(magick)
library(ggside)

source("funs_eyetracking.R")
```

In this neuroaesthetics experiment, gaze data was collected through webgazer.js during each fixation cross and subsequent stimuli.

```{r}
#| code-fold: false

df <- rbind(read.csv("../data/rawdata_eyetracking1.csv"),
               read.csv("../data/rawdata_eyetracking2.csv"))|>
  mutate(Stimulus_right = Stimulus_left + Stimulus_width,
         Stimulus_bottom = Stimulus_top + Stimulus_height,
         GazeWithin = ifelse(
    x >= Stimulus_left & x <= Stimulus_right & y >= Stimulus_top & y <= Stimulus_bottom, TRUE, FALSE
  )) 

df_ppt <- read.csv("../data/data_participants.csv") |>
  select(Participant, starts_with("Eyetracking_")) |>
  pivot_longer(-Participant, names_to="Index", values_to="Value") |>
  filter(!is.na(Value)) |>
  mutate(Participant = fct_reorder(Participant, Value)) |>
  mutate(Index = str_remove(Index, "Eyetracking_Validation"),
         Index = ifelse(Index == "1", "Initial",  "Midtask"))

# Keep only participants that were not rejected as outliers
df <- df[df$Participant %in% df_ppt$Participant,]
```




## Exclusions

::: {.panel-tabset}

### Calibration Scores

Calibration scores relate to the % of gaze in the target areas during the calibration phase. One of themtook place at the beginning, and the second one in the middle.


```{r}
#| fig-width: 12
#| fig-height: 8
#| warning: false

p_val1 <- df_ppt |>
  ggplot(aes(x=Value, y=Participant)) +
  geom_bar(stat="identity", aes(fill=Index), position = position_dodge2(reverse=TRUE)) +
  theme_minimal() +
  labs(title="Calibration Scores", fill="Calibration Phase", color="Calibration Phase", x="Calibration Score", y=NULL) +
  theme(legend.position = "inside", legend.position.inside = c(0.9, 0.1),
        axis.text.y = element_blank()) +
  ggside::geom_xsidedensity(aes(fill=Index, color=Index), alpha=0.3) +
  ggside::theme_ggside_void() +
  scale_fill_manual(values=c("forestgreen", "orange")) +
  scale_color_manual(values=c("forestgreen", "orange"))

p_val2 <- df_ppt |> 
  pivot_wider(names_from="Index", values_from="Value") |>
  ggplot(aes(x=Initial, y=Midtask)) +
  geom_abline(intercept=0, slope=1, linetype="dashed") +
  geom_point2(size=3, alpha=0.5, color="forestgreen") +
  geom_smooth(method="lm", formula = 'y ~ x', color="forestgreen") +
  theme_minimal() +
  labs(title="Initial vs. Midtask Calibration Scores")

p_val1 | p_val2
```


### Fixation Cross Pattern

We assessed the gaze patterns over the fixation cross preceding every stimulus.


```{r}
#| fig-width: 14
#| fig-height: 40
#| warning: false

scores <- df_ppt |> 
  pivot_wider(names_from="Index", values_from="Value") |>  
  mutate(Label = paste0("Score: ", 
                        format_value(Initial, digits=0, zap_small = TRUE),
                        ", ",
                        format_value(Midtask, digits=0, zap_small = TRUE)))



p_fix <- df |>
  filter(Stimulus == "Fixation") |>
  mutate(
    Participant = fct_relevel(Participant, rev(levels(df_ppt$Participant))),
    x = x / ScreenWidth,
    y = 1 - y / ScreenHeight
  ) |>
  ggplot(aes(x=x, y=y)) +
  geom_path(aes(group=interaction(Participant, Stimulus), color=Participant, linewidth=Time),
            alpha=0.7, linewidth=0.2) +
  geom_hline(yintercept = 0.5, linetype="dashed", color="black") +
  geom_vline(xintercept = 0.5, linetype="dashed", color="black") +
  geom_rect(xmin=0, ymin=0, xmax=1, ymax=1, alpha=0, color="black") +
  geom_text(data = scores, color = "darkred",
            aes(x=-0.25, y=-0.25, label=Label), hjust=0, vjust=0) +
  see::scale_color_material_d(guide="none") +
  scale_linewidth_continuous(range=c(1, 0.1), guide="none") +
  scale_x_continuous(labels=scales::percent) +
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(xlim=c(-0.3, 1.3), ylim=c(-0.3, 1.3)) +
  theme_minimal() +
  facet_wrap(~Participant, scales="free", ncol = 10) +
  labs(title="Fixation Cross Pattern", x=NULL, y=NULL)
p_fix
```



### Bad Trials

We computed the proportion of gaze within the target (the stimulus).

```{r}
#| fig-width: 12
#| fig-height: 8
#| warning: false

# By trials
invalid <- df |>
  filter(Stimulus != "Fixation") |>
  summarize(GazeWithin = sum(GazeWithin), # Sum of datapoints on target
            Proportion = sum(GazeWithin) / n(), 
            .by=c("Participant", "Item"))

p_bad1 <- invalid |> 
  ggplot(aes(x=GazeWithin)) +
  stat_density(aes(group = Participant, y = after_stat(density), color = Participant), geom = "line", position = "identity") +
  scale_y_sqrt() +
  theme_minimal() +
  theme(legend.position = "none")  
p_bad1
  
p_bad2 <- invalid |> 
  ggplot(aes(x=Proportion)) +
  geom_histogram(bins=100, aes(y=after_stat(density)), fill="darkgrey") +
  stat_density(aes(group = Participant, y = after_stat(density), color = Participant), 
               geom = "line", position = "identity", alpha = 0.2) +
  labs(x = "% of Gaze on Target", y = "") +
  scale_y_sqrt() +
  scale_x_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(legend.position = "none") 
p_bad2
```




```{r}
#| fig-width: 12
#| fig-height: 8
#| warning: false


# By participants
dfsub_bad <- invalid |>
  summarize(Bad = sum(Proportion < 1/2) / n(), .by=c("Participant"))

p_bad2 <- dfsub_bad |>
  mutate(
    Participant = fct_reorder(Participant, Bad)
    # Participant = fct_relevel(Participant, levels(df_ppt$Participant))
    ) |>
  ggplot(aes(y=Participant, x=Bad)) +
  geom_bar(stat="identity", fill="darkred") +
  scale_x_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.y = element_blank()) +
  labs(x=NULL, y=NULL, title="% of Bad Trials") +
  ggside::geom_xsidedensity(fill="darkred", color="darkred", alpha=0.7) +
  ggside::theme_ggside_void()

p_bad3 <- merge(dfsub_bad, df_ppt, by="Participant") |> 
  ggplot(aes(x=Value, y=Bad)) +
  geom_point2(aes(color=Index), size=3, alpha=0.5) +
  geom_smooth(aes(color=Index, fill=Index), method="lm", formula = 'y ~ x', alpha=0.1) +
  coord_cartesian(ylim=c(0, 1)) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("forestgreen", "orange")) +
  scale_fill_manual(values=c("forestgreen", "orange")) +
  theme_minimal() +
  theme(legend.position = "inside", legend.position.inside = c(0.8, 0.5)) +
  labs(color = "Validation Phase", fill = "Validation Phase", y = "% Bad Trials", title="Validation Scores vs. Bad Trials", x="Validation Score")

p_bad2 | p_bad3
```


```{r}
#| code-fold: false

bad_trials <- invalid[invalid$Proportion < 1/2, c("Participant", "Item")]
n_ori <- nrow(filter(df, Stimulus != "Fixation"))

df <- df |>
  filter(Stimulus != "Fixation") |>
  filter(!paste(Participant, Item) %in% paste(bad_trials$Participant, bad_trials$Item)) |>
  filter(is.finite(x), is.finite(y)) |> 
  select(-GazeWithin)
```

We removed `r insight::format_percent((n_ori - nrow(df)) / n_ori)` "bad" trials (trials with less than 50% of gaze data points on stimulus).



### Bad Participants

#### Sampling Rate

```{r}
sr <- df |> 
  mutate(Delay = c(NA, diff(t)), .by = c("Participant", "Item")) |> 
  filter(t >= 0, Delay > 0, Delay < 0.20) |> 
  mutate(sampling_rate = 1 / Delay) 

sr_ppt <- summarize(sr, 
                    sampling_rate_mad = mad(sampling_rate, na.rm = TRUE),
                    sampling_rate = median(sampling_rate, na.rm = TRUE), 
                    .by = "Participant")

sr_ppt |> 
  ggplot(aes(x = sampling_rate, y = Participant)) +
  geom_pointrange(aes(xmin = sampling_rate - sampling_rate_mad, xmax = sampling_rate + sampling_rate_mad), color="darkred") +
  geom_vline(xintercept = c(15, 35), linetype="dashed", color="black") +
  theme_minimal() +
  theme(axis.text.y = element_blank()) +
  ggside::geom_xsidedensity(aes(y = after_stat(density)), fill="darkred", color="darkred", alpha=0.7) +
  ggside::theme_ggside_void() 
```


```{r}
exclude <- list(slow_framerate = filter(sr_ppt, sampling_rate < 15)$Participant)
df <- filter(df, !Participant %in% exclude$slow_framerate)
```

We excluded `r length(exclude$slow_framerate)` participants with a slow sampling rate (< 15 Hz).

#### Velocity

```{r}
vel <- df |> 
  mutate(velocity = sqrt((x - lag(x))^2 + (y - lag(y))^2) / (t - lag(t)), 
         .by = c("Participant", "Item")) |> 
  summarize(
    MeanVelocity = mean(velocity, na.rm = TRUE),
    MedianVelocity = median(velocity, na.rm = TRUE),
    MaxVelocity = max(velocity, na.rm = TRUE),
    .by = "Participant"
  )

ggplot(vel, aes(x=MedianVelocity)) +
  geom_histogram(bins=100) +
  geom_vline(xintercept = c(150, 3000), linetype="dashed", color="darkred") 
```

```{r}
exclude$Velocity <- filter(vel, MedianVelocity < 150 | MedianVelocity > 3000)$Participant
df <- filter(df, !Participant %in% exclude$Velocity)
```

We excluded `r length(exclude$Velocity)` participants with a very low (< 150 px/s) or very high (> 3000 px/s) median velocity.


#### Movement

```{r}
mov <- df |> 
  summarize(distance = sum(sqrt((x - lag(x))^2 + (y - lag(y))^2), na.rm = TRUE), 
            n_samples = n(), 
            .by = c("Participant", "Item")) 
  

ggplot(mov, aes(x=distance)) +
  geom_histogram(bins=100) +
  geom_vline(xintercept = c(0, 17500), linetype="dashed", color="darkred") 
```

```{r}
exclude$Distance <- filter(mov, distance < 250 | distance > 17500)$Participant
df <- filter(df, !Participant %in% exclude$Distance)
```

We excluded `r length(exclude$Distance)` trials with a very low (< 250 px) or very high (> 17500 px) total distance traveled by gaze.

:::



## Preprocessing

### Resampling

```{r}
progbar <- progress::progress_bar$new(total = length(unique(df$Participant)))
dfeye <- list()
for(ppt in unique(df$Participant)) {
  progbar$tick()
  for(item in unique(df[df$Participant == ppt, "Item"])) {
    dat <- filter(df, Participant == ppt, Item == item) 
    
    dat_interp <- interpolate_xy(dat, screenwidth = unique(dat$ScreenWidth))
    dat_interp$Participant <- ppt
    dat_interp$Item <- item
    dat_interp$ScreenWidth <- unique(dat$ScreenWidth)
    dat_interp$ScreenHeight <- unique(dat$ScreenHeight)
    dat_interp$Stimulus_left <- unique(dat$Stimulus_left)
    dat_interp$Stimulus_top <- unique(dat$Stimulus_top)
    dat_interp$Stimulus_height <- unique(dat$Stimulus_height)
    dat_interp$Stimulus_width <- unique(dat$Stimulus_width)
    dat_interp$Stimulus_right <- unique(dat$Stimulus_right)
    dat_interp$Stimulus_bottom <- unique(dat$Stimulus_bottom)
    dfeye[[paste0(ppt, item)]] <- dat_interp
  }
}
dfeye <- dplyr::bind_rows(dfeye) |> 
  filter(t >= 0, !is.na(velocity))

  
dfeye |> 
  # filter(velocity < 1) |>
  ggplot(aes(x=velocity)) +
  geom_histogram(bins=120, aes(y=after_stat(density))) +
  stat_density(aes(group=Participant, y=after_stat(density), color = Participant), geom="line", position="identity",
               alpha = 0.2) +
  # coord_cartesian(xlim=c(0, 5)) +
  scale_y_sqrt() +
  scale_x_sqrt() +
  theme_minimal() +
  theme(legend.position = "none") 
```


### Fixation Detection

```{r}
get_fixations <- function(
  dfeye,
  dispersion_threshold = 0.07,
  min_duration = 0.15,
  max_duration = 2.0,
  p_within_threshold = 0.5,
  verbose = TRUE
) {
  dffixations <- dfeye |>
    mutate(
      event = detect_fixations_idt(
        t, x, y,
        screenwidth    = ScreenWidth,
        dispersion_threshold = dispersion_threshold,
        min_duration   = min_duration
      ),
      .by = c("Participant", "Item")
    ) |>
    filter(event != "Saccade") |>
    mutate(
      gaze_within = x >= Stimulus_left & x <= Stimulus_right &
                    y >= Stimulus_top  & y <= Stimulus_bottom
    ) |>
    summarise(
      # Compute concentration FIRST using the original x and y vectors.
      # This calculates the mean Euclidean distance from the centroid (average radius in pixels)
      concentration = mean(sqrt((x - mean(x, na.rm = TRUE))^2 + (y - mean(y, na.rm = TRUE))^2), na.rm = TRUE),
      concentration = concentration / first(ScreenWidth),
      x = mean(x, na.rm = TRUE),
      y = mean(y, na.rm = TRUE),
      duration = max(t, na.rm = TRUE) - min(t, na.rm = TRUE),,
      p_within = mean(gaze_within, na.rm = TRUE),
      across(
        c(Stimulus_left, Stimulus_right, Stimulus_top, Stimulus_bottom,
          ScreenWidth, ScreenHeight),
        first
      ),
      .by = c("Participant", "Item", "event")
    )

  if (verbose) {
    message(sprintf(
      "Fixations removed (duration > %.1fs):      %s  [n = %d]",
      max_duration,
      format_percent(mean(dffixations$duration > max_duration, na.rm = TRUE)),
      sum(dffixations$duration > max_duration, na.rm = TRUE)
    ))
    message(sprintf(
      "Fixations removed (p_within < %.2f):       %s  [n = %d]",
      p_within_threshold,
      format_percent(mean(dffixations$p_within < p_within_threshold, na.rm = TRUE)),
      sum(dffixations$p_within < p_within_threshold, na.rm = TRUE)
    ))
  }

  filter(dffixations, duration <= max_duration, p_within >= p_within_threshold)
}
```

#### Parameter Selection

Using a Grid Search.


```{r}
dftask       <- read.csv("../data/data_task.csv")
feat_list    <- c("Fixations_N", "Fixations_DurationMean", "Fixations_DurationSum")
outcome_list <- c("Beauty", "Valence", "Meaning", "Worth", "Reality", "Authenticity")

# Pre-compute once — used in every coverage calculation
total_trial_time <- dfeye |>
  summarise(trial_duration = max(t) - min(t), .by = c("Participant", "Item"))

cv <- function(x) sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)

quality_list <- list()
params_list  <- list()
dist_plots   <- list()

for (disp in c(0.125, 0.175, 0.5)) {
  for (md in c(0.05, 0.075, 0.10, 0.15, 0.20, 0.25, 0.30)) {
    cat(".")
    key         <- paste0("d", disp, "_md", md)
    dffixations <- get_fixations(dfeye, dispersion_threshold = disp,
                                 min_duration = md, verbose = FALSE)

    if (nrow(dffixations) < 10) next
    durations <- dffixations$duration[dffixations$duration > 0]

    # ── Signal quality ──────────────────────────────────────────────────────
    log_dur  <- log(durations) + rnorm(length(durations), sd = 1e-6) # break ties for AD
    ad_stat  <- tryCatch(nortest::ad.test(log_dur)$statistic, error = function(e) NA_real_)
    dens     <- density(durations, from = 0, bw = "SJ")
    coverage <- dffixations |>
      summarise(ft = sum(duration), .by = c("Participant", "Item")) |>
      left_join(total_trial_time, by = c("Participant", "Item")) |>
      summarise(m = mean(ft / trial_duration, na.rm = TRUE)) |>
      pull(m)
    per_ppt  <- dffixations |>
      summarise(n_fix = n(), mean_dur = mean(duration), .by = "Participant")

    quality_list[[key]] <- data.frame(
      dispersion       = disp,
      min_duration     = md,
      n_fixations      = nrow(dffixations),
      coverage         = coverage,
      ad_lognormal     = as.numeric(ad_stat),
      prop_canonical   = mean(durations >= 0.10 & durations <= 0.80, na.rm = TRUE),
      mode_duration    = dens$x[which.max(dens$y)],
      stability_cv_n   = cv(per_ppt$n_fix),
      stability_cv_dur = cv(per_ppt$mean_dur)
    )

    # ── Duration distribution plot ───────────────────────────────────────────
    dist_plots[[key]] <- dffixations |>
      filter(duration < 1) |>
      ggplot(aes(x = duration)) +
      stat_density(aes(group = Participant, y = after_stat(density), color = Participant),
                   geom = "line", alpha = 0.4) +
      stat_density(aes(y = after_stat(density)), geom = "line", linewidth = 1) +
      guides(color = "none") +
      scale_x_sqrt(expand = c(0, 0)) + scale_y_sqrt() +
      labs(title = paste0("d=", disp, " md=", md), x = "Duration (s)", y = NULL) +
      theme_minimal(base_size = 8)

    # ── Outcome sensitivity ──────────────────────────────────────────────────
    # scale() makes z-statistics comparable across parameter settings:
    # Fixations_N at disp=0.01 and disp=0.20 are on very different raw scales.
    features <- dffixations |>
      summarise(
        Fixations_N            = n(),
        Fixations_DurationSum  = sum(duration, na.rm = TRUE),
        Fixations_DurationMean = mean(duration, na.rm = TRUE),
        .by = c("Participant", "Item")
      ) |>
      left_join(dftask, by = c("Participant", "Item"))

    cell_rows <- list()
    for (feat in feat_list) {
      for (outcome in outcome_list) {
        m <- tryCatch(
          glmmTMB::glmmTMB(
            as.formula(paste0(outcome, " ~ scale(", feat, ") + (1|Participant) + (1|Item)")),
            data = features
          ),
          error = function(e) NULL
        )
        if (is.null(m)) next
        cell_rows[[length(cell_rows) + 1]] <-
          parameters::parameters(m, effects = "fixed")[2, ] |>
          dplyr::select(z, p) |>
          dplyr::mutate(Feature = feat, Outcome = outcome,
                        Dispersion = disp, MinDuration = md)
      }
    }
    params_list[[key]] <- dplyr::bind_rows(cell_rows)
  }
}

quality_grid   <- dplyr::bind_rows(quality_list)
outcome_params <- dplyr::bind_rows(params_list)
```


##### Fixation Characteristics

```{r}
# --- Post-hoc: parameter robustness ----------------------------------------
# For each cell, compute the mean absolute deviation of n_fixations
# from its 4 immediate neighbours (up/down/left/right in the grid).
# Low sensitivity to small parameter changes = more trustworthy setting.
qg_snap <- quality_grid |>
  select(dispersion, min_duration, n_fixations)

quality_grid <- quality_grid |>
  mutate(
    robustness_n = map2_dbl(dispersion, min_duration, function(d, md) {

      d_vals  <- sort(unique(qg_snap$dispersion))
      md_vals <- sort(unique(qg_snap$min_duration))

      # Find position in grid, then index ± 1.
      # Works for any spacing — uniform or not.
      d_idx  <- which(d_vals  == d)
      md_idx <- which(md_vals == md)

      d_neighbors  <- d_vals [na.omit(c(d_idx  - 1L, d_idx  + 1L))]
      md_neighbors <- md_vals[na.omit(c(md_idx - 1L, md_idx + 1L))]

      neighbor_n <- qg_snap |>
        filter(
          (dispersion %in% d_neighbors & min_duration == md) |
          (min_duration %in% md_neighbors & dispersion == d)
        ) |>
        pull(n_fixations)

      own_n <- qg_snap |>
        filter(dispersion == d, min_duration == md) |>
        pull(n_fixations)

      if (length(neighbor_n) == 0 || length(own_n) == 0) return(NA_real_)

      mean(abs(neighbor_n - own_n), na.rm = TRUE)
    })
  )


# --- Composite score -------------------------------------------------------
# Z-score and combine metrics (flip sign where lower = better).
quality_grid <- quality_grid |>
  mutate(
    z_ad       = -scale(ad_lognormal)[,1],      # lower AD test is better
    z_coverage = -abs(scale(coverage)[,1]),      # penalise deviation from centre
    z_canon    =  scale(prop_canonical)[,1],
    z_mode     = -abs(scale(mode_duration)[,1]), # penalise extreme modes
    z_stab     = -scale(stability_cv_n)[,1],     # lower CV is better
    z_robust   = -scale(robustness_n)[,1],

    composite  = z_ad + z_coverage + z_canon + z_mode + z_stab + z_robust
  )


# --- Visualise -------------------------------------------------------------

plot_metric <- function(data, var, title, reverse = FALSE) {
  palette <- c("#F44336", "#FFC107", "#CDDC39", "#4CAF50")
  if (reverse) palette <- rev(palette)
  if(var %in% c("coverage", "mode_duration")) {
    palette <- c("#F44336", "#FFC107", "#4CAF50", "#FFC107", "#F44336")
  }
  
  ggplot(data, aes(x = factor(dispersion), y = factor(min_duration),
                   fill = .data[[var]])) +
    geom_tile(color = "white", linewidth = 0.7) +
    geom_text(aes(label = round(.data[[var]], 2)), size = 3, color = "white", fontface = "bold") +
    scale_fill_gradientn(colors = palette) +
    labs(title = title, x = "Dispersion Threshold", y = "Min Duration (s)") +
    theme_minimal() +
    theme(panel.grid = element_blank())
}

p1 <- plot_metric(quality_grid, "ad_lognormal",   "AD test: Log-normal fit (↓)",   reverse = TRUE)
p2 <- plot_metric(quality_grid, "coverage",        "Coverage (0.35–0.75 ideal)")
p3 <- plot_metric(quality_grid, "prop_canonical",  "Prop. canonical range (↑)")
p4 <- plot_metric(quality_grid, "mode_duration",   "Mode duration (s)")
p5 <- plot_metric(quality_grid, "stability_cv_n",  "Stability CV-N (↓)",        reverse = TRUE)
p6 <- plot_metric(quality_grid, "composite",       "Composite score (↑)")

(p1 | p2 | p3) / (p4 | p5 | p6)
```




##### Sensitivity Check against Outcomes

```{r}
outcome_params |> 
  filter(Outcome %in% c("Beauty", "Meaning", "Worth", "Authenticity")) |> 
  ggplot(aes(x=Feature, y=Outcome, fill=p)) +
  geom_tile() +
  scale_fill_gradientn(colors=c("#2196F3", "#00BCD4", "#4CAF50", "#FFEB3B", "white", "white"), 
                       values = c(0, 0.05, 0.1, 0.5, 1),
                       breaks = c(0.05, 0.25, 0.5, 0.75)) +
  facet_grid(MinDuration~Dispersion,labeller = labeller(.rows = label_both, .cols = label_both)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) 



outcome_params |> 
  # filter(Feature %in% c("Fixations_DurationSum")) |> 
  summarize(N_Sig1 = sum(p < 0.1), N_Sig05 = sum(p < 0.05), Mean_p = mean(p), .by = c("Dispersion", "MinDuration")) |>
  arrange(desc(N_Sig05), Mean_p)
```





### Features


#### Gaze


```{r}
early_late_drift <- function(x, y, sw) {
  n <- length(x)
  if (n < 4) return(NA_real_)
  h  <- floor(n / 2)
  ex <- mean(x[seq_len(h)]  / sw, na.rm = TRUE)
  ey <- mean(y[seq_len(h)]  / sw, na.rm = TRUE)
  lx <- mean(x[(h+1):n]    / sw, na.rm = TRUE)
  ly <- mean(y[(h+1):n]    / sw, na.rm = TRUE)
  sqrt((lx - ex)^2 + (ly - ey)^2)
}

# Soft fixation-like velocity threshold: 5% of screen width per second.
# This is a domain constant, not a free parameter — a genuine saccade
# at typical speeds covers far more than this per second.
LOW_VEL_THRESH <- 0.05

dffeatures1 <- dfeye |>
  summarise(
        
    RawGaze_TimeOnTarget = sum(
      x >= first(Stimulus_left) & x <= first(Stimulus_right) &
      y >= first(Stimulus_top)  & y <= first(Stimulus_bottom),
      na.rm = TRUE
    ) / 100,  # 100 Hz → seconds
    
    RawGaze_PropOnTarget = mean(
      x >= first(Stimulus_left) & x <= first(Stimulus_right) &
      y >= first(Stimulus_top)  & y <= first(Stimulus_bottom),
      na.rm = TRUE
    ),

    # Total distance traveled by the raw gaze trace.
    # Captures global scanning activity without any fixation segmentation.
    # Complements MeanJump (which only looks at centroid-to-centroid hops).
    RawGaze_ScanpathLength = sum(
      sqrt(diff(x / first(ScreenWidth))^2 + diff(y / first(ScreenWidth))^2),
      na.rm = TRUE
    ),

    # Proportion of 100 Hz samples with very low velocity.
    # A continuous, parameter-free proxy for total fixation-like dwell time.
    # Should correlate with fixation coverage but without depending on
    # any dispersion or duration cutoff.
    RawGaze_LowVelProp = mean(velocity < LOW_VEL_THRESH, na.rm = TRUE),

    # Velocity SD: clear fixation/saccade alternation produces high SD
    # (bimodal velocity); pure noise or frozen gaze produces low SD.
    # Useful as a data quality indicator as well as a behavioral feature.
    RawGaze_VelocitySD = sd(velocity, na.rm = TRUE),

    # Mean distance from image center (normalized).
    # Captures center bias — a well-known tendency in free viewing —
    # independently of whether fixations were detected.
    RawGaze_CenterBias = mean(
      sqrt((x / first(ScreenWidth)  - 0.5)^2 +
           (y / first(ScreenHeight) - 0.5)^2),
      na.rm = TRUE
    ),

    # Signed horizontal offset from center. Distinct from CenterBias:
    # a participant exploring only the right half has high RawGaze_HorizBias
    # but moderate CenterBias.
    RawGaze_HorizBias = mean(x / first(ScreenWidth) - 0.5, na.rm = TRUE),

    # Shift between first-half and second-half gaze centroids.
    # Captures whether attention migrates across the trial (high drift)
    # or stays anchored in one region (low drift).
    # Entirely time-based — no detection needed.
    RawGaze_EarlyLateDrift = early_late_drift(x, y, first(ScreenWidth)),
    
    RawGaze_KDE_Gini = get_kde_gini(
      x, y,
      stim_left   = first(Stimulus_left),
      stim_right  = first(Stimulus_right),
      stim_top    = first(Stimulus_top),
      stim_bottom = first(Stimulus_bottom)
    ),
    
    RawGaze_VelBimodality = get_velocity_bimodality(velocity),
    
    RawGaze_BCEA = get_bcea(x, y, first(ScreenWidth), first(ScreenHeight), p = 0.68),
    RawGaze_ConvexHullArea = get_convex_hull_area(x, y, first(ScreenWidth), first(ScreenHeight)),

    RawGaze_PrecisionPersistenceCoupling = get_precision_persistence_coupling(
      x, y, t, velocity, first(ScreenWidth), vel_thresh = LOW_VEL_THRESH
    ),
    RawGaze_SlowSpread = get_slow_spread(
      x, y, velocity, first(ScreenWidth), first(ScreenHeight), vel_thresh = LOW_VEL_THRESH
    ),

    .by = c("Participant", "Item")
  )

dffeatures3 <- dfeye |>
  group_by(Participant, Item) |>
  group_modify(~ {
    prof <- get_dispersion_profile(.x$x, .x$y, first(.x$ScreenWidth))
    runs <- get_runlength_stats(.x$velocity, .x$t, vel_thresh = LOW_VEL_THRESH)
    as_tibble(as.list(c(prof, runs)))
  }) |>
  ungroup()
```

#### Fixations


```{r}
dffixations <- get_fixations(dfeye, dispersion_threshold = 0.25, min_duration = 0.1)

dffeatures2 <- dffixations |> 
    summarise(
    # All qualifying fixations
      Fixations_N           = n(),
      Fixations_DurationTotal = sum(duration, na.rm = TRUE),
      Fixations_DurationMean = mean(duration, na.rm = TRUE),
      Fixations_DurationMedian = median(duration, na.rm = TRUE),
  
      # Long AND spatially tight fixations only
      # Fixations_Focal_N           = sum(duration >= 0.20 & within_dispersion < 0.02, na.rm = TRUE),
      # Fixations_Focal_DurationSum = sum(duration[duration >= 0.20 & within_dispersion < 0.02], na.rm = TRUE),
      Fixations_Long_N           = sum(duration >= 0.20, na.rm = TRUE),
      Fixations_Long_DurationSum = sum(duration[duration >= 0.20], na.rm = TRUE),
      Fixations_Long_Prop = mean(duration >= 0.20, na.rm = TRUE),
      SpatialEntropy = get_spatial_entropy(
        x, y,
        stim_left = first(Stimulus_left),
        stim_right = first(Stimulus_right),
        stim_top = first(Stimulus_top),
        stim_bottom = first(Stimulus_bottom)
      ),
      MeanJump = get_mean_jump(x, y, screenwidth = first(ScreenWidth)),
      AngularVariability = get_angular_variability(x, y, screenwidth = first(ScreenWidth)),
      
      ConvexHullArea = get_convex_hull_area(x, y, first(ScreenWidth), first(ScreenHeight)),
      BCEA = get_bcea(x, y, first(ScreenWidth), first(ScreenHeight), p = 0.68),

      .by = c("Participant", "Item")
    ) 
```


```{r}
dffeatures <- left_join(dffeatures1, dffeatures2, dffeatures3, by = c("Participant", "Item"))
```


```{r}
dffeatures |> 
  pivot_longer(-c(Participant, Item)) |>
  ggplot(aes(x=value)) +
  geom_histogram(bins=100, aes(y=after_stat(density)), fill="darkgrey") +
  facet_wrap(~name, scales="free") 


for(f in names(select(dffeatures, -Participant, -Item, -Fixations_Long_N, -Fixations_N,
                      -SpatialEntropy))) {
  lims <- bayestestR::hdi(dffeatures[[f]], ci = 0.95)
  dffeatures[[f]] <- ifelse(dffeatures[[f]] < lims$CI_low | dffeatures[[f]] > lims$CI_high, NA, dffeatures[[f]])
}
```

#### Correlation


```{r}
dffeatures |> 
  select(-Participant, -Item) |>
  correlation::correlation() |>
  cor_sort() |> 
  summary() |> 
  plot()

n_factors(select(dffeatures, -Participant, -Item)) |> 
  plot()
factor_analysis(select(dffeatures, -Participant, -Item), n=4) |> 
  plot()
```



## Validation

```{r}
dftask <- read.csv("../data/data_task.csv")
dftask <- dplyr::left_join(dffeatures, dftask, by = c("Participant", "Item"))

rez <- data.frame()
for(feature in names(select(dffeatures, -Participant, -Item))) {
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Beauty ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Beauty") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Meaning ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Meaning") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Valence ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Valence") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Worth ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask, family = "poisson") |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Worth") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Reality ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Reality") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Authenticity ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Authenticity") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("SelfRelevance ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dftask) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "SelfRelevance") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0(feature, " ~ Condition + (1|Participant) + (1|Item)")), 
                         data=dftask) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Eyetracking") |>
    rbind(rez)
}

rez <- filter(rez, Parameter != "(Intercept)")
arrange(rez, Outcome, p) 

filter(rez2020, p < .05)
filter(rez2510, p < .05)
```

## Figures


### Exploration

```{r}

# # 1. Load your background image
# stim_img <- image_read("../path/to/your/stimulus.jpg")
# 
# # 2. Filter data for ONE participant and ONE item
# df_single <- dffixations |> 
#   filter(Participant == "Subj_01", Item == "Art_01")
# 
# # 3. Plot
# ggplot(df_single, aes(x = x, y = y)) +
#   # Draw the image in the background using the stimulus coordinates
#   annotation_raster(stim_img, 
#                     xmin = first(df_single$Stimulus_left), 
#                     xmax = first(df_single$Stimulus_right),
#                     ymin = first(df_single$Stimulus_top), 
#                     ymax = first(df_single$Stimulus_bottom)) +
#   # Draw Saccades (lines connecting fixations)
#   geom_path(color = "white", alpha = 0.6, linewidth = 0.8) +
#   # Draw Fixations (points sized by duration)
#   geom_point(aes(size = duration), color = "orange", alpha = 0.8) +
#   # Reverse Y axis because webcam coordinates usually start (0,0) at top-left
#   scale_y_reverse() + 
#   coord_fixed(xlim = c(0, first(df_single$ScreenWidth)), 
#               ylim = c(first(df_single$ScreenHeight), 0)) +
#   theme_void() +
#   labs(title = "Scanpath: Single Participant")
```

### Heatmap

```{r}
# 1. Prepare the data for the heatmap
df_agg <- dffixations |> 
  filter(Item == "10226.jpg")

# Multiply duration by 100 (or 1000) to convert to integers, then expand rows
df_agg_weighted <- df_agg |>
  mutate(weight_int = round(duration * 100)) |>
  uncount(weight_int)

stim_img <- image_read("../experiment/stimuli/stimuli/10226.jpg")

# 2. Plotting
ggplot(df_agg_weighted, aes(x = x, y = y)) +
  # Background image
  annotation_raster(stim_img, 
                    xmin = first(df_agg$Stimulus_left), 
                    xmax = first(df_agg$Stimulus_right),
                    ymin = first(df_agg$Stimulus_top), 
                    ymax = first(df_agg$Stimulus_bottom)) +
  
  # Heatmap layer (uses the uncounted/weighted dataframe)
  stat_density_2d(aes(fill = after_stat(level)), 
                  geom = "polygon", alpha = 0.2, bins = 15) +
  scale_fill_viridis_c(option = "inferno", guide = "none") +
  
  # Cross points layer (uses the ORIGINAL df_agg to avoid plotting duplicate points)
  # shape = 4 is an "x", shape = 3 is a "+"
  geom_point(data = df_agg, aes(x = x, y = y), 
             shape = 4, color = "green", size = 1, stroke = 1, alpha = 0.1) +
  
  scale_y_reverse() + 
  coord_fixed(xlim = c(0, first(df_agg$ScreenWidth)), 
              ylim = c(first(df_agg$ScreenHeight), 0)) +
  theme_void() +
  labs(title = "Fixation Heatmap: All Participants")
```

