---
title: "FictionArt - Eyetracking"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---


```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(magick)
library(ggside)

source("funs_eyetracking.R")
```





```{r}
#| code-fold: false

dfori <- read.csv("../data/rawdata_eyetracking.csv") |>
  mutate(Stimulus_right = Stimulus_left + Stimulus_width,
         Stimulus_bottom = Stimulus_top + Stimulus_height,
         GazeWithin = ifelse(
    x >= Stimulus_left & x <= Stimulus_right & y >= Stimulus_top & y <= Stimulus_bottom, TRUE, FALSE
  ))
```



## Exclusions

::: {.panel-tabset}

### Calibration Scores


```{r}
#| fig-width: 12
#| fig-height: 8

dfval <- read.csv("../data/rawdata_participants.csv") |>
  select(Participant, starts_with("Eyetracking_")) |>
  pivot_longer(-Participant, names_to="Index", values_to="Value") |>
  filter(!is.na(Value)) |>
  mutate(Participant = fct_reorder(Participant, Value)) |>
  mutate(Index = str_remove(Index, "Eyetracking_Validation"),
         Index = ifelse(Index == "1", "Initial",  "Midgame"))

p_val1 <- dfval |>
  ggplot(aes(x=Value, y=Participant)) +
  geom_bar(stat="identity", aes(fill=Index), position = position_dodge2(reverse=TRUE)) +
  theme_minimal() +
  labs(title="Calibration Scores", fill="Calibration Phase", color="Calibration Phase", x="Calibration Score", y=NULL) +
  theme(legend.position = "inside", legend.position.inside = c(0.9, 0.1),
        axis.text.y = element_blank()) +
  ggside::geom_xsidedensity(aes(fill=Index, color=Index), alpha=0.3) +
  ggside::theme_ggside_void() +
  scale_fill_manual(values=c("forestgreen", "orange")) +
  scale_color_manual(values=c("forestgreen", "orange"))

p_val2 <- dfval |> 
  pivot_wider(names_from="Index", values_from="Value") |>
  ggplot(aes(x=Initial, y=Midgame)) +
  geom_abline(intercept=0, slope=1, linetype="dashed") +
  geom_point2(size=3, alpha=0.5, color="forestgreen") +
  geom_smooth(method="lm", formula = 'y ~ x', color="forestgreen") +
  theme_minimal() +
  labs(title="Initial vs. Midgame Calibration Scores")

p_val1 | p_val2
```


### Fixation Cross Pattern


```{r}
#| fig-width: 12
#| fig-height: 12

scores <- dfval |> 
  pivot_wider(names_from="Index", values_from="Value") |>  
  mutate(Label = paste0("Score: ", 
                        format_value(Initial, digits=0, zap_small = TRUE),
                        ", ",
                        format_value(Midgame, digits=0, zap_small = TRUE)))


p_fix <- dfori |>
  filter(Stimulus == "Fixation") |>
  mutate(
    Participant = fct_relevel(Participant, rev(levels(dfval$Participant))),
    x = x / ScreenWidth,
    y = 1 - y / ScreenHeight
  ) |>
  ggplot(aes(x=x, y=y)) +
  geom_path(aes(group=interaction(Participant, Stimulus), color=Participant, linewidth=Time),
            alpha=0.7, linewidth=0.2) +
  geom_hline(yintercept = 0.5, linetype="dashed", color="black") +
  geom_vline(xintercept = 0.5, linetype="dashed", color="black") +
  geom_rect(xmin=0, ymin=0, xmax=1, ymax=1, alpha=0, color="black") +
  geom_text(data = scores, color = "darkred",
            aes(x=-0.25, y=-0.25, label=Label), hjust=0, vjust=0) +
  see::scale_color_material_d(guide="none") +
  scale_linewidth_continuous(range=c(1, 0.1), guide="none") +
  scale_x_continuous(labels=scales::percent) +
  scale_y_continuous(labels=scales::percent) +
  coord_cartesian(xlim=c(-0.3, 1.3), ylim=c(-0.3, 1.3)) +
  theme_minimal() +
  facet_wrap(~Participant, scales="free") +
  labs(title="Fixation Cross Pattern", x=NULL, y=NULL)
p_fix
```

### Bad Trials


```{r}
#| fig-width: 12
#| fig-height: 8

# By trials
invalid <- dfori |>
  filter(Stimulus != "Fixation") |>
  summarize(GazeWithin = sum(GazeWithin), prop = sum(GazeWithin) / n(), .by=c("Participant", "Item"))

p_bad1 <- invalid |> 
  ggplot(aes(x=GazeWithin)) +
  stat_density(aes(group = Participant, y = after_stat(density), color = Participant), geom = "line", position = "identity") +
  scale_y_sqrt() +
  theme(legend.position = "none") | 
  invalid |> 
  ggplot(aes(x=prop)) +
  stat_density(aes(group = Participant, y = after_stat(density), color = Participant), geom = "line", position = "identity") +
  scale_y_sqrt() +
  theme(legend.position = "none")
p_bad1

# By participants
dfsub_bad <- invalid |>
  summarize(Bad = sum(prop < 1/3) / n(), .by=c("Participant"))

p_bad2 <- dfsub_bad |>
  mutate(
    # Participant = fct_reorder(Participant, Bad)
    Participant = fct_relevel(Participant, levels(dfval$Participant))
    ) |>
  ggplot(aes(y=Participant, x=Bad)) +
  geom_bar(stat="identity", fill="darkred") +
  scale_x_continuous(labels=scales::percent) +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.y = element_blank()) +
  labs(x=NULL, y=NULL, title="% of Bad Trials") +
  ggside::geom_xsidedensity(fill="darkred", color="darkred", alpha=0.7) +
  ggside::theme_ggside_void()

p_bad3 <- merge(dfsub_bad, dfval, by="Participant") |> 
  ggplot(aes(x=Value, y=Bad)) +
  geom_point2(aes(color=Index), size=3, alpha=0.5) +
  geom_smooth(aes(color=Index, fill=Index), method="lm", formula = 'y ~ x', alpha=0.1) +
  coord_cartesian(ylim=c(0, 1)) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("forestgreen", "orange")) +
  scale_fill_manual(values=c("forestgreen", "orange")) +
  theme_minimal() +
  theme(legend.position = "inside", legend.position.inside = c(0.8, 0.5)) +
  labs(color = "Validation Phase", fill = "Validation Phase", y = "% Bad Trials", title="Validation Scores vs. Bad Trials", x="Validation Score")

p_bad2 | p_bad3
```

:::


```{r fig_eyetracking1}
#| fig-width: 15
#| fig-height: 12

((p_val1 | p_bad2 + theme(axis.text.y = element_blank())) /
  (p_val2 | p_bad3)) | p_fix
```

### Remove Bad Participants

#### Sampling Rate

```{r}
sr <- dfori |> 
  mutate(Delay = c(NA, diff(t)), .by = c("Participant", "Item")) |> 
  filter(t >= 0, Delay > 0, Delay < 0.20) |> 
  mutate(sampling_rate = 1 / Delay) 

srsub <- summarize(sr, sampling_rate = mean(sampling_rate, na.rm = TRUE), .by = "Participant")


sr |>
  ggplot(aes(x = sampling_rate)) +
  geom_vline(xintercept = 29, linetype="dashed", color="black") +
  stat_density(aes(group=Participant, color=Participant), geom = "line", position = "identity") +
  scale_y_sqrt() +
  theme(legend.position = "none") |
    srsub |>
  ggplot(aes(x=sampling_rate)) +
  geom_histogram(bins=30) 
```


```{r}
# TODO: Filter participants that are not in the cleaned-up dftask
bad_ppt <- filter(srsub, sampling_rate < 10)$Participant
dfori <- filter(dfori, !Participant %in% c(bad_ppt))
```

#### Movement

```{r}
vel <- dfori |> 
  mutate(velocity = sqrt((x - lag(x))^2 + (y - lag(y))^2) / (t - lag(t)), 
         .by = c("Participant", "Item")) |> 
  summarize(
    MeanVelocity = mean(velocity, na.rm = TRUE),
    MaxVelocity = max(velocity, na.rm = TRUE),
    .by = "Participant"
  )

ggplot(vel, aes(x=MeanVelocity)) +
  geom_histogram(bins=100)

```

```{r}
# TODO: Filter participants that are not in the cleaned-up dftask
bad_ppt <- filter(vel, MeanVelocity < 0.1 | MeanVelocity > 6000)$Participant
dfori <- filter(dfori, !Participant %in% bad_ppt)
```

### Remove Bad Trials

```{r}
#| code-fold: false

bad_trials <- invalid[invalid$p < 1/3, c("Participant", "Item")]

df <- dfori |>
  filter(Stimulus != "Fixation") |>
  filter(!paste(Participant, Item) %in% paste(bad_trials$Participant, bad_trials$Item)) |>
  filter(is.finite(x), is.finite(y)) |> 
  select(-GazeWithin)
```

We removed `r insight::format_percent((nrow(filter(dfori, Stimulus != "Fixation")) - nrow(df)) / nrow(filter(dfori, Stimulus != "Fixation")))` "bad" trials.



## Preprocessing

### Resampling

```{r}
progbar <- progress::progress_bar$new(total = length(unique(df$Participant)))
dfeye <- list()
for(ppt in unique(df$Participant)) {
  progbar$tick()
  for(item in unique(df[df$Participant == ppt, "Item"])) {
    dat <- filter(df, Participant == ppt, Item == item) 
    
    dat_interp <- interpolate_xy(dat, screenwidth = unique(dat$ScreenWidth))
    dat_interp$Participant <- ppt
    dat_interp$Item <- item
    dat_interp$ScreenWidth <- unique(dat$ScreenWidth)
    dat_interp$ScreenHeight <- unique(dat$ScreenHeight)
    dat_interp$Stimulus_left <- unique(dat$Stimulus_left)
    dat_interp$Stimulus_top <- unique(dat$Stimulus_top)
    dat_interp$Stimulus_height <- unique(dat$Stimulus_height)
    dat_interp$Stimulus_width <- unique(dat$Stimulus_width)
    dat_interp$Stimulus_right <- unique(dat$Stimulus_right)
    dat_interp$Stimulus_bottom <- unique(dat$Stimulus_bottom)
    dfeye[[paste0(ppt, item)]] <- dat_interp
  }
}
dfeye <- dplyr::bind_rows(dfeye) |> 
  filter(t >= 0, !is.na(velocity))

  
dfeye |> 
  filter(velocity < 5) |> 
  ggplot(aes(x=velocity)) +
  geom_histogram(bins=100, aes(y=after_stat(density))) +
  stat_density(aes(group=Participant, y=after_stat(density), color = Participant), geom="line", position="identity") +
  coord_cartesian(xlim=c(0, 5)) +
  scale_y_sqrt() +
  theme(legend.position = "none") 
```


### Fixation Detection

```{r}
get_fixations <- function(dfeye, dispersion_threshold = 0.1, min_duration = 0.1, verbose = TRUE) {
  # Detect fixations
  dffixations <- dfeye  |> 
    mutate(event = detect_fixations_idt(
      t, x, y, screenwidth = ScreenWidth,
      dispersion_threshold = dispersion_threshold, min_duration = min_duration),
      .by = c("Participant", "Item")) |>
    filter(event != "Saccade") |>
    mutate(gaze_within = x >= Stimulus_left & x <= Stimulus_right & y >= Stimulus_top & y <= Stimulus_bottom)
  
  # Compute fixation centroids
  dffixations <- dffixations |>
    summarise(
      x = mean(x, na.rm = TRUE),
      y = mean(y, na.rm = TRUE),
      duration = max(t, na.rm = TRUE) - min(t, na.rm = TRUE),
      p_within = mean(gaze_within, na.rm = TRUE),
      Stimulus_left = first(Stimulus_left),
      Stimulus_right = first(Stimulus_right),
      Stimulus_top = first(Stimulus_top),
      Stimulus_bottom = first(Stimulus_bottom),
      ScreenWidth = first(ScreenWidth),
      ScreenHeight = first(ScreenHeight),
      .by = c("Participant", "Item", "event")
    ) 
  
  # Remove extra long fixations (more than 2 s)
  if(verbose) {
    print(paste0("Proportion of fixations longer than 2s: ", 
               format_percent(mean(dffixations$duration > 2, na.rm = TRUE))))
  }
  dffixations <- filter(dffixations, duration <= 2)
  
  # Remove fixations that are not on the target area
  if(verbose) {
    print(paste0("Proportion of fixations outside the target area: ", 
                 format_percent(mean(dffixations$p_within < 0.5, na.rm = TRUE))))
  }
  
  filter(dffixations, p_within >= 0.5) 
}
```

#### Grid Search

```{r}
dftask <- read.csv("../data/rawdata_task.csv")

feat_list <- c("Fixations_N", "Fixations_DurationMean", "N_Glances", "N_Sustained")
outcome_list <- c("Beauty", "Valence", "Meaning", "Worth")

ps <- list()
params <- data.frame()
for(disp in c(0.04, 0.06, 0.08, 0.1, 0.15, 0.2)) {
  cat(".")
  
  dffixations <- get_fixations(dfeye, dispersion_threshold = disp, min_duration = 0.08, verbose = FALSE)

  ps[[paste0("d", disp)]] <- dffixations |>
    filter(duration < 1) |> 
    ggplot(aes(x = duration)) +
    stat_density(aes(group = Participant, y = after_stat(density), color = Participant), geom = "line", position = "identity",
                 alpha = 0.5) +
    stat_density(aes(y = after_stat(density)), geom = "line", position = "identity", linewidth = 1) +
    guides(color = "none") +
    scale_x_sqrt(expand = c(0, 0)) + 
    scale_y_sqrt() +
    coord_cartesian(xlim = c(0.08, NA)) +
    labs(title = paste0("Dispersion Threshold: ", disp),
         x = "Fixation Duration (s)", y = NULL)
  
  features <- dffixations |> 
    mutate(Type = ifelse(duration < 0.2, "Glance", "Sustained")) |> 
    summarize(
      Fixations_N = n(),
      Fixations_DurationMean = mean(duration, na.rm = TRUE),
      N_Glances = sum(Type == "Glance"),
      N_Sustained = sum(Type == "Sustained"),
      .by = c("Participant", "Item", "Type")
    ) |>
      dplyr::left_join(dftask, by = c("Participant", "Item"))
  
  for(feat in feat_list) {
    for(outcome in outcome_list) {
      m <- lme4::lmer(as.formula(paste0(outcome, " ~ ", feat, " + (1|Participant)")), 
                      data=features)
      params <- parameters::parameters(m, effects="fixed")[2,] |>
        dplyr::select(t, p) |>
        dplyr::mutate(Feature = feat, Outcome = outcome, Dispersion = disp) |> 
        rbind(params)
    }
  }
}

patchwork::wrap_plots(ps)

params |> 
  ggplot(aes(x=Feature, y=Outcome, fill=p)) +
  geom_tile() +
  scale_fill_gradientn(colors=c("darkgreen", "lightgreen", "white", "white"), values = c(0, 0.05, 0.1, 1),
                       breaks = c(0, 0.1, 0.5, 0.75)) +
  facet_wrap(~Dispersion)
```



#### Final

```{r}
dffixations <- get_fixations(dfeye, dispersion_threshold = 0.08, min_duration = 0.08) |> 
  mutate(Type = ifelse(duration < 0.2, "Glance", "Sustained"))
```


### Features

```{r}
dffeatures <- dffixations |> 
    summarise(
      Fixations_N = n(), 
      Fixations_DurationMean = mean(duration, na.rm = TRUE),
      Fixations_DurationMedian = median(duration, na.rm = TRUE),
      N_Glances = sum(Type == "Glance"),
      N_Sustained = sum(Type == "Sustained"),
      SpatialEntropy = get_spatial_entropy(
        x, y,
        stim_left = first(Stimulus_left),
        stim_right = first(Stimulus_right),
        stim_top = first(Stimulus_top),
        stim_bottom = first(Stimulus_bottom)
      ),
      MeanJump = get_mean_jump(x, y, screenwidth = first(ScreenWidth)),
      AngularVariability = get_angular_variability(x, y, screenwidth = first(ScreenWidth)),
      .by = c("Participant", "Item")
    ) |>
      dplyr::left_join(dftask, by = c("Participant", "Item"))
```

## Validation

```{r}

rez <- data.frame()
for(feature in c("Fixations_N", "Fixations_DurationMean", "Fixations_DurationMedian", "N_Glances", "N_Sustained",
                 "SpatialEntropy", "MeanJump", "AngularVariability")) {
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Beauty ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dffeatures) |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Beauty") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Meaning ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dffeatures) |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Meaning") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Valence ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dffeatures) |>
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Valence") |>
    rbind(rez)
  
  rez  <- glmmTMB::glmmTMB(as.formula(paste0("Worth ~ ", feature, " + (1|Participant) + (1|Item)")), 
                         data=dffeatures, family = "poisson") |> 
    parameters::parameters(effects = "fixed") |>
    dplyr::mutate(Feature = feature, Outcome = "Worth") |>
    rbind(rez)
}

rez <- filter(rez, Parameter != "(Intercept)")
arrange(rez, p) 


```


#### OLD

```{r}
get_features <- function(dfeye, dispersion_threshold = 0.05, min_duration = 0.1) {
  
  # Detect fixations
  dffixations <- dfeye  |> 
    mutate(event = detect_fixations_idt(t, x, y, 
                                        dispersion_threshold = dispersion_threshold, 
                                        min_duration = min_duration),
           .by = c("Participant", "Item")) |> 
    mutate(event_n=as.numeric(str_extract_all(event, "\\d+", simplify = TRUE)[,1])) |> 
    filter(event != "Saccade")
  
  # Remove not on target
  dffixations <- dffixations |> 
    mutate(gaze_within = x >= Stimulus_left & x <= Stimulus_right & y >= Stimulus_top & y <= Stimulus_bottom) |> 
    mutate(on_target = mean(gaze_within, na.rm = TRUE), .by = c("Participant", "Item", "event")) |> 
    filter(on_target >= 0.5) 
    
  features <- dffixations |>
    # Compute fixation centroids
    summarise(
      x = mean(x, na.rm = TRUE),
      y = mean(y, na.rm = TRUE),
      delay = max(t, na.rm = TRUE) - min(t, na.rm = TRUE),
      Stimulus_left = first(Stimulus_left),
      Stimulus_right = first(Stimulus_right),
      Stimulus_top = first(Stimulus_top),
      Stimulus_bottom = first(Stimulus_bottom),
      .by = c("Participant", "Item", "event")
    ) |> 
    # Remove extreme durations fixations
    filter(delay < 1) |> 
    # Compute indices
    summarise(
      Fixations_N = n(), 
      Fixations_DurationTotal = sum(delay, na.rm = TRUE), 
      Fixations_DurationMean = mean(delay, na.rm = TRUE),
      Fixations_DurationMedian = median(delay, na.rm = TRUE),
      SpatialEntropy = get_spatial_entropy(
        x, y,
        stim_left = first(Stimulus_left),
        stim_right = first(Stimulus_right),
        stim_top = first(Stimulus_top),
        stim_bottom = first(Stimulus_bottom)
      ),
      MeanJump = get_mean_jump(x, y),
      AngularVariability = get_angular_variability(x, y),
      .by = c("Participant", "Item")
    ) |> 
    # Sanitize
    mutate(
      Fixations_DurationMean = ifelse(Fixations_DurationMean > 2/3, NA, log(Fixations_DurationMean)),
      Fixations_DurationMedian = ifelse(Fixations_DurationMedian > 2/3, NA, log(Fixations_DurationMedian))
    )
  
  features
}

```

### Grid Search

```{r}
dftask <- read.csv("../data/rawdata_task.csv")

# Load required packages
library(parallel)
library(doParallel)
library(foreach)
library(lme4)
library(parameters)
library(progress)

# Set up parallel backend
num_cores <- detectCores() - 1  # Use all cores except one for system stability
registerDoParallel(cores = num_cores)

# Initialize parameters data frame and range
params <- list()
range_mindura <- seq(0.1, 0.7, by = 0.025)
range_thresh <- seq(0.1, 0.2, by = 0.025)
feat_list <- c("Fixations_N", "Fixations_DurationTotal", "SpatialEntropy")
# "Fixations_DurationTotal", "Fixations_DurationMean", "Fixations_DurationMedian","MeanJump", "AngularVariability"
outcome_list <- c("Beauty", "Valence", "Meaning", "Worth")

# Create a progress bar
progbar <- progress::progress_bar$new(total = length(range_thresh) * length(range_mindura),
                                      format = "  [:bar] :percent eta: :eta")

for (thresh in range_thresh) {
  for (mindura in range_mindura) {
    progbar$tick()
    features <- get_features(dfeye, dispersion_threshold = thresh, min_duration = mindura) |>
      dplyr::left_join(dftask, by = c("Participant", "Item"))

    res <- foreach::foreach(feat = feat_list, .combine = dplyr::bind_rows,
                            .packages = c("lme4","parameters","dplyr")) %:%
      foreach::foreach(outcome = outcome_list, .combine = dplyr::bind_rows) %dopar% {
        # build formula
        fml <- as.formula(paste0(outcome, " ~ ", feat, " + (1|Participant)"))
        # drop NAs for the needed columns
        dat <- features |>
          dplyr::select(Participant, dplyr::all_of(c(feat, outcome))) |>
          tidyr::drop_na()

        out <- tryCatch({
          m <- lme4::lmer(fml, data = dat)
          parameters::parameters(m, effects = "fixed")[2, ] |>
            dplyr::select(t, p) |>
            dplyr::mutate(Feature = feat, Outcome = outcome,
                          thresh = thresh, mindura = mindura)
        }, error = function(e) {
          dplyr::tibble(t = NA_real_, p = NA_real_,
                        Feature = feat, Outcome = outcome,
                        thresh = thresh, mindura = mindura)
        })
        out
      }

    params[[paste(thresh, mindura)]] <- res
  }
}

params <- dplyr::bind_rows(params)
stopImplicitCluster()

(params |> 
  summarize(N_sig = sum(p < .05), .by=c("Feature", "mindura", "thresh")) |> 
  ggplot(aes(x=as.factor(thresh), y=as.factor(mindura), fill=N_sig)) +
  geom_tile() +
  scale_fill_gradientn(colors=c("white", "darkred")) +
  facet_grid(~Feature)) / 
  (params |> 
  ggplot(aes(x=as.factor(thresh), y=as.factor(mindura), fill=p)) +
  geom_tile() +
  scale_fill_gradientn(colors=c("darkgreen", "lightgreen", "white", "white"), values = c(0, 0.05, 0.1, 1),
                       breaks = c(0, 0.05, 0.1, 0.5, 0.75)) +
  facet_grid(Feature~Outcome))





params <- data.frame()

range <- c(0.01, seq(0.05, 0.8, by = 0.05))

progbar <- progress::progress_bar$new(total = length(range)^2)
for(thresh in range) {
  for(mindura in range) {
    progbar$tick()
    features <- get_features(dfeye, dispersion_threshold = thresh, min_duration = mindura) |> 
      left_join(dftask, by = c("Participant", "Item"))
    
    for(feat in c("Fixations_N", 
                  # "Fixations_DurationTotal", 
                  # "Fixations_DurationMean", 
                  # "Fixations_DurationMedian",
                  "SpatialEntropy"
                  # "MeanJump", 
                  # "AngularVariability"
                  )) {
      for(outcome in c("Beauty", "Valence", "Meaning", "Worth")) {
        # t0 <- Sys.time()
        m <- lme4::lmer(as.formula(paste0(outcome, " ~ ", feat, " + (1|Participant)")), 
                        data=features, 
                        control = lme4::lmerControl(optimizer = "bobyqa"),
                        REML = TRUE)
        # Sys.time() - t0
        params <- parameters::parameters(m, effects="fixed")[2,] |> 
          select(t, p) |> 
          mutate(Feature = feat, Outcome = outcome, thresh = thresh, mindura=mindura) |> 
          rbind(params)
      }
    }
  }
}
arrange(params, p) |> 
  filter( p < .05)

params |> 
  ggplot(aes(x=as.factor(thresh), y=as.factor(mindura), fill=p)) +
  geom_tile() +
  scale_fill_gradientn(colors=c("darkgreen", "lightgreen", "white", "white"), values = c(0, 0.05, 0.1, 1),
                       breaks = c(0, 0.05, 0.1, 0.5, 0.75)) +
  facet_grid(Feature~Outcome) 
```









STOPPED HERE.















### Final

```{r}
features <- get_features(dfeye, dispersion_threshold = 0.1, min_duration = 0.05) |> 
  left_join(read.csv("../data/rawdata_task.csv"), by = c("Participant", "Item"))

# m <- glmmTMB::glmmTMB(as.formula(paste0("Beauty ~ ", feat, " + (1|Participant)")), data=features)
# params <- rbind(params, parameters::parameters(m, effects="fixed") |> mutate(Feature = feat))
```


## Gaze Patterns


```{r fig_eyetracking2}
#| fig-width: 10
#| fig-height: 15

# plot_eyetrace <- function(stim="NF-1041") {
#   img <- magick::image_read(paste0("../experiment/stimuli/AMFD/", stim, ".jpg")) |>
#     magick::image_resize("400x")
# 
#   dat <- df |>
#     filter(Type == "Image") |>
#     filter(Stimulus == stim) |>
#     mutate(
#       x = datawizard::rescale(x, range=c(0, 1), to=c(0, magick::image_info(img)$width)),
#       y = datawizard::rescale(y, range=c(0, 1), to=c(0, magick::image_info(img)$height))
#     )
# 
#   img |>
#     magick::image_ggplot()  +
#     stat_density_2d(
#       data=dat,
#       aes(x=x, y=y, fill = after_stat(level)),
#       geom = "polygon", alpha=0.1) +
#     # geom_path(
#     #   data=dat,
#     #   aes(x=x, y=y, group = Participant, color=Condition),
#     #   alpha=0.1, linewidth=0.2) +
#     scale_color_manual(values=c("Reality"="red", "Fiction"="blue")) +
#     scale_fill_gradientn(colors=c("blue", "green", "yellow", "orange", "red")) +
#     labs(title=stim) +
#     theme_void() +
#     theme(legend.position="none",
#           strip.text = element_blank(),
#           plot.title = element_text(size = 8))  +
#     facet_grid(~Condition)
# }
# 
# plots <- list()
# for (stim in unique(df$Stimulus)) {
#   plots[[stim]] <- plot_eyetrace(stim)
# }
# patchwork::wrap_plots(plots, ncol=5)
```




## Indices


```{r}
#| code-fold: false

dftask <- left_join(dfindices, read.csv("../data/rawdata_task.csv"), by = join_by(Participant, Item))

# dftask |>
#   ggplot(aes(x = Fixations_N, y = Worth)) +
#   geom_jitter(width = 0.1, height = 0.1) +
#   geom_smooth(method = "lm")

correlation(select(dftask, starts_with("Fixations_"), SpatialEntropy, MeanJump, AngularVariability),
            select(dftask, Beauty, Valence, Meaning, Worth)) |> 
  summary()
```


## Analysis







```{r}
#| code-fold: false

m <- glmmTMB::glmmTMB(distance ~ Condition + (Condition|Participant) + (Condition|Stimulus),
                      data=dat)
insight::display(parameters::parameters(m))
```



```{r}
estimate_means(m, by="Condition") |>
  ggplot(aes(x=Condition)) +
  ggdist::stat_slab(data=filter(dat, Condition=="Reality"), aes(y=distance, fill=Condition), side="left") +
  ggdist::stat_slab(data=filter(dat, Condition=="Fiction"), aes(y=distance, fill=Condition), side="right") +
  geom_line(aes(y=Mean, group=1)) +
  geom_pointrange(aes(y=Mean, ymin=CI_low, ymax=CI_high)) +
  theme_minimal() +
  labs(y="Distance from center", x="Condition")
```


## Dispersion

```{r}
# Exploratory gaze
dat <- df |>
  filter(is.finite(distance)) |>
  filter(distance < sqrt(2)) |>
  summarize(
    sd_position = (sd(x, na.rm=TRUE) + sd(y, na.rm=TRUE)) / 2,
    mad_position = (mad(x, na.rm=TRUE) + mad(y, na.rm=TRUE)) / 2,
    .by=c("Participant", "Condition", "Stimulus")
  )


dat |> 
  pivot_longer(cols=c(sd_position, mad_position), names_to="Metric", values_to="Value") |> 
  ggplot(aes(x=Value, color=Condition)) +
  geom_density(linewidth=1) +
  facet_wrap(~Metric) +
  theme_minimal()
```

```{r}
#| code-fold: false

m <- glmmTMB::glmmTMB(sd_position ~ Condition + (Condition|Participant) + (Condition|Stimulus),
                      data=dat)
insight::display(parameters::parameters(m))
```

```{r}
#| code-fold: false

m <- glmmTMB::glmmTMB(mad_position ~ Condition + (Condition|Participant) + (Condition|Stimulus),
                      data=dat)
insight::display(parameters::parameters(m))
```


