---
title: "FakeArt - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Estimates are computed on the cluster (`./hpc extract`, see server/estimates.R) and read from models/estimates/. -->

## Data Preparation

```{r}
#| warning: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)

df <- read.csv("../data/data_participants.csv")
dftask <- read.csv("../data/data_task.csv") |>
  merge(read.csv("../data/data_eyetracking.csv"), all.x = TRUE) |>
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated"),
         Emotion = fct_relevel(Emotion, "Positive - Low intensity", "Negative - Low intensity", "Positive - High intensity", "Negative - High intensity"),
         Meaning = Meaning * 6,
         Valence = Valence * 6 + 1,
         Worth = factor(Worth * 6, ordered = TRUE),
         SelfRelevance = SelfRelevance * 6)
levels(dftask$Worth) <- c("0", "10", "100", "1000", "10000", "100000")

cols <- c(
  # Condition
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "AI Original" = "#1D9AF5",
  "AI Copy" = "#4CAF50",
  "Not recognized" = "#607D8B")

source("server/estimates.R") # outcome_info, prep_contrasts()
source("report.R")           # make_asis(), make_tables(), make_markdown(), read_estimates()

estimates <- read_estimates(names(outcome_info))
provenance_table(estimates)
```

## How to read this report

Each model is a Bayesian mixed model of one outcome on `Condition * Emotion`
(**Condition**: label shown before the artwork, all of which were human
originals; **Emotion**: normative valence x arousal quadrant), with
`(Condition * Emotion | Participant)` and `(Condition | Item)`.

Each section: model-implied distributions (figures), convergence, marginal
means per condition (response scale), all contrasts between conditions for
every distributional parameter (green = credibly positive, red = credibly
negative, grey = CI includes 0), the same within each emotion quadrant, and an
auto-generated summary. Every table has a folded Markdown twin; the Summary
section writes `data/results_contrasts.csv` and `data/results_means.csv`.

Contrasts (`Level1 - Level2`) are posterior medians with 95% CI and probability
of direction (`pd`). "Credible" = CI excludes 0 (no multiplicity correction).

**Units.** Differences on a bounded scale are in **% of the scale range**: 0-1
sliders and gaze proportions, probabilities (`mu`, `confright`, `confleft`,
`pex`, `bex`, `pmid`, `pzero`, `zoi`, `coi`, ordinal categories) x 100;
Valence and Meaning `response` / 6 x 100. Unbounded parameters (`phi`,
`precright`, `precleft`, `sigma`, `disc`, Shift in stimulus widths) are
marked `raw`. The CSVs carry both.

```{r}
#| label: helpers
#| code-summary: "Reporting helpers (tables, prose, plots)"

# get_*() returns data, make_*() returns output.

param_glossary <- c(
  response = "expected value on the response scale",
  mu = "CHOCO: probability of choosing the upper half of the scale (logit link). Discrete Beta / Beta: mean of the latent Beta",
  confright = "CHOCO: mean confidence (position within the upper half) when the upper half is chosen",
  confleft = "CHOCO: mean confidence within the lower half when the lower half is chosen",
  precright = "CHOCO: precision (inverse spread) of ratings within the upper half",
  precleft = "CHOCO: precision of ratings within the lower half",
  pex = "CHOCO: probability of an extreme response (exactly 0 or 1)",
  bex = "CHOCO: balance of the extreme mass towards 1 (> 0.5) or 0 (< 0.5)",
  pmid = "CHOCO: probability of answering exactly at the midpoint",
  phi = "precision of the latent Beta (higher = more agreement / less dispersion)",
  pzero = "probability of the hurdle category 0",
  sigma = "LogNormal: scale (spread) parameter on the log scale",
  zoi = "probability of an exact 0 or 1", coi = "conditional probability that an extreme is 1 rather than 0",
  disc = "ordinal discrimination"
)

# Generated summary of the credible effects
make_summary <- function(dat, dat_emo, outcome) {
  info <- outcome_info[[outcome]]
  main_pars <- c("response", "mu")
  out <- c(sprintf("**%s** (%s). Scale: %s. Differences are posterior medians with 95%% CI, in %% of the scale range for bounded parameters and on the parameter's own scale for those marked `raw`; `pd` is the probability of direction. An effect is called credible when the CI excludes 0.", info$label, info$family, info$scale), "")
  for (con in levels(dat$Contrast)) {
    d <- dat[dat$Contrast == con, ]
    if (nrow(d) == 0) next
    cred <- d[d$Credible, ]
    if (nrow(cred) == 0) {
      out <- c(out, sprintf("- **%s**: no credible difference on any parameter (%s).", con, paste(unique(d$Parameter), collapse = ", ")))
      next
    }
    cred <- cred[order(!cred$Parameter %in% main_pars & !grepl("^response", cred$Parameter), cred$Parameter), ]
    up <- cred[cred$Difference > 0, ]; down <- cred[cred$Difference < 0, ]
    fmt <- function(x) paste(sprintf("`%s` %s%s %s", x$Parameter, x$Diff, ifelse(x$Unit == "%", "%", ""), x$CI), collapse = "; ")
    parts <- c(if (nrow(down)) sprintf("lower %s", fmt(down)), if (nrow(up)) sprintf("higher %s", fmt(up)))
    ns <- setdiff(unique(d$Parameter), cred$Parameter)
    out <- c(out, sprintf("- **%s**: %s.%s", con, paste(parts, collapse = "; "),
                          if (length(ns)) sprintf(" No credible difference on %s.", paste0("`", ns, "`", collapse = ", ")) else ""))
  }
  if (!is.null(dat_emo) && nrow(dat_emo) > 0 && "Emotion" %in% names(dat_emo)) {
    out <- c(out, "", "By stimulus emotion (same contrasts within each valence x arousal quadrant, main parameter only):")
    for (con in levels(dat$Contrast)) {
      d <- dat_emo[dat_emo$Contrast == con & (dat_emo$Parameter %in% main_pars | grepl("^response", dat_emo$Parameter)), ]
      if (nrow(d) == 0) next
      d <- d[d$Parameter == d$Parameter[1], ] # first main parameter available
      cred <- d[d$Credible, ]
      out <- c(out, sprintf("- **%s** on `%s`: credible in %s%s.", con, d$Parameter[1],
                            if (nrow(cred)) paste(sprintf("%s (%s%s %s)", cred$Emotion, cred$Diff, ifelse(cred$Unit == "%", "%", ""), cred$CI), collapse = ", ") else "no quadrant",
                            if (nrow(cred) && nrow(cred) < nrow(d)) sprintf("; not in %s", paste(setdiff(d$Emotion, cred$Emotion), collapse = ", ")) else ""))
    }
  }
  make_asis("", '::: {.callout-tip title="Summary of credible effects (generated from the tables above)"}', "", out, "", ":::", "")
}

# One model section's tables and summary. prep_contrasts() is re-run locally
# so scaling/labelling changes need no re-extraction.
make_report <- function(est) {
  rep <- est$report
  info <- outcome_info[[rep$outcome]]
  dat <- prep_contrasts(rep$contrasts, rep$outcome)
  dat_emo <- prep_contrasts(rep$contrasts_emo, rep$outcome)
  extra <- if (!is.null(rep$contrasts_extra)) prep_contrasts(rep$contrasts_extra, rep$outcome) else NULL
  means_fmt <- rep$means
  num <- vapply(means_fmt, is.numeric, logical(1))
  means_fmt[num] <- lapply(means_fmt[num], insight::format_value, zap_small = TRUE)
  cols <- c("Contrast", "Parameter", "Diff", "CI", "Unit", "pd_fmt", "Effect")
  # Digest of credible parameters per contrast, then the full tables
  credible <- list(est$contrasts_credible, est$contrasts_extra_credible)
  credible <- credible[!vapply(credible, is.null, logical(1))]
  make_asis(
    vapply(credible, function(x) as.character(knitr::knit_print(gt::gt(x))), ""),
    "",
    make_tables(rep$diag, c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct", "Criterion"),
                sprintf("%s: convergence", info$label)),
    make_tables(means_fmt, names(means_fmt),
                sprintf("%s: marginal means per label condition (response scale)", info$label)),
    make_tables(dat, cols, sprintf("%s: all contrasts between label conditions", info$label)),
    if (!is.null(extra)) make_tables(extra, cols, sprintf("%s: %s", info$label, rep$extra_title)) else "",
    # Markdown only (36-72 rows)
    make_markdown(dat_emo[c("Emotion", cols)],
                  sprintf("%s: contrasts within each stimulus emotion", info$label)),
    make_summary(dat, dat_emo, rep$outcome)
  )
}


# Figures -------------------------------------------------------------------

# CHOCO density per condition from the marginal parameters (est$marginal).
# `adjust` scales the curve to match the histogram.
get_marginal_densities <- function(dat_par, adjust = 2) {
  dat_dens <- data.frame()
  dat_annot <- data.frame()
  for (row in 1:nrow(dat_par)) {
    x <- seq(0, 1, length.out = 201)
    y <- cogmod::dcogmod_choco(
      x = x, p = dat_par$Mu[row], confleft = dat_par$Confleft[row], confright = dat_par$Confright[row],
      precleft = dat_par$Precleft[row], precright = dat_par$Precright[row],
      pmid = dat_par$Pmid[row], pex = dat_par$Pex[row], bex = dat_par$Bex[row]
    )
    y <- y * adjust
    dat_dens <- rbind(dat_dens, data.frame(Condition = dat_par$Condition[row], x = x, y = y))

    # Modes of each half, sized by the probability of that half
    dat_annot <- rbind(dat_annot, data.frame(
      Condition = dat_par$Condition[row],
      right_y = max(y[x > 0.5]), left_y = max(y[x < 0.5]),
      right_x = 0.5 + x[which.max(y[x > 0.5])], left_x = x[which.max(y[x < 0.5])],
      right_size = dat_par$Mu[row], left_size = 1 - dat_par$Mu[row]
    ))
  }


  offset <- 1 - (rev(as.numeric(dat_par$Condition)) / 3)
  max_y <- max(dat_dens$y)
  dat_par$Mean_y <- 1.2 * max_y - offset * (1.2 * max_y - max_y)

  list(par=dat_par, dens=dat_dens, annot=dat_annot)
}

# The same per emotion quadrant (est$marginal_emo)
get_marginal_densities_emo <- function(dat_par, adjust = 2) {
  out <- list(par = data.frame(), dens = data.frame(), annot = data.frame())
  for (emo in unique(dat_par$Emotion)) {
    dat <- get_marginal_densities(dat_par[dat_par$Emotion == emo, ], adjust = adjust)
    dat[["dens"]]$Emotion <- emo
    dat[["annot"]]$Emotion <- emo
    for (el in c("par", "dens", "annot")) out[[el]] <- rbind(out[[el]], dat[[el]])
  }
  lv <- rev(levels(dftask$Emotion))
  out$dens$Emotion <- fct_relevel(out$dens$Emotion, lv)
  out$annot$Emotion <- fct_relevel(out$annot$Emotion, lv)
  out
}

get_choco_plot <- function(dat, title = "Beauty", observed = title, xlabs = c("0% - Ugly", "100% - Beautiful"), facet = NULL, ...) {
   dat_obs <- dftask
   dat_obs$obs <- dat_obs[[observed]]
   dat_obs <- dat_obs[!is.na(dat_obs$obs), ]

  p <- dat$dens |>
    ggplot(aes(x = x, y = y)) +
    geom_histogram(data = dat_obs, aes(x = obs, y = after_stat(density)), alpha = 0.1, bins = 47) +
    geom_segment(data = dat$annot, aes(
      x = right_x, xend = right_x,
      y = 0, yend = right_y, color = Condition
    ), linewidth = 0.5, linetype = "dashed") +
    geom_segment(data = dat$annot, aes(
      x = left_x, xend = left_x,
      y = 0, yend = left_y, color = Condition
    ), linewidth = 0.5, linetype = "dashed") +
    geom_point(data = dat$annot, aes(x = right_x, y = 0, color = Condition, size = right_size * 6)) +
    geom_point(data = dat$annot, aes(x = left_x, y = 0, color = Condition, size = left_size * 6)) +
    geom_pointrange(data = dat$par, aes(x = Mean, y = Mean_y, xmin = Mean_low, xmax = Mean_high, color = Condition), linewidth = 0.5) +
    geom_line(aes(color = Condition), linewidth = 1.3) +
    labs(y = "Likelihood of Response", title = title) +
    scale_size_identity() +
    scale_color_manual(values = cols) +
    scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1),
                       labels = c(xlabs[1], "25%", "50%",  "75%", xlabs[2])) +
    theme_minimal() +
    theme(axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(face = "bold"))

  if(!is.null(facet)) p <- p + facet_wrap(facet, ...)
  p
}

# `pred_long` = est$discrete(_emo): predicted proportion per response category.
# `shift` = 1 maps ordinal category indices 1..k onto a 0-based scale.
get_discrete_plot <- function(pred_long, title = "Valence", observed = title, facet = NULL, shift = 0, ...) {
   dat_obs <- dftask
   dat_obs$obs <- dat_obs[[observed]]
   dat_obs <- dat_obs[!is.na(dat_obs$obs), ]

   if(title == "Worth") dat_obs$obs <- as.numeric(dat_obs$obs)

  pred_long$iter_value <- pred_long$iter_value - shift

  p <- dat_obs |>
    ggplot(aes(x = obs)) +
    geom_bar(alpha = 0.1, aes(y = after_stat(prop))) +
    geom_line(
    data = pred_long,
    aes(x = iter_value, y = median, group = Condition, colour = Condition),
    position = position_dodge(width = 0.25, reverse = TRUE), linewidth = 1.3
  )  +
    geom_pointrange(
    data = pred_long,
    aes(x = iter_value, y = median,  ymin = lower,  ymax = upper,  color = Condition),
    position = position_dodge(width = 0.25, reverse = TRUE)
  ) +
    labs(y = "Likelihood of Response", title = title) +
    scale_size_identity() +
    scale_color_manual(values = cols) +
    theme_minimal() +
    theme(axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(face = "bold"))

  if(!is.null(facet)) p <- p + facet_wrap(facet, ...)
  p
}

# `dens` = est$density: one posterior-predictive density per draw
get_density_plot <- function(dens, observed, bins = 40, alpha = 0.5, facet = NULL, xlim = NULL) {
  p <- dftask |>
    ggplot(aes(x = .data[[observed]])) +
    geom_histogram(aes(y = after_stat(density)), bins = bins) +
    geom_line(data = dens, alpha = alpha,
              aes(x = x, y = y, group = interaction(Condition, iter_group), color = Condition))
  if (!is.null(xlim)) p <- p + coord_cartesian(xlim = xlim)
  if (!is.null(facet)) p <- p + facet_wrap(facet)
  p
}
```

```{r}
#| label: glossary

knitr::kable(
  data.frame(
    Model = vapply(outcome_info, `[[`, "", "label"),
    Outcome = names(outcome_info),
    Family = vapply(outcome_info, `[[`, "", "family"),
    Scale = vapply(outcome_info, `[[`, "", "scale"),
    row.names = NULL
  ),
  caption = "Outcomes, model families and response scales.", format = "pipe"
)

knitr::kable(
  data.frame(Parameter = names(param_glossary), Meaning = unname(param_glossary)),
  caption = "Distributional parameters that appear in the contrast tables.", format = "pipe"
)
```

## Distributions

::: {.panel-tabset}

### Phase 1

```{r}
#| label: fig-dist-phase1
#| fig-cap: "Observed distributions of the Phase 1 ratings (Beauty 0-1, Valence 1-7, Meaning 0-6, Worth in 6 money categories) and of the four gaze features, pooled over conditions."
#| fig-alt: "Observed distributions of the Phase 1 ratings (Beauty 0-1, Valence 1-7, Meaning 0-6, Worth in 6 money categories) and of the four gaze features, pooled over conditions."
#| warning: false

p_dist_beauty <- dftask |> 
  ggplot(aes(x=Beauty)) +
  geom_histogram(aes(y=after_stat(density)), bins = 47, fill = colorRampPalette(c("#1976D2", "#0D47A1"))(47))

p_dist_valence <- dftask |> 
  ggplot(aes(x=Valence)) +
  geom_bar(fill = colorRampPalette(c("#388E3C", "#1B5E20"))(7)) 
  
p_dist_meaning <- dftask |> 
  ggplot(aes(x=Meaning)) +
  geom_bar(fill = colorRampPalette(c("#512DA8", "#311B92"))(7))

p_dist_worth <- dftask |> 
  ggplot(aes(x=Worth)) +
  geom_bar(fill = colorRampPalette(c("#FBC02D", "#F57F17"))(6)) 

p_dist_entropy <- dftask |> 
  ggplot(aes(x=Gaze_Entropy)) +
  geom_histogram(aes(y=after_stat(density)), bins = 100, fill = colorRampPalette(c("#455A64", "#263238"))(100)) 

p_dist_shift <- dftask |> 
  ggplot(aes(x=Gaze_Shift)) +
  geom_histogram(aes(y=after_stat(density)), bins = 100, fill = colorRampPalette(c("#455A64", "#263238"))(100)) 

p_dist_pleft <- dftask |> 
  ggplot(aes(x=Gaze_pLeft)) +
  geom_histogram(aes(y=after_stat(density)), bins = 51, fill = colorRampPalette(c("#455A64", "#263238"))(51)) 

p_dist_pcenter <- dftask |> 
  ggplot(aes(x=Gaze_pCenter)) +
  geom_histogram(aes(y=after_stat(density)), bins = 51, fill = colorRampPalette(c("#455A64", "#263238"))(51))

wrap_plots(
  (p_dist_beauty + labs(title = "Beauty")), 
    (p_dist_valence + labs(title = "Valence")),
    (p_dist_meaning + labs(title = "Meaning")), 
    (p_dist_worth + labs(title = "Worth")),
    (p_dist_entropy + labs(title = "Entropy")),
    (p_dist_shift + labs(title = "Shift")),
    (p_dist_pleft + labs(title = "pLeft")),
    (p_dist_pcenter + labs(title = "pCenter")),
  ncol = 4
)

```

```{r}
#| eval: false
# Run by hand: bare panels for figures/figure1.pptx
# (ppt/media/image7,8,9,13,15,16,17,18).

dist_theme <- list(
  scale_x_continuous(expand = c(0, 0)),
  scale_y_continuous(expand = c(0, 0)),
  theme_void(),
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(face = "bold"))
)


ggsave(p_dist_beauty + dist_theme, filename = "figures/dist_beauty.png", width = 6, height = 4, dpi = 300)
ggsave(p_dist_valence + dist_theme, filename = "figures/dist_valence.png", width = 6, height = 4, dpi = 300)
ggsave(p_dist_meaning + dist_theme, filename = "figures/dist_meaning.png", width = 6, height = 4, dpi = 300)
ggsave(p_dist_worth + dist_theme[-1] + scale_x_discrete(expand = c(0, 0)), filename = "figures/dist_worth.png", width = 6, height = 4, dpi = 300) # Worth is a factor: discrete x scale
ggsave(p_dist_entropy + dist_theme, filename = "figures/dist_entropy.png", width = 6, height = 1.5, dpi = 300)
ggsave(p_dist_shift + dist_theme, filename = "figures/dist_shift.png", width = 6, height = 1.5, dpi = 300)
ggsave(p_dist_pleft + dist_theme, filename = "figures/dist_pleft.png", width = 6, height = 1.5, dpi = 300)
ggsave(p_dist_pcenter + dist_theme, filename = "figures/dist_pcenter.png", width = 6, height = 1.5, dpi = 300)
```

### Phase 2 and Follow-Up

```{r}
#| label: fig-dist-phase2
#| fig-cap: "Observed distributions of the Phase 2 sliders (Syntheticness: 0 = AI-Generated, 1 = Human; Authenticity: 0 = Copy, 1 = Original) and of the follow-up outcomes (Beauty rated again, Self-Relevance 0-6, Perceived Artificiality 0-1)."
#| fig-alt: "Observed distributions of the Phase 2 sliders (Syntheticness: 0 = AI-Generated, 1 = Human; Authenticity: 0 = Copy, 1 = Original) and of the follow-up outcomes (Beauty rated again, Self-Relevance 0-6, Perceived Artificiality 0-1)."
#| warning: false

p_dist_reality <- dftask |> 
  ggplot(aes(x=Reality)) +
  geom_histogram(aes(y=after_stat(density)), bins = 51, fill = colorRampPalette(c("#C2185B", "#880E4F"))(51))

p_dist_authenticity <- dftask |> 
  ggplot(aes(x=Authenticity)) +
  geom_histogram(aes(y=after_stat(density)), bins = 51, fill = colorRampPalette(c("#E64A19", "#BF360C"))(51))

p_dist_beauty2 <- dftask |> 
  ggplot(aes(x=Beauty2)) +
  geom_histogram(aes(y=after_stat(density)), bins = 47, fill = colorRampPalette(c("#0097A7", "#006064"))(47))

p_dist_selfrel <- dftask |> 
  ggplot(aes(x=SelfRelevance)) +
  geom_bar(fill = colorRampPalette(c("#00796B", "#004D40"))(7))  

p_dist_artificiality <- dftask |> 
  ggplot(aes(x=PerceivedArtificiality)) +
  geom_histogram(aes(y=after_stat(density)), bins = 21, fill = colorRampPalette(c("#AFB42B", "#827717"))(21))

wrap_plots(
  (p_dist_reality + labs(title = "Syntheticness")), 
    (p_dist_authenticity + labs(title = "Authenticity")),
    (p_dist_beauty2 + labs(title = "Beauty (follow-up)")), 
    (p_dist_selfrel + labs(title = "Self-Relevance")),
    (p_dist_artificiality + labs(title = "Artificiality")),
  ncol = 3
)
```

:::


## Phase 1 - Ratings

::: {.panel-tabset}

### Beauty


```{r}
#| label: tables-beauty

make_report(estimates$Beauty)
```


```{r}
#| label: fig-beauty
#| fig-cap: "Beauty: observed ratings (grey histogram, 0 = Ugly, 1 = Beautiful) with the model-implied CHOCO density for each label condition. The two dots per condition on the x-axis mark the modal rating within the lower and upper half of the scale, sized by the probability of choosing that half (mu); the point-ranges above are the marginal means with 95% CI."
#| fig-alt: "Beauty: observed ratings (grey histogram, 0 = Ugly, 1 = Beautiful) with the model-implied CHOCO density for each label condition. The two dots per condition on the x-axis mark the modal rating within the lower and upper half of the scale, sized by the probability of choosing that half (mu); the point-ranges above are the marginal means with 95% CI."
#| fig-width: 10
#| fig-height: 7

dens_beauty <- get_marginal_densities(estimates$Beauty$marginal, adjust = 0.8)
p_beauty <- get_choco_plot(dens_beauty, title = "Beauty", xlabs = c("0%\nUgly", "100%\nBeautiful"))
p_beauty
```

```{r}
#| label: fig-beauty-emotion
#| fig-cap: "Beauty by stimulus emotion quadrant: as the previous figure, one panel per valence x arousal quadrant of the artworks."
#| fig-alt: "Beauty by stimulus emotion quadrant: as the previous figure, one panel per valence x arousal quadrant of the artworks."

dens_beauty_emo <- get_marginal_densities_emo(estimates$Beauty$marginal_emo, adjust = 0.8)
p_beauty_emo <- get_choco_plot(dens_beauty_emo, title = "Beauty",
                               xlabs = c("0%\nUgly", "100%\nBeautiful"), facet = ~Emotion)
p_beauty_emo
```


### Valence


```{r}
#| label: tables-valence

make_report(estimates$Valence)
```


```{r}
#| label: fig-valence
#| fig-cap: "Valence (1 = Negative, 7 = Positive): observed proportion of each response (grey bars) and the model-implied probability of each response per label condition (points with 95% CI)."
#| fig-subcap:
#|   - "Overall"
#|   - "By stimulus emotion quadrant"
#| layout-ncol: 1

p_valence <- get_discrete_plot(estimates$Valence$discrete, title = "Valence") +
    scale_x_continuous(breaks = 1:7, labels = c("-3\nNegative", "-2", "-1", "0", "+1", "+2", "+3\nPositive"))
p_valence

get_discrete_plot(estimates$Valence$discrete_emo, title = "Valence", facet = ~Emotion) +
    scale_x_continuous(breaks = 1:7, labels = c("-3\nNegative", "-2", "-1", "0", "+1", "+2", "+3\nPositive"))
```


### Meaning


```{r}
#| label: tables-meaning

make_report(estimates$Meaning)
```

```{r}
#| label: fig-meaning
#| fig-cap: "Meaning (0 = Not at all, 6 = Very much): observed proportion of each response (grey bars) and the model-implied probability per label condition (points with 95% CI)."
#| fig-subcap:
#|   - "Overall"
#|   - "By stimulus emotion quadrant"
#| layout-ncol: 1

p_meaning <- get_discrete_plot(estimates$Meaning$discrete, title = "Meaning") +
    scale_x_continuous(breaks = 0:6, labels = c("0\nNot at all", 1:5, "6\nVery much"))
p_meaning

get_discrete_plot(estimates$Meaning$discrete_emo, title = "Meaning", facet = ~Emotion) +
    scale_x_continuous(breaks = 0:6, labels = c("0\nNot at all", 1:5, "6\nVery much"))
```

### Worth


```{r}
#| label: tables-worth

make_report(estimates$Worth)
```

```{r}
#| label: fig-worth
#| fig-cap: "Worth ($0 to $100,000, six ordered categories): observed proportion of each category (grey bars) and the model-implied probability per label condition (points with 95% CI)."
#| fig-subcap:
#|   - "Overall"
#|   - "By stimulus emotion quadrant"
#| layout-ncol: 1

p_worth <- get_discrete_plot(estimates$Worth$discrete, title = "Worth") +
    scale_x_continuous(breaks = 1:6, labels = c("$0", "$10", "$100", "$1,000", "$10,000", "$100,000"))
p_worth

get_discrete_plot(estimates$Worth$discrete_emo, title = "Worth", facet = ~Emotion) +
    scale_x_continuous(breaks = 1:6, labels = c("$0", "$10", "$100", "$1,000", "$10,000", "$100,000"))
```

:::


### Figure 2

```{r}
#| label: fig-figure2
#| fig-cap: "Effect of the label condition on the four Phase 1 aesthetic judgments (Beauty, Valence, Meaning, Worth). Grey shows the observed distribution of ratings; coloured elements show the model-implied response distribution per label condition with 95% CIs."
#| fig-alt: "Four-panel grid showing the effect of the label condition (Human Original, Human Forgery, AI-Generated) on Beauty, Valence, Meaning and Worth ratings."
#| fig-width: 12
#| fig-height: 9

# Manuscript Figure 2. Legend from the Valence panel only (Beauty's keys differ).
figure2 <- wrap_plots(
  p_beauty + guides(colour = "none"),
  p_valence,
  p_meaning + guides(colour = "none"),
  p_worth + guides(colour = "none"),
  ncol = 2
) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom", legend.title = element_blank())

figure2

ggsave("figures/figure2.png", figure2, width = 12, height = 9, dpi = 300, bg = "white")
```


## Phase 1 - Eye-Tracking

::: {.panel-tabset}

### Entropy


```{r}
#| label: tables-entropy

make_report(estimates$Entropy)
```

```{r}
#| label: fig-entropy
#| fig-cap: "Gaze entropy: observed distribution (histogram) with posterior-predictive densities per label condition (50 draws each)."
#| fig-alt: "Gaze entropy: observed distribution (histogram) with posterior-predictive densities per label condition (50 draws each)."

get_density_plot(estimates$Entropy$density, observed = "Gaze_Entropy", bins = 40)
```


### pLeft


```{r}
#| label: tables-pleft

make_report(estimates$pLeft)
```


```{r}
#| label: fig-pleft
#| fig-cap: "Gaze laterality (proportion of samples on the left half of the image): observed distribution with posterior-predictive densities per label condition (50 draws each)."
#| fig-alt: "Gaze laterality (proportion of samples on the left half of the image): observed distribution with posterior-predictive densities per label condition (50 draws each)."

get_density_plot(estimates$pLeft$density, observed = "Gaze_pLeft", bins = 40)
```


### pCenter


```{r}
#| label: tables-pcenter

make_report(estimates$pCenter)
```

```{r}
#| label: fig-pcenter
#| fig-cap: "Gaze centeredness (proportion of samples in the central region): observed distribution with posterior-predictive densities per label condition (50 draws each)."
#| fig-alt: "Gaze centeredness (proportion of samples in the central region): observed distribution with posterior-predictive densities per label condition (50 draws each)."

get_density_plot(estimates$pCenter$density, observed = "Gaze_pCenter", bins = 40)
```


### Shift


```{r}
#| label: tables-shift

make_report(estimates$Shift)
```

```{r}
#| label: fig-shift
#| fig-cap: "Gaze maximal shift (largest within-trial relocation of the gaze centroid, in stimulus widths, truncated at 1): observed distribution with posterior-predictive densities per label condition (500 draws), one panel per stimulus emotion quadrant."
#| fig-alt: "Gaze maximal shift (largest within-trial relocation of the gaze centroid, in stimulus widths, truncated at 1): observed distribution with posterior-predictive densities per label condition (500 draws), one panel per stimulus emotion quadrant."

get_density_plot(estimates$Shift$density, observed = "Gaze_Shift", bins = 100,
                 alpha = 0.05, facet = ~Emotion, xlim = c(0, 1))
```


:::


## Phase 2

::: {.panel-tabset}

### Syntheticness


```{r}
#| label: tables-reality

make_report(estimates$Reality)
```


```{r}
#| label: fig-reality
#| fig-cap: "Syntheticness (Phase 2 slider, 0 = AI-Generated, 1 = Human Creation): observed ratings with the model-implied CHOCO density per label condition; dots mark the modal rating in each half of the scale sized by the probability of choosing that half, point-ranges are marginal means with 95% CI."
#| fig-alt: "Syntheticness (Phase 2 slider, 0 = AI-Generated, 1 = Human Creation): observed ratings with the model-implied CHOCO density per label condition; dots mark the modal rating in each half of the scale sized by the probability of choosing that half, point-ranges are marginal means with 95% CI."
#| fig-width: 10
#| fig-height: 7

dens_reality <- get_marginal_densities(estimates$Reality$marginal, adjust = 0.5)
p_reality <- get_choco_plot(dens_reality, title = "Syntheticness", observed = "Reality", xlabs = c("0%\nAI-Generated", "100%\nHuman-Creation"))
p_reality
```


### Authenticity


```{r}
#| label: tables-authenticity

make_report(estimates$Authenticity)
```


```{r}
#| label: fig-authenticity
#| fig-cap: "Authenticity (Phase 2 slider, 0 = Copy, 1 = Original): observed ratings with the model-implied CHOCO density per label condition; dots mark the modal rating in each half of the scale sized by the probability of choosing that half, point-ranges are marginal means with 95% CI."
#| fig-alt: "Authenticity (Phase 2 slider, 0 = Copy, 1 = Original): observed ratings with the model-implied CHOCO density per label condition; dots mark the modal rating in each half of the scale sized by the probability of choosing that half, point-ranges are marginal means with 95% CI."
#| fig-width: 10
#| fig-height: 7

dens_authenticity <- get_marginal_densities(estimates$Authenticity$marginal, adjust = 0.5)
p_authenticity <- get_choco_plot(dens_authenticity, title = "Authenticity", xlabs = c("0%\nCopy", "100%\nOriginal"))
p_authenticity
```


:::


## Follow-up

::: {.panel-tabset}

### Beauty2


```{r}
#| label: tables-beauty2

make_report(estimates$Beauty2)
```

```{r}
#| label: fig-beauty2
#| fig-cap: "Beauty rated again in the follow-up session (after participants were told all artworks were human originals): observed ratings with the model-implied CHOCO density per original label condition."
#| fig-alt: "Beauty rated again in the follow-up session (after participants were told all artworks were human originals): observed ratings with the model-implied CHOCO density per original label condition."
#| fig-width: 10
#| fig-height: 7

dens_beauty2 <- get_marginal_densities(estimates$Beauty2$marginal, adjust = 0.5)
p_beauty2 <- get_choco_plot(dens_beauty2, title = "Beauty2", xlabs = c("0%\nUgly", "100%\nBeautiful"))
p_beauty2
```


### Self-Relevance


```{r}
#| label: tables-selfrelevance

make_report(estimates$SelfRelevance)
```


```{r}
#| label: fig-selfrelevance
#| fig-cap: "Self-Relevance (0 = Not at all, 6 = Very much; follow-up session): observed proportion of each response and the model-implied probability per original label condition."
#| fig-subcap:
#|   - "Overall"
#|   - "By stimulus emotion quadrant"
#| layout-ncol: 1

get_discrete_plot(estimates$SelfRelevance$discrete, title = "SelfRelevance", shift = 1) +
    scale_x_continuous(breaks = 0:6, labels = c("0\nNot at all", 1:5, "6\nVery much"))

get_discrete_plot(estimates$SelfRelevance$discrete_emo, title = "SelfRelevance", facet = ~Emotion, shift = 1) +
    scale_x_continuous(breaks = 0:6, labels = c("0\nNot at all", 1:5, "6\nVery much"))
```


### Artificiality


```{r}
#| label: tables-artificiality

make_report(estimates$Artificiality)
```


```{r}
#| label: fig-artificiality
#| fig-cap: "Perceived Artificiality (follow-up, items judged as new; 0 = Very Human, 1 = Very Artificial): observed ratings with the model-implied CHOCO density per original label condition."
#| fig-alt: "Perceived Artificiality (follow-up, items judged as new; 0 = Very Human, 1 = Very Artificial): observed ratings with the model-implied CHOCO density per original label condition."
#| fig-width: 10
#| fig-height: 7

dens_artificiality <- get_marginal_densities(estimates$Artificiality$marginal, adjust = 0.8)
p_artificiality <- get_choco_plot(dens_artificiality, title = "Artificiality", observed = "PerceivedArtificiality", xlabs = c("0%\nVery Human", "100%\nVery Artificial"))
p_artificiality
```


:::

## Summary

- `data/results_contrasts.csv`: every contrast x parameter x (overall or emotion quadrant), raw and % columns.
- `data/results_means.csv`: marginal means per label condition (response scale).

```{r}
#| label: summary-collect

# Document order (outcome_info is grouped by family)
section_order <- c("Beauty", "Valence", "Meaning", "Worth",
                   "Entropy", "pLeft", "pCenter", "Shift",
                   "Reality", "Authenticity",
                   "Beauty2", "SelfRelevance", "Artificiality")
# unname(): bind_rows() reads the names of two named lists as columns
reps <- unname(lapply(estimates[section_order], `[[`, "report"))

results_contrasts <- bind_rows(
  lapply(reps, function(r) mutate(r$contrasts, Emotion = "Overall")),
  lapply(reps, function(r) r$contrasts_emo)
) |>
  select(Outcome, Emotion, Contrast, Parameter, Unit, Difference, CI_low, CI_high,
         Difference_pct, CI_low_pct, CI_high_pct, pd, Credible, Effect) |>
  mutate(Contrast = as.character(Contrast)) |>
  arrange(Outcome, Emotion, Contrast, Parameter)
write.csv(results_contrasts, "../data/results_contrasts.csv", row.names = FALSE)

results_means <- bind_rows(lapply(reps, function(r) cbind(Outcome = r$diag$Model, r$means)))
write.csv(results_means, "../data/results_means.csv", row.names = FALSE)

diag_all <- bind_rows(lapply(reps, `[[`, "diag"))
make_tables(diag_all, names(diag_all), "Convergence of all models")
```

```{r}
#| label: fig-summary-beauty-reality
#| fig-width: 10
#| fig-height: 7
#| fig-cap: "Beauty (Phase 1, left) and Syntheticness (Phase 2, right) by label condition: observed ratings with model-implied CHOCO densities, marginal means with 95% CI above."
#| fig-alt: "Two panels of histograms with overlaid density curves in three colours, one per label condition."

(p_beauty | p_reality) +
  plot_layout(guides = "collect")
```

```{r}
#| label: fig-summary-effects
#| fig-width: 12
#| fig-height: 10
#| fig-cap: "Effect of the label condition on the main parameters of every model (posterior median difference with 95% CI, in percent of each scale's range). Rows: contrast; columns: outcome; y-axis: parameter. Large points with error bars are the overall contrasts, small shapes the contrasts within each stimulus emotion quadrant. Green = credibly positive, red = credibly negative, orange = CI includes 0. Gaze_Shift is omitted (no bounded scale)."
#| fig-alt: "Grid of dot-and-whisker plots, one cell per contrast and outcome, coloured by direction and credibility of the effect."

rez_con <- results_contrasts |>
  filter(Parameter %in% c("response", "mu", "confright", "confleft", "pzero"), Unit == "%") |>
  mutate(Difference = Difference_pct, CI_low = CI_low_pct, CI_high = CI_high_pct) |>
  mutate(Effect = fct_relevel(Effect, "Negative", "n.s.", "Positive"),
         Contrast = fct_relevel(Contrast, "AI-Generated - Human Original", "Human Forgery - Human Original", "AI-Generated - Human Forgery"))

rez_con |>
  filter(Emotion == "Overall") |>
  ggplot(aes(x = Difference, y = Parameter, color = Effect)) +
  geom_point(size = 2) +
  geom_errorbar(aes(xmin = CI_low, xmax = CI_high), width = 0.2) +
  geom_point(data = filter(rez_con, Emotion != "Overall"), aes(shape = Emotion), size = 2, position = position_nudge(y = 0.18)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  facet_grid(
  Contrast ~ Outcome,
  scales = "free_y",
  switch = "y"
) +
  scale_shape_manual(values = c("Positive - High intensity" = "square plus", "Positive - Low intensity" = "square",
                                "Negative - Low intensity" = "circle", "Negative - High intensity" = "circle plus")) +
  scale_y_discrete(position = "right") +
  scale_color_manual(values = c("Negative" = "#F44336", "n.s." = "#FF9800", "Positive" = "#4CAF50")) +
  theme_bw() +
  labs(
    title = "Effect Sizes by Contrast and Outcome",
    x = "Difference in % of the scale range (with 95% CI)",
    y = "Model Parameter"
  ) +
  theme(
  strip.placement = "outside",
  strip.background = element_rect(fill = "grey90"),
  strip.text.y.left = element_text(angle = 0),
  legend.position = "bottom"
)
```

```{r}
#| label: summary-table

credible_main <- results_contrasts |>
  filter(Emotion == "Overall", Credible, Parameter %in% c("response", "mu") | grepl("^response", Parameter)) |>
  mutate(shown_d = ifelse(Unit == "%", Difference_pct, Difference),
         shown_lo = ifelse(Unit == "%", CI_low_pct, CI_low),
         shown_hi = ifelse(Unit == "%", CI_high_pct, CI_high),
         Diff = insight::format_value(shown_d, zap_small = TRUE),
         CI = sprintf("[%s, %s]", insight::format_value(shown_lo, zap_small = TRUE), insight::format_value(shown_hi, zap_small = TRUE)),
         pd_fmt = insight::format_pd(pd, name = NULL)) |>
  select(Outcome, Contrast, Parameter, Diff, CI, Unit, pd_fmt, Effect)

make_tables(credible_main, names(credible_main),
            "Credible overall effects of the label on the main parameter of each model (response / mu), in % of the scale range")
```

## Animations

### Beauty

```{python}
#| warning: false
#| message: false
#| eval: false

import matplotlib.pyplot as plt
import matplotlib.animation as animation
import pandas as pd
import numpy as np


# ─── Data from R ──────────────────────────────────────────────────────────────
df_dens  = r.dens_beauty["dens"]
df_annot = r.dens_beauty["annot"]
df_par   = r.dens_beauty["par"]
df_task  = r.dftask

conditions = ["Human Original", "Human Forgery", "AI-Generated"]
colors = {
    "Human Original": "#F51D56",
    "Human Forgery":  "#F5A41D",
    "AI-Generated":   "#1D9AF5",
}

# ─── Figure — match minimal R aesthetic ───────────────────────────────────────
fig, ax = plt.subplots(figsize=(12, 8), dpi=150)
fig.patch.set_facecolor("white")
ax.set_facecolor("white")

max_y = df_dens["y"].max()

# Slider-scale band below y = 0 — tightened up vs. before.
slider_y = -max_y * 0.20     # vertical position of the slider track
pct_y    = slider_y - max_y * 0.09   # live % readout, just under the pill
anchor_y = slider_y - max_y * 0.20   # "Ugly" / "Beautiful" anchor labels
y_bottom = -max_y * 0.32             # margin below the anchor labels
ax.set_xlim(0, 1)
ax.set_ylim(y_bottom, max_y * 1.55)

for spine in ["top", "right", "bottom"]:
    ax.spines[spine].set_visible(False)
ax.spines["left"].set_color("#cccccc")
ax.spines["left"].set_linewidth(0.8)
ax.spines["left"].set_bounds(0, max_y * 1.55)

ax.tick_params(length=0, labelbottom=False)
ax.set_yticks([])
ax.set_xticks([0, 0.25, 0.50, 0.75, 1.0])
ax.set_ylabel("Likelihood of Response", fontsize=11, color="#333333", labelpad=8)
ax.grid(True, alpha=0.2, linestyle="-", color="#aaaaaa", linewidth=0.5, zorder=0)
ax.set_axisbelow(True)

ax.hist(df_task["Beauty"].dropna(), bins=47, density=True,
        alpha=0.1, color="gray", zorder=1)

# ─── Slider track + static anchors (the handle + % readout are animated, set up below) ─
ax.plot([0, 1], [slider_y, slider_y], color="#cccccc", linewidth=3,
        solid_capstyle="round", zorder=2, clip_on=False)
ax.plot([0, 1], [slider_y, slider_y], "o", markersize=6,
        color="#bbbbbb", zorder=3, clip_on=False)
ax.text(0, anchor_y, "Ugly", ha="center", va="top",
        fontsize=10.5, color="#666666", style="italic", clip_on=False)
ax.text(1, anchor_y, "Beautiful", ha="center", va="top",
        fontsize=10.5, color="#666666", style="italic", clip_on=False)

# ─── Frame plan ───────────────────────────────────────────────────────────────
F_LINE  = 55   # frames per density line
PAUSE   = 10   # quiet gap between phases
F_SLIDE = 40   # pointranges slide in
F_DROP  = 40   # vertical lines fall
F_DOT   = 18   # bottom dots grow in
TAIL    = 30   # hold at end

p1_end   = 3 * F_LINE                  # 165
p2_start = p1_end   + PAUSE            # 175
p2_end   = p2_start + F_SLIDE          # 215
p3_start = p2_end   + PAUSE            # 225
p3_end   = p3_start + F_DROP           # 265
p4_start = p3_end                      # 265  (dots pop as lines finish)
p4_end   = p4_start + F_DOT            # 283
N_FRAMES = p4_end   + TAIL             # 313

# Slider-handle intro: middle → wait → slow drag left → brief pause → drag
# right to settle on the Human Original mean.
HANDLE_START = 0.5
HANDLE_LEFT  = 0.15     # how far left it explores before committing
F_WAIT       = 40
F_DRAG_LEFT  = 80       # the first drag left
F_PAUSE_LEFT = 10
F_DRAG_RIGHT = 90       # On the way to the answer
h_wait_end  = F_WAIT
h_left_end  = h_wait_end  + F_DRAG_LEFT
h_pause_end = h_left_end  + F_PAUSE_LEFT
h_end       = h_pause_end + F_DRAG_RIGHT   
assert h_end <= N_FRAMES

# ─── Pre-process data per condition ───────────────────────────────────────────
dens  = {c: df_dens [df_dens ["Condition"] == c].sort_values("x").reset_index(drop=True) for c in conditions}
annot = {c: df_annot[df_annot["Condition"] == c].iloc[0]  for c in conditions}
par   = {c: df_par  [df_par  ["Condition"] == c].iloc[0]  for c in conditions}

# ─── Artists ──────────────────────────────────────────────────────────────────
# Phase 1: smooth density curves
dens_lines = {}
for cond in conditions:
    (l,) = ax.plot([], [], lw=2, color=colors[cond], zorder=3,
                   solid_capstyle="round", label=cond)
    dens_lines[cond] = l

# Phase 2: horizontal pointranges (line + centre dot)
pr_segs = {}
pr_dots = {}
for cond in conditions:
    (s,) = ax.plot([], [], lw=1.2, color=colors[cond], zorder=5, solid_capstyle="round")
    (d,) = ax.plot([], [], "o",    ms=0,  color=colors[cond], zorder=6)
    pr_segs[cond] = s
    pr_dots[cond] = d

# Phase 3: vertical dashed lines (left & right per condition)
vl_left  = {}
vl_right = {}
for cond in conditions:
    (ll,) = ax.plot([], [], "--", lw=0.9, color=colors[cond], alpha=0.75, zorder=4)
    (lr,) = ax.plot([], [], "--", lw=0.9, color=colors[cond], alpha=0.75, zorder=4)
    vl_left[cond]  = ll
    vl_right[cond] = lr

# Phase 4: bottom dots — clip_on=False so they're not half-swallowed by the axis
bdot_left  = {}
bdot_right = {}
for cond in conditions:
    (dl,) = ax.plot([], [], "o", color=colors[cond], zorder=7, clip_on=False)
    (dr,) = ax.plot([], [], "o", color=colors[cond], zorder=7, clip_on=False)
    bdot_left[cond]  = dl
    bdot_right[cond] = dr

ax.legend(
    handles=[dens_lines[c] for c in conditions],
    labels=conditions,
    frameon=False, loc="upper right",
    fontsize=9, title="Condition", title_fontsize=9.5,
)

handle_text = ax.text(HANDLE_START, slider_y, "Beauty", ha="center", va="center",
                       fontsize=9.5, color="white", fontweight="bold", zorder=5,
                       clip_on=False,
                       bbox=dict(boxstyle="round,pad=0.55", facecolor="#555555", edgecolor="none"))
pct_text = ax.text(HANDLE_START, pct_y, "50%", ha="center", va="top",
                    fontsize=9, color="#888888", clip_on=False)

# ─── Easing ───────────────────────────────────────────────────────────────────
def ease_out(t: float) -> float:
    t = max(0.0, min(1.0, t))
    return 1 - (1 - t) ** 2

def ease_in_out(t: float) -> float:
    t = max(0.0, min(1.0, t))
    return t * t * (3 - 2 * t)
  
# ─── Update ───────────────────────────────────────────────────────────────────
def update(frame: int):

    # ── Phase 1: draw density lines one by one, left→right ────────────────────
    for i, cond in enumerate(conditions):
        fs, fe = i * F_LINE, (i + 1) * F_LINE
        d = dens[cond]
        if frame >= fe:
            dens_lines[cond].set_data(d["x"], d["y"])
        elif frame >= fs:
            t = ease_out((frame - fs) / F_LINE)
            n = max(1, int(t * len(d)))
            dens_lines[cond].set_data(d["x"].iloc[:n], d["y"].iloc[:n])

    # ── Phase 2: all three pointranges slide in from the left simultaneously ───
    if frame >= p2_start:
        t = ease_out((frame - p2_start) / F_SLIDE)
        for cond in conditions:
            p = par[cond]
            low, high, mean, y_pr = p["Mean_low"], p["Mean_high"], p["Mean"], p["Mean_y"]
            cur_hi = low + t * (high - low)
            pr_segs[cond].set_data([low, cur_hi], [y_pr, y_pr])
            # Centre dot appears once the sliding front reaches the mean position
            frac = (mean - low) / max(high - low, 1e-9)
            if t >= frac:
                dot_t = ease_out((t - frac) / max(1.0 - frac, 1e-9))
                pr_dots[cond].set_data([mean], [y_pr])
                pr_dots[cond].set_markersize(5.5 * dot_t)
            else:
                pr_dots[cond].set_data([], [])

    # ── Phase 3: vertical lines fall downward from the density peak ────────────
    # Top stays pinned at the curve; bottom drops from peak → 0
    if frame >= p3_start:
        t = ease_out((frame - p3_start) / F_DROP)
        for cond in conditions:
            a = annot[cond]
            bot_r = a["right_y"] * (1 - t)   # bottom falls from right_y to 0
            bot_l = a["left_y"]  * (1 - t)
            vl_right[cond].set_data([a["right_x"], a["right_x"]], [bot_r, a["right_y"]])
            vl_left[cond].set_data( [a["left_x"],  a["left_x"] ], [bot_l, a["left_y"] ])

    # ── Phase 4: bottom dots grow in at y = 0 ─────────────────────────────────
    # Sizes mirror R's geom_point(aes(size = right_size * 6)) with scale_size_identity()
    # ggplot size in mm → matplotlib markersize in pts: × 2.835
    if frame >= p4_start:
        t = ease_out((frame - p4_start) / F_DOT)
        for cond in conditions:
            a = annot[cond]
            ms_r = a["right_size"] * 6 * 2.835 * t
            ms_l = a["left_size"]  * 6 * 2.835 * t
            bdot_right[cond].set_data([a["right_x"]], [0])
            bdot_right[cond].set_markersize(max(0.1, ms_r))
            bdot_left[cond].set_data( [a["left_x"]],  [0])
            bdot_left[cond].set_markersize(max(0.1, ms_l))
            
    # ── Slider handle: middle → wait → drag left → drag right to the mean ─────
    target_x = par["Human Original"]["Mean"]
    if frame <= h_wait_end:
        x = HANDLE_START
    elif frame <= h_left_end:
        t = ease_in_out((frame - h_wait_end) / F_DRAG_LEFT)
        x = HANDLE_START + t * (HANDLE_LEFT - HANDLE_START)
    elif frame <= h_pause_end:
        x = HANDLE_LEFT
    elif frame <= h_end:
        t = ease_in_out((frame - h_pause_end) / F_DRAG_RIGHT)
        x = HANDLE_LEFT + t * (target_x - HANDLE_LEFT)
    else:
        x = target_x

    handle_text.set_x(x)
    pct_text.set_x(x)
    pct_text.set_text(f"{x * 100:.0f}%")

    return (
        list(dens_lines.values())
        + list(pr_segs.values())
        + list(pr_dots.values())
        + list(vl_left.values())
        + list(vl_right.values())
        + list(bdot_left.values())
        + list(bdot_right.values())
        + [handle_text, pct_text]
    )

# ─── Build & save ─────────────────────────────────────────────────────────────
ani = animation.FuncAnimation(
    fig, update,
    frames=N_FRAMES,
    interval=40,
    blit=False,   # False is safer with clip_on=False artists
    repeat=False,
)

ani.save("figures/anim_beauty.gif", writer="pillow", fps=30, dpi=150)
plt.close()
print("✓ Saved anim_beauty.gif")
```

### Beauty by Emotion


```{python}
#| warning: false
#| message: false
#| eval: false

import matplotlib.pyplot as plt
from matplotlib.patches import Polygon
from matplotlib.colors import to_rgb
from PIL import Image
import pandas as pd
import numpy as np

# ─── Data from R ──────────────────────────────────────────────────────────────
df_dens_neutral  = r.dens_beauty["dens"]
df_annot_neutral = r.dens_beauty["annot"]
df_par_neutral   = r.dens_beauty["par"]

df_dens_emo  = r.dens_beauty_emo["dens"]
df_annot_emo = r.dens_beauty_emo["annot"]
df_par_emo   = r.dens_beauty_emo["par"]

df_task = r.dftask

conditions = ["Human Original", "Human Forgery", "AI-Generated"]
colors = {
    "Human Original": "#F51D56",
    "Human Forgery":  "#F5A41D",
    "AI-Generated":   "#1D9AF5",
}

# ─── Cycle order (loops back to Neutral) ──────────────────────────────────────
state_order = [
    "Neutral",
    "Positive - High intensity",
    "Positive - Low intensity",
    "Negative - Low intensity",
    "Negative - High intensity",
]
N_STATES = len(state_order)

quadrant_coords = {
    "Neutral":                    (0.0,   0.0),
    "Positive - High intensity":  (0.65,  0.65),
    "Positive - Low intensity":   (0.65, -0.65),
    "Negative - Low intensity":   (-0.65, -0.65),
    "Negative - High intensity":  (-0.65,  0.65),
}

quad_colors = {
    "Neutral":                    "#1a1a1a",
    "Positive - High intensity":  "#2E9E4F",
    "Positive - Low intensity":   "#2E9E4F",
    "Negative - Low intensity":   "#D1453D",
    "Negative - High intensity":  "#D1453D",
}

# ─── Build per-state, per-condition lookups ───────────────────────────────────
def build_state_dict(dens_df, annot_df, par_df, emotion=None):
    out = {}
    for cond in conditions:
        if emotion is None:
            d = dens_df[dens_df["Condition"] == cond].sort_values("x").reset_index(drop=True)
            a = annot_df[annot_df["Condition"] == cond].iloc[0]
            p = par_df[par_df["Condition"] == cond].iloc[0]
        else:
            d = dens_df[(dens_df["Condition"] == cond) & (dens_df["Emotion"] == emotion)] \
                    .sort_values("x").reset_index(drop=True)
            a = annot_df[(annot_df["Condition"] == cond) & (annot_df["Emotion"] == emotion)].iloc[0]
            p = par_df[(par_df["Condition"] == cond) & (par_df["Emotion"] == emotion)].iloc[0]
        out[cond] = {"x": d["x"].to_numpy(), "y": d["y"].to_numpy(), "annot": a, "par": p}
    return out

states = {"Neutral": build_state_dict(df_dens_neutral, df_annot_neutral, df_par_neutral, emotion=None)}
for emo in state_order[1:]:
    states[emo] = build_state_dict(df_dens_emo, df_annot_emo, df_par_emo, emotion=emo)

# ─── Global axis scaling ────────────────────────────────────────────────────
max_y = max(df_dens_neutral["y"].max(), df_dens_emo["y"].max())
all_par = pd.concat([df_par_neutral, df_par_emo], ignore_index=True, sort=False)
y_top = max(max_y * 1.35, all_par["Mean_y"].max() * 1.15)
y_bottom = -max_y * 0.12

# ─── Figure ────────────────────────────────────────────────────────────────────
fig, ax = plt.subplots(figsize=(11, 8), dpi=150)
fig.patch.set_facecolor("white")
ax.set_facecolor("white")

# reserve headroom above the axes so the raised legend/quadrant never clip
fig.subplots_adjust(top=0.97, bottom=0.10, left=0.07, right=0.95)

ax.set_xlim(0, 1)
ax.set_ylim(y_bottom, y_top)
for spine in ["top", "right", "bottom"]:
    ax.spines[spine].set_visible(False)
ax.spines["left"].set_color("#cccccc")
ax.spines["left"].set_linewidth(0.8)
ax.spines["left"].set_bounds(0, y_top)
ax.tick_params(length=0, labelbottom=True)
ax.set_yticks([])
ax.set_xticks([0, 0.25, 0.50, 0.75, 1.0])
ax.set_xticklabels(["0%\nUgly", "25%", "50%", "75%", "100%\nBeautiful"], fontsize=9.5)
ax.set_ylabel("Likelihood of Response", fontsize=11, color="#333333", labelpad=8, fontweight='bold')
ax.set_xlabel("Beauty Rating", fontsize=11, color="#333333", labelpad=10, fontweight='bold')
ax.grid(True, alpha=0.2, linestyle="-", color="#aaaaaa", linewidth=0.5, zorder=0)
ax.set_axisbelow(True)

if "Beauty" in df_task.columns:
    ax.hist(df_task["Beauty"].dropna(), bins=47, density=True,
            alpha=0.1, color="gray", zorder=1)

# ─── Artists: density curves, pointranges, vertical lines, bottom dots ────────
dens_lines, pr_segs, pr_dots = {}, {}, {}
vl_left, vl_right, bdot_left, bdot_right = {}, {}, {}, {}
for cond in conditions:
    (l,)  = ax.plot([], [], lw=2, color=colors[cond], zorder=3, solid_capstyle="round", label=cond)
    (s,)  = ax.plot([], [], lw=1.2, color=colors[cond], zorder=5, solid_capstyle="round")
    (d,)  = ax.plot([], [], "o", ms=5.5, color=colors[cond], zorder=6)
    (ll,) = ax.plot([], [], "--", lw=0.9, color=colors[cond], alpha=0.75, zorder=4)
    (lr,) = ax.plot([], [], "--", lw=0.9, color=colors[cond], alpha=0.75, zorder=4)
    (dl,) = ax.plot([], [], "o", color=colors[cond], zorder=7, clip_on=False)
    (dr,) = ax.plot([], [], "o", color=colors[cond], zorder=7, clip_on=False)
    dens_lines[cond] = l
    pr_segs[cond]    = s
    pr_dots[cond]    = d
    vl_left[cond]    = ll
    vl_right[cond]   = lr
    bdot_left[cond]  = dl
    bdot_right[cond] = dr

leg = ax.legend(
    handles=[dens_lines[c] for c in conditions], labels=conditions,
    frameon=False, loc="upper right", bbox_to_anchor=(0.995, 0.9),
    fontsize=9, title="Condition", title_fontsize=9.5,
)
leg.get_title().set_fontweight("bold")
leg.get_title().set_color("#333333")

# ─── Valence × Intensity quadrant inset ───────────────────────────────────────
QUAD_SIZE = 0.33
ax_quad = ax.inset_axes([-0.04, 0.86 - QUAD_SIZE, QUAD_SIZE, QUAD_SIZE])
ax_quad.set_xlim(-1.6, 1.6)
ax_quad.set_ylim(-1.6, 1.6)
ax_quad.set_aspect("equal")
ax_quad.set_facecolor("white")
ax_quad.patch.set_alpha(0.85)
for spine in ax_quad.spines.values():
    spine.set_visible(False)
ax_quad.set_xticks([])
ax_quad.set_yticks([])

ax_quad.set_title("Emotion", fontsize=9.5, fontweight="bold", color="#333333", pad=6)

ax_quad.annotate("", xy=(1.3, 0), xytext=(-1.3, 0),
                  arrowprops=dict(arrowstyle="-|>", color="#cccccc", lw=0.8,
                                   shrinkA=0, shrinkB=0))
ax_quad.annotate("", xy=(0, 1.3), xytext=(0, -1.3),
                  arrowprops=dict(arrowstyle="-|>", color="#cccccc", lw=0.8,
                                   shrinkA=0, shrinkB=0))

ax_quad.text(-1.4, 0.12, "Negative", ha="left", va="bottom", fontsize=7.6, color="#888888")
ax_quad.text(1.4, 0.12, "Positive", ha="right", va="bottom", fontsize=7.6, color="#888888")
ax_quad.text(0.12, 1.32, "High", ha="left", va="center", fontsize=7.6, color="#888888")
ax_quad.text(0.12, -1.32, "Low", ha="left", va="center", fontsize=7.6, color="#888888")

def star_vertices(cx, cy, outer_r, spikiness, n_points=5, rotation=np.pi / 2):
    spikiness = np.clip(spikiness, 0.0, 1.0)
    inner_r = outer_r * (1 - spikiness * 0.62)
    n = n_points * 2
    angles = rotation + np.arange(n) * (2 * np.pi / n)
    radii = np.where(np.arange(n) % 2 == 0, outer_r, inner_r)
    return np.column_stack([cx + radii * np.cos(angles), cy + radii * np.sin(angles)])

quad_dot = Polygon(star_vertices(0, 0, 0.20, 0.0), closed=True,
                    facecolor=quad_colors["Neutral"], edgecolor="white",
                    linewidth=0.7, zorder=6)
ax_quad.add_patch(quad_dot)

# ─── Easing / interpolation helpers ───────────────────────────────────────────
def ease_in_out(t: float) -> float:
    t = max(0.0, min(1.0, t))
    return t * t * (3 - 2 * t)

def lerp(a, b, t):
    return a + t * (b - a)

def lerp_color(c0, c1, t):
    rgb0, rgb1 = np.array(to_rgb(c0)), np.array(to_rgb(c1))
    return tuple(lerp(rgb0, rgb1, t))

# ─── Frame plan ───────────────────────────────────────────────────────────────
F_HOLD  = 45
F_TRANS = 55
SEG = F_HOLD + F_TRANS
N_FRAMES = N_STATES * SEG  # last morph lands back on Neutral -> seamless loop

# ─── Update (mutates all artists for a given frame) ───────────────────────────
def update(frame: int):
    s = frame // SEG
    local = frame % SEG
    cur_state = state_order[s]
    nxt_state = state_order[(s + 1) % N_STATES]
    t = 0.0 if local < F_HOLD else ease_in_out((local - F_HOLD) / F_TRANS)

    cur = states[cur_state]
    nxt = states[nxt_state]

    for cond in conditions:
        c0, c1 = cur[cond], nxt[cond]
        y = lerp(c0["y"], c1["y"], t)
        dens_lines[cond].set_data(c0["x"], y)

        a0, a1 = c0["annot"], c1["annot"]
        p0, p1 = c0["par"], c1["par"]

        rx = lerp(a0["right_x"], a1["right_x"], t)
        ry = lerp(a0["right_y"], a1["right_y"], t)
        lx = lerp(a0["left_x"],  a1["left_x"],  t)
        ly = lerp(a0["left_y"],  a1["left_y"],  t)
        r_size = lerp(a0["right_size"], a1["right_size"], t)
        l_size = lerp(a0["left_size"],  a1["left_size"],  t)

        vl_right[cond].set_data([rx, rx], [0, ry])
        vl_left[cond].set_data([lx, lx], [0, ly])
        bdot_right[cond].set_data([rx], [0])
        bdot_right[cond].set_markersize(max(0.1, r_size * 6 * 2.835))
        bdot_left[cond].set_data([lx], [0])
        bdot_left[cond].set_markersize(max(0.1, l_size * 6 * 2.835))

        mean   = lerp(p0["Mean"], p1["Mean"], t)
        m_low  = lerp(p0["Mean_low"], p1["Mean_low"], t)
        m_high = lerp(p0["Mean_high"], p1["Mean_high"], t)
        m_y    = lerp(p0["Mean_y"], p1["Mean_y"], t)

        pr_segs[cond].set_data([m_low, m_high], [m_y, m_y])
        pr_dots[cond].set_data([mean], [m_y])

    qx0, qy0 = quadrant_coords[cur_state]
    qx1, qy1 = quadrant_coords[nxt_state]
    qx, qy = lerp(qx0, qx1, t), lerp(qy0, qy1, t)

    col = lerp_color(quad_colors[cur_state], quad_colors[nxt_state], t)
    spikiness = np.clip(qy / 0.65, 0.0, 1.0)
    quad_dot.set_xy(star_vertices(qx, qy, 0.20, spikiness))
    quad_dot.set_facecolor(col)

# Manual render loop with a fixed global GIF palette 
def render_frame_image():
    fig.canvas.draw()
    buf = np.asarray(fig.canvas.buffer_rgba())
    return Image.fromarray(buf).convert("RGB")

# Sample a handful of frames spanning every hold + transition, so the shared
# palette actually contains black, green, red, and the in-between hues.
calibration_frames = sorted(set(
    [0, N_FRAMES - 1] +
    [i * SEG for i in range(N_STATES)] +
    [i * SEG + F_HOLD // 2 for i in range(N_STATES)] +
    [i * SEG + F_HOLD + F_TRANS // 2 for i in range(N_STATES)]
))
calib_imgs = []
for f in calibration_frames:
    update(f)
    calib_imgs.append(render_frame_image())

calib_strip = Image.new("RGB", (calib_imgs[0].width, calib_imgs[0].height * len(calib_imgs)))
for i, im_ in enumerate(calib_imgs):
    calib_strip.paste(im_, (0, i * im_.height))
base_palette_img = calib_strip.quantize(colors=256, method=Image.MEDIANCUT)

# Now render every real frame and quantize it against that ONE shared palette.
# dither=Image.NONE keeps flat color regions (backgrounds, lines) perfectly
# stable frame-to-frame -- this is what actually removes the flicker.
quantized_frames = []
for frame in range(N_FRAMES):
    update(frame)
    img = render_frame_image()
    quantized_frames.append(img.quantize(palette=base_palette_img, dither=Image.NONE))

# NOTE: do NOT pass optimize=True below -- it can silently re-quantize frames
# per-frame and reintroduce the exact flicker we just fixed.
quantized_frames[0].save(
    "figures/anim_beauty_emotion.gif",
    save_all=True,
    append_images=quantized_frames[1:],
    duration=33,   # ~30fps
    loop=0,
    disposal=2,
)
plt.close()
print("✓ Saved anim_beauty_emotion.gif")
```

