---
title: "FakeArt - Memory Results"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Estimates are computed on the cluster (`./hpc extract`, see server/estimates.R) and read from models/estimates/. -->

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)

df <- read.csv("../data/data_memory_task.csv") |>
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated", "New Items"),
         AnswerCondition = fct_relevel(AnswerCondition, "Human Original", "Human Forgery", "AI-Generated", "Not recognized"),
         AnswerBelief = fct_relevel(AnswerBelief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "Not recognized"),
         Belief = fct_relevel(Belief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "None"))

dfsub <- read.csv("../data/data_participants.csv") |> 
  filter(Participant %in% df$Participant)

cols <- c(
  # Condition
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "AI Original" = "#1D9AF5",
  "AI Copy" = "#4CAF50",
  "Not recognized" = "#607D8B",
  # Style
  "Abstract and Avant-garde" = "#E41A1C", 
  "Classical" = "#377EB8", 
  "Impressionist and Expressionist" = "#4DAF4A",
  "Romantic and Realism" = "#FF7F00"
)

source("server/estimates.R") # memory_info
source("report.R")           # make_asis(), make_tables(), make_markdown(), read_estimates()

estimates <- read_estimates(names(memory_info))
provenance_table(estimates)
```

## How to read this report

Four Bayesian categorical mixed models of what participants remembered in the
follow-up session (220 participants × 96 items = 21,120 rows: 48 seen in Phase 1,
48 new).

| model | outcome | predictor | levels of the predictor |
| --- | --- | --- | --- |
| **Memory of Condition** | `AnswerCondition`: which label the participant recalls being shown | `Condition`: the label actually shown in Phase 1 | Human Original, Human Forgery, AI-Generated, **New Items** (never seen) |
| **Memory of Beliefs** | `AnswerBelief`: what the participant recalls believing the artwork was | `Belief`: what they actually reported believing in Phase 2 | Human Original, Human Forgery, AI Original, AI Copy, None |
| **Memory of the Condition by Belief** | `AnswerCondition` | `Condition` **+** `Belief` (additive; old items with a recorded belief only, 10,416 rows) | Belief: Human Original, Human Forgery, AI Original, AI Copy |
| **Memory by Phase-1 Appraisal** (MemoryAppraisal, its own section) | `AnswerCondition` | `Condition` + Phase-1 beauty and valence, each centred within participant, with quadratic terms (old items only, 10,560 rows) | continuous |
| **Memory of Beliefs, controlling the appraisal** (MemoryBeliefAppraisal) | `AnswerBelief` | `Belief` + Phase-1 beauty, follow-up beauty and self-relevance of the artwork, each centred within participant (old items with a recorded belief, 10,416 rows) | Belief levels as above; ratings continuous |
| **Memory of the Condition by Belief, controlling the appraisal** (MemoryConditionAppraisal) | `AnswerCondition` | `Condition` + `Belief` + the same three ratings (same rows) | as above |
| **Durability** (Beauty2Recognition, Beauty2Reality; their own section) | `Beauty2`, the follow-up beauty slider (CHOCO) | `Condition * Recognition` (old items, 10,560 rows); `Condition * Reality_w + Beauty_w` (Phase-2 syntheticness and Phase-1 beauty, centred within participant; 217 participants) | Recognition Yes / No; continuous |

All outcomes include **Not recognized** (item judged "new"): correct for
`New Items`, forgetting for the seen levels. The third model asks whether the
recalled label is reconstructed from one's own Phase-2 belief: its `Belief`
means and contrasts are averaged over the label actually shown (computed over
the observed trials, see `memory_observed()` in `server/estimates.R`), so a
`Belief` effect is the effect of the belief with the label held constant.
The two "controlling the appraisal" models (2026-09-26) ask whether those
`Belief` effects are memory of the belief or a fresh inference from the
current impression of the work: follow-up beauty and self-relevance were rated
right before the memory questions, Phase-1 beauty is what drove the belief in
the first place. Their `Belief` contrasts are computed the same way (ratings
at their observed values); the ratings' own effects come from population-level
predictions over a grid of each rating (`by_rating`, as MemoryAppraisal).
The durability models ask whether the (null) label effect on follow-up beauty
hides a residual effect among the artworks still recognised, or an effect
carried by the syntheticness belief the label had induced in Phase 2.

Each section: figure of the probability of each answer per level, convergence,
marginal means, contrasts (coloured tables of interest + the complete set), and
an auto-generated summary. Every table has a folded Markdown twin; the Summary
section writes `data/results_memory_contrasts.csv` and
`data/results_memory_means.csv`.

Estimates are probabilities and contrasts (`Level1 - Level2`) differences of
probabilities, reported in percentage points as posterior medians with 95% CI
and probability of direction (`pd`). "Credible" = CI excludes 0 (no
multiplicity correction).

## Delay

```{r}
dfsub |> 
  ggplot(aes(x=Delay)) +
  geom_histogram(bins=30) +
  theme_minimal()
```

The mean and median days between the two experiments were `r insight::format_value(mean(dfsub$Delay))` and `r insight::format_value(median(dfsub$Delay))`, respectively.

## Memory of Condition

### Main Model

```{r}
# Dodging order of the answers in the figures
make_group <- function(resp, covariate = NULL) {
  group <- case_when(  
    resp == "Not recognized" ~ 0,
    resp == "Human Original" ~ 1,
    resp == "AI-Generated" ~ 2,
    resp == "AI Original" ~ 2,
    resp == "Human Forgery" ~ 3,
    resp == "AI Copy" ~ 4,
    .default = NA)
  
  if(!is.null(covariate)) {
    covariate <- insight::format_value(normalize(covariate), style_positive="plus")
    group <- paste0(group, covariate)
  }
  group
}

dat_cond1 <- estimates$MemoryCondition$means |>
  mutate(group = make_group(Response))

p_cond1 <- dat_cond1 |> 
  ggplot(aes(x=Condition,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1,
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Experimental Condition",
       title = "Memory of the Experimental Condition") +
  theme_minimal() 
p_cond1
```

```{r}
make_contrasts <- function(c, answer=NULL, condition=NULL, title="Marginal Contrasts") {

  if(!is.null(answer)) {
    c <- filter(c, str_detect(Response1, answer) & str_detect(Response2, answer))
  }
  if(!is.null(condition)) {
    c <- filter(c, str_detect(Level1, condition) & str_detect(Level2, condition))
  }

  # Collapse a constant Response/Level pair into one Category column
  if(length(unique(c$Response1)) == 1 & all(c$Response1 == c$Response2)) {
    c <- cbind(data.frame("Category" = c$Response1[1]), c)
    c$Response1 <- NULL
    c$Response2 <- NULL
  }
  if(length(unique(c$Level1)) == 1 & all(c$Level1 == c$Level2)) {
    c <- cbind(data.frame("Category" = c$Level1[1]), c)
    c$Level1 <- NULL
    c$Level2 <- NULL
  }

  c <- arrange(c, desc(abs(Median)))
  t <- format_table(c, zap_small = TRUE)

  t$effectsize <- as.numeric(c$Median)
  t$sig <- as.numeric(c$pd)

  g <- gt::gt(t) |>
    gt::data_color(columns = "effectsize", target_columns = "Median", method = "numeric",
palette = c("red", "red", "white", "green", "green"), domain = c(-0.7, 0.7)) |>
    gt::data_color(columns = "sig", target_columns = "pd", fn = \(x) {
      ifelse(x > 0.99, "#FFC107", ifelse(x > 0.97, "#FFEB3B", ifelse(x > 0.95, "#FFF59D", "white")))
    }) |>
    gt::cols_hide(c("effectsize", "sig")) |>
    gt::tab_header(title = title)

  # Markdown twin: colour coding replaced by an Effect column
  md <- t[setdiff(names(t), c("effectsize", "sig"))]
  md$Effect <- ifelse(sign(c$CI_low) != sign(c$CI_high), "n.s.",
                      ifelse(c$Median < 0, "Negative", "Positive"))
  make_asis(as.character(knitr::knit_print(g)), "", make_markdown(md, title), "")
}

# Convergence, marginal means and the complete contrast set
make_memory_tables <- function(est) {
  means_fmt <- as.data.frame(est$means)[c(est$by, "Response", "Median", "CI_low", "CI_high")]
  num <- vapply(means_fmt, is.numeric, logical(1))
  means_fmt[num] <- lapply(means_fmt[num], insight::format_value, zap_small = TRUE)

  all_con <- as.data.frame(est$contrasts)
  all_con$Effect <- ifelse(sign(all_con$CI_low) != sign(all_con$CI_high), "n.s.",
                           ifelse(all_con$Median < 0, "Negative", "Positive"))
  all_fmt <- all_con[c("Level1", "Response1", "Level2", "Response2", "Median", "CI_low", "CI_high", "pd", "Effect")]
  n <- vapply(all_fmt, is.numeric, logical(1))
  all_fmt[n] <- lapply(all_fmt[n], insight::format_value, zap_small = TRUE)

  make_asis(
    make_tables(est$diag,
                c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws",
                  "Max_Rhat", "Min_ESS_ratio", "Divergent_pct", "Criterion"),
                sprintf("%s: convergence", est$label)),
    make_tables(means_fmt, names(means_fmt),
                sprintf("%s: probability of each answer per %s (marginal means)", est$label, est$by)),
    # Markdown only (120-300 rows)
    make_markdown(all_fmt, sprintf("%s: all %d contrasts", est$label, nrow(all_fmt)))
  )
}

# Generated summary of the credible same-answer contrasts
make_memory_summary <- function(est) {
  d <- as.data.frame(est$contrasts)
  d <- d[d$Response1 == d$Response2, ]
  d$Credible <- sign(d$CI_low) == sign(d$CI_high)
  pp <- function(x) insight::format_value(100 * x)
  out <- c(sprintf(
    "**%s.** Each row of the model is the probability of one answer. The differences below are between %s levels *within* the same answer, in percentage points, as posterior medians with 95%% CI; `pd` is the probability of direction. An effect is called credible when the CI excludes 0. Contrasts *across* answers are in the full table above.",
    est$label, est$by), "")
  for (r in unique(d$Response1)) {
    dr <- d[d$Response1 == r, ]
    cred <- dr[dr$Credible, ]
    if (nrow(cred) == 0) {
      out <- c(out, sprintf("- **%s**: no credible difference between any pair of %s levels.", r, est$by))
      next
    }
    cred <- cred[order(-abs(cred$Median)), ]
    out <- c(out, sprintf("- **%s**: %s.%s", r,
      paste(sprintf("%s - %s %s pp [%s, %s]", cred$Level1, cred$Level2,
                    pp(cred$Median), pp(cred$CI_low), pp(cred$CI_high)), collapse = "; "),
      if (nrow(cred) < nrow(dr)) sprintf(" The other %d pair(s) are not credible.", nrow(dr) - nrow(cred)) else ""))
  }
  make_asis("", '::: {.callout-tip title="Summary of credible effects (generated from the tables above)"}',
            "", out, "", ":::", "")
}
```

```{r}
make_memory_tables(estimates$MemoryCondition)
```

```{r}
c <- estimates$MemoryCondition$contrasts
make_contrasts(c, answer="Not recognized",
               title="Memory of Condition: forgetting ('Not recognized') by condition")
make_contrasts(c, condition="Human Original",
               title="Memory of Condition: which answer, within the Human Original condition")
make_contrasts(c, condition="New Items",
               title="Memory of Condition: which answer, within the New Items condition")
```

```{r}
make_memory_summary(estimates$MemoryCondition)
```


## Memory of Beliefs

### Main Model

```{r}
dat_belief1a <- estimates$MemoryBelief$means |>
  mutate(group = make_group(Response))

p_belief1a <- dat_belief1a |> 
  ggplot(aes(x=Belief,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1, 
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Original Belief",
       title = "Memory of Beliefs") +
  theme_minimal()
p_belief1a
```

```{r}
make_memory_tables(estimates$MemoryBelief)
```

```{r}
c <- estimates$MemoryBelief$contrasts
make_contrasts(c, answer="Not recognized",
               title="Memory of Beliefs: forgetting ('Not recognized') by original belief")
make_contrasts(c, condition="Human Original",
               title="Memory of Beliefs: which answer, within the Human Original belief")
```

```{r}
make_memory_summary(estimates$MemoryBelief)
```

## Memory of the Condition by Belief

Does the recalled label follow what the participant came to believe about the
artwork (Phase 2), once the label actually shown is controlled for?

```{r}
dat_cb <- estimates$MemoryConditionBelief$means |>
  mutate(group = make_group(Response))

dat_cb |>
  ggplot(aes(x = Belief, y = Median, color = Response)) +
  geom_line(aes(group = group), position = position_dodge(width = 0.1), linewidth = 1,
            show.legend = FALSE) +
  geom_pointrange(aes(group = group, ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0, 1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "Proportion of answers (averaged over the label shown)", color = "Recalled label",
       x = "Own belief in Phase 2", title = "Memory of the Condition by Belief") +
  theme_minimal()
```

```{r}
make_memory_tables(estimates$MemoryConditionBelief)
```

```{r}
c <- estimates$MemoryConditionBelief$contrasts
make_contrasts(c, answer = "AI-Generated",
               title = "Memory of the Condition by Belief: recalling 'AI-Generated', by own belief")
make_contrasts(c, answer = "Human Original",
               title = "Memory of the Condition by Belief: recalling 'Human Original', by own belief")
make_contrasts(c, answer = "Human Forgery",
               title = "Memory of the Condition by Belief: recalling 'Human Forgery', by own belief")
```

Among **recognised** items only (each answer probability divided by the
probability of recognising the item, per draw), and the difference from the
Human Original belief:

```{r}
#| results: asis

D <- estimates$MemoryConditionBelief$draws # draws x Belief x answer
rec <- 1 - D[, , "Not recognized"]
describe_pp <- function(x) {
  ci <- bayestestR::eti(x)
  data.frame(Median = 100 * median(x), CI_low = 100 * ci$CI_low, CI_high = 100 * ci$CI_high,
             pd = as.numeric(bayestestR::p_direction(x)))
}
dat_rec <- bind_rows(lapply(setdiff(dimnames(D)[[3]], "Not recognized"), function(a) {
  bind_rows(lapply(dimnames(D)[[2]], function(b) {
    p <- D[, b, a] / rec[, b]
    p0 <- D[, "Human Original", a] / rec[, "Human Original"]
    cbind(data.frame(Answer = a, Belief = b),
          setNames(describe_pp(p)[1:3], c("P", "P_low", "P_high")),
          describe_pp(p - p0))
  }))
})) |>
  mutate(P = sprintf("%s [%s, %s]", insight::format_value(P), insight::format_value(P_low), insight::format_value(P_high)),
         Diff = ifelse(Belief == "Human Original", "", insight::format_value(Median)),
         CI = ifelse(Belief == "Human Original", "", sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high))),
         pd_fmt = ifelse(Belief == "Human Original", "", insight::format_pd(pd, name = NULL)),
         Effect = ifelse(Belief == "Human Original", "",
                         ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")))) |>
  rename(Contrast = Answer)
make_tables(dat_rec, c("Contrast", "Belief", "P", "Diff", "CI", "pd_fmt", "Effect"),
            "Memory of the Condition by Belief: P(recalled label | recognised), in %, and difference from the Human Original belief (percentage points)")
```

```{r}
make_memory_summary(estimates$MemoryConditionBelief)
```

## Memory or Re-inference? Controlling for the Appraisal

The recalled belief follows the actual Phase-2 belief (Memory of Beliefs),
and the recalled label follows it too (Memory of the Condition by Belief).
But the belief was itself driven by beauty ("beautiful = human",
`5_realitydeterminants.qmd`), and beauty and self-relevance are rated again
right before the memory questions, so both correspondences could be fresh
inferences from the current impression of the work rather than memories.
**MemoryBeliefAppraisal** and **MemoryConditionAppraisal** (`server/models.R`)
add the Phase-1 beauty (what drove the belief), the follow-up beauty and the
self-relevance of the artwork (the current impression), centred within
participant, to the two models above. A `Belief` effect that survives them
is what memory has to explain; a rating effect on the answer, with the belief
held constant, is re-inference.

```{r}
# Same-answer cells the manuscript quotes, in the two models with and without
# the ratings: Level1 - Level2 on the probability of `Response`, in
# percentage points. memory_observed() stores each pair once, in either
# orientation, so the sign is flipped where needed.
cell_contrast <- function(est, level1, level2, response) {
  c <- as.data.frame(est$contrasts)
  r <- c[c$Response1 == response & c$Response2 == response &
           ((c$Level1 == level1 & c$Level2 == level2) | (c$Level1 == level2 & c$Level2 == level1)), ]
  if (nrow(r) != 1) return(data.frame(Median = NA, CI_low = NA, CI_high = NA, pd = NA))
  k <- if (r$Level1 == level1) 1 else -1
  data.frame(Median = k * r$Median, CI_low = min(k * r$CI_low, k * r$CI_high),
             CI_high = max(k * r$CI_low, k * r$CI_high), pd = r$pd)
}
compare_models <- function(cells, with, without) {
  fmt <- function(x) sprintf("%s [%s, %s]", insight::format_value(100 * x$Median),
                             insight::format_value(100 * x$CI_low), insight::format_value(100 * x$CI_high))
  eff <- function(x) ifelse(sign(x$CI_low) != sign(x$CI_high), "n.s.", ifelse(x$Median < 0, "Negative", "Positive"))
  bind_rows(lapply(seq_len(nrow(cells)), function(i) {
    a <- cell_contrast(without, cells$Level1[i], cells$Level2[i], cells$Response[i])
    b <- cell_contrast(with, cells$Level1[i], cells$Level2[i], cells$Response[i])
    data.frame(Answer = cells$Response[i], Contrast = paste(cells$Level1[i], "-", cells$Level2[i]),
               Without = fmt(a), Effect_without = eff(a), With = fmt(b), Effect_with = eff(b))
  }))
}
rating_labels <- c(Beauty_w = "Phase-1 beauty", Beauty2_w = "Follow-up beauty", SR_w = "Self-relevance")
rating_cols <- c("Phase-1 beauty" = "#E91E63", "Follow-up beauty" = "#9C27B0", "Self-relevance" = "#26A69A")
fmt_eff <- function(d) {
  d |> mutate(Effect = ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")),
              Diff = insight::format_value(Median),
              CI = sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high)),
              pd_fmt = insight::format_pd(pd, name = NULL))
}
rating_tables <- function(est, what) {
  fixed <- est$by_rating$fixed |>
    filter(str_detect(Parameter, "Beauty_w|Beauty2_w|SR_w")) |>
    mutate(Answer = str_match(Parameter, "^b_mu([^_]+)_")[, 2],
           Term = rating_labels[str_remove(Parameter, "^b_mu[^_]+_")]) |>
    fmt_eff()
  eff <- memory_grid_effects(est$by_rating)$effects |>
    filter(Type == "unique", Effect %in% c("-2 SD", "+2 SD")) |>
    mutate(Predictor = rating_labels[Predictor], At = Effect) |>
    fmt_eff()
  make_asis(
    make_tables(fixed, c("Answer", "Term", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: fixed effects of the ratings (log-odds of each answer vs. the reference answer, per full range of the rating; belief and label held constant)", what)),
    make_tables(eff, c("Outcome", "Predictor", "At", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: P(recognised) and P(answer | recognised) at -2 / +2 SD of the rating minus at the participant's mean (other ratings at the mean, averaged over the beliefs and labels), percentage points", what))
  )
}
plot_rating_curves <- function(est, title) {
  memory_grid_effects(est$by_rating)$curves |>
    filter(Type == "unique", abs(x) <= 0.5) |>
    mutate(Predictor = rating_labels[Predictor]) |>
    ggplot(aes(x = 100 * x, y = Median, color = Predictor, fill = Predictor)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) +
    facet_wrap(~fct_relevel(Outcome, "P(recognised)"), scales = "free_y", nrow = 1) +
    scale_color_manual(values = rating_cols) +
    scale_fill_manual(values = rating_cols) +
    labs(x = "Rating relative to the participant's mean (points of the scale)", y = "Probability (%)",
         color = NULL, fill = NULL, title = title,
         caption = "Population-level predictions (random effects at 0; other ratings at the participant's mean; averaged over the beliefs and labels) with 95% CI.") +
    theme_minimal() +
    theme(legend.position = "top", strip.text = element_text(face = "bold", size = 8))
}
```

### Memory of Beliefs, controlling the appraisal

```{r}
estimates$MemoryBeliefAppraisal$means |>
  mutate(group = make_group(Response)) |>
  ggplot(aes(x = Belief, y = Median, color = Response)) +
  geom_line(aes(group = group), position = position_dodge(width = 0.1), linewidth = 1, show.legend = FALSE) +
  geom_pointrange(aes(group = group, ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1), key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0, 1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "Proportion of answers (ratings at their observed values)", color = "Answer", x = "Original Belief",
       title = "Memory of Beliefs, controlling the appraisal") +
  theme_minimal()
```

```{r}
make_memory_tables(estimates$MemoryBeliefAppraisal)
```

```{r}
#| results: asis

belief_cells <- tribble(
  ~Level1, ~Level2, ~Response,
  "AI Original", "Human Original", "AI Original",
  "AI Original", "Human Forgery", "AI Original",
  "AI Original", "Human Original", "Human Original",
  "Human Original", "Human Forgery", "Human Original",
  "Human Forgery", "Human Original", "Human Forgery",
  "AI Copy", "AI Original", "AI Copy"
)
make_asis(make_tables(
  compare_models(belief_cells, estimates$MemoryBeliefAppraisal, estimates$MemoryBelief),
  c("Answer", "Contrast", "Without", "Effect_without", "With", "Effect_with"),
  "Memory of Beliefs: the same-answer Belief contrasts (percentage points) without and with the three ratings in the model"))
```

```{r}
#| results: asis

rating_tables(estimates$MemoryBeliefAppraisal, "Memory of Beliefs, controlling the appraisal")
```

```{r}
#| fig-width: 12
#| fig-height: 4

plot_rating_curves(estimates$MemoryBeliefAppraisal, "Recalled belief by the ratings of the artwork (belief held constant)")
```

```{r}
make_memory_summary(estimates$MemoryBeliefAppraisal)
```

### Memory of the Condition by Belief, controlling the appraisal

```{r}
estimates$MemoryConditionAppraisal$means |>
  mutate(group = make_group(Response)) |>
  ggplot(aes(x = Belief, y = Median, color = Response)) +
  geom_line(aes(group = group), position = position_dodge(width = 0.1), linewidth = 1, show.legend = FALSE) +
  geom_pointrange(aes(group = group, ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1), key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0, 1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "Proportion of answers (averaged over the label shown; ratings observed)", color = "Recalled label",
       x = "Own belief in Phase 2", title = "Memory of the Condition by Belief, controlling the appraisal") +
  theme_minimal()
```

```{r}
make_memory_tables(estimates$MemoryConditionAppraisal)
```

```{r}
#| results: asis

label_cells <- tribble(
  ~Level1, ~Level2, ~Response,
  "AI Original", "Human Original", "AI-Generated",
  "AI Original", "Human Original", "Human Original",
  "Human Forgery", "Human Original", "Human Forgery",
  "AI Original", "Human Original", "Not recognized"
)
make_asis(make_tables(
  compare_models(label_cells, estimates$MemoryConditionAppraisal, estimates$MemoryConditionBelief),
  c("Answer", "Contrast", "Without", "Effect_without", "With", "Effect_with"),
  "Memory of the Condition by Belief: the same-answer Belief contrasts (percentage points, label shown held constant) without and with the three ratings in the model"))
```

```{r}
#| results: asis

rating_tables(estimates$MemoryConditionAppraisal, "Memory of the Condition by Belief, controlling the appraisal")
```

```{r}
#| fig-width: 12
#| fig-height: 4

plot_rating_curves(estimates$MemoryConditionAppraisal, "Recalled label by the ratings of the artwork (label shown and belief held constant)")
```

```{r}
make_memory_summary(estimates$MemoryConditionAppraisal)
```

```{r}
#| results: asis

# Generated reading of the two comparisons
reading <- function(cells, with, without) {
  vapply(seq_len(nrow(cells)), function(i) {
    a <- cell_contrast(without, cells$Level1[i], cells$Level2[i], cells$Response[i])
    b <- cell_contrast(with, cells$Level1[i], cells$Level2[i], cells$Response[i])
    sprintf("%s (%s - %s): %s -> %s pp, %s", cells$Response[i], cells$Level1[i], cells$Level2[i],
            insight::format_value(100 * a$Median), insight::format_value(100 * b$Median),
            ifelse(sign(b$CI_low) != sign(b$CI_high), "not credible with the ratings", "still credible"))
  }, character(1))
}
make_asis("", '::: {.callout-tip title="Memory or re-inference? (generated)"}', "",
          "**Recalled belief** (Belief contrasts without -> with the three ratings):", "",
          paste0("- ", reading(belief_cells, estimates$MemoryBeliefAppraisal, estimates$MemoryBelief)), "",
          "**Recalled label** (label shown held constant):", "",
          paste0("- ", reading(label_cells, estimates$MemoryConditionAppraisal, estimates$MemoryConditionBelief)), "",
          "A Belief contrast that keeps its size with the ratings in the model is not explained by the current impression of the work (follow-up beauty, self-relevance) nor by the Phase-1 appraisal that produced the belief; one that shrinks to zero was re-inference. The rating tables say which impression the answers follow: the current one (follow-up beauty, self-relevance) or the Phase-1 one.",
          "", ":::", "")
```

## Memory by Phase-1 Appraisal

Hypothesis 1 of the follow-up preregistration (`memory/ethics/preregistration.md`,
after Lee et al., 2023; Salgues et al., 2024): artworks that received
**extreme** aesthetic ratings in Phase 1, positive *or* negative, are better
recognised than those rated neutrally -- a U-shaped relation that a linear
predictor cannot show. The Phase-1 ratings were given ~47 days before the
memory test and exist for old items only, so they speak to what was encoded;
the follow-up ratings (self-relevance, follow-up beauty) were given in the
same trial as the recognition judgment and raise false alarms as much as
hits (`6_selfrelevance.qmd`, section C).

### Observed

```{r}
#| fig-width: 10
#| fig-height: 4.5

old <- df |>
  filter(Type == "Old", !is.na(Beauty), !is.na(Valence)) |>
  mutate(Beauty_w = Beauty - mean(Beauty), Valence_w = Valence - mean(Valence), .by = "Participant")
hit_bins <- bind_rows(
  mutate(old, Rating = "Beauty", Scale = "Absolute (% of the scale)",
         Bin = cut(100 * Beauty, c(-1, 0, 15, 30, 45, 55, 70, 85, 99.99, 100))),
  mutate(old, Rating = "Valence", Scale = "Absolute (% of the scale)",
         Bin = cut(100 * Valence, c(-1, 1, 20, 40, 60, 80, 99, 100))),
  mutate(old, Rating = "Beauty", Scale = "Relative to the participant's mean (points)",
         Bin = cut(100 * Beauty_w, c(-100, -50, -35, -20, -10, 0, 10, 20, 35, 100))),
  mutate(old, Rating = "Valence", Scale = "Relative to the participant's mean (points)",
         Bin = cut(100 * Valence_w, c(-100, -50, -33, -17, 0, 17, 33, 50, 100)))
) |>
  summarise(x = mean(100 * ifelse(str_starts(Scale, "Absolute"), ifelse(Rating == "Beauty", Beauty, Valence),
                                  ifelse(Rating == "Beauty", Beauty_w, Valence_w))),
            p = mean(Recognition == "Yes"), n = n(), .by = c(Rating, Scale, Bin)) |>
  mutate(SE = sqrt(p * (1 - p) / n))

ggplot(hit_bins, aes(x = x, y = 100 * p, color = Rating)) +
  geom_hline(yintercept = 100 * mean(old$Recognition == "Yes"), linetype = "dotted", color = "grey60") +
  geom_line(alpha = 0.6) +
  geom_pointrange(aes(ymin = 100 * (p - 1.96 * SE), ymax = 100 * (p + 1.96 * SE), size = n)) +
  facet_wrap(~Scale, scales = "free_x") +
  scale_size(range = c(0.1, 0.7), guide = "none") +
  scale_color_manual(values = c(Beauty = "#E91E63", Valence = "#FF9800")) +
  labs(x = "Phase-1 rating", y = "Recognised at follow-up (%)", color = NULL,
       caption = "Old items; observed hit rates per bin with 95% CI (not model-based). Dotted line: overall hit rate. Point size: number of trials.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold"))
```

### Model

**MemoryAppraisal** (`server/models.R`): the recalled label, with "Not
recognized" carrying recognition as in the models above, on the label shown
and on Phase-1 beauty and valence, each centred within participant and
entered with a quadratic term (old items only; participant intercepts and
linear slopes, item intercepts). Beauty and valence correlate strongly
within participant, so the **unique** curves move one rating with the other
held at the participant's mean, and the **joint** curves move it with the
other following along their within-person regression (how the two usually
co-vary). "Extremity" is the average of the -2 SD and +2 SD predictions
minus the prediction at the mean (> 0: both extremes above the mean, a U);
"Asymmetry" is +2 SD minus -2 SD.

```{r}
#| results: asis

appraisal_ready <- file.exists("models/estimates/MemoryAppraisal.rds")
if (!appraisal_ready) {
  make_asis("", '::: {.callout-warning title="Estimates not available yet"}',
            "`MemoryAppraisal`: in `analysis/server`, `./hpc combine MemoryAppraisal` (check 4,000 draws), `./hpc extract MemoryAppraisal`, then `./hpc pull 'estimates/MemoryAppraisal.rds'`.",
            ":::", "")
} else {
  est_app <- read_estimates("MemoryAppraisal")$MemoryAppraisal
  app <- memory_grid_effects(est_app)
  fixed <- est_app$fixed |>
    filter(str_detect(Parameter, "Beauty|Valence")) |>
    mutate(Answer = str_match(Parameter, "^b_mu([^_]+)_")[, 2],
           Term = str_remove(Parameter, "^b_mu[^_]+_"),
           Effect = ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")),
           Diff = insight::format_value(Median),
           CI = sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high)),
           pd_fmt = insight::format_pd(pd, name = NULL))
  eff <- app$effects |>
    mutate(Effect_label = Effect,
           Effect = ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")),
           Diff = insight::format_value(Median),
           CI = sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high)),
           pd_fmt = insight::format_pd(pd, name = NULL),
           Contrast = paste(Outcome, "-", Type, "path"))
  make_asis(
    make_tables(est_app$diag, c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct"),
                "Convergence of MemoryAppraisal"),
    make_tables(fixed, c("Answer", "Term", "Diff", "CI", "pd_fmt", "Effect"),
                "MemoryAppraisal: fixed effects of the ratings (log-odds of each answer vs. 'Human Original'; ratings on 0-1)"),
    make_tables(filter(eff, Outcome == "P(recognised)"), c("Contrast", "Predictor", "Effect_label", "Diff", "CI", "pd_fmt", "Effect"),
                "MemoryAppraisal: P(recognised) at -2 / -1 / +1 / +2 SD of the rating minus at the participant's mean, in percentage points"),
    make_tables(filter(eff, Outcome != "P(recognised)", Effect_label %in% c("-2 SD", "+2 SD", "Extremity", "Asymmetry")),
                c("Contrast", "Predictor", "Effect_label", "Diff", "CI", "pd_fmt", "Effect"),
                "MemoryAppraisal: recalled label among recognised artworks, at the extremes of the rating minus at the mean, in percentage points")
  )
}
```

```{r}
#| fig-width: 10
#| fig-height: 7
#| eval: !expr appraisal_ready

app$curves |>
  filter(abs(x) <= 0.5) |>
  mutate(Predictor = recode(Predictor, Beauty_w = "Phase-1 beauty", Valence_w = "Phase-1 valence"),
         Type = recode(Type, unique = "Unique (other rating at its mean)", joint = "Joint (other rating follows)")) |>
  ggplot(aes(x = 100 * x, y = Median, color = Predictor, fill = Predictor)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
  geom_line(linewidth = 1) +
  facet_grid(fct_relevel(Outcome, "P(recognised)") ~ Type, scales = "free_y") +
  scale_color_manual(values = c("Phase-1 beauty" = "#E91E63", "Phase-1 valence" = "#FF9800")) +
  scale_fill_manual(values = c("Phase-1 beauty" = "#E91E63", "Phase-1 valence" = "#FF9800")) +
  labs(x = "Phase-1 rating relative to the participant's mean (points of the scale)", y = "Probability (%)",
       color = NULL, fill = NULL,
       caption = "Population-level predictions (random effects at 0, averaged over the labels shown) with 95% CI.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold", size = 8))
```

```{r}
#| eval: !expr appraisal_ready

write.csv(app$effects, "../data/results_memory_appraisal.csv", row.names = FALSE)
```

The observed bins and the model disagree at the negative end, and the
reason is the artworks themselves: across items, the works that people rated
as uglier and more negative (relative to their own average) were the more
memorable ones, as were those of higher normative arousal (item-level
correlations below). The raw bins mix this item memorability with the effect
of a person's own appraisal; the model's item intercepts separate them.
Within items, rating a work as more beautiful or more positive than one's
average goes with better recognition, increasingly so at the top of the
range, while rating it as much less beautiful than average does not help:
the extremity effect of the preregistration holds on the positive side only,
the same asymmetric (convex) pattern as self-relevance and authenticity
against beauty (`6_selfrelevance.qmd`, `5_realitydeterminants.qmd`,
"Exploratory checks"). The Phase-1 appraisal also shaped the recalled label,
with the label actually shown held constant: among recognised works, those
rated as less beautiful (and less positive) than average were more often
remembered as "AI-Generated", and those rated as more beautiful more often as
"Original" -- the "beautiful = human" cue of Phase 2 at work in memory, in
line with the reconstruction of the label from one's own belief (Memory of
the Condition by Belief).

```{r}
items_mem <- old |>
  summarise(Hit = mean(Recognition == "Yes"), Beauty_w = mean(Beauty_w), Valence_w = mean(Valence_w),
            Arousal = first(Norms_Arousal), .by = "Item")
knitr::kable(data.frame(
  With = c("Mean relative beauty", "Mean relative valence", "Normative arousal (VAPS)"),
  r = sprintf("%.2f", c(cor(items_mem$Hit, items_mem$Beauty_w), cor(items_mem$Hit, items_mem$Valence_w), cor(items_mem$Hit, items_mem$Arousal)))
), format = "pipe", caption = "Item-level correlations of the hit rate (48 old items)")
```

## Durability: Follow-up Beauty by Recognition and by the Phase-2 Belief

On average the label no longer affects follow-up beauty (`3_models.qmd`,
Beauty2: AI-Generated - Human Original -0.9% [-2.0, 0.1]). Two models ask
whether that null hides something (`server/models.R`, 2026-09-25):

- **Beauty2Recognition**: `Beauty2 ~ Condition * Recognition` (CHOCO, old
  items). Does a residual label effect survive among the artworks the
  participant still recognises? The recognition answer follows the beauty
  rating in the same trial, so it stands for the item's memory status.
- **Beauty2Reality**: `Beauty2 ~ Condition * Reality_w + Beauty_w` (CHOCO,
  the 217 participants with Phase-2 and follow-up data). Does the
  syntheticness belief the label induced in Phase 2 carry into follow-up
  beauty, beyond the Phase-1 beauty of the same work? The label moved
  `Reality` in Phase 2, so `mediation_effects()` (as in
  `5_realitydeterminants.qmd`) splits the label effect on follow-up beauty
  into a direct part and a part carried by the belief.

```{r}
#| results: asis

durability_ready <- all(file.exists(file.path("models/estimates", c("Beauty2Recognition.rds", "Beauty2Reality.rds"))))
if (!durability_ready) {
  make_asis("", '::: {.callout-warning title="Estimates not available yet"}',
            "`Beauty2Recognition` / `Beauty2Reality`: in `analysis/server`, `./hpc combine <model>` (check 4,000 draws), `./hpc extract <model>`, then `./hpc pull 'estimates/<model>.rds'`.",
            ":::", "")
}
```

```{r}
#| results: asis
#| eval: !expr durability_ready

est_rec <- read_estimates("Beauty2Recognition")$Beauty2Recognition
est_rea <- read_estimates("Beauty2Reality")$Beauty2Reality
par_names <- c(response = "Mean response", mu = "P(beautiful side)", confright = "Confidence, beautiful side", confleft = "Confidence, ugly side")
# Beauty2Recognition: label contrasts within each recognition answer, and the
# recognition contrast, in % of the slider / percentage points of a dpar
rec_within <- prep_contrasts(est_rec$contrasts_emo, "Beauty2") |>
  filter(Parameter %in% names(par_names)) |>
  mutate(Parameter = par_names[as.character(Parameter)]) |>
  arrange(Recognition, Contrast, Parameter)
rec_between <- prep_contrasts(est_rec$contrasts_extra, "Beauty2") |>
  filter(Parameter %in% names(par_names)) |>
  mutate(Parameter = par_names[as.character(Parameter)])
means_rec <- est_rec$means_by |> mutate(across(c(Estimate, CI_low, CI_high), \(x) insight::format_value(100 * x)))
# Beauty2Reality: mediation through the Phase-2 belief, the belief slope per
# label, the Phase-1 beauty slope
med <- mediation_effects(est_rea)
med_mu <- mediation_effects(est_rea, par = "mu")
slopes <- bind_rows(mutate(grid_slopes(est_rea), What = "Phase-2 syntheticness (per +10%)"),
                    mutate(covariate_slopes(est_rea, "Beauty_w"), What = "Phase-1 beauty (per +10%)")) |> fmt_eff()
make_asis(
  make_tables(bind_rows(est_rec$diag, est_rea$diag), c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct"),
              "Convergence of the durability models"),
  make_tables(means_rec, c("Condition", "Recognition", "Estimate", "CI_low", "CI_high"),
              "Beauty2Recognition: follow-up beauty (% of the slider) per label and recognition answer"),
  make_tables(rec_within, c("Recognition", "Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Beauty2Recognition: label contrasts within artworks judged 'seen before' (Yes) and not (No), % of the slider / percentage points"),
  make_tables(rec_between, c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Beauty2Recognition: recognised minus unrecognised artworks (averaged over the labels)"),
  make_tables(fmt_eff(rename(med$effects, Path = Effect)), c("Contrast", "Path", "Diff", "CI", "pd_fmt", "Effect"),
              "Beauty2Reality: label effect on follow-up beauty at the participant's mean Phase-1 beauty (% of the slider), split into the part carried by the Phase-2 syntheticness belief (Indirect) and the rest (Direct); 'Mediator (a)' = label effect on the belief (% of its slider, these participants)"),
  make_tables(fmt_eff(rename(med_mu$effects, Path = Effect)), c("Contrast", "Path", "Diff", "CI", "pd_fmt", "Effect"),
              "Beauty2Reality: the same on P(beautiful side) (percentage points)"),
  make_tables(slopes, c("What", "Level", "Diff", "CI", "pd_fmt", "Effect"),
              "Beauty2Reality: slopes of follow-up beauty (% of the slider) on the Phase-2 belief per label (and their differences), and on Phase-1 beauty")
)
```

```{r}
#| fig-width: 11
#| fig-height: 4.5
#| eval: !expr durability_ready

p1 <- est_rec$means_by |>
  ggplot(aes(x = Recognition, y = 100 * Estimate, color = Condition)) +
  geom_pointrange(aes(ymin = 100 * CI_low, ymax = 100 * CI_high), position = position_dodge(width = 0.4)) +
  scale_color_manual(values = cols) +
  labs(x = "Recognised at follow-up", y = "Follow-up beauty (%)", title = "By recognition") +
  theme_minimal() + theme(legend.position = "top")
g <- est_rea$grid
P <- est_rea$grid_draws
curve <- bind_rows(lapply(seq_len(nrow(g)), function(i) {
  ci <- bayestestR::hdi(P[, i], ci = 0.95)
  data.frame(g[i, ], Median = 100 * median(P[, i]), CI_low = 100 * ci$CI_low, CI_high = 100 * ci$CI_high)
})) |> filter(abs(Reality_w) <= 0.5)
p2 <- ggplot(curve, aes(x = 100 * Reality_w, y = Median, color = Condition, fill = Condition)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = cols) + scale_fill_manual(values = cols) +
  labs(x = "Phase-2 syntheticness relative to the participant's mean (points; higher = more human)", y = "Follow-up beauty (%)",
       title = "By the Phase-2 belief (Phase-1 beauty at the participant's mean)") +
  theme_minimal() + theme(legend.position = "top")
p1 + p2 + plot_layout(widths = c(1, 2))
```

Reading the tables. **Beauty2Recognition**: recognised artworks are rated
more beautiful than unrecognised ones under every label (the familiarity /
liking link also seen in `MemorySR`), and the label contrasts are null
among unrecognised artworks; among recognised ones the mean response shows
no credible AI penalty either, but the probability of choosing the
"beautiful" side does drop for AI-labelled works -- a small residual trace
in the categorical choice, on the works the participant still remembers.
**Beauty2Reality**: the syntheticness belief formed in Phase 2 predicts
follow-up beauty beyond the Phase-1 beauty of the same work, under every
label (the "believed human = beautiful later" slope), and through it the
AI label carries a small negative indirect effect. The "Total" and "Direct"
rows are *not* total label effects: they hold Phase-1 beauty at the
participant's mean, and the label had lowered that rating by ~7%, so an
AI-labelled work with the same Phase-1 rating as an Original is an
intrinsically more appealing work, which rebounds at follow-up (the
positive "direct" term is this conditioning on a label-affected covariate,
not a lasting benefit of the label). The unconditional label effect on
follow-up beauty is the `Beauty2` model's (`3_models.qmd`).

```{r}
#| eval: !expr durability_ready

write.csv(bind_rows(
  mutate(rec_within, Model = "Beauty2Recognition", Table = "Label contrast within recognition", Contrast = as.character(Contrast)) |>
    select(Model, Table, Recognition, Contrast, Parameter, Median = Difference_pct, CI_low = CI_low_pct, CI_high = CI_high_pct, pd, Effect),
  mutate(rec_between, Model = "Beauty2Recognition", Table = "Recognition contrast", Contrast = as.character(Contrast)) |>
    select(Model, Table, Contrast, Parameter, Median = Difference_pct, CI_low = CI_low_pct, CI_high = CI_high_pct, pd, Effect),
  mutate(med$effects, Model = "Beauty2Reality", Table = "Mediation (response)", Parameter = "response") |>
    rename(Effect_type = Effect) |> select(Model, Table, Contrast, Parameter, Effect_type, Median, CI_low, CI_high, pd),
  mutate(med_mu$effects, Model = "Beauty2Reality", Table = "Mediation (mu)", Parameter = "mu") |>
    rename(Effect_type = Effect) |> select(Model, Table, Contrast, Parameter, Effect_type, Median, CI_low, CI_high, pd),
  mutate(slopes, Model = "Beauty2Reality", Table = What, Contrast = Level, Parameter = "response") |>
    select(Model, Table, Contrast, Parameter, Median, CI_low, CI_high, pd, Effect)
), "../data/results_memory_durability.csv", row.names = FALSE)
```

## Summary

- `data/results_memory_contrasts.csv`: every contrast (level × answer pair), probability scale, with `pd` and `Credible`.
- `data/results_memory_means.csv`: probability of each answer per level.
- `data/results_memory_durability.csv`: the Beauty2Recognition / Beauty2Reality tables (label contrasts within recognition, recognition contrast, mediation through the Phase-2 belief, slopes).

```{r}
#| label: memory-summary

results_memory_contrasts <- bind_rows(lapply(unname(estimates), function(e) {
  d <- as.data.frame(e$contrasts)
  d$Model <- e$outcome
  d$Predictor <- e$by
  d$Credible <- sign(d$CI_low) == sign(d$CI_high)
  d[c("Model", "Predictor", "Level1", "Response1", "Level2", "Response2",
      "Median", "CI_low", "CI_high", "pd", "Credible")]
})) |>
  arrange(Model, Response1, Response2, Level1, Level2)
write.csv(results_memory_contrasts, "../data/results_memory_contrasts.csv", row.names = FALSE)

results_memory_means <- bind_rows(lapply(unname(estimates), function(e) {
  d <- as.data.frame(e$means)
  data.frame(Model = e$outcome, Predictor = e$by, Level = as.character(d[[e$by]]),
             Response = as.character(d$Response), Median = d$Median,
             CI_low = d$CI_low, CI_high = d$CI_high)
})) |>
  arrange(Model, Level, Response)
write.csv(results_memory_means, "../data/results_memory_means.csv", row.names = FALSE)

make_tables(bind_rows(lapply(unname(estimates), `[[`, "diag")),
            c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws",
              "Max_Rhat", "Min_ESS_ratio", "Divergent_pct", "Criterion"),
            "Convergence of the memory models")
```

```{r}
#| label: memory-credible

credible <- results_memory_contrasts |>
  filter(Credible, Response1 == Response2) |>
  mutate(Answer = Response1,
         Contrast = paste(Level1, "-", Level2),
         Diff_pp = insight::format_value(100 * Median),
         CI = sprintf("[%s, %s]", insight::format_value(100 * CI_low), insight::format_value(100 * CI_high)),
         pd_fmt = insight::format_pd(pd, name = NULL),
         Effect = ifelse(Median < 0, "Negative", "Positive")) |>
  arrange(Model, Answer, desc(abs(Median))) |>
  select(Model, Answer, Contrast, Diff_pp, CI, pd_fmt, Effect)

make_tables(credible, names(credible),
            "Credible differences in the probability of each answer between levels, in percentage points")
```
