---
title: "FictionArt - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute:
  cache: true
---

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)


df <- read.csv("../data/data_memory_task.csv") |> 
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated", "New Items"),
         AnswerCondition = fct_relevel(AnswerCondition, "Human Original", "Human Forgery", "AI-Generated", "Not recognized"),
         AnswerBelief = fct_relevel(AnswerBelief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "Not recognized"),
         Belief = fct_relevel(Belief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "None"))

dfsub <- read.csv("../data/data_participants.csv") |> 
  filter(Participant %in% df$Participant)

cols <- c(
  # Condition
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "AI Original" = "#1D9AF5",
  "AI Copy" = "#4CAF50",
  "Not recognized" = "#607D8B",
  # Style
  "Abstract and Avant-garde" = "#E41A1C", 
  "Classical" = "#377EB8", 
  "Impressionist and Expressionist" = "#4DAF4A", 
  "Romantic and Realism" = "#FF7F00"
)
```


## Delay

```{r}
dfsub |> 
  ggplot(aes(x=Delay)) +
  geom_histogram(bins=30) +
  theme_minimal()
```

The mean and median days between the two experiments were `r insight::format_value(mean(dfsub$Delay))` and `r insight::format_value(median(dfsub$Delay))`, respectively.


## Memory of Condition

### Main 

```{r}
#| message: false

m_cond1 <- brm(AnswerCondition ~ Condition + (1|Participant) + (1|Item),
    data = df,
    family = categorical(link = "logit"),
    algorithm = "meanfield",
    iter = 8000,
    backend = "cmdstanr")
```

```{r}
# Modify the order of dodging based on the groups for visualization
make_group <- function(resp, covariate = NULL) {
  group <- case_when(  
    resp == "Not recognized" ~ 0,
    resp == "Human Original" ~ 1,
    resp == "AI-Generated" ~ 2,
    resp == "AI Original" ~ 2,
    resp == "Human Forgery" ~ 3,
    resp == "AI Copy" ~ 4,
    .default = NA)
  
  if(!is.null(covariate)) {
    covariate <- insight::format_value(normalize(covariate), style_positive="plus")
    group <- paste0(group, covariate)
  }
  group
}

dat_cond1 <- estimate_means(m_cond1, by=c("Condition")) |> 
  mutate(group = make_group(Response))

p_cond1 <- dat_cond1 |> 
  ggplot(aes(x=Condition,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1,
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Experimental Condition",
       title = "Memory of the Experimental Condition") +
  theme_minimal() 
p_cond1
```

```{r}
make_contrasts <- function(c, answer=NULL, condition=NULL) {
  # We can detect via the space because answer comes first
  c$Response1 <- case_when(
    str_detect(c$Level1, "Human Original ") ~ "Human Original",
    str_detect(c$Level1, "Human Forgery ") ~ "Human Forgery",
    str_detect(c$Level1, "AI-Generated ") ~ "AI-Generated",
    str_detect(c$Level1, "Not recognized ") ~ "Not recognized",
    str_detect(c$Level1, "AI Copy ") ~ "AI Copy",
    str_detect(c$Level1, "AI Original ") ~ "AI Original",
    .default = NA
  )
  c$Response2 <- case_when(
    str_detect(c$Level2, "Human Original ") ~ "Human Original",
    str_detect(c$Level2, "Human Forgery ") ~ "Human Forgery",
    str_detect(c$Level2, "AI-Generated ") ~ "AI-Generated",
    str_detect(c$Level2, "Not recognized ") ~ "Not recognized",
    str_detect(c$Level2, "AI Copy ") ~ "AI Copy",
    str_detect(c$Level2, "AI Original ") ~ "AI Original",
    .default = NA
  )
  c$Level1 <- str_remove(c$Level1, "Human Original |Human Forgery |AI-Generated |Not recognized |AI Original |AI Copy ")
  c$Level2 <- str_remove(c$Level2, "Human Original |Human Forgery |AI-Generated |Not recognized |AI Original |AI Copy ")
  
  if(!is.null(answer)) {
    c <- filter(c, str_detect(Response1, answer) & str_detect(Response2, answer))
  }
  if(!is.null(condition)) {
    c <- filter(c, str_detect(Level1, condition) & str_detect(Level2, condition))
  }
  
  # Remove duplicated cols
  if(length(unique(c$Response1)) == 1 & all(c$Response1 == c$Response2)) {
    c <- cbind(data.frame("Category" = c$Response1[1]), c)
    c$Response1 <- NULL
    c$Response2 <- NULL
  }
  if(length(unique(c$Level1)) == 1 & all(c$Level1 == c$Level2)) {
    c <- cbind(data.frame("Category" = c$Level1[1]), c)
    c$Level1 <- NULL
    c$Level2 <- NULL
  }
  
  c <- arrange(c, desc(abs(Median))) 
  t <- format_table(c, zap_small = TRUE)
  
  t$effectsize <- as.numeric(c$Median)
  t$sig <- as.numeric(c$pd)
  
  gt::gt(t) |> 
    gt::data_color(columns = "effectsize", target_columns = "Median", method = "numeric",
palette = c("red", "red", "white", "green", "green"), domain = c(-0.7, 0.7)) |> 
    gt::data_color(columns = "sig", target_columns = "pd", fn = \(x) {
      ifelse(x > 0.99, "#FFC107", ifelse(x > 0.97, "#FFEB3B", ifelse(x > 0.95, "#FFF59D", "white")))
    }) |> 
    gt::cols_hide(c("effectsize", "sig")) |> 
    gt::tab_header(title = "Marginal Contrasts")
}

c <- estimate_contrasts(m_cond1, contrast = c("Condition"), test = "pd")
make_contrasts(c, answer="Not recognized") 
make_contrasts(c, condition="Human Original")
make_contrasts(c, condition="New Items")
```


### Self-Relevance

```{r}
#| message: false

m_cond2a <- brm(AnswerCondition ~ Condition * SelfRelevance + (1|Participant),
    data = df,
    family = categorical(link = "logit"),
    algorithm = "meanfield",
    iter = 8000,
    backend = "cmdstanr")
```

```{r}
dat_cond2a <- estimate_means(m_cond2a, by=c("Condition", "SelfRelevance"), length = 7) |> 
  mutate(group = make_group(Response, SelfRelevance),
         SelfRelevance = fct_reorder(format_percent(SelfRelevance, digits = 0), SelfRelevance))

p_cond2a <- dat_cond2a |> 
  ggplot(aes(x=Condition,  y = Median, color = Response)) +
  geom_line(aes(group=group, alpha=SelfRelevance), position = position_dodge(width=0.2), linewidth = 1,
            show.legend = c(color = FALSE)) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high, alpha=SelfRelevance), position = position_dodge(width=0.2),
                  show.legend = c(alpha = FALSE), key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  scale_alpha_discrete(breaks = c("0%", "50%", "100%")) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Experimental Condition",
       title = "Effect of Self-Relevance") +
  theme_minimal()
p_cond2a
```

```{r}
c <- estimate_contrasts(m_cond2a, contrast = c("Condition", "SelfRelevance"), test = "pd")

# Specific contrast
c[c$Parameter == "Human Original Human Original 1.000 - Human Original Human Original 0.000",]
```



### Beauty

```{r}
#| message: false

m_cond2b <- brm(AnswerCondition ~ Condition * poly(Beauty, 2) + (1|Participant),
    data = filter(df, !is.na(Beauty)),
    family = categorical(link = "logit"),
    algorithm = "meanfield",
    iter = 8000,
    backend = "cmdstanr")
```

```{r}
dat_cond2b <- estimate_means(m_cond2b, by=c("Condition", "Beauty"), length = 7) |> 
  mutate(group = make_group(Response, Beauty),
         Beauty = fct_reorder(format_percent(Beauty, digits = 0), Beauty))

p_cond2b <- dat_cond2b |> 
  ggplot(aes(x=Condition,  y = Median, color = Response)) +
  # geom_line(aes(group=group, alpha=Beauty), position = position_dodge(width=0.8), linewidth = 1) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high, alpha=Beauty), position = position_dodge(width=0.8),
                  show.legend = c(alpha = FALSE), key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  scale_alpha_discrete(breaks = c("0%", "50%", "100%")) +
  guides(alpha = "none", color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Experimental Condition",
       title = "Effect of Beauty") +
  theme_minimal() 
p_cond2b
```

```{r}
#| fig-width: 14
#| fig-height: 12

((p_cond1 + theme(legend.position = "none")) | (p_cond2a / p_cond2b) +
  plot_layout(guides = "collect")) + 
  plot_annotation(title = "Do you remember how this artwork was labelled?", theme = theme(plot.title = element_text(hjust = 0.5, face="italic", size=rel(1.5))))
```

## Memory of Beliefs

### Main

```{r}
#| message: false

m_belief1a <- brm(AnswerBelief ~ Belief + (1|Participant),
    data = df,
    family = categorical(link = "logit"),
    algorithm = "meanfield",
    iter = 8000,
    backend = "cmdstanr")
```

```{r}
dat_belief1a <- estimate_means(m_belief1a, by=c("Belief")) |> 
  mutate(group = make_group(Response))

p_belief1a <- dat_belief1a |> 
  ggplot(aes(x=Belief,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1, 
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Original Belief",
       title = "Memory of Beliefs") +
  theme_minimal()
p_belief1a
```

```{r}
c <- estimate_contrasts(m_belief1a, contrast = c("Belief"), test = "pd")
make_contrasts(c, answer="Not recognized") 
make_contrasts(c, condition="Human Original")
```

### Continuous

```{r}
#| message: false

m_belief1b <- brm(AnswerBelief ~ poly(Reality, 2) * poly(Authenticity, 2) + (1|Participant),
    data = filter(df, Type == "Old", !is.na(Reality)),
    family = categorical(link = "logit"),
    algorithm = "meanfield",
    iter = 12000,
    backend = "cmdstanr")
```

```{r}
dat_belief1b <- estimate_means(m_belief1b, by=c("Reality", "Authenticity"), length = c(13, 5)) |> 
  mutate(
    group = make_group(Response, Authenticity),
    Authenticity = fct_reorder(format_percent(Authenticity, digits = 0), Authenticity))

p_belief1b <- dat_belief1b |> 
  ggplot(aes(x=Reality,  y = Median, color = Response)) +
  geom_line(aes(group=group, alpha=Authenticity), position = position_dodge(width=0.2), linewidth = 1,
                  key_glyph = "path", show.legend = c(color = FALSE)) +
  geom_pointrange(data=filter(dat_belief1b, round(Reality, 6) %in% c(0, 0.5, 1)),
                  aes(group=group, ymin = CI_low, ymax = CI_high, alpha=Authenticity), position = position_dodge(width=0.2),
                  key_glyph = "point", show.legend = c(alpha = FALSE)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,0.8), expand = c(0, 0)) +
  scale_x_continuous(labels = scales::percent, breaks = c(0, 0.5, 1)) +
  scale_color_manual(values = cols) +
  scale_alpha_discrete(breaks = c("0%", "50%", "100%")) +
  guides(color = "none") +
  labs(y="Proportion of answers", color = "Answer", x =  "AI vs. Human", alpha  = "Copy vs. Original",
       title = "Continuous Effect of Beliefs") +
  theme_minimal() +
  facet_grid(~Response)
p_belief1b
```

```{r}
#| fig-width: 12
#| fig-height: 14

p_belief1a / p_belief1b + 
  plot_layout(guides = "collect") + 
  plot_annotation(title = "Do you remember your own judgments?",
                  theme = theme(plot.title = element_text(hjust = 0.5, face="italic", size=rel(1.5))))
```



## Participant-level

In this recognition task, in which people were presented old and new items, and had to 1) answer if they recognize  it or not, and if so then remember the condition it was presented in as well as the memory of their own belief that they had about the item.

### Compute Indidces 


- **dprime**:  Sensitivity index quantifying how well a participant discriminates *old* from *new* items. Higher values indicate better recognition accuracy; 0 reflects chance-level discrimination.
- **c** : Parametric response bias criterion. Negative values indicate a liberal bias (more “old” responses), positive values a conservative bias (more “new” responses), and 0 indicates no bias.
- **BiasCondition_Human**:  Among all recognised items, the proportion labelled *Human Original*. Higher values indicate a stronger tendency to classify recognised items as human, regardless of their original condition assignment.
- **BiasCondition_Forgery**: Among all recognised items, the proportion labelled *Human Forgery*. This reflects a bias towards attributing recognised items to manipulated human sources, regardless of their original condition assignment.
- **BiasCondition_AI**: Among all recognised items, the proportion labelled *AI-Generated*. Higher values indicate a stronger general tendency to attribute recognised items to AI, regardless of their original condition assignment.
- **BiasBelief_HumanOriginal**: Proportion of recognised items for which participants remember having believed they were *Human Original*.
- **BiasBelief_HumanForgery**:  Proportion remembered as *Human Forgery*, indicating recalled suspicion of human tampering.
- **BiasBelief_AIOriginal**: Proportion remembered as *AI Original*, indicating remembered beliefs that items were originally produced by AI.
- **BiasBelief_AICopy**: Proportion remembered as *AI Copy*, reflecting recalled beliefs that items were AI-generated and derivative.
- **BiasBelief_Human**: Combined proportion of *Human Original + Human Forgery*. Represents the tendency to remember having believed items were human rather than AI.
- **BiasBelief_Authentic**: Combined proportion of *Human Original + AI Original*. Captures the tendency to recall having believed items were “authentic” originals rather than copies or forgeries.
  
  

```{r}
# log-linear corrected rates to avoid 0/1 extremes
ll_rate <- function(count, total) {
  (count + 0.5) / (total + 1)
}

# parametric SDT: d' and c
sdt_metrics <- function(hit_rate, fa_rate) {
  # qnorm works with rates strictly in (0,1)
  z_hit <- qnorm(hit_rate)
  z_fa  <- qnorm(fa_rate)
  dprime <- z_hit - z_fa
  criterion_c <- -0.5 * (z_hit + z_fa)
  tibble(dprime = dprime, c = criterion_c)
}

dffeatures <- df |>
  summarise(
    n_old  = sum(Type == "Old", na.rm = TRUE),
    n_new  = sum(Type == "New", na.rm = TRUE),
    hits   = sum(Recognition == "Yes" & Type == "Old", na.rm = TRUE),
    misses = sum(Recognition == "No"  & Type == "Old", na.rm = TRUE),
    fa     = sum(Recognition == "Yes" & Type == "New", na.rm = TRUE),
    cr     = sum(Recognition == "No"  & Type == "New", na.rm = TRUE),
    .by = "Participant"
  ) |>
  mutate(
    p_hit = ll_rate(hits, n_old),
    p_fa  = ll_rate(fa, n_new)
  ) |>
  mutate(
    map2_dfr(p_hit, p_fa, sdt_metrics)
  ) |> 
  select(Participant, dprime, c)

# Condition memory bias
dffeatures <- df |>
  summarise(n = n(), .by = c("Participant", "AnswerCondition")) |> 
  complete(Participant, AnswerCondition, fill = list(n = 0)) |> 
  filter(AnswerCondition != "Not recognized") |> 
  mutate(Total = sum(n), .by = "Participant") |> 
  mutate(p = n / Total) |> 
  select(-n, -Total) |>
  mutate(AnswerCondition = str_replace(AnswerCondition, "AI-Generated", "BiasCondition_AI"),
         AnswerCondition = str_replace(AnswerCondition, "Human Original", "BiasCondition_Human"),
         AnswerCondition = str_replace(AnswerCondition, "Human Forgery", "BiasCondition_Forgery")) |>
  pivot_wider(names_from = AnswerCondition, values_from = p) |> 
  full_join(dffeatures, by = "Participant")

# Belief memory bias
dffeatures <- df |>
  summarise(n = n(), .by = c("Participant", "AnswerBelief")) |> 
  complete(Participant, AnswerBelief, fill = list(n = 0)) |> 
  filter(AnswerBelief != "Not recognized") |> 
  mutate(Total = sum(n), .by = "Participant") |> 
  mutate(p = n / Total) |> 
  select(-n, -Total) |>
  mutate(AnswerBelief = str_replace(AnswerBelief, "AI Original", "BiasBelief_AIOriginal"),
         AnswerBelief = str_replace(AnswerBelief, "AI Copy", "BiasBelief_AICopy"),
         AnswerBelief = str_replace(AnswerBelief, "Human Original", "BiasBelief_HumanOriginal"),
         AnswerBelief = str_replace(AnswerBelief, "Human Forgery", "BiasBelief_HumanForgery")) |>
  pivot_wider(names_from = AnswerBelief, values_from = p) |> 
  mutate(BiasBelief_Human = BiasBelief_HumanOriginal + BiasBelief_HumanForgery,
         BiasBelief_Authentic = BiasBelief_HumanOriginal + BiasBelief_AIOriginal) |>
  full_join(dffeatures, by = "Participant")
```


### Correlation

```{r}
#| fig-width: 8
#| fig-height: 8

df2 <- dfsub |> 
  select(Participant, Gender, Age, Education, Delay, Art_Expertise, 
         BAIT_AI_Use, BAIT_AI_Knowledge, BAIT_Negative, BAIT_Positive, BAIT_ArtRealistic, BAIT_Total,
         VVIQ_Total, LifeSatisfaction, PHQ4_Anxiety, PHQ4_Depression, starts_with("MINT_"), -MINT_AttentionCheck) |> 
  mutate(Gender = case_when(
    Gender == "Male" ~ 0,
    Gender == "Female" ~ 1,
    .default =  NA
    ),
    BAIT_AI_Use = case_when(
      BAIT_AI_Use == "Never" ~ 0,
      BAIT_AI_Use == "A few times per month" ~ 1,
      BAIT_AI_Use == "A few times per week" ~ 2,
      BAIT_AI_Use == "Once a day" ~ 3,
      BAIT_AI_Use == "A few times per day" ~ 4,
      .default = NA
    ),
    Education = case_when(
      Education == "High school" ~ 0,
      Education == "Bachelor" ~ 1,
      Education == "Master" ~ 2,
      Education == "Doctorate" ~ 3,
      .default = NA
    ))

cleanlabels <- function(params) {
  params <- as.character(params)
  params[str_detect(params, "MINT_")] <- paste0(params[str_detect(params, "MINT_")], ")")
  params <- str_replace_all(params, "MINT_", "MINT (")
  params <- str_replace_all(params, "VVIQ_Total", "VVIQ")
  params <- str_replace_all(params, "PHQ4_", "PHQ4 - ")
  params <- str_replace_all(params, "LifeSatisfaction", "Life Satisfaction")
  params <- str_replace_all(params, "Delay", "Recognition Interval")
  params <- str_replace_all(params, "Art_Expertise", "Art Expertise")
  params <- str_replace_all(params, "BAIT_AI_Use", "AI - Usage Frequency")
  params <- str_replace_all(params, "BAIT_AI_Knowledge", "AI - Expertise")
  params <- str_replace_all(params, "BAIT_Negative", "BAIT - Negative Expectations")
  params <- str_replace_all(params, "BAIT_Positive", "BAIT - Positive Expectations")
  params <- str_replace_all(params, "BAIT_ArtRealistic", "BAIT - Art Realism")
  params <- str_replace_all(params, "BAIT_Total", "BAIT - Total")
  
  params <- str_replace_all(params, "BiasCondition_", "Bias for Condition ")
  params <- str_replace_all(params, "BiasBelief_HumanOriginal", "Bias for Belief - Human Original")
  params <- str_replace_all(params, "BiasBelief_HumanForgery", "Bias for Belief - Human Forgery")
  params <- str_replace_all(params, "BiasBelief_AIOriginal", "Bias for Belief - AI Original")
  params <- str_replace_all(params, "BiasBelief_AICopy", "Bias for Belief - AI Copy")
  params <- str_replace_all(params, "BiasBelief_Human", "Bias for Belief - Human")
  params <- str_replace_all(params, "BiasBelief_Authentic", "Bias for Belief - Authentic")
  params <- str_replace_all(params, "dprime", "Sensitivity (d')")
  params[params == "c"] <-  "Response Bias (c)"
  factor(params, levels = sort(as.character(unique(params))))
}

r <- dffeatures |> 
  correlation::correlation(df2, p_adjust="none") |> 
  correlation::cor_sort() |>
  mutate(label = ifelse(p < .05, paste0(insight::format_value(r, lead_zero = FALSE, zap_small = TRUE)), ""),
         Parameter1 = cleanlabels(Parameter1),
         Parameter2 = cleanlabels(Parameter2))
r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""

xnames <- levels(r$Parameter1)
ynames <- levels(r$Parameter2)

xcol <- case_when(
  str_detect(xnames, "MINT") ~ "#00838F",
  str_detect(xnames, "BAIT") ~ "#EF6C00",
  str_detect(xnames, "AI -") ~ "#FF9800",
  str_detect(xnames, "PHQ4") ~ "#9C27B0",
  str_detect(xnames, "BPQ") ~ "#795548",
  .default = "#424242"
)
ycol <- case_when(
  str_detect(ynames, "MINT") ~ "#00838F",
  str_detect(ynames, "BAIT") ~ "#EF6C00",
  str_detect(ynames, "AI -") ~ "#FF9800",
  str_detect(ynames, "PHQ4") ~ "#9C27B0",
  str_detect(ynames, "BPQ") ~ "#795548",
  .default = "#424242"
)
xbold <- case_when(
  xnames %in% c("Awareness", "MINT - Awareness") ~ "bold",
  str_detect(xnames, "Visceroception") ~ "bold",
  str_detect(xnames, "Deficit") ~ "bold",
  .default = "plain"
)
ybold <- case_when(
  ynames %in% c("Awareness", "MINT - Awareness") ~ "bold",
  str_detect(ynames, "Visceroception") ~ "bold",
  str_detect(ynames, "Deficit") ~ "bold",
  .default = "plain"
)

r |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=label), size=3) +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, limits = c(-1, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1, color = xcol, face = xbold),
        axis.text.y = element_text(color = ycol, face = ybold),
        legend.position = "none",
        axis.title = element_blank())
```

