---
title: "FakeArt - Memory Results"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Estimates are computed on the cluster (`./hpc extract`, see server/estimates.R) and read from models/estimates/. -->

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)

df <- read.csv("../data/data_memory_task.csv") |>
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated", "New Items"),
         AnswerCondition = fct_relevel(AnswerCondition, "Human Original", "Human Forgery", "AI-Generated", "Not recognized"),
         AnswerBelief = fct_relevel(AnswerBelief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "Not recognized"),
         Belief = fct_relevel(Belief, "Human Original", "Human Forgery", "AI Original", "AI Copy", "None"))

dfsub <- read.csv("../data/data_participants.csv") |> 
  filter(Participant %in% df$Participant)

cols <- c(
  # Condition
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "AI Original" = "#1D9AF5",
  "AI Copy" = "#4CAF50",
  "Not recognized" = "#607D8B",
  # Style
  "Abstract and Avant-garde" = "#E41A1C", 
  "Classical" = "#377EB8", 
  "Impressionist and Expressionist" = "#4DAF4A",
  "Romantic and Realism" = "#FF7F00"
)

source("server/estimates.R") # memory_info
source("report.R")           # make_asis(), make_tables(), make_markdown(), read_estimates()

estimates <- read_estimates(names(memory_info))
provenance_table(estimates)
```

## How to read this report

Three Bayesian categorical mixed models of what participants remembered in the
follow-up session (220 participants × 96 items = 21,120 rows: 48 seen in Phase 1,
48 new).

| model | outcome | predictor | levels of the predictor |
| --- | --- | --- | --- |
| **Memory of Condition** | `AnswerCondition`: which label the participant recalls being shown | `Condition`: the label actually shown in Phase 1 | Human Original, Human Forgery, AI-Generated, **New Items** (never seen) |
| **Memory of Beliefs** | `AnswerBelief`: what the participant recalls believing the artwork was | `Belief`: what they actually reported believing in Phase 2 | Human Original, Human Forgery, AI Original, AI Copy, None |
| **Memory of the Condition by Belief** | `AnswerCondition` | `Condition` **+** `Belief` (additive; old items with a recorded belief only, 10,416 rows) | Belief: Human Original, Human Forgery, AI Original, AI Copy |

All outcomes include **Not recognized** (item judged "new"): correct for
`New Items`, forgetting for the seen levels. The third model asks whether the
recalled label is reconstructed from one's own Phase-2 belief: its `Belief`
means and contrasts are averaged over the label actually shown (computed over
the observed trials, see `memory_observed()` in `server/estimates.R`), so a
`Belief` effect is the effect of the belief with the label held constant.

Each section: figure of the probability of each answer per level, convergence,
marginal means, contrasts (coloured tables of interest + the complete set), and
an auto-generated summary. Every table has a folded Markdown twin; the Summary
section writes `data/results_memory_contrasts.csv` and
`data/results_memory_means.csv`.

Estimates are probabilities and contrasts (`Level1 - Level2`) differences of
probabilities, reported in percentage points as posterior medians with 95% CI
and probability of direction (`pd`). "Credible" = CI excludes 0 (no
multiplicity correction).

## Delay

```{r}
dfsub |> 
  ggplot(aes(x=Delay)) +
  geom_histogram(bins=30) +
  theme_minimal()
```

The mean and median days between the two experiments were `r insight::format_value(mean(dfsub$Delay))` and `r insight::format_value(median(dfsub$Delay))`, respectively.

## Memory of Condition

### Main Model

```{r}
# Dodging order of the answers in the figures
make_group <- function(resp, covariate = NULL) {
  group <- case_when(  
    resp == "Not recognized" ~ 0,
    resp == "Human Original" ~ 1,
    resp == "AI-Generated" ~ 2,
    resp == "AI Original" ~ 2,
    resp == "Human Forgery" ~ 3,
    resp == "AI Copy" ~ 4,
    .default = NA)
  
  if(!is.null(covariate)) {
    covariate <- insight::format_value(normalize(covariate), style_positive="plus")
    group <- paste0(group, covariate)
  }
  group
}

dat_cond1 <- estimates$MemoryCondition$means |>
  mutate(group = make_group(Response))

p_cond1 <- dat_cond1 |> 
  ggplot(aes(x=Condition,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1,
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Experimental Condition",
       title = "Memory of the Experimental Condition") +
  theme_minimal() 
p_cond1
```

```{r}
make_contrasts <- function(c, answer=NULL, condition=NULL, title="Marginal Contrasts") {

  if(!is.null(answer)) {
    c <- filter(c, str_detect(Response1, answer) & str_detect(Response2, answer))
  }
  if(!is.null(condition)) {
    c <- filter(c, str_detect(Level1, condition) & str_detect(Level2, condition))
  }

  # Collapse a constant Response/Level pair into one Category column
  if(length(unique(c$Response1)) == 1 & all(c$Response1 == c$Response2)) {
    c <- cbind(data.frame("Category" = c$Response1[1]), c)
    c$Response1 <- NULL
    c$Response2 <- NULL
  }
  if(length(unique(c$Level1)) == 1 & all(c$Level1 == c$Level2)) {
    c <- cbind(data.frame("Category" = c$Level1[1]), c)
    c$Level1 <- NULL
    c$Level2 <- NULL
  }

  c <- arrange(c, desc(abs(Median)))
  t <- format_table(c, zap_small = TRUE)

  t$effectsize <- as.numeric(c$Median)
  t$sig <- as.numeric(c$pd)

  g <- gt::gt(t) |>
    gt::data_color(columns = "effectsize", target_columns = "Median", method = "numeric",
palette = c("red", "red", "white", "green", "green"), domain = c(-0.7, 0.7)) |>
    gt::data_color(columns = "sig", target_columns = "pd", fn = \(x) {
      ifelse(x > 0.99, "#FFC107", ifelse(x > 0.97, "#FFEB3B", ifelse(x > 0.95, "#FFF59D", "white")))
    }) |>
    gt::cols_hide(c("effectsize", "sig")) |>
    gt::tab_header(title = title)

  # Markdown twin: colour coding replaced by an Effect column
  md <- t[setdiff(names(t), c("effectsize", "sig"))]
  md$Effect <- ifelse(sign(c$CI_low) != sign(c$CI_high), "n.s.",
                      ifelse(c$Median < 0, "Negative", "Positive"))
  make_asis(as.character(knitr::knit_print(g)), "", make_markdown(md, title), "")
}

# Convergence, marginal means and the complete contrast set
make_memory_tables <- function(est) {
  means_fmt <- as.data.frame(est$means)[c(est$by, "Response", "Median", "CI_low", "CI_high")]
  num <- vapply(means_fmt, is.numeric, logical(1))
  means_fmt[num] <- lapply(means_fmt[num], insight::format_value, zap_small = TRUE)

  all_con <- as.data.frame(est$contrasts)
  all_con$Effect <- ifelse(sign(all_con$CI_low) != sign(all_con$CI_high), "n.s.",
                           ifelse(all_con$Median < 0, "Negative", "Positive"))
  all_fmt <- all_con[c("Level1", "Response1", "Level2", "Response2", "Median", "CI_low", "CI_high", "pd", "Effect")]
  n <- vapply(all_fmt, is.numeric, logical(1))
  all_fmt[n] <- lapply(all_fmt[n], insight::format_value, zap_small = TRUE)

  make_asis(
    make_tables(est$diag,
                c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws",
                  "Max_Rhat", "Min_ESS_ratio", "Divergent_pct", "Criterion"),
                sprintf("%s: convergence", est$label)),
    make_tables(means_fmt, names(means_fmt),
                sprintf("%s: probability of each answer per %s (marginal means)", est$label, est$by)),
    # Markdown only (120-300 rows)
    make_markdown(all_fmt, sprintf("%s: all %d contrasts", est$label, nrow(all_fmt)))
  )
}

# Generated summary of the credible same-answer contrasts
make_memory_summary <- function(est) {
  d <- as.data.frame(est$contrasts)
  d <- d[d$Response1 == d$Response2, ]
  d$Credible <- sign(d$CI_low) == sign(d$CI_high)
  pp <- function(x) insight::format_value(100 * x)
  out <- c(sprintf(
    "**%s.** Each row of the model is the probability of one answer. The differences below are between %s levels *within* the same answer, in percentage points, as posterior medians with 95%% CI; `pd` is the probability of direction. An effect is called credible when the CI excludes 0. Contrasts *across* answers are in the full table above.",
    est$label, est$by), "")
  for (r in unique(d$Response1)) {
    dr <- d[d$Response1 == r, ]
    cred <- dr[dr$Credible, ]
    if (nrow(cred) == 0) {
      out <- c(out, sprintf("- **%s**: no credible difference between any pair of %s levels.", r, est$by))
      next
    }
    cred <- cred[order(-abs(cred$Median)), ]
    out <- c(out, sprintf("- **%s**: %s.%s", r,
      paste(sprintf("%s - %s %s pp [%s, %s]", cred$Level1, cred$Level2,
                    pp(cred$Median), pp(cred$CI_low), pp(cred$CI_high)), collapse = "; "),
      if (nrow(cred) < nrow(dr)) sprintf(" The other %d pair(s) are not credible.", nrow(dr) - nrow(cred)) else ""))
  }
  make_asis("", '::: {.callout-tip title="Summary of credible effects (generated from the tables above)"}',
            "", out, "", ":::", "")
}
```

```{r}
make_memory_tables(estimates$MemoryCondition)
```

```{r}
c <- estimates$MemoryCondition$contrasts
make_contrasts(c, answer="Not recognized",
               title="Memory of Condition: forgetting ('Not recognized') by condition")
make_contrasts(c, condition="Human Original",
               title="Memory of Condition: which answer, within the Human Original condition")
make_contrasts(c, condition="New Items",
               title="Memory of Condition: which answer, within the New Items condition")
```

```{r}
make_memory_summary(estimates$MemoryCondition)
```


## Memory of Beliefs

### Main Model

```{r}
dat_belief1a <- estimates$MemoryBelief$means |>
  mutate(group = make_group(Response))

p_belief1a <- dat_belief1a |> 
  ggplot(aes(x=Belief,  y = Median, color = Response)) +
  geom_line(aes(group=group), position = position_dodge(width=0.1), linewidth = 1, 
            show.legend = FALSE) +
  geom_pointrange(aes(group=group, ymin = CI_low, ymax = CI_high), position = position_dodge(width=0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0,1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y="Proportion of answers", color = "Answer", x =  "Original Belief",
       title = "Memory of Beliefs") +
  theme_minimal()
p_belief1a
```

```{r}
make_memory_tables(estimates$MemoryBelief)
```

```{r}
c <- estimates$MemoryBelief$contrasts
make_contrasts(c, answer="Not recognized",
               title="Memory of Beliefs: forgetting ('Not recognized') by original belief")
make_contrasts(c, condition="Human Original",
               title="Memory of Beliefs: which answer, within the Human Original belief")
```

```{r}
make_memory_summary(estimates$MemoryBelief)
```

## Memory of the Condition by Belief

Does the recalled label follow what the participant came to believe about the
artwork (Phase 2), once the label actually shown is controlled for?

```{r}
dat_cb <- estimates$MemoryConditionBelief$means |>
  mutate(group = make_group(Response))

dat_cb |>
  ggplot(aes(x = Belief, y = Median, color = Response)) +
  geom_line(aes(group = group), position = position_dodge(width = 0.1), linewidth = 1,
            show.legend = FALSE) +
  geom_pointrange(aes(group = group, ymin = CI_low, ymax = CI_high), position = position_dodge(width = 0.1),
                  key_glyph = "point") +
  scale_y_continuous(label = scales::percent, limits = c(0, 1), expand = c(0, 0)) +
  scale_color_manual(values = cols) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "Proportion of answers (averaged over the label shown)", color = "Recalled label",
       x = "Own belief in Phase 2", title = "Memory of the Condition by Belief") +
  theme_minimal()
```

```{r}
make_memory_tables(estimates$MemoryConditionBelief)
```

```{r}
c <- estimates$MemoryConditionBelief$contrasts
make_contrasts(c, answer = "AI-Generated",
               title = "Memory of the Condition by Belief: recalling 'AI-Generated', by own belief")
make_contrasts(c, answer = "Human Original",
               title = "Memory of the Condition by Belief: recalling 'Human Original', by own belief")
make_contrasts(c, answer = "Human Forgery",
               title = "Memory of the Condition by Belief: recalling 'Human Forgery', by own belief")
```

Among **recognised** items only (each answer probability divided by the
probability of recognising the item, per draw), and the difference from the
Human Original belief:

```{r}
#| results: asis

D <- estimates$MemoryConditionBelief$draws # draws x Belief x answer
rec <- 1 - D[, , "Not recognized"]
describe_pp <- function(x) {
  ci <- bayestestR::eti(x)
  data.frame(Median = 100 * median(x), CI_low = 100 * ci$CI_low, CI_high = 100 * ci$CI_high,
             pd = as.numeric(bayestestR::p_direction(x)))
}
dat_rec <- bind_rows(lapply(setdiff(dimnames(D)[[3]], "Not recognized"), function(a) {
  bind_rows(lapply(dimnames(D)[[2]], function(b) {
    p <- D[, b, a] / rec[, b]
    p0 <- D[, "Human Original", a] / rec[, "Human Original"]
    cbind(data.frame(Answer = a, Belief = b),
          setNames(describe_pp(p)[1:3], c("P", "P_low", "P_high")),
          describe_pp(p - p0))
  }))
})) |>
  mutate(P = sprintf("%s [%s, %s]", insight::format_value(P), insight::format_value(P_low), insight::format_value(P_high)),
         Diff = ifelse(Belief == "Human Original", "", insight::format_value(Median)),
         CI = ifelse(Belief == "Human Original", "", sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high))),
         pd_fmt = ifelse(Belief == "Human Original", "", insight::format_pd(pd, name = NULL)),
         Effect = ifelse(Belief == "Human Original", "",
                         ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")))) |>
  rename(Contrast = Answer)
make_tables(dat_rec, c("Contrast", "Belief", "P", "Diff", "CI", "pd_fmt", "Effect"),
            "Memory of the Condition by Belief: P(recalled label | recognised), in %, and difference from the Human Original belief (percentage points)")
```

```{r}
make_memory_summary(estimates$MemoryConditionBelief)
```

## Summary

- `data/results_memory_contrasts.csv`: every contrast (level × answer pair), probability scale, with `pd` and `Credible`.
- `data/results_memory_means.csv`: probability of each answer per level.

```{r}
#| label: memory-summary

results_memory_contrasts <- bind_rows(lapply(unname(estimates), function(e) {
  d <- as.data.frame(e$contrasts)
  d$Model <- e$outcome
  d$Predictor <- e$by
  d$Credible <- sign(d$CI_low) == sign(d$CI_high)
  d[c("Model", "Predictor", "Level1", "Response1", "Level2", "Response2",
      "Median", "CI_low", "CI_high", "pd", "Credible")]
})) |>
  arrange(Model, Response1, Response2, Level1, Level2)
write.csv(results_memory_contrasts, "../data/results_memory_contrasts.csv", row.names = FALSE)

results_memory_means <- bind_rows(lapply(unname(estimates), function(e) {
  d <- as.data.frame(e$means)
  data.frame(Model = e$outcome, Predictor = e$by, Level = as.character(d[[e$by]]),
             Response = as.character(d$Response), Median = d$Median,
             CI_low = d$CI_low, CI_high = d$CI_high)
})) |>
  arrange(Model, Level, Response)
write.csv(results_memory_means, "../data/results_memory_means.csv", row.names = FALSE)

make_tables(bind_rows(lapply(unname(estimates), `[[`, "diag")),
            c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws",
              "Max_Rhat", "Min_ESS_ratio", "Divergent_pct", "Criterion"),
            "Convergence of the memory models")
```

```{r}
#| label: memory-credible

credible <- results_memory_contrasts |>
  filter(Credible, Response1 == Response2) |>
  mutate(Answer = Response1,
         Contrast = paste(Level1, "-", Level2),
         Diff_pp = insight::format_value(100 * Median),
         CI = sprintf("[%s, %s]", insight::format_value(100 * CI_low), insight::format_value(100 * CI_high)),
         pd_fmt = insight::format_pd(pd, name = NULL),
         Effect = ifelse(Median < 0, "Negative", "Positive")) |>
  arrange(Model, Answer, desc(abs(Median))) |>
  select(Model, Answer, Contrast, Diff_pp, CI, pd_fmt, Effect)

make_tables(credible, names(credible),
            "Credible differences in the probability of each answer between levels, in percentage points")
```
