---
title: "FakeArt - Determinants of Reality Beliefs"
editor: source
editor_options:
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Estimates are computed on the cluster (`./hpc extract RealityBeauty AuthenticityBeauty`, see server/estimates.R: mediation_info, get_mediation_estimates()) and read from models/estimates/. The mediation itself (mediation_effects()) runs here, on the stored predictions. -->

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)


cols <- c(
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  # Type of follow-up item (ArtificialityBeauty)
  "Old" = "#8E24AA",
  "New" = "#607D8B")

source("server/estimates.R") # mediation_info, mediation_effects(), prep_contrasts()
source("report.R")           # make_asis(), make_tables(), make_markdown(), read_estimates()

estimates <- read_estimates(c(names(mediation_info), names(appraisal_info), names(items_info)))
# The label effects of the main models (Condition * Emotion), for comparison
reference <- read_estimates(c("Beauty", "Reality", "Authenticity"))
provenance_table(c(estimates, reference))

# The mediation, once per model (bootstrap of the label -> beauty path over
# participants, one resample per posterior draw), on the mean response and on
# the main CHOCO parameters (same bootstrap draws for all)
# (ArtificialityBeauty is not a mediation: by = Type, see its own section)
main_models <- c("RealityBeauty", "AuthenticityBeauty")
control_models <- c(RealityBeauty = "RealityBeautyControl", AuthenticityBeauty = "AuthenticityBeautyControl")
mediation <- lapply(estimates[c(main_models, control_models)], mediation_effects)
choco_pars <- c("mu", "confright", "confleft")
mediation_pars <- lapply(estimates[main_models], function(e) {
  lapply(setNames(nm = choco_pars), function(p) mediation_effects(e, par = p))
})
# Joint appraisal mediators and item properties (their own sections)
appraisal_models <- c(Syntheticness = "RealityAppraisal", Authenticity = "AuthenticityAppraisal")
appraisal <- lapply(estimates[appraisal_models], function(e) {
  lapply(setNames(nm = c("response", choco_pars)), function(p) appraisal_effects(e, par = p))
})
items_models <- c(Syntheticness = "RealityItems", Authenticity = "AuthenticityItems")
items <- lapply(estimates[items_models], function(e) {
  lapply(setNames(nm = c("response", "mu")), function(p) items_effects(e, par = p))
})

# Plain-language names of the CHOCO parameters, per belief (right = the "1" end)
par_labels <- list(
  RealityBeauty = c(response = "Mean response (syntheticness)",
                    mu = "p(Human side) [mu]",
                    confright = "Confidence on the Human side [confright]",
                    confleft = "Confidence on the AI side [confleft]"),
  AuthenticityBeauty = c(response = "Mean response (authenticity)",
                         mu = "p(Original side) [mu]",
                         confright = "Confidence on the Original side [confright]",
                         confleft = "Confidence on the Copy side [confleft]"),
  ArtificialityBeauty = c(response = "Mean response (perceived artificiality)",
                          mu = "p(Artificial side) [mu]",
                          confright = "Confidence on the Artificial side [confright]",
                          confleft = "Confidence on the Human side [confleft]"))
```

## How to read this report

The question is whether the labels lower the Phase-2 reality beliefs
**directly**, or **through the lower beauty they induced in Phase 1**
(label → beauty → belief). The label is randomised and beauty is rated
before the belief, so the label → belief effect decomposes as a mediation.
The reverse path (belief → beauty) cannot be tested: the only Phase-1
"belief" is the label itself.

| model | outcome | predictors | data |
| --- | --- | --- | --- |
| **RealityBeauty** | `Reality` (syntheticness; 0 = AI-Generated, 1 = Human Creation) | `Condition * Beauty_w` | 317 participants × 48 trials |
| **AuthenticityBeauty** | `Authenticity` (0 = Copy / Forgery, 1 = Original) | `Condition * Beauty_w` | same |
| **RealityBeautyControl**, **AuthenticityBeautyControl** | as above | `Condition * Beauty_w + Beauty2_w` | 217 follow-up participants × 48 trials |
| **RealityAppraisal**, **AuthenticityAppraisal** | as above | `Condition * (Beauty_w + Valence_w + Meaning_w + Worth_w)` | 317 participants × 48 trials |
| **RealityItems**, **AuthenticityItems** | as above | `Condition + Style + z(VAPS norms)` | 317 participants × 48 trials |
| **ArtificialityBeauty** | `PerceivedArtificiality` (0 = Very Human, 1 = Very Artificial), follow-up | `Type * Beauty2_w` (Type = Old / New item) | 220 participants, every item judged "new" |

Both are CHOCO models with `Condition * Beauty_w` on `mu`, `confright` and
`confleft` (random `Condition * Beauty_w` slopes over participants,
`Condition + Beauty_w` over items), on the precisions (item intercept only)
and on `pex` / `bex` / `pmid` (participant intercept only). `Beauty_w` is the
Phase-1 beauty centred within participant: its slope is "this artwork vs.
my other artworks", and it is 0 at a participant's average beauty. There is
no Emotion term.

What each section reports, all in **% of the belief slider** unless stated
otherwise, as posterior medians with 95% CI (HDI for the mediation) and the
probability of direction (`pd`); "credible" = CI excludes 0:

- **Predicted belief by beauty**: the population-level prediction per label
  across `Beauty_w` (random effects at 0, 95% CI), for the mean response
  (the expected value of the CHOCO mixture) and for its three main
  parameters: `mu`, the probability of answering on the right-hand side of
  the slider (Human / Original), and `confright` / `confleft`, the confidence
  (distance from the midpoint) of the answers on each side. They show whether
  the label and beauty act on the *choice* or on the *confidence* in it.
- **Label contrasts at average beauty**: the label effect with beauty held at
  the participant's mean (`Beauty_w = 0`), for every CHOCO parameter. Compare
  with the label effect of the main model (no beauty term), shown alongside.
- **Beauty slopes**: the change in the belief per +10% of the beauty slider,
  per label, and the differences between labels (the interaction on the
  response scale: does a "fake" label weaken the beauty cue?).
- **Mediation**, for each contrast `c1 - c0`, with `E[Y | c, m]` the
  prediction under label `c` at beauty `m`, and `M_c` the mean `Beauty_w`
  under label `c`:
  - *Mediator (a)*: `M_c1 - M_c0`, in % of the **beauty** slider;
  - *Total*: `E[Y | c1, M_c1] - E[Y | c0, M_c0]`;
  - *Direct*: `E[Y | c1, M_c0] - E[Y | c0, M_c0]` (the label, beauty held
    where the reference label leaves it);
  - *Indirect*: `E[Y | c1, M_c1] - E[Y | c1, M_c0]` (beauty moved as the label
    moves it, the label held fixed);
  - *Proportion mediated*: Indirect / Total, only meaningful when the Total
    is credible.
- **Mediation by parameter**: the same Total / Direct / Indirect effects on
  `mu`, `confright` and `confleft` (percentage points of each parameter).

**Appraisal components.** Beauty is only one of the four Phase-1 ratings,
and the others were lowered by the labels too. The appraisal models enter
beauty, valence, meaning and worth of the same trial as *joint* mediators
(each rescaled to 0-1 and centred within participant), with their
interaction with the label. For each contrast: the direct effect, the joint
indirect effect (all four ratings shifted as the label shifts them) and the
*unique* indirect effect of each rating (only that rating shifted, the others
held where the reference label leaves them: slope under the target label ×
the label's shift in that rating, bootstrapped over participants). Worth is
a divergent test: a downstream valuation, not expected to carry a unique
route to the belief. Within participants, beauty correlates .76 with
valence, .62 with worth and .44 with meaning, so unique effects of the
collinear ratings are estimated less precisely than the joint one.

**Item properties.** Style and the VAPS norms (liking, valence, arousal,
complexity, familiarity; z-scored over the 48 items) as item-level
predictors: which artworks are judged synthetic or copied, independently of
the label and of the participant's own ratings. Descriptive (48 items).

Two further sections address the objection that beauty and belief could
share a common cause (some works are simply more appealing, and look more
human, to a given person), and whether the "less beautiful → more
artificial" inference needs a label at all:

- **Robustness: label-free beauty.** The same models on the follow-up
  participants, with the follow-up beauty of the same artwork (`Beauty2_w`,
  centred within participant) added as a covariate. It was rated ~47 days
  later, after the debrief, and the label had no effect on it: a label-free
  measure of how appealing the work is to that person. Predictions and
  mediation are computed at `Beauty2_w = 0`. If the Phase-1 beauty slope and
  the direct / indirect effects hold, the mediation is not reducible to
  stable appeal.
- **Never-labelled artworks.** In the follow-up, artworks judged "new" were
  rated for how easily they could be AI-generated. The 48 new items never
  carried a label; the model gives the slope of perceived artificiality on
  follow-up beauty for new vs. old (missed) items.

Caveats: predictions are evaluated at the mean beauty per label (an
approximation for a non-linear model) and at the population level (random
effects at 0); measurement error in beauty attenuates the slope, so the
indirect effect is a lower bound; beauty is not randomised, so a
person-specific appeal of the artwork could drive both beauty and belief
(the planned control is follow-up beauty, `Beauty2`).

## Convergence

```{r}
#| results: asis

convergence_by_class <- function(est) {
  est$convergence |>
    mutate(Class = case_when(
      startsWith(variable, "b_") | startsWith(variable, "Intercept") ~ "b (fixed effects)",
      startsWith(variable, "sd_") ~ "sd (random-effect SDs)",
      startsWith(variable, "cor_") ~ "cor (random-effect correlations)",
      .default = "other")) |>
    summarise(N = n(), Max_Rhat = round(max(rhat, na.rm = TRUE), 3),
              Min_ESS_bulk = round(min(ess_bulk, na.rm = TRUE)), .by = "Class") |>
    mutate(Model = est$outcome, .before = 1)
}

make_asis(
  make_tables(bind_rows(lapply(estimates, `[[`, "diag")),
              c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct"),
              "Convergence of the determinants models"),
  make_tables(bind_rows(lapply(estimates, convergence_by_class)),
              c("Model", "Class", "N", "Max_Rhat", "Min_ESS_bulk"),
              "Convergence by parameter class (the fixed effects are what the report uses)")
)
```

```{r}
# Helpers shared by both model sections

# Credible / Effect (sign) / formatted columns. The mediation tables' own
# "Effect" (Total, Direct, ...) is kept as "Path".
format_effects <- function(dat) {
  if ("Effect" %in% names(dat)) dat <- rename(dat, Path = Effect)
  dat |>
    mutate(Credible = sign(CI_low) == sign(CI_high),
           Effect = ifelse(!Credible, "n.s.", ifelse(Median < 0, "Negative", "Positive")),
           Diff = insight::format_value(Median, zap_small = TRUE),
           CI = sprintf("[%s, %s]", insight::format_value(CI_low, zap_small = TRUE),
                        insight::format_value(CI_high, zap_small = TRUE)),
           pd_fmt = insight::format_pd(pd, name = NULL))
}

plot_predictions <- function(name, xlab = "Phase-1 beauty relative to the participant's mean (Beauty_w)") {
  est <- estimates[[name]]
  by <- if (is.null(est$by)) "Condition" else est$by
  labs_par <- par_labels[[name]]
  mats <- c(list(response = est$grid_draws), est$grid_dpars[choco_pars])
  pred <- bind_rows(lapply(names(mats), function(p) {
    P <- mats[[p]]
    cbind(est$grid, Parameter = labs_par[[p]],
          Median = apply(P, 2, median),
          CI_low = apply(P, 2, quantile, 0.025),
          CI_high = apply(P, 2, quantile, 0.975))
  })) |>
    mutate(Parameter = factor(Parameter, levels = labs_par))

  ggplot(pred, aes(x = .data[[est$mediator]], color = .data[[by]], fill = .data[[by]])) +
    geom_ribbon(aes(ymin = 100 * CI_low, ymax = 100 * CI_high), alpha = 0.15, color = NA) +
    geom_line(aes(y = 100 * Median), linewidth = 1) +
    facet_wrap(~Parameter, scales = "free_y") +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    labs(x = xlab, y = "Predicted value (%)",
         color = ifelse(by == "Condition", "Label", by), fill = ifelse(by == "Condition", "Label", by),
         caption = "Population-level predictions (random effects at 0) with 95% CI.") +
    theme_minimal() +
    theme(legend.position = "top", strip.text = element_text(face = "bold"))
}

section_tables <- function(name, reference_name) {
  est <- estimates[[name]]
  med <- mediation[[name]]

  con <- prep_contrasts(est$contrasts, est$outcome) |>
    filter(Parameter %in% c("response", "mu", "confright", "confleft", "pex", "bex", "pmid"))
  ref <- prep_contrasts(reference[[reference_name]]$contrasts, reference_name) |>
    filter(Parameter == "response") |>
    mutate(Parameter = "response (main model, no beauty term)")
  con <- bind_rows(con, ref) |> arrange(Contrast)

  make_asis(
    make_tables(con, c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: label contrasts at average beauty (%% of the slider for response and the probability parameters)", est$label)),
    make_tables(format_effects(med$slopes), c("Condition", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: change per +10%% of Phase-1 beauty (%% of the belief slider), per label and between labels", est$label)),
    make_tables(format_effects(med$effects), c("Contrast", "Path", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: mediation of the label effect by Phase-1 beauty", est$label)),
    make_tables(
      bind_rows(lapply(choco_pars, function(p) {
        mutate(mediation_pars[[name]][[p]]$effects, Parameter = par_labels[[name]][[p]])
      })) |>
        filter(Effect %in% c("Total", "Direct", "Indirect")) |>
        format_effects() |>
        arrange(Contrast),
      c("Contrast", "Parameter", "Path", "Diff", "CI", "pd_fmt", "Effect"),
      sprintf("%s: mediation by CHOCO parameter (percentage points of each parameter)", est$label))
  )
}
```

## Syntheticness

```{r}
#| fig-width: 10
#| fig-height: 7.5

plot_predictions("RealityBeauty")
```

```{r}
#| results: asis

section_tables("RealityBeauty", "Reality")
```

## Authenticity

```{r}
#| fig-width: 10
#| fig-height: 7.5

plot_predictions("AuthenticityBeauty")
```

```{r}
#| results: asis

section_tables("AuthenticityBeauty", "Authenticity")
```

## Appraisal components

```{r}
#| fig-width: 10
#| fig-height: 5.5

dat_app <- bind_rows(lapply(names(appraisal_models), function(o) {
  mutate(appraisal[[o]]$response$effects, Belief = o)
})) |>
  mutate(Contrast = fct_relevel(Contrast, contrast_order))

dat_app |>
  filter(Path %in% c("Direct", "Indirect (Beauty)", "Indirect (Valence)", "Indirect (Meaning)", "Indirect (Worth)")) |>
  mutate(Path = fct_relevel(Path, "Direct", "Indirect (Beauty)", "Indirect (Valence)", "Indirect (Meaning)", "Indirect (Worth)")) |>
  ggplot(aes(x = Median, y = Path, xmin = CI_low, xmax = CI_high, color = Path)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_pointrange() +
  facet_grid(Belief ~ Contrast) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = c("Direct" = "#7E57C2", "Indirect (Beauty)" = "#E91E63", "Indirect (Valence)" = "#FF9800",
                                "Indirect (Meaning)" = "#26A69A", "Indirect (Worth)" = "#795548"), guide = "none") +
  labs(x = "Effect of the label (% of the belief slider, 95% HDI)", y = NULL) +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"))
```

```{r}
#| results: asis

tab_app <- dat_app |>
  mutate(Contrast = paste0(Belief, ": ", Contrast)) |>
  format_effects() |>
  mutate(Path = fct_relevel(Path, "Total", "Direct", "Indirect (joint)", "Indirect (joint, exact)")) |>
  arrange(Contrast, Path)

tab_cues <- bind_rows(lapply(names(appraisal_models), function(o) {
  mutate(appraisal[[o]]$response$cues, Contrast = o)
})) |>
  format_effects()

tab_app_pars <- bind_rows(lapply(names(appraisal_models), function(o) {
  bind_rows(lapply(choco_pars, function(p) {
    mutate(appraisal[[o]][[p]]$effects, Parameter = par_labels[[main_models[match(o, names(appraisal_models))]]][[p]])
  })) |>
    mutate(Contrast = paste0(o, ": ", Contrast))
})) |>
  filter(Path %in% c("Direct", "Indirect (Beauty)", "Indirect (Valence)", "Indirect (Meaning)", "Indirect (Worth)")) |>
  format_effects() |>
  arrange(Contrast, Parameter, Path)

make_asis(
  make_tables(tab_app, c("Contrast", "Path", "Diff", "CI", "pd_fmt", "Effect"),
              "Decomposition of the label effect by the four Phase-1 ratings (% of the belief slider; Mediator rows: % of that rating's scale)"),
  make_tables(tab_cues, c("Contrast", "Mediator", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
              "Unique change in the belief per +10% of each rating, the others held constant, per label and between labels"),
  make_tables(tab_app_pars, c("Contrast", "Parameter", "Path", "Diff", "CI", "pd_fmt", "Effect"),
              "Direct and unique indirect effects on the CHOCO parameters (percentage points)")
)
```

## Robustness: label-free beauty

The same decomposition with the follow-up beauty of the artwork as a
covariate (participants who returned for the follow-up), next to the main
models (all participants). *Mediator (a)* is in % of the beauty slider, the
other paths in % of the belief slider.

```{r}
#| results: asis

dat_rob <- bind_rows(lapply(main_models, function(n) {
  outcome <- ifelse(n == "RealityBeauty", "Syntheticness", "Authenticity")
  bind_rows(
    mutate(mediation[[n]]$effects, Model = "Main (all participants)"),
    mutate(mediation[[control_models[[n]]]]$effects, Model = "+ follow-up beauty (follow-up participants)")
  ) |>
    mutate(Contrast = paste0(outcome, ": ", Contrast))
})) |>
  filter(Effect %in% c("Mediator (a)", "Total", "Direct", "Indirect")) |>
  format_effects() |>
  mutate(Path = fct_relevel(Path, "Mediator (a)", "Total", "Direct", "Indirect")) |>
  arrange(Contrast, Path, desc(Model))

dat_rob_slopes <- bind_rows(lapply(main_models, function(n) {
  outcome <- ifelse(n == "RealityBeauty", "Syntheticness", "Authenticity")
  bind_rows(
    mutate(mediation[[n]]$slopes, Model = "Main", Predictor = "Phase-1 beauty"),
    mutate(mediation[[control_models[[n]]]]$slopes, Model = "+ follow-up beauty", Predictor = "Phase-1 beauty"),
    mutate(rename(covariate_slopes(estimates[[control_models[[n]]]], "Beauty2_w"), Condition = Level),
           Model = "+ follow-up beauty", Predictor = "Follow-up beauty")
  ) |>
    mutate(Contrast = outcome)
})) |>
  format_effects()

make_asis(
  make_tables(dat_rob, c("Contrast", "Path", "Model", "Diff", "CI", "pd_fmt", "Effect"),
              "Mediation of the label effect by Phase-1 beauty, with and without controlling for follow-up beauty"),
  make_tables(dat_rob_slopes, c("Contrast", "Predictor", "Model", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
              "Change in the belief per +10% of beauty (% of the belief slider), per label and between labels")
)
```

## Never-labelled artworks: perceived artificiality

```{r}
#| fig-width: 10
#| fig-height: 7.5

plot_predictions("ArtificialityBeauty", xlab = "Follow-up beauty relative to the participant's mean (Beauty2_w)")
```

```{r}
#| results: asis

est_art <- estimates$ArtificialityBeauty
dat_art <- bind_rows(lapply(c("response", choco_pars), function(p) {
  mutate(grid_slopes(est_art, par = p), Contrast = par_labels$ArtificialityBeauty[[p]])
})) |>
  format_effects()
dat_art_type <- prep_contrasts(est_art$contrasts, est_art$outcome) |>
  filter(Parameter %in% c("response", "mu", "confright", "confleft"))
make_asis(
  make_tables(dat_art_type, c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Perceived artificiality: New - Old items at average follow-up beauty (% of the slider / of the parameter)"),
  make_tables(dat_art, c("Contrast", "Level", "Diff", "CI", "pd_fmt", "Effect"),
              "Change in perceived artificiality per +10% of follow-up beauty, for old (missed) and new (never labelled) items, and their difference")
)
```

## Item properties

```{r}
#| fig-width: 9
#| fig-height: 4.5

dat_items <- bind_rows(lapply(names(items_models), function(o) {
  bind_rows(
    mutate(items[[o]]$response$slopes, Parameter = "Mean response"),
    mutate(items[[o]]$mu$slopes, Parameter = par_labels[[main_models[match(o, names(items_models))]]][["mu"]])
  ) |>
    mutate(Belief = o)
}))

dat_items |>
  ggplot(aes(x = Median, y = Predictor, xmin = CI_low, xmax = CI_high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_pointrange(color = "#37474F") +
  facet_grid(Belief ~ Parameter, scales = "free_x") +
  scale_y_discrete(limits = rev) +
  labs(x = "Change per +1 SD of the normative rating (percentage points, 95% HDI)", y = "VAPS norm") +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"))
```

```{r}
#| results: asis

make_asis(
  make_tables(format_effects(mutate(dat_items, Contrast = paste0(Belief, " - ", Parameter))),
              c("Contrast", "Predictor", "Diff", "CI", "pd_fmt", "Effect"),
              "Change per +1 SD of each VAPS norm, the others held constant (averaged over labels and styles)"),
  make_tables(bind_rows(lapply(names(items_models), function(o) mutate(items[[o]]$response$style_means, Contrast = o))) |>
                format_effects(),
              c("Contrast", "Style", "Diff", "CI"),
              "Predicted belief per style (% of the slider, norms at their mean, averaged over labels)"),
  make_tables(bind_rows(lapply(names(items_models), function(o) {
                mutate(items[[o]]$response$style_contrasts, Style = Contrast, Contrast = o)
              })) |> format_effects(),
              c("Contrast", "Style", "Diff", "CI", "pd_fmt", "Effect"),
              "Differences between styles (% of the belief slider)")
)
```

## Summary

```{r}
#| fig-width: 10
#| fig-height: 5

dat_med <- bind_rows(lapply(names(mediation), function(n) {
  mutate(mediation[[n]]$effects, Model = n, Outcome = estimates[[n]]$label)
}))

dat_med |>
  filter(Model %in% main_models, Effect %in% c("Total", "Direct", "Indirect")) |>
  mutate(Effect = fct_relevel(Effect, "Total", "Direct", "Indirect"),
         Contrast = fct_relevel(Contrast, contrast_order),
         Outcome = str_remove(Outcome, " by Phase-1 Beauty")) |>
  ggplot(aes(x = Median, y = Effect, xmin = CI_low, xmax = CI_high, color = Effect)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_pointrange() +
  facet_grid(Outcome ~ Contrast) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = c("Total" = "#212121", "Direct" = "#7E57C2", "Indirect" = "#26A69A"), guide = "none") +
  labs(x = "Effect of the label (% of the belief slider, 95% HDI)", y = NULL) +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"))
```

Auto-generated summary of the mediation (for text readers):

```{r}
#| results: asis

fmt <- function(d, e) {
  r <- d[d$Effect == e, ]
  sprintf("%s [%s, %s]", insight::format_value(r$Median), insight::format_value(r$CI_low), insight::format_value(r$CI_high))
}
lines <- unlist(lapply(split(dat_med, list(dat_med$Outcome, dat_med$Contrast), drop = TRUE), function(d) {
  total_credible <- with(d[d$Effect == "Total", ], sign(CI_low) == sign(CI_high))
  sprintf("- **%s, %s**: total %s, direct %s, indirect %s%s (label effect on beauty: %s%% of the beauty slider).",
          d$Outcome[1], d$Contrast[1], fmt(d, "Total"), fmt(d, "Direct"), fmt(d, "Indirect"),
          if (total_credible) paste0("; ", fmt(d, "Proportion mediated"), "% mediated") else "; total not credible, proportion not interpretable",
          fmt(d, "Mediator (a)"))
}))
make_asis(lines)
```

Files written:

- `data/results_determinants_mediation.csv`: mediator path, total, direct, indirect effect and proportion mediated per model × contrast.
- `data/results_determinants_slopes.csv`: beauty slopes per label and their differences (and, for the control models, the follow-up beauty slope).
- `data/results_determinants_artificiality.csv`: slopes of perceived artificiality on follow-up beauty per item type, response and CHOCO parameters.
- `data/results_determinants_appraisal.csv`: decomposition by the four Phase-1 ratings (total, direct, joint and unique indirect effects, rating shifts), response and CHOCO parameters.
- `data/results_determinants_items.csv`: slopes per SD of each VAPS norm and style differences.
- `data/results_determinants_contrasts.csv`: label contrasts at average beauty, every CHOCO parameter.

```{r}
write.csv(dat_med, "../data/results_determinants_mediation.csv", row.names = FALSE)
bind_rows(
  bind_rows(lapply(names(mediation), function(n) mutate(mediation[[n]]$slopes, Model = n, Predictor = "Beauty_w", .before = 1))),
  bind_rows(lapply(control_models, function(n) {
    mutate(rename(covariate_slopes(estimates[[n]], "Beauty2_w"), Condition = Level), Model = n, Predictor = "Beauty2_w", .before = 1)
  }))
) |>
  write.csv("../data/results_determinants_slopes.csv", row.names = FALSE)
bind_rows(lapply(c("response", choco_pars), function(p) mutate(grid_slopes(estimates$ArtificialityBeauty, par = p), Parameter = p, .before = 1))) |>
  write.csv("../data/results_determinants_artificiality.csv", row.names = FALSE)
bind_rows(lapply(names(appraisal_models), function(o) {
  bind_rows(lapply(names(appraisal[[o]]), function(p) mutate(appraisal[[o]][[p]]$effects, Belief = o, Parameter = p, .before = 1)))
})) |>
  write.csv("../data/results_determinants_appraisal.csv", row.names = FALSE)
bind_rows(lapply(names(items_models), function(o) {
  bind_rows(lapply(names(items[[o]]), function(p) {
    bind_rows(
      mutate(rename(items[[o]][[p]]$slopes, Term = Predictor), Type = "Norm slope (per SD)"),
      mutate(rename(items[[o]][[p]]$style_contrasts, Term = Contrast), Type = "Style difference")
    ) |>
      mutate(Belief = o, Parameter = p, .before = 1)
  }))
})) |>
  write.csv("../data/results_determinants_items.csv", row.names = FALSE)
bind_rows(lapply(estimates, function(e) {
  prep_contrasts(e$contrasts, e$outcome) |>
    mutate(Model = e$outcome) |>
    select(Model, Contrast, Parameter, Difference, CI_low, CI_high, Difference_pct, CI_low_pct, CI_high_pct, pd, Credible, Effect)
})) |>
  write.csv("../data/results_determinants_contrasts.csv", row.names = FALSE)
```
