---
title: "FakeArt - Self-Relevance"
editor: source
editor_options:
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Estimates are computed on the cluster (`./hpc extract BeautySR BeautySRControl MeaningSR RealitySR AuthenticitySR ArtificialitySR`, see server/estimates.R: sr_models, mediation_info, appraisal_info) and read from models/estimates/. The moderation and decomposition (moderation_effects(), appraisal_effects(), grid_slopes(), covariate_slopes()) run here, on the stored predictions. A model section whose estimates are not there yet prints a note instead (ready() / pending()), so the descriptive sections render on their own. -->

## Data Preparation

```{r}
#| warning: false
#| code-fold: false
#| error: false

library(tidyverse)
library(easystats)
library(patchwork)

cols <- c(
  "Human Original" = "#F51D56",
  "Human Forgery" = "#F5A41D",
  "AI-Generated" = "#1D9AF5",
  "New Items" = "#607D8B",
  # Type of follow-up item (ArtificialitySR, recognition)
  "Old" = "#8E24AA",
  "New" = "#607D8B")

source("server/estimates.R") # sr_models, mediation_info, appraisal_info, moderation_effects(), appraisal_effects()
source("report.R")           # make_asis(), make_tables(), read_estimates(), provenance_table()

# Phase-1/2 trials of the 220 follow-up participants (their 48 old items),
# with the follow-up ratings of the same artwork. The *_w columns are centred
# within participant over these 48 items, as fa_prepare_sr() does (models.R).
dfsr <- read.csv("../data/data_task.csv") |>
  filter(!is.na(SelfRelevance)) |>
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated"),
         SR = round(SelfRelevance * 6)) |>
  mutate(across(c(SelfRelevance, Beauty2, Beauty, Valence, Meaning, Worth, Reality, Authenticity),
                \(x) x - mean(x, na.rm = TRUE), .names = "{.col}_w"),
         .by = "Participant")

# Follow-up file: 220 participants x 96 items (48 old, 48 new), centred over the 96
dfmem <- read.csv("../data/data_memory_task.csv") |>
  mutate(Condition = fct_relevel(Condition, "Human Original", "Human Forgery", "AI-Generated", "New Items"),
         Type = fct_relevel(Type, "Old", "New"),
         AnswerCondition = fct_relevel(AnswerCondition, "Human Original", "Human Forgery", "AI-Generated", "Not recognized"),
         SR = round(SelfRelevance * 6)) |>
  mutate(across(c(SelfRelevance, Beauty2), \(x) x - mean(x, na.rm = TRUE), .names = "{.col}_w"),
         .by = "Participant")

dfsub <- read.csv("../data/data_participants.csv") |>
  filter(Participant %in% dfmem$Participant)

# Estimates: the self-relevance models extracted so far, plus the models
# they are compared with (label effects without an SR term; the beauty-only
# versions of the belief models, same participants)
has_est <- setNames(file.exists(file.path("models", "estimates", paste0(sr_models, ".rds"))), sr_models)
ready <- function(...) all(has_est[c(...)])
estimates <- read_estimates(sr_models[has_est])
reference <- read_estimates(c("SelfRelevance", "Beauty", "Meaning", "Reality", "Authenticity",
                              "RealityBeautyControl", "AuthenticityBeautyControl", "ArtificialityBeauty"))
provenance_table(c(estimates, reference))

# Printed in place of a section whose estimates are missing
pending <- function(...) {
  miss <- c(...)[!has_est[c(...)]]
  if (length(miss) == 0) return(invisible(NULL))
  make_asis(
    "",
    '::: {.callout-warning title="Estimates not available yet"}',
    sprintf("%s: in `analysis/server`, `./hpc combine <model>` (check 4,000 draws), `./hpc extract <model>`, then `./hpc pull 'estimates/*.rds'`. This section fills in on the next render.",
            paste0("`", miss, "`", collapse = ", ")),
    ":::",
    "")
}

# Plain-language names of the parameters, per outcome (right = the "1" end)
par_labels <- list(
  Beauty = c(response = "Mean response (beauty)",
             mu = "p(Beautiful side) [mu]",
             confright = "Confidence on the Beautiful side [confright]",
             confleft = "Confidence on the Ugly side [confleft]"),
  Meaning = c(response = "Mean response (meaning)",
              mu = "Mean of the Discrete Beta [mu]",
              pzero = "p(Not at all meaningful) [pzero]"),
  Reality = c(response = "Mean response (syntheticness)",
              mu = "p(Human side) [mu]",
              confright = "Confidence on the Human side [confright]",
              confleft = "Confidence on the AI side [confleft]"),
  Authenticity = c(response = "Mean response (authenticity)",
                   mu = "p(Original side) [mu]",
                   confright = "Confidence on the Original side [confright]",
                   confleft = "Confidence on the Copy side [confleft]"),
  PerceivedArtificiality = c(response = "Mean response (perceived artificiality)",
                             mu = "p(Artificial side) [mu]",
                             confright = "Confidence on the Artificial side [confright]",
                             confleft = "Confidence on the Human side [confleft]"))
predictor_labels <- c(Beauty = "Phase-1 beauty", SR = "Self-relevance", Beauty2 = "Follow-up beauty")

# (A) Moderation: label gap at low / average / high SR and SR slope per label,
# on the mean response and every modelled parameter
moderation_models <- intersect(c("BeautySR", "BeautySRControl", "BeautySRBetween", "MeaningSR"), names(estimates))
moderation <- lapply(setNames(nm = moderation_models), function(n) {
  info <- mediation_info[[n]]
  rng <- if (info$outcome == "Meaning") 6 else 1
  lapply(setNames(nm = c("response", info$dpars)), function(p) moderation_effects(estimates[[n]], par = p, range = rng))
})

# (B) Phase-1 beauty, SR and follow-up beauty as joint predictors of the beliefs
belief_models <- c(Syntheticness = "RealitySR", Authenticity = "AuthenticitySR")
belief_models <- belief_models[belief_models %in% names(estimates)]
beliefs <- lapply(belief_models, function(n) {
  lapply(setNames(nm = c("response", appraisal_info[[n]]$dpars)), function(p) appraisal_effects(estimates[[n]], par = p))
})
```

## How to read this report

Self-relevance (SR: "how much does this artwork relate to your own
experiences, personality or life?", 0 = Not at all to 6 = Very much) was
rated in the follow-up session, about 47 days after Phase 1, *after* the
debrief (all artworks were genuine human originals) and right after the
follow-up beauty rating, for the 48 old and 48 new artworks. The Phase-1 label
did not move it (see "Self-relevance ratings"). SR is therefore a label-free
measure of how much a person connects with a work, and it enters the models
as a **moderator or a predictor, never as a mediator of the label**.

The section follows the plan of the manuscript's "The Role of
Self-Relevance":

| question | model | outcome | predictors | data |
| --- | --- | --- | --- | --- |
| **(A)** Does self-relevance narrow the label gap (RQ3)? | **BeautySR** | Phase-1 `Beauty` (CHOCO) | `Condition * SR_w` | 220 follow-up participants × 48 old items |
|  | **MeaningSR** | Phase-1 `Meaning` (Discrete Beta, zero hurdle) | `Condition * SR_w` on `mu`, `phi`, `pzero` | same |
|  | **BeautySRControl** | Phase-1 `Beauty` | `Condition * (SR_w + Beauty2_w)` | same |
|  | **BeautySRBetween** | Phase-1 `Beauty` | `Condition * (SR_w + SR_b)`, `SR_b` = the participant's mean SR (centred) | same |
| **(B)** "Self-relevant = human"? | **RealitySR** | `Reality` (syntheticness; 0 = AI, 1 = Human) | `Condition * (Beauty_w + SR_w + Beauty2_w)` | 217 participants (follow-up and Phase 2) × 48 |
|  | **AuthenticitySR** | `Authenticity` (0 = Copy, 1 = Original) | same | same |
|  | **ArtificialitySR** | `PerceivedArtificiality` (0 = Very Human, 1 = Very Artificial) | `Type * (Beauty2_w + SR_w)` (Type = Old / New) | 220 participants, every item judged "new" |
| **(C)** Self-relevance and memory | *not defined yet*: categorical models as in `4_memory.qmd` | `AnswerCondition` / `AnswerBelief` | | 220 × 96 |
| **(D)** Individual differences | *not defined yet*: participant-level indices in `7_correlates.qmd` | | | 220 participants |

```{r}
#| results: asis

knitr::kable(
  tibble(Model = sr_models, Estimates = ifelse(has_est, "available", "not yet extracted")),
  format = "pipe", caption = "Status of the self-relevance models at render time."
)
```

`SR_w`, `Beauty_w`, `Beauty2_w` are the ratings on 0-1, centred within
participant over the model's rows: a slope reads "this artwork vs. my other
artworks", and 0 is the participant's average. Within participants, SR
correlates about .57 with follow-up beauty and .40 with Phase-1 beauty (see
"Self-relevance and the other ratings"), so follow-up beauty (label-free as
well) is the competing predictor wherever SR could stand for liking.

What the sections report, as posterior medians with 95% CI (HDI) and the
probability of direction (`pd`); "credible" = CI excludes 0:

- **(A) Label gap by self-relevance** (`moderation_effects()`): the label
  contrast (e.g. AI-Generated − Human Original) at low (−1 SD of `SR_w` over
  trials), average (0) and high (+1 SD) self-relevance, and **High − Low**,
  its change over that range (the interaction on the response scale). The
  gap *narrows* with SR when High − Low has the opposite sign to the gap
  (positive for a negative AI-Generated − Human Original gap). Also the **SR
  slope** per label (change per +10% of the SR scale, ≈ 0.6 points on 0-6)
  and its differences between labels. Units: % of the rating's scale (beauty
  slider; 6-point range for meaning) for the mean response, percentage
  points for the parameters (`mu`, `confright`, `confleft`, `pzero`).
  BeautySRControl evaluates everything at `Beauty2_w = 0` and adds the
  follow-up beauty slope per label: is it self-relevance or liking that goes
  with a larger or smaller gap?
- **(B) Self-relevance and human origin** (`appraisal_effects()`): the
  *unique* change in the belief per +10% of each predictor (Phase-1 beauty,
  SR, follow-up beauty), the others held at the participant's average, per
  label and between labels. Next to them, the same slopes from the models
  without SR (`RealityBeautyControl` / `AuthenticityBeautyControl`, same 217
  participants): does SR take over part of the "beautiful = human" cue? The
  decomposition of the label effect is also given; as the label moves
  neither SR nor follow-up beauty, their indirect effects should be ≈ 0.
  ArtificialitySR asks the same without any label: the SR and follow-up
  beauty slopes of perceived artificiality for old (missed) and new (never
  labelled) items.
- **(C, D)** are observed (not model-based) for now: recognition, source
  memory and false-memory attributions by SR (next to follow-up beauty), and
  participant-level indices (mean SR, SR–beauty coupling, the observed label
  gap) with their dispositional correlates.

Caveats: SR was rated ~47 days later and after the debrief, so a moderation
reads "works that a person *later* finds self-relevant were penalised less
(or more) by the label"; predictions are population-level (random effects at
0) and linear in `SR_w`, while SR is zero-inflated (about 38% of the ratings
are 0) and `r sum(summarise(dfmem, v = sd(SelfRelevance), .by = "Participant")$v == 0)`
participants gave the same SR to every artwork (`SR_w` = 0 throughout).

## Convergence

```{r}
#| results: asis

pending(sr_models)
```

```{r}
#| results: asis
#| eval: !expr length(estimates) > 0

convergence_by_class <- function(est) {
  est$convergence |>
    mutate(Class = case_when(
      startsWith(variable, "b_") | startsWith(variable, "Intercept") ~ "b (fixed effects)",
      startsWith(variable, "sd_") ~ "sd (random-effect SDs)",
      startsWith(variable, "cor_") ~ "cor (random-effect correlations)",
      .default = "other")) |>
    summarise(N = n(), Max_Rhat = round(max(rhat, na.rm = TRUE), 3),
              Min_ESS_bulk = round(min(ess_bulk, na.rm = TRUE)), .by = "Class") |>
    mutate(Model = est$outcome, .before = 1)
}

make_asis(
  make_tables(bind_rows(lapply(estimates, `[[`, "diag")),
              c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct"),
              "Convergence of the self-relevance models"),
  make_tables(bind_rows(lapply(estimates, convergence_by_class)),
              c("Model", "Class", "N", "Max_Rhat", "Min_ESS_bulk"),
              "Convergence by parameter class (the fixed effects are what the report uses)")
)
```

```{r}
# Helpers shared by the model sections

# Credible / Effect (sign) / formatted columns
format_effects <- function(dat) {
  dat |>
    mutate(Credible = sign(CI_low) == sign(CI_high),
           Effect = ifelse(!Credible, "n.s.", ifelse(Median < 0, "Negative", "Positive")),
           Diff = insight::format_value(Median, zap_small = TRUE),
           CI = sprintf("[%s, %s]", insight::format_value(CI_low, zap_small = TRUE),
                        insight::format_value(CI_high, zap_small = TRUE)),
           pd_fmt = insight::format_pd(pd, name = NULL))
}

# Observed trial means (x100: % of the 0-1 scale) with a 95% CI, per rating level
observed_by <- function(data, outcome, by = "Condition", level = "SR") {
  data |>
    filter(!is.na(.data[[outcome]]), !is.na(.data[[level]])) |>
    summarise(Mean = 100 * mean(.data[[outcome]]),
              SE = 100 * sd(.data[[outcome]]) / sqrt(n()),
              n = n(), .by = all_of(c(by, level))) |>
    mutate(Outcome = outcome)
}

plot_observed <- function(dat, by = "Condition", xlab = "Self-relevance (follow-up, 0-6)") {
  dat |>
    ggplot(aes(x = SR, y = Mean, color = .data[[by]])) +
    geom_line(position = position_dodge(width = 0.4), alpha = 0.6) +
    geom_pointrange(aes(ymin = Mean - 1.96 * SE, ymax = Mean + 1.96 * SE, size = n),
                    position = position_dodge(width = 0.4)) +
    facet_wrap(~Outcome, scales = "free_y") +
    scale_x_continuous(breaks = 0:6) +
    scale_size(range = c(0.1, 0.6), guide = "none") +
    scale_color_manual(values = cols) +
    labs(x = xlab, y = "Observed mean (% of the scale)",
         color = ifelse(by == "Condition", "Phase-1 label", by),
         caption = "Trial means with 95% CI (not model-based; trials are not independent). Point size: number of trials.") +
    theme_minimal() +
    theme(legend.position = "top", strip.text = element_text(face = "bold"))
}

# Population-level predictions over SR_w, per label (or Type)
plot_predictions <- function(name, xlab = "Self-relevance relative to the participant's mean (SR_w, 0-1 scale)") {
  est <- estimates[[name]]
  by <- est$by
  outcome <- mediation_info[[name]]$outcome
  labs_par <- par_labels[[outcome]]
  mats <- c(list(response = est$grid_draws), est$grid_dpars)
  mats <- mats[intersect(names(labs_par), names(mats))]
  rng <- if (outcome == "Meaning") 6 else 1
  pred <- bind_rows(lapply(names(mats), function(p) {
    P <- 100 * mats[[p]] / ifelse(p == "response", rng, 1)
    cbind(est$grid, Parameter = labs_par[[p]],
          Median = apply(P, 2, median),
          CI_low = apply(P, 2, quantile, 0.025),
          CI_high = apply(P, 2, quantile, 0.975))
  })) |>
    mutate(Parameter = factor(Parameter, levels = labs_par))
  sd_x <- est$mediator_summary[["SD"]] %||% 0.2

  ggplot(pred, aes(x = .data[[est$mediator]], color = .data[[by]], fill = .data[[by]])) +
    geom_vline(xintercept = c(-sd_x, sd_x), linetype = "dotted", color = "grey60") +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
    geom_line(aes(y = Median), linewidth = 1) +
    facet_wrap(~Parameter, scales = "free_y") +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    labs(x = xlab, y = "Predicted value (%)",
         color = ifelse(by == "Condition", "Label", by), fill = ifelse(by == "Condition", "Label", by),
         caption = "Population-level predictions (random effects at 0; follow-up beauty, where modelled, at the participant's mean) with 95% CI.\nDotted lines: -1 / +1 SD of SR_w over trials (Low / High in the tables).") +
    theme_minimal() +
    theme(legend.position = "top", strip.text = element_text(face = "bold"))
}

# (A) tables: label contrasts at average SR (and the main model's), label
# gaps at low / average / high SR, SR slopes per label
moderation_tables <- function(name) {
  est <- estimates[[name]]
  info <- mediation_info[[name]]
  labs_par <- par_labels[[info$outcome]]
  mod <- moderation[[name]]
  lab <- function(d, p) mutate(d, Parameter = factor(labs_par[[p]], levels = labs_par))

  con <- prep_contrasts(est$contrasts, info$outcome) |>
    filter(Parameter %in% names(labs_par)) |>
    mutate(Parameter = unname(labs_par[as.character(Parameter)]))
  ref <- prep_contrasts(reference[[info$outcome]]$contrasts, info$outcome) |>
    filter(Parameter == "response") |>
    mutate(Parameter = "Mean response, main model (all participants, no SR term)")
  at_labels <- c(Low = "Low SR (-1 SD)", Average = "Average SR", High = "High SR (+1 SD)", `High - Low` = "High - Low")
  gaps <- bind_rows(lapply(names(mod), function(p) lab(mod[[p]]$gaps, p))) |>
    format_effects() |>
    mutate(Contrast = factor(Contrast, levels = contrast_order),
           At = factor(at_labels[At], levels = at_labels)) |>
    arrange(Contrast, Parameter, At)
  slopes <- bind_rows(lapply(names(mod), function(p) lab(mod[[p]]$slopes, p))) |>
    format_effects() |>
    arrange(Parameter)

  make_asis(
    make_tables(bind_rows(con, ref) |> arrange(Contrast), c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: label contrasts at average self-relevance (%% of the scale / percentage points)", est$label)),
    make_tables(gaps, c("Contrast", "Parameter", "At", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: label gap at low, average and high self-relevance, and its change (High - Low)", est$label)),
    make_tables(slopes, c("Parameter", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
                sprintf("%s: change per +10%% of self-relevance, per label and between labels", est$label))
  )
}
```

## Self-relevance ratings

```{r}
#| fig-width: 9
#| fig-height: 4

dfmem |>
  summarise(n = n(), .by = c(Condition, SR)) |>
  mutate(p = n / sum(n), .by = "Condition") |>
  ggplot(aes(x = SR, y = p, fill = Condition)) +
  geom_col(position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = 0:6, labels = c("0\nNot at all", 1:5, "6\nVery much")) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Self-relevance (follow-up)", y = "Proportion of ratings", fill = "Phase-1 label") +
  theme_minimal() +
  theme(legend.position = "top")
```

Self-relevance was rated for `r nrow(dfmem)` artworks by
`r n_distinct(dfmem$Participant)` participants; `r insight::format_value(100 * mean(dfmem$SR == 0), digits = 1)`%
of the ratings are 0 ("Not at all") and `r insight::format_value(100 * mean(dfmem$SR >= 5), digits = 1)`%
are 5 or 6. The label effect on SR, from the SelfRelevance model (cumulative;
the change in the probability of answering each category, in percentage
points):

```{r}
#| results: asis

prep_contrasts(reference$SelfRelevance$contrasts, "SelfRelevance") |>
  filter(startsWith(Parameter, "response")) |>
  make_tables(c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Effect of the Phase-1 label on follow-up self-relevance (SelfRelevance model)")
```

### Self-relevance and the other ratings

Pooled within-participant correlations over the 48 old items (each rating
centred on the participant's mean; descriptive, trials are not independent):

```{r}
vars_w <- c("Self-relevance" = "SelfRelevance_w", "Follow-up beauty" = "Beauty2_w", "Beauty" = "Beauty_w",
            "Valence" = "Valence_w", "Meaning" = "Meaning_w", "Worth" = "Worth_w",
            "Syntheticness" = "Reality_w", "Authenticity" = "Authenticity_w")
r_w <- cor(dfsr[vars_w], use = "pairwise.complete.obs")
dimnames(r_w) <- list(names(vars_w), names(vars_w))
knitr::kable(round(r_w, 2), format = "pipe", caption = "Within-participant correlations (old items)")
```

## (A) Does self-relevance narrow the label gap?

The question the Introduction sets up (RQ3, after Vessel et al., 2023): is
the Phase-1 penalty of the AI-Generated (and Forgery) label smaller for works
the person finds self-relevant?

### Observed

```{r}
#| fig-width: 10
#| fig-height: 4.5

bind_rows(observed_by(dfsr, "Beauty"), observed_by(dfsr, "Meaning")) |>
  mutate(Outcome = recode(Outcome, Beauty = "Phase-1 beauty", Meaning = "Phase-1 meaning")) |>
  plot_observed()
```

### Beauty

```{r}
#| results: asis

pending("BeautySR")
```

```{r}
#| fig-width: 10
#| fig-height: 7.5
#| eval: !expr ready("BeautySR")

plot_predictions("BeautySR")
```

```{r}
#| results: asis
#| eval: !expr ready("BeautySR")

moderation_tables("BeautySR")
```

### Meaning

The `pzero` rows ask whether a self-relevant work escapes the "not at all
meaningful" answer that the AI label provokes.

```{r}
#| results: asis

pending("MeaningSR")
```

```{r}
#| fig-width: 10
#| fig-height: 4
#| eval: !expr ready("MeaningSR")

plot_predictions("MeaningSR")
```

```{r}
#| results: asis
#| eval: !expr ready("MeaningSR")

moderation_tables("MeaningSR")
```

### The categorical components on the odds scale

The gap tables above are in percentage points. For a probability parameter
(beauty's `mu`, the probability of the "beautiful" side; meaning's `pzero`),
a label effect that is constant on the log-odds scale shrinks in percentage
points as the baseline probability approaches 0 or 1, so a smaller gap at
high self-relevance can be scale compression rather than a weaker label
effect. `moderation_odds()` (estimates.R) gives, at -1 SD and +1 SD of
self-relevance, the two probabilities and their odds ratio, and the
difference in log odds ratios between the two levels ("High - Low"; 0 = no
moderation on the odds scale). This is the check behind the manuscript's
statement (2026-09-25) that self-relevance does not attenuate the label
penalty on any component: the AI label about doubles the odds of a "not at
all meaningful" answer at both levels of self-relevance.

```{r}
#| results: asis
#| eval: !expr ready("BeautySR", "MeaningSR")

odds_table <- function(name, par, what) {
  moderation_odds(estimates[[name]], par = par) |>
    mutate(
      Contrast = factor(Contrast, levels = contrast_order),
      `P (reference)` = ifelse(is.na(P_ref), "", sprintf("%.1f%% [%.1f, %.1f]", P_ref, P_ref_low, P_ref_high)),
      `P (label)` = ifelse(is.na(P), "", sprintf("%.1f%% [%.1f, %.1f]", P, P_low, P_high)),
      Estimate = ifelse(At == "High - Low",
                        sprintf("log-OR difference %.2f [%.2f, %.2f]", OR, OR_low, OR_high),
                        sprintf("OR %.2f [%.2f, %.2f]", OR, OR_low, OR_high)),
      Effect = ifelse(At == "High - Low",
                      ifelse(sign(OR_low) == sign(OR_high), ifelse(OR < 0, "Negative", "Positive"), "n.s."),
                      ifelse(OR_low > 1 | OR_high < 1, ifelse(OR < 1, "Negative", "Positive"), "n.s."))
    ) |>
    arrange(Contrast) |>
    (\(d) make_tables(d, c("Contrast", "At", "P (reference)", "P (label)", "Estimate", "Effect"),
                      sprintf("%s: %s at -1 SD (Low) and +1 SD (High) of self-relevance, on the odds scale", estimates[[name]]$label, what)))()
}
make_asis(
  odds_table("MeaningSR", "pzero", "probability of answering 'not at all meaningful' (pzero)"),
  odds_table("BeautySR", "mu", "probability of the 'beautiful' side (mu)")
)
```

### Controlling for follow-up beauty

The same model with follow-up beauty as a competing moderator
(predictions at `Beauty2_w = 0`). The last table puts the two side by side:
the change in the label gap per +10% of each rating (the differences between
labels of each slope), with and without follow-up beauty in the model.

```{r}
#| results: asis

pending("BeautySRControl")
```

```{r}
#| fig-width: 10
#| fig-height: 7.5
#| eval: !expr ready("BeautySRControl")

plot_predictions("BeautySRControl")
```

```{r}
#| results: asis
#| eval: !expr ready("BeautySRControl")

est_ctrl <- estimates$BeautySRControl
b2_slopes <- bind_rows(lapply(c("response", mediation_info$BeautySRControl$dpars), function(p) {
  covariate_slopes(est_ctrl, "Beauty2_w", par = p, pairs = TRUE) |>
    mutate(Parameter = factor(par_labels$Beauty[[p]], levels = par_labels$Beauty))
})) |>
  rename(Condition = Level) |>
  format_effects() |>
  arrange(Parameter)

gap_change <- bind_rows(
  mutate(moderation$BeautySRControl$response$slopes, Predictor = "Self-relevance", Model = "BeautySRControl"),
  mutate(rename(covariate_slopes(est_ctrl, "Beauty2_w", pairs = TRUE), Condition = Level),
         Predictor = "Follow-up beauty", Model = "BeautySRControl"),
  if (ready("BeautySR")) mutate(moderation$BeautySR$response$slopes, Predictor = "Self-relevance", Model = "BeautySR (no follow-up beauty)")
) |>
  filter(Condition %in% contrast_order) |>
  mutate(Contrast = factor(Condition, levels = contrast_order)) |>
  format_effects() |>
  arrange(Contrast, Predictor, Model)

make_asis(
  moderation_tables("BeautySRControl"),
  make_tables(b2_slopes, c("Parameter", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
              "Phase-1 beauty: change per +10% of follow-up beauty (SR at average), per label and between labels"),
  make_tables(gap_change, c("Contrast", "Predictor", "Model", "Diff", "CI", "pd_fmt", "Effect"),
              "Change in the label gap in Phase-1 beauty (% of the slider) per +10% of self-relevance or of follow-up beauty")
)
```

### Between persons: the participant's average self-relevance

`SR_w` compares an artwork with the participant's other artworks, so a person
who finds every work self-relevant and one who finds none are alike at
`SR_w = 0`. **BeautySRBetween** adds each participant's mean SR (`SR_b`, 0-1,
centred on the mean of the participant means) next to `SR_w` (a
within-between, or Mundlak, decomposition): its `Condition x SR_b` terms ask
whether people who find art more self-relevant show a smaller label gap. The
`SR_w` terms estimate the same within-person moderation as BeautySR. `SR_b`
slopes are per +10% of the participant's mean SR (0.6 points of the 0-6
scale); the participant means have an SD of
`r insight::format_value(6 * sd(summarise(dfsr, m = mean(SelfRelevance), .by = "Participant")$m))`
points. Between-person differences are open to scale use (a participant who
answers high on every slider), which the within-person slopes are not.

```{r}
#| results: asis

pending("BeautySRBetween")
```

```{r}
#| results: asis
#| eval: !expr ready("BeautySRBetween")

est_btw <- estimates$BeautySRBetween
sr_b_sd <- sd(summarise(dfsr, m = mean(SelfRelevance), .by = "Participant")$m)
btw_slopes <- bind_rows(lapply(c("response", mediation_info$BeautySRBetween$dpars), function(p) {
  covariate_slopes(est_btw, "SR_b", par = p, pairs = TRUE) |>
    mutate(Parameter = factor(par_labels$Beauty[[p]], levels = par_labels$Beauty))
})) |>
  rename(Condition = Level) |>
  format_effects() |>
  arrange(Parameter)

gap_levels <- bind_rows(
  mutate(moderation$BeautySRBetween$response$slopes, Predictor = "Self-relevance, within person (SR_w)", Model = "BeautySRBetween"),
  mutate(rename(covariate_slopes(est_btw, "SR_b", pairs = TRUE), Condition = Level),
         Predictor = "Self-relevance, participant's mean (SR_b)", Model = "BeautySRBetween"),
  if (ready("BeautySR")) mutate(moderation$BeautySR$response$slopes, Predictor = "Self-relevance, within person (SR_w)", Model = "BeautySR (within only)")
) |>
  filter(Condition %in% contrast_order) |>
  mutate(Contrast = factor(Condition, levels = contrast_order)) |>
  format_effects() |>
  arrange(Contrast, Predictor, Model)

make_asis(
  moderation_tables("BeautySRBetween"),
  make_tables(btw_slopes, c("Parameter", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
              "Phase-1 beauty: change per +10% of the participant's mean self-relevance (SR_b), per label and between labels"),
  make_tables(gap_levels, c("Contrast", "Predictor", "Model", "Diff", "CI", "pd_fmt", "Effect"),
              sprintf("Change in the label gap in Phase-1 beauty (%% of the slider) per +10%% of self-relevance, within and between persons (1 SD of the participant means = %.0f%% of the scale)", 100 * sr_b_sd))
)
```

## (B) Self-relevance and human origin

Are works that feel self-relevant judged more human and more original, over
and above how beautiful they are, and does that need a label?

### Observed

```{r}
#| fig-width: 10
#| fig-height: 4.5

bind_rows(observed_by(dfsr, "Reality"), observed_by(dfsr, "Authenticity")) |>
  mutate(Outcome = recode(Outcome, Reality = "Syntheticness (0 = AI, 100 = Human)",
                          Authenticity = "Authenticity (0 = Copy, 100 = Original)")) |>
  plot_observed()
```

```{r}
#| fig-width: 6
#| fig-height: 4.5

observed_by(filter(dfmem, Recognition == "No"), "PerceivedArtificiality", by = "Type") |>
  mutate(Outcome = "Perceived artificiality, items judged new (0 = Very Human, 100 = Very Artificial)") |>
  plot_observed(by = "Type")
```

### Syntheticness and authenticity

```{r}
#| results: asis

pending("RealitySR", "AuthenticitySR")
```

```{r}
#| fig-width: 10
#| fig-height: 5.5
#| eval: !expr length(beliefs) > 0

dat_cues <- bind_rows(lapply(names(beliefs), function(o) mutate(beliefs[[o]]$response$cues, Belief = o))) |>
  mutate(Predictor = factor(predictor_labels[Mediator], levels = predictor_labels))

dat_cues |>
  filter(Condition %in% levels(dfsr$Condition)) |>
  mutate(Condition = factor(Condition, levels = levels(dfsr$Condition))) |>
  ggplot(aes(x = Median, y = Predictor, xmin = CI_low, xmax = CI_high, color = Condition)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_pointrange(position = position_dodge(width = 0.5)) +
  facet_wrap(~Belief) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = cols) +
  labs(x = "Change in the belief per +10% of the predictor (% of the belief slider, 95% HDI)", y = NULL,
       color = "Label", caption = "The other two predictors held at the participant's average.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold"))
```

```{r}
#| results: asis
#| eval: !expr length(beliefs) > 0

tab_cues <- bind_rows(lapply(names(beliefs), function(o) {
  labs_par <- par_labels[[appraisal_info[[belief_models[[o]]]]$outcome]]
  bind_rows(lapply(names(beliefs[[o]]), function(p) {
    mutate(beliefs[[o]][[p]]$cues, Parameter = labs_par[[p]])
  })) |>
    mutate(Contrast = o)
})) |>
  mutate(Predictor = factor(predictor_labels[Mediator], levels = predictor_labels)) |>
  format_effects() |>
  arrange(Contrast, Predictor, Parameter)

# The same slopes without SR in the model (same 217 participants)
tab_ref <- bind_rows(lapply(names(beliefs), function(o) {
  n <- belief_models[[o]]
  ctrl <- reference[[paste0(appraisal_info[[n]]$outcome, "BeautyControl")]]
  bind_rows(
    mutate(dat_cues[dat_cues$Belief == o, ], Model = n),
    mutate(rename(grid_slopes(ctrl), Condition = Level), Predictor = "Phase-1 beauty", Model = paste0(ctrl$outcome, " (no SR)")),
    mutate(rename(covariate_slopes(ctrl, "Beauty2_w", pairs = TRUE), Condition = Level), Predictor = "Follow-up beauty", Model = paste0(ctrl$outcome, " (no SR)"))
  ) |>
    mutate(Contrast = o)
})) |>
  mutate(Predictor = factor(Predictor, levels = predictor_labels),
         Condition = factor(Condition, levels = c(levels(dfsr$Condition), contrast_order))) |>
  format_effects() |>
  arrange(Contrast, Predictor, Condition, Model)

tab_dec <- bind_rows(lapply(names(beliefs), function(o) {
  mutate(beliefs[[o]]$response$effects, Contrast = paste0(o, ": ", Contrast))
})) |>
  filter(Path %in% c("Total", "Direct", "Indirect (Beauty)", "Indirect (SR)", "Indirect (Beauty2)",
                     "Mediator (Beauty)", "Mediator (SR)", "Mediator (Beauty2)")) |>
  mutate(Path = str_replace_all(Path, c("\\(SR\\)" = "(Self-relevance)", "\\(Beauty2\\)" = "(Follow-up beauty)", "\\(Beauty\\)" = "(Phase-1 beauty)"))) |>
  format_effects()

tab_con <- bind_rows(lapply(names(beliefs), function(o) {
  n <- belief_models[[o]]
  outcome <- appraisal_info[[n]]$outcome
  bind_rows(
    prep_contrasts(estimates[[n]]$contrasts, outcome) |> mutate(Model = n),
    prep_contrasts(reference[[outcome]]$contrasts, outcome) |> mutate(Model = paste(outcome, "(main model, no rating terms)"))
  ) |>
    filter(Parameter %in% c("response", "mu", "confright", "confleft")) |>
    mutate(Contrast = paste0(o, ": ", Contrast))
})) |>
  arrange(Contrast, Parameter)

make_asis(
  make_tables(tab_cues, c("Contrast", "Predictor", "Parameter", "Condition", "Diff", "CI", "pd_fmt", "Effect"),
              "Unique change in the belief per +10% of each predictor, the others at the participant's average, per label and between labels (% of the slider / percentage points)"),
  make_tables(tab_ref, c("Contrast", "Predictor", "Condition", "Model", "Diff", "CI", "pd_fmt", "Effect"),
              "Mean response: the same slopes with and without self-relevance in the model"),
  make_tables(tab_dec, c("Contrast", "Path", "Diff", "CI", "pd_fmt", "Effect"),
              "Decomposition of the label effect (% of the belief slider; Mediator rows: the label's shift in that rating, % of its scale)"),
  make_tables(tab_con, c("Contrast", "Model", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Label contrasts at the participant's average ratings, next to the main model")
)
```

### Never-labelled artworks: perceived artificiality

```{r}
#| results: asis

pending("ArtificialitySR")
```

```{r}
#| fig-width: 10
#| fig-height: 7.5
#| eval: !expr ready("ArtificialitySR")

plot_predictions("ArtificialitySR")
```

```{r}
#| results: asis
#| eval: !expr ready("ArtificialitySR")

est_art <- estimates$ArtificialitySR
labs_art <- par_labels$PerceivedArtificiality
dat_art <- bind_rows(lapply(c("response", mediation_info$ArtificialitySR$dpars), function(p) {
  bind_rows(
    mutate(grid_slopes(est_art, par = p), Predictor = "Self-relevance", Model = "ArtificialitySR"),
    mutate(covariate_slopes(est_art, "Beauty2_w", par = p, pairs = TRUE), Predictor = "Follow-up beauty", Model = "ArtificialitySR"),
    mutate(grid_slopes(reference$ArtificialityBeauty, par = p), Predictor = "Follow-up beauty", Model = "ArtificialityBeauty (no SR)")
  ) |>
    mutate(Parameter = factor(labs_art[[p]], levels = labs_art))
})) |>
  mutate(Predictor = factor(Predictor, levels = predictor_labels)) |>
  format_effects() |>
  arrange(Predictor, Parameter, Model)

make_asis(
  make_tables(prep_contrasts(est_art$contrasts, "PerceivedArtificiality") |> filter(Parameter %in% c("response", "mu", "confright", "confleft")),
              c("Contrast", "Parameter", "Diff", "CI", "pd_fmt", "Effect"),
              "Perceived artificiality: New - Old items at average ratings (% of the slider / percentage points)"),
  make_tables(dat_art, c("Predictor", "Parameter", "Model", "Level", "Diff", "CI", "pd_fmt", "Effect"),
              "Change in perceived artificiality per +10% of self-relevance or follow-up beauty, for old (missed) and new (never labelled) items, and their difference")
)
```

## (C) Self-relevance and memory

The self-reference effect (Lee et al., 2023; Salgues et al., 2024) predicts
better memory for self-relevant works. Observed rates and an lme4 pilot
first, then the categorical model (`MemorySR`, as in `4_memory.qmd`) that
separates hits from false alarms. The models of the recalled belief and label
with SR as a covariate are in `4_memory.qmd` ("Memory or Re-inference?").
Chance levels: 1/3 for the label, 1/4 for the belief.

```{r}
#| fig-width: 10
#| fig-height: 4.5

# "Yes" rate by rating level, for old (hits) and new (false alarms) items,
# by SR and, for comparison, by follow-up beauty on the same 0-6 grid
bind_rows(
  mutate(dfmem, Level = SR, Predictor = "Self-relevance (0-6)"),
  mutate(dfmem, Level = round(Beauty2 * 6), Predictor = "Follow-up beauty (slider, 7 bins)")
) |>
  summarise(p = mean(Recognition == "Yes"), n = n(), .by = c(Predictor, Type, Level)) |>
  mutate(SE = sqrt(p * (1 - p) / n)) |>
  ggplot(aes(x = Level, y = 100 * p, color = Type)) +
  geom_line(alpha = 0.6) +
  geom_pointrange(aes(ymin = 100 * (p - 1.96 * SE), ymax = 100 * (p + 1.96 * SE), size = n)) +
  facet_wrap(~Predictor) +
  scale_x_continuous(breaks = 0:6) +
  scale_size(range = c(0.1, 0.6), guide = "none") +
  scale_color_manual(values = cols, labels = c(Old = "Old (hits)", New = "New (false alarms)")) +
  labs(x = "Rating level", y = "Answered \"seen before\" (%)", color = NULL,
       caption = "Observed rates with 95% CI (not model-based). Point size: number of trials.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold"))
```

Self-relevance and follow-up beauty correlate, so the rates below split the
items at the participant's own mean on both:

```{r}
dfmem |>
  mutate(SR = ifelse(SelfRelevance_w > 0, "SR above own mean", "SR at or below own mean"),
         Beauty = ifelse(Beauty2_w > 0, "Beauty above own mean", "Beauty at or below own mean")) |>
  summarise(Yes = 100 * mean(Recognition == "Yes"), n = n(), .by = c(Type, SR, Beauty)) |>
  mutate(Yes = sprintf("%.1f%% (n = %d)", Yes, n)) |>
  select(-n) |>
  pivot_wider(names_from = Type, values_from = Yes, names_prefix = "Seen before: ") |>
  arrange(SR, Beauty) |>
  knitr::kable(format = "pipe", caption = "\"Seen before\" rate by self-relevance and follow-up beauty (relative to the participant's mean)")
```

Both ratings were given in the same trial as the recognition judgment, so a
higher "seen before" rate for self-relevant or beautiful works can be better
memory (more hits) or a bias to call a liked work familiar (more false
alarms too). An lme4 pilot (not reported) separates the two: "seen before"
on item type and both ratings (centred within participant over the 96
artworks, with quadratic terms); the `New items x` rows are the difference in
slope for new items (false alarms) relative to old items (hits).

```{r}
#| label: pilot-false-alarms
#| cache: true
#| cache.extra: !expr rlang::hash(dfmem)
#| warning: false

pilot_fa <- dfmem |>
  filter(!is.na(SelfRelevance_w), !is.na(Beauty2_w)) |>
  mutate(Seen = as.integer(Recognition == "Yes"), SR_w = SelfRelevance_w) |>
  (\(d) pilot_coefs("Seen ~ Type * (SR_w + I(SR_w^2) + Beauty2_w + I(Beauty2_w^2)) + (Type | Participant) + (1 | Item)",
                    d, family = binomial))()
```

```{r}
#| results: asis

make_asis(make_tables(
  pilot_fa |>
    filter(Term != "(Intercept)") |>
    mutate(Term = pilot_term(Term), z = Estimate / SE,
           Effect = ifelse(abs(z) < 1.96, "n.s.", ifelse(Estimate < 0, "Negative", "Positive")),
           across(c(Estimate, SE, z), \(x) insight::format_value(x))),
  c("Term", "Estimate", "SE", "z", "Effect"),
  "lme4 pilot: log-odds of answering \"seen before\" (ratings on 0-1, centred within participant; reference: old items)"))
```

Self-relevance and follow-up beauty raise the "seen before" rate at least as
much for new artworks as for old ones (the `New items x` slope differences
are close to zero): in this design they index a bias to judge a
self-relevant or liked work as familiar, not better memory. Any model-based
test of a self-reference effect on memory must therefore include the new
items (as `MemoryCondition` does, with its `New Items` level), so that an
effect on hits can be told apart from one on false alarms. The Phase-1
appraisal, rated before any memory judgment and for old items only, is the
cleaner predictor of what was encoded (`4_memory.qmd`, "Memory by Phase-1
Appraisal").

### Model: MemorySR

**MemorySR** (`server/models.R`, 2026-09-25): the categorical model of the
recalled label (as `MemoryCondition`, "Not recognized" carrying recognition)
on all 96 items, with self-relevance and follow-up beauty (centred within
participant over the 96 artworks, quadratic terms as `MemoryAppraisal`)
given separate slopes for old and new items (`Type:`). The Old slopes are
the effect on hits, the New slopes the effect on false alarms; a
self-reference effect on *memory* needs the two to differ. Predictions per
label are averaged over the three old labels ("Old") and shown against the
new items ("New"). Probabilities compress near 0, and the false-alarm rate
is near 10% while the hit rate is near 45%, so the comparison that matters
is on the odds scale (last table).

```{r}
#| results: asis

memsr_ready <- file.exists("models/estimates/MemorySR.rds")
if (!memsr_ready) {
  make_asis("", '::: {.callout-warning title="Estimates not available yet"}',
            "`MemorySR`: in `analysis/server`, `./hpc combine MemorySR` (check 4,000 draws), `./hpc extract MemorySR`, then `./hpc pull 'estimates/MemorySR.rds'`.",
            ":::", "")
}
```

```{r}
#| results: asis
#| eval: !expr memsr_ready

est_sr <- read_estimates("MemorySR")$MemorySR
g_sr <- est_sr$grid
D_sr <- est_sr$draws
old_levels <- setdiff(unique(g_sr$Level), "New Items")
rows <- lapply(setNames(nm = c(old_levels, "New Items")), function(l) which(g_sr$Level == l))
# Old: the three labels averaged (same grid order within each level)
D_old <- Reduce(`+`, lapply(old_levels, function(l) D_sr[, rows[[l]], , drop = FALSE])) / length(old_levels)
est_old <- list(grid = mutate(g_sr[rows[[old_levels[1]]], ], Level = "Old"), draws = D_old)
est_new <- list(grid = mutate(g_sr[rows[["New Items"]], ], Level = "New"), draws = D_sr[, rows[["New Items"]], , drop = FALSE])
fx_old <- memory_grid_effects(est_old)
fx_new <- memory_grid_effects(est_new)
sr_labels <- c(SR_w = "Self-relevance", Beauty2_w = "Follow-up beauty")
fmt_pp <- function(d) {
  d |> mutate(Predictor = sr_labels[Predictor],
              Effect_at = Effect,
              Effect = ifelse(sign(CI_low) != sign(CI_high), "n.s.", ifelse(Median < 0, "Negative", "Positive")),
              Diff = insight::format_value(Median),
              CI = sprintf("[%s, %s]", insight::format_value(CI_low), insight::format_value(CI_high)),
              pd_fmt = insight::format_pd(pd, name = NULL))
}
rec_pp <- bind_rows(fx_old$effects, fx_new$effects) |>
  filter(Outcome == "P(recognised)", Effect %in% c("-2 SD", "+2 SD")) |> fmt_pp()
lab_pp <- fx_old$effects |>
  filter(Outcome != "P(recognised)", Type == "unique", Effect %in% c("-2 SD", "+2 SD")) |> fmt_pp()
# Odds scale: log odds of "seen before" at +/-2 SD minus at the mean, for
# old (hits) and new (false alarms) items, and their difference
lo <- function(est, type, pred, at) {
  g <- est$grid; i <- which(g$Type == type & g$Predictor == pred & !is.na(g$At) & g$At == at)
  p <- 1 - est$draws[, i, "Not recognized"]
  log(p / (1 - p))
}
odds <- bind_rows(lapply(c("unique", "joint"), function(type) bind_rows(lapply(names(sr_labels), function(pred) bind_rows(lapply(c("-2 SD", "+2 SD"), function(at) {
  d_old <- lo(est_old, type, pred, at) - lo(est_old, type, pred, "Mean")
  d_new <- lo(est_new, type, pred, at) - lo(est_new, type, pred, "Mean")
  desc <- function(x) { ci <- bayestestR::hdi(x, ci = 0.95); c(median(x), ci$CI_low, ci$CI_high, as.numeric(bayestestR::p_direction(x))) }
  o <- desc(d_old); n <- desc(d_new); dd <- desc(d_new - d_old)
  data.frame(Type = type, Predictor = sr_labels[pred], At = at,
             `Old (hits)` = sprintf("%.2f [%.2f, %.2f]", o[1], o[2], o[3]),
             `New (false alarms)` = sprintf("%.2f [%.2f, %.2f]", n[1], n[2], n[3]),
             `New - Old` = sprintf("%.2f [%.2f, %.2f]", dd[1], dd[2], dd[3]),
             pd_fmt = insight::format_pd(dd[4], name = NULL),
             Effect = ifelse(sign(dd[2]) != sign(dd[3]), "n.s.", ifelse(dd[1] < 0, "Negative", "Positive")),
             check.names = FALSE)
}))))))
make_asis(
  make_tables(est_sr$diag, c("Model", "Family", "N_obs", "N_participants", "Chains", "Draws", "Max_Rhat", "Min_ESS_ratio", "Divergent_pct"),
              "Convergence of MemorySR"),
  make_tables(rec_pp, c("Level", "Type", "Predictor", "Effect_at", "Diff", "CI", "pd_fmt", "Effect"),
              "MemorySR: P(\"seen before\") at -2 / +2 SD of the rating minus at the participant's mean, for old items (hits, averaged over the three labels) and new items (false alarms), percentage points (unique: other rating at the mean; joint: it follows along)"),
  make_tables(odds, c("Type", "Predictor", "At", "Old (hits)", "New (false alarms)", "New - Old", "pd_fmt", "Effect"),
              "MemorySR: the same on the log-odds scale (log odds ratio of \"seen before\" at -2 / +2 SD vs. the mean), and the difference between new and old items (0 = the rating raises false alarms as much as hits)"),
  make_tables(lab_pp, c("Type", "Predictor", "Effect_at", "Outcome", "Diff", "CI", "pd_fmt", "Effect"),
              "MemorySR: recalled label among recognised old artworks at -2 / +2 SD of the rating minus at the mean (label shown averaged), percentage points")
)
```

```{r}
#| fig-width: 11
#| fig-height: 4
#| eval: !expr memsr_ready

bind_rows(fx_old$curves, fx_new$curves) |>
  filter(Type == "unique", abs(x) <= 0.5, Outcome == "P(recognised)") |>
  mutate(Predictor = sr_labels[Predictor], Level = fct_relevel(Level, "Old", "New")) |>
  ggplot(aes(x = 100 * x, y = Median, color = Level, fill = Level)) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
  geom_line(linewidth = 1) +
  facet_wrap(~Predictor) +
  scale_color_manual(values = c(Old = "#F51D56", New = "#607D8B"), labels = c(Old = "Old (hits)", New = "New (false alarms)")) +
  scale_fill_manual(values = c(Old = "#F51D56", New = "#607D8B"), labels = c(Old = "Old (hits)", New = "New (false alarms)")) +
  labs(x = "Rating relative to the participant's mean (points of the scale)", y = "Answered \"seen before\" (%)",
       color = NULL, fill = NULL,
       caption = "Population-level predictions (random effects at 0; the other rating at the participant's mean; old items averaged over the three labels) with 95% CI.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold"))
```

```{r}
#| eval: !expr memsr_ready

write.csv(bind_rows(
  mutate(bind_rows(fx_old$effects, fx_new$effects), Table = "Probability (pp)"),
  mutate(odds, Table = "Log odds ratio")
), "../data/results_selfrelevance_memory.csv", row.names = FALSE)
```

### Observed: source memory by self-relevance

```{r}
#| fig-width: 10
#| fig-height: 4.5

# Source memory of the items recognised as old, by SR (binned: 5-6 are rare)
sr_bins <- function(x) cut(x, c(-1, 0, 2, 4, 6), labels = c("0", "1-2", "3-4", "5-6"))
dfmem |>
  filter(Type == "Old", Recognition == "Yes") |>
  mutate(SR_bin = sr_bins(SR)) |>
  reframe(tibble(Question = c("Label (chance 33%)", "Own Phase-2 belief (chance 25%)"),
                 p = c(mean(as.character(AnswerCondition) == as.character(Condition)),
                       mean((AnswerBelief == Belief)[Belief != "None"])),
                 n = c(n(), sum(Belief != "None"))),
          .by = "SR_bin") |>
  mutate(SE = sqrt(p * (1 - p) / n)) |>
  ggplot(aes(x = SR_bin, y = 100 * p, color = Question, group = Question)) +
  geom_hline(yintercept = c(100 / 3, 25), linetype = "dotted", color = "grey60") +
  geom_line(alpha = 0.6) +
  geom_pointrange(aes(ymin = 100 * (p - 1.96 * SE), ymax = 100 * (p + 1.96 * SE))) +
  scale_color_manual(values = c("#7E57C2", "#26A69A")) +
  labs(x = "Self-relevance (follow-up)", y = "Correct source answer (%)", color = NULL,
       caption = "Items recognised as old; observed rates with 95% CI.") +
  theme_minimal() +
  theme(legend.position = "top")
```

Which label do people attach to what they recognise? For old items the
answer can be correct; for new items (false alarms) every label is
fabricated, and a "Human Original" attribution to a self-relevant but never
seen work would be the false-memory counterpart of "self-relevant = human".

```{r}
#| fig-width: 10
#| fig-height: 4.5

dfmem |>
  filter(Recognition == "Yes") |>
  mutate(SR_bin = sr_bins(SR),
         AnswerCondition = fct_drop(AnswerCondition)) |>
  summarise(n = n(), .by = c(Condition, SR_bin, AnswerCondition)) |>
  mutate(p = n / sum(n), N = sum(n), .by = c(Condition, SR_bin)) |>
  ggplot(aes(x = SR_bin, y = 100 * p, fill = AnswerCondition)) +
  geom_col(position = "stack", width = 0.8) +
  geom_text(data = \(d) distinct(d, Condition, SR_bin, N), aes(x = SR_bin, y = 104, label = paste0("n=", N)),
            inherit.aes = FALSE, size = 2.8, color = "grey40") +
  facet_wrap(~Condition, nrow = 1, labeller = as_labeller(\(x) ifelse(x == "New Items", "New items (false alarms)", paste("Shown as", x)))) +
  scale_fill_manual(values = cols) +
  labs(x = "Self-relevance (follow-up)", y = "Recalled label (%)", fill = "Recalled label",
       caption = "Items answered \"seen before\"; observed proportions.") +
  theme_minimal() +
  theme(legend.position = "top", strip.text = element_text(face = "bold"))
```

## (D) Individual differences

Observed participant-level indices (the model-based ones, with their
reliability, belong in `7_correlates.qmd`): the participant's mean SR, the
**SR–beauty coupling** (correlation of SR with follow-up beauty over their 96
artworks), and the observed label gaps in Phase-1 beauty (mean over 16
artworks per label, % of the slider; noisy).

```{r}
dfind <- dfmem |>
  summarise(SR_mean = 100 * mean(SelfRelevance),
            Coupling = suppressWarnings(cor(SelfRelevance, Beauty2)),
            .by = "Participant") |>
  left_join(
    dfsr |>
      summarise(Beauty = 100 * mean(Beauty), .by = c(Participant, Condition)) |>
      pivot_wider(names_from = Condition, values_from = Beauty) |>
      transmute(Participant,
                Gap_AI = `AI-Generated` - `Human Original`,
                Gap_Forgery = `Human Forgery` - `Human Original`),
    by = "Participant") |>
  left_join(select(dfsub, Participant, MINT_Awareness, MINT_Deficit, MINT_Visceroception,
                   BAIT_Positive, BAIT_Negative, Art_Expertise), by = "Participant")

describe_distribution(select(dfind, SR_mean, Coupling, Gap_AI, Gap_Forgery)) |>
  as.data.frame() |>
  select(Variable, Mean, SD, Min, Max, n) |>
  knitr::kable(format = "pipe", digits = 2, caption = "Participant-level indices (SR_mean and gaps in % of the scale)")
```

```{r}
correlation::correlation(select(dfind, SR_mean, Coupling),
                         select(dfind, Gap_AI, Gap_Forgery, MINT_Awareness, MINT_Deficit, MINT_Visceroception,
                                BAIT_Positive, BAIT_Negative, Art_Expertise),
                         p_adjust = "none") |>
  as.data.frame() |>
  transmute(Index = Parameter1, With = Parameter2,
            r = sprintf("%.2f", r),
            CI = sprintf("[%.2f, %.2f]", CI_low, CI_high),
            p = insight::format_p(p, name = NULL), n = n_Obs) |>
  knitr::kable(format = "pipe", row.names = FALSE, caption = "Pearson correlations of the SR indices (exploratory, no correction; questionnaire scores are NA after a failed attention check)")
```

## Manuscript figure

`figures/figure_selfrelevance.png`, the figure of the manuscript's "The Role
of Self-Relevance": Phase-1 beauty and meaning by self-relevance, per label,
from BeautySR and MeaningSR. Self-relevance is continuous in the models
(`SR_w`, linear on the link scale), and the x-axis is `SR_w` in points of the
0-6 scale (0 = the participant's own mean). Lines and ribbons: population-level
predictions with 95% CI (the observed means by self-relevance are in "(A)
Observed" above).

```{r}
#| label: fig-figure-selfrelevance
#| fig-width: 10.5
#| fig-height: 4.5
#| eval: !expr ready("BeautySR", "MeaningSR")

fig_outcomes <- c(BeautySR = "Beauty", MeaningSR = "Meaningfulness")
sd_pts <- 6 * estimates$BeautySR$mediator_summary[["SD"]] # Low / High in the tables

fig_pred <- bind_rows(lapply(names(fig_outcomes), function(n) {
  est <- estimates[[n]]
  P <- 100 * est$grid_draws / ifelse(mediation_info[[n]]$outcome == "Meaning", 6, 1)
  tibble(Condition = est$grid$Condition, x = 6 * est$grid$SR_w, Outcome = fig_outcomes[[n]],
         Median = apply(P, 2, median),
         CI_low = apply(P, 2, quantile, 0.025),
         CI_high = apply(P, 2, quantile, 0.975))
})) |>
  filter(abs(x) <= 3)

figure_selfrelevance <- ggplot(fig_pred, aes(x = x, color = Condition, fill = Condition)) +
  geom_vline(xintercept = c(-sd_pts, sd_pts), linetype = "dotted", color = "grey60") +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.15, color = NA) +
  geom_line(aes(y = Median), linewidth = 1.3) +
  facet_wrap(~Outcome, scales = "free_y") +
  scale_x_continuous(breaks = -3:3, labels = c("-3", "-2", "-1", "Own\nmean", "+1", "+2", "+3")) +
  scale_color_manual(values = cols[levels(dfsr$Condition)]) +
  scale_fill_manual(values = cols[levels(dfsr$Condition)]) +
  labs(x = "Self-relevance at follow-up (points above or below the participant's own mean, 0-6 scale)",
       y = "Phase 1 rating (% of the scale)") +
  theme_minimal() +
  theme(legend.position = "bottom", legend.title = element_blank(),
        strip.text = element_text(face = "bold", size = 12))

ggsave("figures/figure_selfrelevance.png", figure_selfrelevance, width = 10.5, height = 4.5, dpi = 300, bg = "white")
figure_selfrelevance
```

## Summary

Auto-generated summary of the model-based results (for text readers):

```{r}
#| results: asis

fmt <- function(r) {
  f <- function(x) insight::format_value(x, zap_small = TRUE)
  sprintf("%s [%s, %s]", f(r$Median), f(r$CI_low), f(r$CI_high))
}
lines <- c()
for (n in names(moderation)) {
  g <- moderation[[n]]$response$gaps
  s <- moderation[[n]]$response$slopes
  lines <- c(lines, sprintf("- **%s** (%% of the scale): %s", estimates[[n]]$label, paste(vapply(contrast_order, function(ct) {
    d <- g[g$Contrast == ct, ]
    sprintf("%s gap %s at low SR, %s at high SR (change %s)", ct, fmt(d[d$At == "Low", ]), fmt(d[d$At == "High", ]), fmt(d[d$At == "High - Low", ]))
  }, ""), collapse = "; ")),
  sprintf("  - SR slope per +10%%: %s.", paste(sprintf("%s %s", levels(dfsr$Condition), vapply(levels(dfsr$Condition), function(cnd) fmt(s[s$Condition == cnd, ]), "")), collapse = ", ")))
}
for (o in names(beliefs)) {
  cues <- beliefs[[o]]$response$cues
  lines <- c(lines, sprintf("- **%s** (%s; %% of the slider per +10%% of the predictor, others at average): %s.", o, belief_models[[o]],
    paste(vapply(names(predictor_labels), function(k) {
      sprintf("%s: %s", predictor_labels[[k]], paste(sprintf("%s %s", levels(dfsr$Condition), vapply(levels(dfsr$Condition), function(cnd) {
        fmt(cues[cues$Mediator == k & cues$Condition == cnd, ])
      }, "")), collapse = ", "))
    }, ""), collapse = "; ")))
}
if (ready("ArtificialitySR")) {
  sl <- grid_slopes(estimates$ArtificialitySR)
  cv <- covariate_slopes(estimates$ArtificialitySR, "Beauty2_w", pairs = TRUE)
  lines <- c(lines, sprintf("- **Perceived artificiality** (items judged new, %% of the slider per +10%%): SR slope Old %s, New %s; follow-up beauty slope Old %s, New %s.",
    fmt(sl[sl$Level == "Old", ]), fmt(sl[sl$Level == "New", ]), fmt(cv[cv$Level == "Old", ]), fmt(cv[cv$Level == "New", ])))
}
if (length(lines) == 0) lines <- "- No self-relevance model has been extracted yet (see the Convergence section)."
make_asis(lines)
```

Files written (once the corresponding estimates exist):

- `data/results_selfrelevance_moderation.csv`: (A) label gaps at low / average / high SR and their change, SR slopes per label, and (BeautySRControl) the follow-up beauty slopes; mean response and every modelled parameter.
- `data/results_selfrelevance_beliefs.csv`: (B) unique slopes of Phase-1 beauty, SR and follow-up beauty per label (`Cue`), the decomposition of the label effect (`Decomposition`), and the perceived-artificiality slopes per item type.
- `data/results_selfrelevance_contrasts.csv`: label contrasts at average ratings, every parameter, per model.

```{r}
#| eval: !expr length(estimates) > 0

if (length(moderation) > 0) {
  bind_rows(lapply(names(moderation), function(n) {
    bind_rows(lapply(names(moderation[[n]]), function(p) {
      bind_rows(
        mutate(moderation[[n]][[p]]$gaps, Table = "Gap"),
        mutate(rename(moderation[[n]][[p]]$slopes, Contrast = Condition), Table = "SR slope"),
        if (n == "BeautySRControl") mutate(rename(covariate_slopes(estimates[[n]], "Beauty2_w", par = p, pairs = TRUE), Contrast = Level), Table = "Beauty2 slope"),
        if (n == "BeautySRBetween") mutate(rename(covariate_slopes(estimates[[n]], "SR_b", par = p, pairs = TRUE), Contrast = Level), Table = "SR_b slope")
      ) |>
        mutate(Model = n, Parameter = p, .before = 1)
    }))
  })) |>
    write.csv("../data/results_selfrelevance_moderation.csv", row.names = FALSE)
}

beliefs_out <- bind_rows(
  bind_rows(lapply(names(beliefs), function(o) {
    bind_rows(lapply(names(beliefs[[o]]), function(p) {
      bind_rows(
        mutate(rename(beliefs[[o]][[p]]$cues, Predictor = Mediator, Contrast = Condition), Table = "Cue"),
        mutate(rename(beliefs[[o]][[p]]$effects, Predictor = Path), Table = "Decomposition")
      ) |>
        mutate(Model = belief_models[[o]], Parameter = p, .before = 1)
    }))
  })),
  if (ready("ArtificialitySR")) bind_rows(lapply(c("response", mediation_info$ArtificialitySR$dpars), function(p) {
    bind_rows(
      mutate(rename(grid_slopes(estimates$ArtificialitySR, par = p), Contrast = Level), Predictor = "SR"),
      mutate(rename(covariate_slopes(estimates$ArtificialitySR, "Beauty2_w", par = p, pairs = TRUE), Contrast = Level), Predictor = "Beauty2")
    ) |>
      mutate(Model = "ArtificialitySR", Parameter = p, Table = "Slope by Type", .before = 1)
  }))
)
if (nrow(beliefs_out) > 0) write.csv(beliefs_out, "../data/results_selfrelevance_beliefs.csv", row.names = FALSE)

bind_rows(lapply(names(estimates), function(n) {
  outcome <- if (n %in% names(mediation_info)) mediation_info[[n]]$outcome else appraisal_info[[n]]$outcome
  prep_contrasts(estimates[[n]]$contrasts, outcome) |>
    mutate(Model = n) |>
    select(Model, Contrast, Parameter, Difference, CI_low, CI_high, Difference_pct, CI_low_pct, CI_high_pct, pd, Credible, Effect)
})) |>
  write.csv("../data/results_selfrelevance_contrasts.csv", row.names = FALSE)
```

## Exploratory checks: centring and shape

Not reported in the manuscript; kept as a record of what was checked
(2026-09-24), for this paper's robustness and for future studies. The
models above centre self-relevance (and beauty) within participant and enter
it linearly. The checks below probe both with quick frequentist fits (lme4
linear mixed models on the 0-100 scale, mgcv GAMs); the rationale for the
centring is set out in `5_realitydeterminants.qmd` ("Exploratory checks").
In short: centring keeps the units of the scale and removes only the
participant's average; it is the right predictor for within-person questions
(is *this* artwork, more self-relevant than my others, penalised less?), and
the between-person question (are people who find art self-relevant less
biased?) needs the participant's mean as a second predictor, not a raw
rating. That question is answered by **BeautySRBetween** in (A); the pilots
below extend the comparison to the other models.

### Within-participant centring

```{r}
#| label: pilot-sr-centring
#| cache: true
#| cache.extra: !expr rlang::hash(list(dfsr, dfmem))
#| warning: false

# Three versions of each rated predictor x: x_w (centred within participant,
# as fitted), x_raw (grand-mean centred), x_w + x_b (x_b = participant mean,
# centred on the mean of the participant means)
add_wb <- function(d, vars) {
  for (v in names(vars)) {
    x <- d[[vars[[v]]]]
    m <- ave(x, d$Participant)
    d[[paste0(v, "_w")]] <- x - m
    d[[paste0(v, "_raw")]] <- x - mean(x)
    d[[paste0(v, "_b")]] <- m - mean(m[!duplicated(d$Participant)])
  }
  d
}
spec3 <- function(rhs_w, rhs_raw, rhs_wb) c("Within (as fitted)" = rhs_w, "Raw" = rhs_raw, "Within + between" = rhs_wb)
run_specs <- function(y, specs, d) {
  bind_rows(lapply(names(specs), function(s) mutate(pilot_coefs(paste(y, specs[[s]]), d), Specification = s, Outcome = y)))
}

# (A) Phase-1 beauty and meaning on the label and SR
d_a <- dfsr |>
  filter(!is.na(Beauty2)) |>
  add_wb(c(SR = "SelfRelevance")) |>
  mutate(Beauty = 100 * Beauty, Meaning = 100 * Meaning)
specs_a <- spec3("~ Condition * SR_w + (Condition + SR_w | Participant) + (1 | Item)",
                 "~ Condition * SR_raw + (Condition + SR_raw | Participant) + (1 | Item)",
                 "~ Condition * (SR_w + SR_b) + (Condition + SR_w | Participant) + (1 | Item)")
pilot_sr_a <- bind_rows(run_specs("Beauty", specs_a, d_a), run_specs("Meaning", specs_a, d_a))

# ...and the label gap per absolute SR level (0, 1-2, 3-4, 5-6), no linearity
d_a$SR_bin <- cut(round(6 * d_a$SelfRelevance), c(-1, 0, 2, 4, 6), labels = c("0", "1-2", "3-4", "5-6"))
pilot_sr_bins <- bind_rows(lapply(c("Beauty", "Meaning"), function(y) {
  mutate(pilot_coefs(paste(y, "~ 0 + SR_bin / Condition + (Condition | Participant) + (1 | Item)"), d_a), Outcome = y)
})) |>
  filter(str_detect(Term, "Condition")) |>
  mutate(SR = str_extract(Term, "(?<=SR_bin)[^:]+"), Contrast = str_remove(str_extract(Term, "Condition.*"), "Condition"))

# (B) beliefs on the label, Phase-1 beauty, SR and follow-up beauty
d_b <- dfsr |>
  filter(!is.na(Beauty2), !is.na(Reality)) |>
  add_wb(c(Beauty = "Beauty", SR = "SelfRelevance", Beauty2 = "Beauty2")) |>
  mutate(Reality = 100 * Reality, Authenticity = 100 * Authenticity)
re_b <- "(Condition + Beauty_w + SR_w + Beauty2_w || Participant) + (1 | Item)"
specs_b <- spec3(paste("~ Condition * (Beauty_w + SR_w + Beauty2_w) +", re_b),
                 "~ Condition * (Beauty_raw + SR_raw + Beauty2_raw) + (Condition + Beauty_raw + SR_raw + Beauty2_raw || Participant) + (1 | Item)",
                 paste("~ Condition * (Beauty_w + SR_w + Beauty2_w) + Beauty_b + SR_b + Beauty2_b +", re_b))
pilot_sr_b <- bind_rows(run_specs("Reality", specs_b, d_b), run_specs("Authenticity", specs_b, d_b))

# (B) perceived artificiality of the artworks judged new
d_art <- dfmem |>
  filter(!is.na(PerceivedArtificiality), !is.na(Beauty2), !is.na(SelfRelevance)) |>
  add_wb(c(Beauty2 = "Beauty2", SR = "SelfRelevance")) |>
  mutate(PerceivedArtificiality = 100 * PerceivedArtificiality)
specs_art <- spec3("~ Type * (Beauty2_w + SR_w) + (Type + Beauty2_w + SR_w || Participant) + (1 | Item)",
                   "~ Type * (Beauty2_raw + SR_raw) + (Type + Beauty2_raw + SR_raw || Participant) + (1 | Item)",
                   "~ Type * (Beauty2_w + SR_w) + Beauty2_b + SR_b + (Type + Beauty2_w + SR_w || Participant) + (1 | Item)")
pilot_sr_art <- run_specs("PerceivedArtificiality", specs_art, d_art)
```

```{r}
#| results: asis

make_asis(
  make_tables(pilot_table(pilot_sr_a), c("Outcome", "Specification", "Term", "Unit", "Diff", "SE", "Effect"),
              "lme4 pilots, (A): Phase-1 ratings on the label and SR, three versions of SR (slopes for Originals; 'x' rows: difference in slope under a label; Effect: |t| > 1.96)"),
  make_tables(pilot_sr_bins |>
                mutate(Effect = ifelse(abs(Estimate / SE) < 1.96, "n.s.", ifelse(Estimate < 0, "Negative", "Positive")),
                       Diff = insight::format_value(Estimate), SE = insight::format_value(SE)) |>
                arrange(Outcome, Contrast, SR),
              c("Outcome", "Contrast", "SR", "Diff", "SE", "Effect"),
              "lme4 pilot: label gap (vs. Originals, % of the scale) at each absolute level of self-relevance (0-6)"),
  make_tables(pilot_table(filter(pilot_sr_b, !str_detect(Term, "^Condition[^:]*$"))), c("Outcome", "Specification", "Term", "Unit", "Diff", "SE", "Effect"),
              "lme4 pilots, (B): beliefs on the label, Phase-1 beauty, SR and follow-up beauty, three versions of each predictor"),
  make_tables(pilot_table(filter(pilot_sr_art, Term != "TypeNew")), c("Outcome", "Specification", "Term", "Unit", "Diff", "SE", "Effect"),
              "lme4 pilots, (B): perceived artificiality of the artworks judged new (reference: old items)")
)
```

None of the conclusions depends on the centring: the label gaps and the SR
slopes are virtually the same in the three versions; the label differences
in the SR slope are small in all of them (at most about -0.4 per +10% of SR
within persons, i.e. if anything a slightly *wider* gap for more
self-relevant works, and about 0 with the raw rating), so none shows a
narrowing of the gap; and the label gap is flat across the absolute levels of
self-relevance (only the rare 5-6 ratings are imprecise). The between-person
terms add two things: people who find art more self-relevant
overall rate it as much more meaningful (a between-person slope about twice
the within-person one) and judge it as more human-made; and the AI gap in
beauty tends to be smaller for them (see BeautySRBetween in (A) for the
Bayesian estimate).

### Shape of the self-relevance links

The preregistration of the follow-up expected extreme Phase-1 appraisals,
positive or negative, to go with high self-relevance (after Lee et al., 2023;
Salgues et al., 2024), i.e. a U-shaped relation that the linear models above
cannot show. Observed first:

```{r}
#| results: asis

beauty_bins <- function(x) cut(x, c(-Inf, 0, .15, .3, .45, .55, .7, .85, .9999, Inf),
                               labels = c("= 0", "0-15", "15-30", "30-45", "45-55", "55-70", "70-85", "85-100", "= 100"))
sr_by_beauty <- bind_rows(
  summarise(mutate(dfsr, Bin = beauty_bins(Beauty)), SR = mean(6 * SelfRelevance), n = n(), .by = "Bin") |>
    mutate(Rating = "Phase-1 beauty"),
  summarise(mutate(filter(dfsr, !is.na(Beauty2)), Bin = beauty_bins(Beauty2)), SR = mean(6 * SelfRelevance), n = n(), .by = "Bin") |>
    mutate(Rating = "Follow-up beauty")
) |>
  arrange(Rating, Bin) |>
  mutate(SR = sprintf("%.2f (n = %d)", SR, n)) |>
  select(-n) |>
  pivot_wider(names_from = Rating, values_from = SR)
make_asis(make_tables(sr_by_beauty, c("Bin", "Phase-1 beauty", "Follow-up beauty"),
                      "Observed mean self-relevance (0-6) by beauty (% of the slider; the exact ends as their own bins), old items"))
```

```{r}
#| label: pilot-sr-quadratic
#| cache: true
#| cache.extra: !expr rlang::hash(dfsr)
#| warning: false

d_q <- dfsr |>
  filter(!is.na(Beauty2)) |>
  mutate(SR = 100 * SelfRelevance, SR_w = SelfRelevance_w, Beauty100 = 100 * Beauty, Meaning100 = 100 * Meaning)
pilot_sr_quad <- bind_rows(
  mutate(pilot_coefs("SR ~ Beauty_w + I(Beauty_w^2) + (Beauty_w | Participant) + (1 | Item)", d_q), Model = "SR ~ Phase-1 beauty"),
  mutate(pilot_coefs("SR ~ Beauty2_w + I(Beauty2_w^2) + (Beauty2_w | Participant) + (1 | Item)", d_q), Model = "SR ~ follow-up beauty"),
  mutate(pilot_coefs("SR ~ Valence_w + I(Valence_w^2) + (Valence_w | Participant) + (1 | Item)", d_q), Model = "SR ~ Phase-1 valence"),
  mutate(pilot_coefs("Beauty100 ~ Condition * (SR_w + I(SR_w^2)) + (Condition + SR_w | Participant) + (1 | Item)", d_q), Model = "Phase-1 beauty ~ SR (BeautySR)"),
  mutate(pilot_coefs("Meaning100 ~ Condition * (SR_w + I(SR_w^2)) + (Condition + SR_w | Participant) + (1 | Item)", d_q), Model = "Phase-1 meaning ~ SR (MeaningSR)")
)

gam_q <- mutate(d_q, Participant = factor(Participant), Item = factor(Item))
pilot_sr_gam <- bind_rows(lapply(c("Phase-1 beauty" = "Beauty", "Follow-up beauty" = "Beauty2"), function(x) {
  g <- mgcv::bam(as.formula(paste("SR ~ s(", x, ", k = 8) + s(Participant, bs = 're') + s(Item, bs = 're')")),
                 data = gam_q, discrete = TRUE, method = "fREML")
  nd <- data.frame(v = seq(0, 1, length.out = 101), Participant = gam_q$Participant[1], Item = gam_q$Item[1])
  names(nd)[1] <- x
  p <- predict(g, nd, exclude = c("s(Participant)", "s(Item)"), se.fit = TRUE)
  data.frame(x = nd[[x]], Fit = p$fit, SE = p$se.fit)
}), .id = "Rating")
```

```{r}
#| results: asis

make_asis(make_tables(
  pilot_sr_quad |>
    filter(str_detect(Term, "_w")) |>
    mutate(Term = pilot_term(Term), z = Estimate / SE,
           Effect = ifelse(abs(z) < 1.96, "n.s.", ifelse(Estimate < 0, "Negative", "Positive")),
           across(c(Estimate, SE, z), \(x) insight::format_value(x))),
  c("Model", "Term", "Estimate", "SE", "z", "Effect"),
  "lme4 pilots: linear and quadratic terms (outcome in %, predictor on 0-1 centred within participant; positive quadratic = convex)"))
```

```{r}
#| fig-width: 9
#| fig-height: 4

ggplot(pilot_sr_gam, aes(x = 100 * x, y = 6 * Fit / 100)) +
  geom_ribbon(aes(ymin = 6 * (Fit - 1.96 * SE) / 100, ymax = 6 * (Fit + 1.96 * SE) / 100), alpha = 0.15) +
  geom_line(linewidth = 1) +
  facet_wrap(~Rating) +
  labs(x = "Beauty (% of the slider, 50 = neutral)", y = "Self-relevance (0-6)",
       caption = "GAM smooths (k = 8) with participant and item random intercepts.") +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"))
```

Self-relevance rises monotonically with beauty, from the very ugly works
(the least self-relevant of all) to the very beautiful ones. The large
positive quadratic terms reflect **convexity**: self-relevance increases
slowly across the ugly half of the slider and steeply across the beautiful
half, with a step around the neutral point. The vertex of the fitted parabola
lies at the edge of, or outside, the range of the data, so the quadratic does
not describe a U. The preregistered "extreme appraisal, positive or negative
-> high self-relevance" pattern is therefore not supported; only its positive
half is. In the direction the models use (Phase-1 ratings on SR), the
quadratic terms are not credible, so the linear `SR_w` of BeautySR and
MeaningSR is adequate.
