---
title: "FakeArt - Interindividual Differences"
editor: source
editor_options:
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    keep-md: true
---

<!-- Participant-level indices are computed on the cluster (`./hpc individual`, get_individual() in server/estimates.R) and read from models/individual/. -->

## Data Preparation

```{r}
#| warning: false
#| code-fold: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggnewscale)

source("server/estimates.R") # outcome_info
source("report.R")           # read_estimates(), provenance_table(), make_tables()

dfsub <- read.csv("../data/data_participants.csv")

cols_index <- c("Baseline" = "#E91E63", "Forgery" = "#F5A41D", "AI" = "#1D9AF5", "Slope" = "#8E24AA")
fmt_r <- function(x) sub("^(-?)0\\.", "\\1.", sprintf("%.2f", x)) # .45, -.07

# Models with participant-level indices, in the order of 3_models.qmd, then the
# determinants models (5_realitydeterminants.qmd) with a participant-level slope
models <- intersect(c("Beauty", "Valence", "Meaning", "Worth", "Reality", "Authenticity", "Beauty2", "SelfRelevance", "Artificiality"),
                    names(Filter(function(x) !is.null(x$individual), outcome_info)))
slope_models <- names(Filter(function(x) !is.null(x$individual), mediation_info))
individual <- read_estimates(c(models, slope_models), dir = "individual")
provenance_table(individual)

# One row per Participant x Model x Parameter x Index (posterior Mean and SD),
# features ordered by model, parameter (registry order) and index
df_long <- bind_rows(lapply(individual, function(e) mutate(e$individual, Model = e$outcome))) |>
  mutate(Model = factor(Model, levels = c(models, slope_models)),
         Parameter = factor(Parameter, levels = unique(unlist(lapply(c(outcome_info[models], mediation_info[slope_models]), `[[`, "individual")))),
         Index = factor(Index, levels = names(cols_index))) |>
  arrange(Model, Parameter, Index) |>
  mutate(Feature = fct_inorder(paste(Model, Parameter, Index, sep = "_")))
features <- levels(df_long$Feature)

# One column per feature (posterior means)
df_wide <- df_long |>
  select(Participant, Feature, Mean) |>
  pivot_wider(names_from = Feature, values_from = Mean)
```

Participant characteristics used as correlates. Gender is coded 0 = female,
1 = male (the 2 "other" excluded), so its correlations are point-biserial;
education and AI use are ordinal ranks. Questionnaire scores are missing for
participants who failed that questionnaire's attention check.

```{r}
#| label: traits

traits <- c("Age" = "Demographics", "Gender (male)" = "Demographics", "Education" = "Demographics",
            "Art expertise" = "Demographics",
            "AI knowledge" = "AI attitudes", "AI use" = "AI attitudes", "AI attitudes (positive)" = "AI attitudes",
            "AI attitudes (negative)" = "AI attitudes", "AI art realism" = "AI attitudes", "Manipulation distrust" = "AI attitudes",
            "Visual imagery (VVIQ)" = "Imagery & mood", "Depression" = "Imagery & mood",
            "Anxiety" = "Imagery & mood", "Life satisfaction" = "Imagery & mood")

df_traits <- dfsub |>
  transmute(Participant,
            Age,
            `Gender (male)` = case_when(Gender == "Male" ~ 1, Gender == "Female" ~ 0),
            Education = as.numeric(factor(Education, levels = c("High school", "Bachelor", "Master", "Doctorate"))),
            `Art expertise` = Art_Expertise,
            `AI knowledge` = BAIT_AI_Knowledge,
            `AI use` = as.numeric(factor(BAIT_AI_Use, levels = c("Never", "A few times per month", "A few times per week",
                                                                 "Once a day", "A few times per day"))),
            `AI attitudes (positive)` = BAIT_Positive,
            `AI attitudes (negative)` = BAIT_Negative,
            `AI art realism` = BAIT_ArtRealistic,
            `Manipulation distrust` = ManipulationDistrust,
            `Visual imagery (VVIQ)` = VVIQ_Total,
            Depression = PHQ4_Depression,
            Anxiety = PHQ4_Anxiety,
            `Life satisfaction` = LifeSatisfaction,
            across(c(starts_with("MINT_"), -MINT_AttentionCheck))) |>
  rename_with(\(x) str_replace(x, "^MINT_", "MINT "), starts_with("MINT_"))
traits <- c(traits, setNames(rep("Interoception", sum(startsWith(names(df_traits), "MINT"))),
                             grep("^MINT", names(df_traits), value = TRUE)))
trait_vars <- data.frame(Score = names(traits), Row = names(traits), RowGroup = unname(traits))

# Order variables by the similarity of their correlation profiles (rows of m):
# hierarchical clustering, branches reordered by average correlation
cluster_order <- function(m) {
  if (nrow(m) < 3) return(rownames(m))
  dend <- reorder(as.dendrogram(hclust(dist(m), method = "average")), rowMeans(m, na.rm = TRUE))
  rownames(m)[order.dendrogram(dend)]
}

# Correlations between row and column variables (data frames with Score, the
# column name in `data`, and the Row / RowGroup or Column / ColGroup it is shown
# as), FDR-corrected across the whole table. Within each group, rows are
# ordered by cluster_order() (RowKey); columns keep their given order.
cor_grid <- function(data, rows, cols) {
  d <- data |>
    correlation(select = rows$Score, select2 = cols$Score, p_adjust = "none") |>
    as.data.frame() |>
    mutate(p_fdr = p.adjust(p, method = "fdr"),
           Label = paste0(fmt_r(r), ifelse(p_fdr < .05, "*", "")),
           Row = rows$Row[match(Parameter1, rows$Score)],
           RowGroup = factor(rows$RowGroup[match(Parameter1, rows$Score)], levels = unique(rows$RowGroup)),
           Column = factor(cols$Column[match(Parameter2, cols$Score)], levels = unique(cols$Column)),
           ColGroup = factor(cols$ColGroup[match(Parameter2, cols$Score)], levels = unique(cols$ColGroup)))
  row_levels <- unlist(lapply(split(d, d$RowGroup), \(g) {
    m <- xtabs(r ~ Parameter1 + Parameter2, data = g)
    cluster_order(unclass(m))
  }), use.names = FALSE)
  mutate(d, RowKey = factor(Parameter1, levels = row_levels))
}

cor_markdown <- function(d, title) {
  d |>
    mutate(Col = paste(ColGroup, Column, sep = ": ")) |>
    arrange(ColGroup, Column, RowGroup, RowKey) |>
    mutate(Row = paste(RowGroup, Row, sep = ": ")) |>
    select(Row, Col, Label) |>
    pivot_wider(names_from = Col, values_from = Label) |>
    make_markdown(title) |>
    make_asis()
}

# col_fill: optional strip colours per column group (named by ColGroup), in
# which case the column-group strips are drawn below the columns
cor_heatmap <- function(d, base_size = 13, text_size = 3.4, col_fill = NULL) {
  facets <- if (is.null(col_fill)) {
    facet_grid(RowGroup ~ ColGroup, scales = "free", space = "free")
  } else {
    ggh4x::facet_grid2(RowGroup ~ ColGroup, scales = "free", space = "free", switch = "x",
                       strip = ggh4x::strip_themed(
                         background_x = ggh4x::elem_list_rect(fill = unname(col_fill[levels(droplevels(d$ColGroup))]), colour = NA),
                         text_x = ggh4x::elem_list_text(colour = "white", face = "bold")))
  }
  d |>
    ggplot(aes(x = Column, y = fct_rev(RowKey))) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = Label, fontface = ifelse(p < .05, "bold", "plain")), size = text_size) +
    facets +
    scale_fill_gradient2(low = "#1D9AF5", mid = "white", high = "#F51D56", midpoint = 0, limits = c(-0.5, 0.5),
                         breaks = c(-0.5, -0.25, 0, 0.25, 0.5), labels = fmt_r, oob = scales::squish, name = "Correlation") +
    scale_x_discrete(position = "top") +
    scale_y_discrete(labels = setNames(d$Row, d$Parameter1)) +
    labs(x = NULL, y = NULL) +
    theme_minimal(base_size = base_size) +
    theme(axis.text.x.top = element_text(angle = 45, hjust = 0, vjust = 0),
          panel.grid = element_blank(),
          strip.text = element_text(face = "bold"),
          strip.text.y = element_text(angle = 0, hjust = 0),
          legend.position = "bottom", legend.key.width = unit(3, "lines"))
}
```

## Individual Indices

For each participant and distributional parameter, on the link scale, averaged
over the four emotion quadrants and excluding item effects:

- **Baseline**: the parameter in the Human Original condition
- **Forgery**: Human Forgery − Human Original
- **AI**: AI-Generated − Human Original

Parameters without a participant-level label effect in the model (Worth's
`disc`) have a Baseline only. For Worth, `mu` is the latent location relative
to the shared thresholds and `disc` the participant's discrimination (response
precision), analogous to `phi` / `prec` in the other models.

One index comes from the determinants models of `5_realitydeterminants.qmd`:

- **RealityBeauty `mu` Slope**: the participant's slope of the syntheticness
  choice (`mu`, the probability of answering on the "Human" side) on their own
  Phase-1 beauty (centred within participant), per full range of the beauty
  slider, averaged over the labels: how strongly the participant takes beauty
  as a sign of human authorship (the "beautiful = human" inference).

Models not included (yet):

- **ArtificialityBeauty** (follow-up; *to consider*): the analogous slope of
  perceived artificiality on follow-up beauty (items judged new) is the most
  reliable participant-level slope of the determinants models (D-vour .67
  [.62, .71] in a check on its 2026-09-23 fit, against .44 for the
  RealityBeauty slope) and it correlates with the RealityBeauty slope across
  sessions, ~47 days apart and on different items (r = −.24 [−.36, −.11], n =
  217; roughly −.44 once corrected for both reliabilities). A candidate once
  the rule for participants missing from some models (220 here) is settled
  (see Beauty2); until then, a cross-session validation of the RealityBeauty
  slope. The other determinants models were checked and left out: the label
  modulation of the slopes (D-vour ≤ .11), the per-rating slopes of the
  Appraisal models (≤ .28; collinear mediators), AuthenticityBeauty's slope
  (.29), the *BeautyControl models (their Phase-1 beauty slope correlates .99
  with RealityBeauty's; follow-up beauty slopes .24 / .32) and the Items
  models (label slopes only, which duplicate the indices above).

- **Beauty2** (follow-up): 220 participants; waiting for a rule on how the
  analyses handle participants missing from some models.
- **SelfRelevance** (follow-up): a moderator of the label effect (RQ3) rather
  than an outcome of it; also 220 participants.
- **Artificiality** (follow-up): only old items judged new, i.e. about 9
  trials per label per participant (some none), selected by forgetting.
- **Gaze** (Entropy, Laterality, Centeredness, Max. Shift): no population
  label effect, a sample-count covariate to fix in the prediction grid, and
  274 participants.
- **MemoryCondition, MemoryBelief**: categorical models without Emotion, so no
  baselines and contrasts; their recognition, accuracy and tendency indices are
  assessed separately (see Memory).

`Between_SD` is the SD of the participants' posterior means; `Posterior_SD`
the average posterior SD of a participant's index relative to the sample
(`SD_rel`, which excludes the uncertainty of the population effect).

```{r}
#| label: individual-summary

summary_ind <- df_long |>
  summarise(N = n(),
            Average = mean(Mean),
            Between_SD = sd(Mean),
            Posterior_SD = mean(SD_rel),
            .by = c(Model, Parameter, Index)) |>
  arrange(Model, Parameter, Index) |>
  mutate(across(where(is.numeric) & !N, \(x) insight::format_value(x)))

make_tables(summary_ind, names(summary_ind), "Participant-level indices (link scale)")
```

```{r}
#| label: fig-individual
#| fig-cap: "Distribution of the participants' posterior means per index, on the link scale of each parameter."
#| fig-width: 16
#| fig-height: 18

df_long |>
  ggplot(aes(x = Mean, fill = Index)) +
  geom_histogram(bins = 40) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  facet_wrap(~ Feature, scales = "free", ncol = 6, labeller = as_labeller(\(x) str_replace_all(x, "_", " "))) +
  scale_fill_manual(values = cols_index) +
  labs(x = "Posterior mean (link scale)", y = "Participants") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Reliability

D-vour (`performance::performance_dvour()`): the variability of the
participants' posterior means relative to their average posterior
uncertainty, $\sigma_B^2 / (\sigma_B^2 + \mu_{SD}^2)$, with the posterior SD
taken relative to the sample (`SD_rel`). > .75: strong individual differences;
~ .5: use with caution; < .5: dominated by uncertainty. 95% CIs from 2,000
bootstrap resamples of participants. The posterior SD also carries the
uncertainty of the model's hyperparameters, so D-vour is likely conservative
for the contrasts.

```{r}
#| label: reliability

# The indices as a modelbased::estimate_grouplevel() table
as_grouplevel <- function(d) {
  out <- data.frame(Group = "Participant", Level = d$Participant, Parameter = d$Feature,
                    Coefficient = d$Mean, SD = d$SD_rel)
  attr(out, "coef_name") <- "Coefficient"
  class(out) <- c("estimate_grouplevel", "data.frame")
  out
}
dvour <- function(d) performance::performance_dvour(as_grouplevel(d))[c("Parameter", "D_vour")]

# D-vour per Feature with 95% CI from bootstrap resamples of participants. The
# bootstrap applies performance_dvour()'s formula, sd^2 / (sd^2 + mean(SD)^2),
# to participant x feature matrices (same result, a fraction of the time).
get_dvour <- function(df, n_boot = 2000) {
  wide <- function(v) pivot_wider(df[c("Participant", "Feature", v)], names_from = Feature, values_from = all_of(v))
  M <- as.matrix(wide("Mean")[-1])
  S <- as.matrix(wide("SD_rel")[-1])
  boot <- replicate(n_boot, {
    i <- sample(nrow(M), replace = TRUE)
    v <- apply(M[i, , drop = FALSE], 2, var, na.rm = TRUE)
    v / (v + colMeans(S[i, , drop = FALSE], na.rm = TRUE)^2)
  })
  ci <- data.frame(Parameter = colnames(M),
                   CI_low = apply(boot, 1, quantile, 0.025),
                   CI_high = apply(boot, 1, quantile, 0.975))
  dvour(df) |>
    left_join(ci, by = "Parameter") |>
    mutate(Feature = factor(Parameter, levels = levels(df$Feature)), Parameter = NULL) |>
    left_join(distinct(df, Feature, Model, Parameter, Index), by = "Feature")
}

set.seed(1234)
df_rel <- get_dvour(df_long)

df_rel |>
  mutate(across(c(D_vour, CI_low, CI_high), \(x) insight::format_value(x))) |>
  make_tables(c("Model", "Parameter", "Index", "D_vour", "CI_low", "CI_high"),
              "Reliability (D-vour) of the participant-level indices")
```

```{r}
#| label: fig-reliability
#| fig-cap: "Reliability (D-vour) of each participant-level index, with 95% bootstrap CI. Dashed lines at .5 and .75."
#| fig-width: 9
#| fig-height: 11

df_rel |>
  ggplot(aes(x = D_vour, y = fct_rev(Parameter), color = Index)) +
  geom_vline(xintercept = c(0.5, 0.75), linetype = "dashed", color = "grey70") +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high), position = position_dodge(width = 0.6, reverse = TRUE)) +
  facet_grid(Model ~ ., scales = "free_y", space = "free_y") +
  scale_color_manual(values = cols_index) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, 0.01)) +
  labs(x = "D-vour", y = NULL, color = NULL) +
  theme_minimal() +
  theme(legend.position = "top", strip.text.y = element_text(angle = 0, face = "bold"))
```

```{r}
#| label: fig-caterpillar
#| fig-cap: "Participants' posterior means (±1 posterior SD relative to the sample) for the `mu` indices, sorted, with the distribution of the posterior means on top and the reliability (D-vour) of each index. Wide bars relative to the spread of the points mean low reliability."
#| fig-width: 12
#| fig-height: 24.5

df_long |>
  filter(Parameter == "mu") |>
  mutate(Rank = rank(Mean, ties.method = "first"), .by = Feature) |>
  ggplot(aes(x = Mean, y = Rank, color = Index)) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerange(aes(xmin = Mean - SD_rel, xmax = Mean + SD_rel), alpha = 0.3) +
  geom_point(size = 0.6) +
  geom_xsidedensity(aes(y = after_stat(scaled), fill = Index), color = NA, alpha = 0.6) +
  geom_text(data = filter(df_rel, Parameter == "mu"), aes(x = -Inf, y = Inf, label = paste("D-vour =", fmt_r(D_vour))),
            hjust = -0.1, vjust = 1.5, size = 3.5, fontface = "bold") +
  facet_wrap(~ Feature, scales = "free_x", ncol = 3, labeller = as_labeller(\(x) str_replace_all(x, "_", " "))) +
  scale_color_manual(values = cols_index) +
  scale_fill_manual(values = cols_index) +
  scale_xsidey_continuous(breaks = NULL) +
  labs(x = "Posterior mean (link scale)", y = "Participants (sorted)") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.y = element_blank(), ggside.panel.scale = 0.25)
```



## Structure

### Correlation Matrix


```{r}
#| label: correlation

df_cor <- df_wide |>
  select(all_of(features)) |>
  correlation(p_adjust = "none", redundant = TRUE) |>
  cor_sort()
order <- levels(df_cor$Parameter1)

df_cor <- as.data.frame(df_cor) |>
  mutate(Parameter1 = factor(Parameter1, levels = order),
         Parameter2 = factor(Parameter2, levels = order)) |>
  filter(as.integer(Parameter1) > as.integer(Parameter2))

df_cor |>
  mutate(r = fmt_r(r)) |>
  select(Parameter1, Parameter2, r) |>
  pivot_wider(names_from = Parameter2, values_from = r) |>
  arrange(Parameter1) |>
  make_markdown("Correlations between participant-level indices") |>
  make_asis()
```

```{r}
#| label: fig-correlation
#| fig-cap: "Correlations between participant-level indices, clustered. Lower triangle: Pearson r (bold: p < .05, uncorrected). Diagonal: D-vour (orange = low, green = high)."
#| fig-width: 22
#| fig-height: 21

lab <- function(x) str_replace_all(x, c("_" = " ", " Baseline" = " (Baseline)", " Forgery$" = " (Forgery)", " AI$" = " (AI)"))

df_diag <- df_rel |>
  mutate(x = factor(Feature, levels = order), y = x, label = fmt_r(D_vour))

df_cor |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r), color = "white") +
  geom_text(aes(label = fmt_r(r), fontface = ifelse(p < .05, "bold", "plain")), size = 1.9) +
  scale_fill_gradient2(low = "#1D9AF5", mid = "white", high = "#F51D56", midpoint = 0, limits = c(-1, 1), name = "Correlation") +
  ggnewscale::new_scale_fill() +
  geom_tile(data = df_diag, aes(x = x, y = y, fill = D_vour), color = "white") +
  geom_text(data = df_diag, aes(x = x, y = y, label = label), size = 1.9, fontface = "italic") +
  scale_fill_gradient(low = "#FF9800", high = "#4CAF50", limits = c(0, 1), name = "Reliability") +
  scale_x_discrete(limits = order, labels = lab, drop = FALSE) +
  scale_y_discrete(limits = rev(order), labels = lab, drop = FALSE) +
  coord_fixed() +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), panel.grid = element_blank())
```

### Exploratory Graph Analysis

Bootstrapped hierarchical EGA (`EGAnet::bootEGA(EGA.type = "hierEGA")`, 500
parametric bootstraps, pairwise-complete correlations) on the indices with
D-vour > 1/3. Higher-order communities use Leiden (modularity); lower-order
communities use EGAnet's recommended Louvain with consensus clustering. Item
stability is the share of bootstraps in which an index lands in its empirical
community. The dimension scores for the correlates come from this single EGA
(no second round on a stability-filtered set).

The beauty slope of syntheticness (RealityBeauty `mu` Slope) is left out
although its D-vour exceeds 1/3: it is nearly orthogonal to every other index
(all |r| ≤ .18, see the correlation matrix), so it forms no community of its
own. With it included (tried 2026-09-24) the empirical EGA placed it, weakly,
in *Anti-fake bias* and left every other index where it was, but in bootstrap
samples where it is isolated, `bootEGA()` fails. It enters the correlates
directly instead.

::: {.callout-note collapse="true" title="Why not Leiden at both levels"}
The lower order of hierarchical EGA is Louvain's *first* aggregation level;
Leiden returns only its final, fully aggregated partition. With Leiden at both
levels (tried 2026-09-23, 100 bootstraps), the lower order merges into 4
communities (Phase-1 appraisal and precision; Phase-1 label sensitivity;
Phase-2 location and confidence; Phase-2 precision), close to the higher order
above, and the higher order becomes a single community in 74% of bootstraps:
the hierarchy disappears. That 4-community partition is itself stable (the
modal solution in 67% of bootstraps, against 32% for the 9-community lower
order here), so it is the natural choice if a coarser, single-level reduction
is ever preferred.
:::

Node labels: **Bea**uty, **Val**ence, **Mea**ning, **Wor**th, **Syn**theticness
(`Reality`), **Aut**henticity; `cR` / `cL` = confright / confleft, `pR` / `pL` =
precright / precleft, `p0` = pzero; **B** = Baseline, **F** = Forgery,
**AI** = AI-Generated.

```{r}
#| label: ega
#| warning: false
#| message: false

library(EGAnet) # also registers the plot methods when ega-fit comes from the cache

short <- function(x) {
  x |>
    str_replace_all(c("^Beauty" = "Bea", "^Valence" = "Val", "^Meaning" = "Mea", "^Worth" = "Wor",
                      "^Reality" = "Syn", "^Authenticity" = "Aut",
                      "_confright" = "_cR", "_confleft" = "_cL", "_precright" = "_pR", "_precleft" = "_pL",
                      "_pzero" = "_p0", "_Baseline$" = "_B", "_Forgery$" = "_F")) |>
    str_replace_all("_", " ")
}

# The determinants slope is left out (see the text above) and enters the
# correlates directly
ega_features <- as.character(df_rel$Feature[df_rel$D_vour > 1/3 & !df_rel$Model %in% slope_models])
d_ega <- setNames(df_wide[ega_features], short(ega_features))
```

```{r}
#| label: ega-fit
#| warning: false
#| message: false
#| cache: true
#| cache.extra: !expr rlang::hash(d_ega)

# Cached (~3 min); invalidated whenever the selected indices change
ega <- EGAnet::hierEGA(d_ega, higher.algorithm = "leiden", plot.EGA = FALSE)
ega_boot <- EGAnet::bootEGA(d_ega, EGA.type = "hierEGA", algorithm = "leiden", iter = 500,
                            seed = 1234, ncores = max(1, parallel::detectCores() - 2),
                            plot.itemStability = FALSE, verbose = FALSE)
```

```{r}
#| label: ega-tables

stab <- ega_boot$stability
df_ega <- data.frame(Index = names(d_ega), Feature = ega_features,
                     Lower = ega$lower_order$wc,
                     Higher = ega$higher_order$wc[as.character(ega$lower_order$wc)],
                     Stability_Lower = stab$lower_order$item.stability$item.stability$empirical.dimensions[names(d_ega)],
                     Stability_Higher = stab$higher_order$item.stability$item.stability$empirical.dimensions[names(d_ega)]) |>
  arrange(Higher, Lower)

df_ega |>
  mutate(across(starts_with("Stability"), \(x) insight::format_value(x))) |>
  make_tables(names(df_ega), "Hierarchical EGA: community membership and item stability")

bind_rows(
  mutate(as.data.frame(ega_boot$lower_order$frequency), Order = "Lower"),
  mutate(as.data.frame(ega_boot$higher_order$frequency), Order = "Higher")
) |>
  make_tables(c("Order", "# of Factors", "Frequency"), "Number of communities across bootstraps")
```

```{r}
#| label: fig-ega-stability
#| fig-cap: "Item stability: share of the 500 bootstraps in which each index is assigned to its empirical community, at the lower (left) and higher (right) order. Colour: lower-order community; shape: higher-order community. Dashed line at .70."
#| fig-width: 11
#| fig-height: 8

df_ega |>
  pivot_longer(starts_with("Stability"), names_to = "Order", names_prefix = "Stability_", values_to = "Stability") |>
  mutate(Order = factor(Order, levels = c("Lower", "Higher")),
         Lower = factor(Lower), Higher = factor(Higher),
         Index = factor(Index, levels = rev(df_ega$Index))) |>
  ggplot(aes(x = Stability, y = Index, color = Lower, shape = Higher)) +
  geom_vline(xintercept = 0.7, linetype = "dashed", color = "grey70") +
  geom_segment(aes(x = 0, xend = Stability, yend = Index), color = "grey85") +
  geom_point(size = 3) +
  facet_wrap(~Order) +
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1), expand = c(0.02, 0.02)) +
  labs(x = "Item stability", y = NULL, color = "Lower-order\ncommunity", shape = "Higher-order\ncommunity") +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"), panel.spacing = unit(2, "lines"))
```

```{r}
#| label: fig-ega-network
#| fig-cap: "Hierarchical EGA network of the participant-level indices (empirical sample). Bottom: indices coloured by lower-order community (edges: partial correlations, green positive, red negative); top: lower-order communities grouped into higher-order communities."
#| fig-width: 14
#| fig-height: 11
#| warning: false
#| message: false

plot(ega, plot.type = "multilevel", label.size = 3.5, node.size = 9)
```

```{r}
#| label: ega-communities

# Tentative labels, keyed by a characteristic member so they follow the
# content if the community numbering changes
labels_lower <- c("Bea mu B" = "Aesthetic\nsensitivity", "Bea mu AI" = "Anti-fake\nbias",
                  "Val phi B" = "Rating\nconsistency", "Bea cL B" = "Ugliness\nextremity",
                  "Syn mu B" = "Realness\ntendency", "Syn cR B" = "Realness\nconviction",
                  "Syn cL B" = "Fakeness\nconviction", "Syn pR B" = "Realness\nconsistency",
                  "Syn pL B" = "Fakeness\nconsistency")
labels_higher <- c("Bea mu B" = "Aesthetic appraisal", "Syn mu B" = "Realness beliefs",
                   "Syn pR B" = "Belief consistency")
community_label <- function(members, labels) {
  key <- intersect(names(labels), members)
  if (length(key) == 1) labels[[key]] else paste(members[1], "...")
}

tree_items <- df_ega |> mutate(x = row_number(), Lower = factor(Lower), Higher = factor(Higher))
tree_higher <- summarise(tree_items, Label = community_label(Index, labels_higher), .by = Higher)

# Community colours (edit here), keyed by label: one hue family per higher-order
# community (dark shade), lighter shades for its lower-order communities.
# Unlabelled communities are grey.
colors_higher <- c("Aesthetic appraisal" = "#4A148C",
                   "Realness beliefs"    = "#004D40",
                   "Belief consistency"  = "#3E2723")
colors_lower <- c("Aesthetic sensitivity" = "#6F1FA7",
                  "Anti-fake bias"        = "#942AC3",
                  "Rating consistency"    = "#BA34DF",
                  "Ugliness extremity"    = "#E040FB",
                  "Realness tendency"     = "#0C7573",
                  "Realness conviction"   = "#199DA6",
                  "Fakeness conviction"   = "#26C6DA",
                  "Realness consistency"  = "#6F5751",
                  "Fakeness consistency"  = "#A1887F")
tree_lower <- summarise(tree_items, Label = str_replace_all(community_label(Index, labels_lower), "\n", " "), .by = Lower)
pal_lower <- setNames(coalesce(unname(colors_lower[tree_lower$Label]), "grey50"), tree_lower$Lower)
pal_higher <- setNames(coalesce(unname(colors_higher[tree_higher$Label]), "grey30"), paste0("H", tree_higher$Higher))

# Direction of each connection: sign of the index's network loading on its
# lower-order community, and of the community's loading on its higher-order one
loads_lower <- ega$parameters$lower_loadings
loads_higher <- suppressMessages(EGAnet::net.loads(ega$higher_order))$std
edge_sign <- function(x) factor(ifelse(x < 0, "Negative", "Positive"), levels = c("Positive", "Negative"))
tree_items <- mutate(tree_items, Sign = edge_sign(loads_lower[cbind(Index, as.character(Lower))]))

# Network scores (one row per participant, in the order of df_wide)
scores_lower <- ega$parameters$lower_scores
scores_higher <- EGAnet::net.scores(scores_lower, A = ega$higher_order)$scores$std.scores
r_higher <- cor(scores_higher, use = "pairwise.complete.obs")
tree_arcs <- as.data.frame(t(combn(colnames(r_higher), 2))) |>
  setNames(c("From", "To")) |>
  mutate(r = r_higher[cbind(From, To)],
         Color = ifelse(r > 0, "#F51D56", "#1D9AF5"),
         Pair = paste(From, To))
```

Community labels. Phase 1: *Aesthetic sensitivity* (the Baseline level of all
four ratings: finding the Originals beautiful, pleasant, meaningful and
valuable), *Anti-fake bias* (the AI, and Forgery for Worth, contrasts: how much
a non-original label lowers the ratings), *Rating consistency* (the precision
of the ratings) and *Ugliness extremity* (how far into "not beautiful" a
participant goes, and how consistently, when they choose that side). Phase 2:
*Realness tendency* (the propensity to judge the works human and original),
*Realness* / *Fakeness conviction* (how extreme the judgments are on the human
/ original and on the AI / copy side) and *Realness* / *Fakeness consistency*
(their precision).

```{r}
#| label: fig-ega-matrix
#| fig-cap: "Correlations and hierarchical structure of the indices entering the EGA (D-vour > 1/3), in community order. Lower half: Pearson r (bold: p < .05, uncorrected). Diagonal: D-vour. Upper half: each index connects to its lower-order community, and each lower-order community to its higher-order community (edge width: item stability; dashed: negative network loading). Arcs: correlations between the higher-order network scores (red positive, blue negative)."
#| fig-width: 20
#| fig-height: 19.5

# Layout: the indices sit along the diagonal in tree order. A point at position s
# along the diagonal and depth d away from it (towards the upper right) is drawn
# at x = s + d, y = n + 1 - s + d; the correlation cells fill the lower-left half.
n <- nrow(tree_items)
mid <- (n + 1) / 2
d_lower <- 4.5
d_higher <- 8.5
to_xy <- function(df) mutate(df, x = s + d, y = n + 1 - s + d)

# Correlations and reliability, in tree order
tri_cor <- df_wide[tree_items$Feature] |>
  correlation(p_adjust = "none", redundant = TRUE) |>
  as.data.frame() |>
  mutate(i = match(Parameter2, tree_items$Feature), j = match(Parameter1, tree_items$Feature)) |>
  filter(j > i)
tri_diag <- tree_items |>
  left_join(select(df_rel, Feature, D_vour), by = "Feature") |>
  mutate(Color = pal_lower[as.character(Lower)])

# Tree nodes, pulled towards the middle of the diagonal so that they stay above it
tri_lower <- tree_items |>
  summarise(s = mid + 0.8 * (mean(x) - mid), Higher = first(Higher), Stability = mean(Stability_Higher),
            Label = community_label(Index, labels_lower), .by = Lower) |>
  mutate(d = d_lower, Color = pal_lower[as.character(Lower)],
         Sign = edge_sign(loads_higher[cbind(as.character(Lower), as.character(Higher))])) |>
  to_xy()
tri_higher <- tri_lower |>
  summarise(s = mid + 0.6 * (mean(s) - mid), .by = Higher) |>
  left_join(select(tree_higher, Higher, Label), by = "Higher") |>
  mutate(d = d_higher, Color = pal_higher[paste0("H", Higher)]) |>
  to_xy()

# Edges: smooth steps from one depth to the next
curve <- function(s0, d0, s1, d1, t = seq(0, 1, length.out = 50)) {
  data.frame(s = s0 + (s1 - s0) * (3 * t^2 - 2 * t^3), d = d0 + (d1 - d0) * t)
}
tri_edges <- bind_rows(
  transmute(tree_items, Edge = paste("i", x), s0 = x, d0 = 0.5, Lower, Sign,
            s1 = tri_lower$s[match(Lower, tri_lower$Lower)], d1 = d_lower, Stability = Stability_Lower),
  transmute(tri_lower, Edge = paste("l", Lower), s0 = s, d0 = d_lower, Lower, Sign,
            s1 = tri_higher$s[match(Higher, tri_higher$Higher)], d1 = d_higher, Stability)
) |>
  reframe(curve(s0, d0, s1, d1), .by = c(Edge, Lower, Sign, Stability)) |>
  mutate(Color = pal_lower[as.character(Lower)]) |>
  to_xy()

# Correlations between higher-order scores: arcs bulging away from the diagonal
tri_arcs <- tree_arcs |>
  mutate(s1 = tri_higher$s[match(From, tri_higher$Higher)], s2 = tri_higher$s[match(To, tri_higher$Higher)],
         h = 1.5 + 0.15 * abs(s2 - s1)) # clears the node boxes; grows with the span so nested arcs barely cross
tri_arc_paths <- tri_arcs |>
  reframe(t = seq(0, 1, length.out = 60), .by = c(Pair, r, Color, s1, s2, h)) |>
  mutate(s = s1 + t * (s2 - s1), d = d_higher + h * sin(pi * t)) |>
  to_xy()
tri_arc_labels <- tri_arcs |>
  mutate(s = (s1 + s2) / 2, d = d_higher + h) |>
  to_xy()

p_ega_matrix <- ggplot() +
  # Correlations (lower-left half)
  geom_tile(data = tri_cor, aes(x = i, y = n + 1 - j, fill = r), color = "white") +
  geom_text(data = tri_cor, aes(x = i, y = n + 1 - j, label = fmt_r(r), fontface = ifelse(p < .05, "bold", "plain")), size = 3.7) +
  scale_fill_gradient2(low = "#1D9AF5", mid = "white", high = "#F51D56", midpoint = 0, limits = c(-1, 1), breaks = c(-1, 0, 1), name = "Correlation",
                       guide = guide_colourbar(order = 1)) +
  new_scale_fill() +
  # Reliability (diagonal)
  geom_tile(data = tri_diag, aes(x = x, y = n + 1 - x, fill = D_vour), color = "white") +
  geom_text(data = tri_diag, aes(x = x, y = n + 1 - x, label = fmt_r(D_vour)), size = 3.7, fontface = "italic") +
  scale_fill_gradient(low = "#FF9800", high = "#4CAF50", limits = c(0, 1), breaks = c(0, 0.5, 1), name = "Reliability",
                      guide = guide_colourbar(order = 2)) +
  new_scale_fill() +
  # Index labels (rows on the left, columns at the bottom)
  geom_text(data = tri_diag, aes(x = 0.3, y = n + 1 - x, label = lab(Feature), color = Color), hjust = 1, size = 4.8) +
  geom_text(data = tri_diag, aes(x = x, y = 0.3, label = lab(Feature), color = Color), angle = 45, hjust = 1, vjust = 1, size = 4.8) +
  # Tree (upper-right half)
  geom_path(data = tri_edges, aes(x = x, y = y, group = Edge, color = Color, linewidth = Stability, linetype = Sign), alpha = 0.7) +
  scale_linewidth_continuous(range = c(0.2, 2.5), limits = c(0, 1), breaks = c(0.2, 0.8), name = "Stability",
                             guide = guide_legend(order = 4, direction = "vertical")) +
  scale_linetype_manual(values = c("Positive" = "solid", "Negative" = "22"), name = "Loading", drop = FALSE,
                        guide = guide_legend(order = 3, direction = "vertical")) +
  new_scale("linewidth") +
  geom_path(data = tri_arc_paths, aes(x = x, y = y, group = Pair, color = Color, linewidth = pmin(abs(r), 0.5)), alpha = 0.8) +
  scale_linewidth_continuous(range = c(0.8, 3), limits = c(0, 0.5), guide = "none") +
  geom_label(data = tri_lower, aes(x = x, y = y, label = Label, fill = Color), color = "white", fontface = "bold",
             size = 4.8, lineheight = 0.9, label.r = unit(0.4, "lines"), label.padding = unit(0.4, "lines"), linewidth = 0) +
  geom_label(data = tri_higher, aes(x = x, y = y, label = Label, fill = Color), color = "white", fontface = "bold",
             size = 6.2, label.r = unit(0.5, "lines"), label.padding = unit(0.55, "lines"), linewidth = 0) +
  geom_label(data = tri_arc_labels, aes(x = x, y = y, label = fmt_r(r), color = Color),
             fill = "white", size = 6, fontface = "bold", linewidth = 0) +
  scale_color_identity() +
  scale_fill_identity() +
  coord_fixed(clip = "off") +
  scale_x_continuous(limits = c(-5.4, max(tri_arc_paths$x, tri_higher$x) + 2.6), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-5.3, max(tri_arc_paths$y, tri_edges$y) + 0.8), expand = c(0, 0)) +
  theme_void(base_size = 20) +
  theme(legend.position = "inside", legend.position.inside = c(0.99, 0.99), legend.justification = c(1, 1),
        legend.direction = "horizontal", legend.box = "horizontal", legend.box.just = "top",
        legend.title.position = "top", legend.title = element_text(size = 17), legend.text = element_text(size = 14),
        legend.key.width = unit(1.6, "lines"), legend.key.height = unit(0.9, "lines"),
        legend.spacing.x = unit(1.5, "lines"))
p_ega_matrix
```


## Memory

Participant-level indices from the two follow-up memory models (220
participants), from the predicted answer probabilities with item effects
excluded, on the logit scale. Accuracy and tendencies are conditional on the
item being recognised:

- **Recognition**: *Hits*, the probability of recognising an old item
  (averaged over its labels); *False alarms*, of calling a new item seen
  (label model only).
- **Accuracy**: the probability of recalling the correct label
  (MemoryCondition) or one's own Phase-2 belief (MemoryBelief), averaged over
  the actual labels / beliefs.
- **Tendency**: the probability of recalling an item as each category,
  whatever it actually was.

Only their reliability is assessed here; they are not part of the structure
analyses above. MemoryCondition's participant-level correlations are its
worst-converged parameters (max Rhat 1.13).

```{r}
#| label: memory-reliability

# MemoryConditionBelief (label recall by own belief) tests reconstruction; it
# has no participant-level indices
memory_models <- c("MemoryCondition", "MemoryBelief")
df_mem <- read_estimates(memory_models, dir = "individual") |>
  lapply(\(e) mutate(e$individual, Model = e$outcome)) |>
  bind_rows() |>
  mutate(Model = factor(Model, levels = memory_models),
         Parameter = factor(Parameter, levels = c("Recognition", "Accuracy", "Tendency")),
         Index = fct_inorder(Index)) |>
  arrange(Model, Parameter) |>
  mutate(Feature = fct_inorder(paste(Model, Parameter, Index, sep = "_")))

set.seed(1234)
df_mem_rel <- get_dvour(df_mem) |>
  left_join(summarise(df_mem, Probability = mean(plogis(Mean)), .by = Feature), by = "Feature")

df_mem_rel |>
  mutate(across(c(Probability, D_vour, CI_low, CI_high), \(x) insight::format_value(x))) |>
  make_tables(c("Model", "Parameter", "Index", "Probability", "D_vour", "CI_low", "CI_high"),
              "Reliability (D-vour) of the memory indices (Probability: sample average)")
```

```{r}
#| label: fig-memory-reliability
#| fig-cap: "Reliability (D-vour) of the memory indices, with 95% bootstrap CI. Dashed lines at .5 and .75."
#| fig-width: 9
#| fig-height: 6

df_mem_rel |>
  ggplot(aes(x = D_vour, y = fct_rev(Index), color = Parameter)) +
  geom_vline(xintercept = c(0.5, 0.75), linetype = "dashed", color = "grey70") +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high)) +
  facet_grid(Model ~ ., scales = "free_y", space = "free_y") +
  scale_color_manual(values = c("Recognition" = "#607D8B", "Accuracy" = "#4CAF50", "Tendency" = "#9C27B0")) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, 0.01)) +
  labs(x = "D-vour", y = NULL, color = NULL) +
  theme_minimal() +
  theme(legend.position = "top", strip.text.y = element_text(angle = 0, face = "bold"))
```

The memory indices with D-vour > 1/3 (all but the two accuracy indices, which
are dominated by uncertainty) are used as correlates, on the logit scale:
*Recognition* (hits and false alarms), and the tendency to recall a recognised
item's label (*Recalled label*) or one's own Phase-2 belief (*Recalled
belief*) as each category. Within a model the tendencies sum to 1, so they are
not independent of each other.

```{r}
#| label: memory-correlates

mem_vars <- df_mem_rel |>
  filter(D_vour > 1/3) |>
  transmute(Score = as.character(Feature), Column = as.character(Index),
            ColGroup = case_when(Parameter == "Recognition" ~ "Recognition",
                                 Model == "MemoryCondition" ~ "Recalled label",
                                 .default = "Recalled belief"))
df_mem_wide <- df_mem |>
  filter(Feature %in% mem_vars$Score) |>
  select(Participant, Feature, Mean) |>
  pivot_wider(names_from = Feature, values_from = Mean)

df_mem_cor <- df_mem_wide |>
  left_join(df_traits, by = "Participant") |>
  cor_grid(trait_vars, mem_vars)
cor_markdown(df_mem_cor, "Correlations between memory indices and participant characteristics (*: FDR-corrected p < .05)")
```

```{r}
#| label: fig-memory-correlates
#| fig-cap: "Correlations between the reliable memory indices (columns) and participant characteristics (220 participants), ordered within each group by the similarity of their correlation profiles. Bold: p < .05 (uncorrected); *: p < .05 after FDR correction across the whole table."
#| fig-width: 11
#| fig-height: 12

cor_heatmap(df_mem_cor)
```

## Correlates

Correlations between the dimension scores (the EGA network scores of the
higher-order communities, *Overall*, and of their lower-order communities) and
the participant characteristics (see Data Preparation) and reliable memory
indices (see Memory; 220 participants), and of the beauty slope of
syntheticness (*Beauty = human*, entered directly: it is not part of the EGA).
Phase-2 scores and the slope are missing for the 7 participants without
Phase-2 data.

The scores follow the direction of the loadings: a high *Anti-fake bias* score
is a *higher* AI (and Forgery) − Original contrast, i.e. a smaller penalty for
the non-original labels. *Belief consistency* (the precision of the Phase-2
judgments) is left out: none of its scores correlates with any of these
variables (all |r| ≤ .11).

```{r}
#| label: correlates

# Dimension scores: higher-order ("Overall") and lower-order, grouped by higher-order community
dim_vars <- bind_rows(
  transmute(tree_higher, Score = paste0("H", Higher), Higher, Column = "Overall"),
  tree_items |>
    summarise(Column = str_replace_all(community_label(Index, labels_lower), "\n", " "), .by = c(Lower, Higher)) |>
    transmute(Score = paste0("L", Lower), Higher, Column)
) |>
  mutate(ColGroup = tree_higher$Label[match(Higher, tree_higher$Higher)]) |>
  arrange(Higher, Column != "Overall") |>
  filter(ColGroup != labels_higher[["Syn pR B"]]) |> # Belief consistency: no correlates
  # The determinants slope, not part of the EGA (posterior means, link scale)
  bind_rows(tibble(Score = "RealityBeauty_mu_Slope", Column = "Beauty slope", ColGroup = "Beauty = human"))

# Strip colours: those of the higher-order communities in the EGA figure
fill_higher <- c(setNames(pal_higher[paste0("H", tree_higher$Higher)], tree_higher$Label),
                 "Beauty = human" = cols_index[["Slope"]])

df_scores <- bind_cols(Participant = df_wide$Participant,
                       setNames(as.data.frame(scores_higher), paste0("H", colnames(scores_higher))),
                       setNames(as.data.frame(scores_lower), paste0("L", colnames(scores_lower))),
                       df_wide["RealityBeauty_mu_Slope"])

# Rows: participant characteristics, then the memory indices
row_vars <- bind_rows(trait_vars, transmute(mem_vars, Score, Row = Column, RowGroup = ColGroup))

df_correlates <- df_scores |>
  left_join(df_traits, by = "Participant") |>
  left_join(df_mem_wide, by = "Participant") |>
  cor_grid(row_vars, dim_vars)
cor_markdown(df_correlates, "Correlations between dimension scores and participant characteristics and memory indices (*: FDR-corrected p < .05)")
```

```{r}
#| label: fig-correlates
#| fig-cap: "Correlations between the dimension scores (columns, grouped by higher-order community; Overall = the higher-order score) and participant characteristics and follow-up memory indices (rows; ordered within each group by the similarity of their correlation profiles). Bold: p < .05 (uncorrected); *: p < .05 after FDR correction across the whole table."
#| fig-width: 10.5
#| fig-height: 15.5

cor_heatmap(df_correlates, col_fill = fill_higher)
```

### Figure 4

```{r}
#| label: fig-figure4
#| fig-cap: "Structure and correlates of the participant-level indices. Top: correlations between the indices entering the EGA (lower half), their reliability (diagonal) and their hierarchical community structure (upper half). Bottom: correlations between the community scores and participant characteristics and follow-up memory indices."
#| fig-alt: "Top: triangular correlation matrix of the participant-level indices with a tree of their lower- and higher-order communities drawn above the diagonal. Bottom: heatmap of correlations between the community scores and participant characteristics and memory indices."
#| fig-width: 20
#| fig-height: 33.9

# Manuscript Figure 4 (Figure 3 is the determinants figure of 5_realitydeterminants.qmd).
# The legend of the matrix (top) also covers the correlates (bottom).
# free(): the matrix is not aligned with the heatmap's panels, so that it can use the full width
figure4 <- free(p_ega_matrix) /
  (cor_heatmap(df_correlates, base_size = 20, text_size = 5.2, col_fill = fill_higher) +
     theme(legend.position = "none", plot.margin = margin(t = 0.1, unit = "in"))) +
  plot_layout(heights = c(19.4, 14.5))

figure4

ggsave("figures/figure4.png", figure4, width = 20, height = 33.9, dpi = 300, bg = "white")
```
